### 2018-09-21 gji_extraguide.tex
Initial ShareLaTeX Import

%%gji_extra_guide.tex

\documentclass[extra,mreferee]{gji}
%\usepackage{timet}

\usepackage{graphicx}
\graphicspath{ {./figures} }
\usepackage{subfig}
\usepackage{caption}
\usepackage{floatrow}
\usepackage{amsmath}
\usepackage{color}
\floatsetup[figure]{style=plain,subcapbesideposition=top}
%\usepackage[margin=70mm]{geometry}

%\usepackage{subfig}

\title[\texttt{gji\_extra.sty} ]  
  {\texttt{GLAD-M25} - global adjoint tomography model}

\author[]  {Wenjie lei, Jeroen Tromp, ...}

\newcommand{\btx}{\textsc{BibTeX}}

\begin{document}

\maketitle

\section{Introduction}
With the development of high performance computing and numerical methods, it is now possible to using adjoint method to image the interior the globe using thousands of earthquakes.

There are few agreements about the earth model and yet many unknown to be resolved. There are quite a lot of global models exits however there is no such con-sense.

The GLAD-M25 is the first earth model that incorporate the P and S wave speed using full waveform inversion. Also, people are using specific set of phases in their inversion. For P models, people are using P phase and other body wave phases and for S models, people are using mostly S wave phases and surface waves to constrain the structure. Those two kinds of models usually reveals very different parts of the earth. For example, for P wave, people used it the image the subduction slabs and it is not very good at image lower mantle structures, such as plumes and lower mantle convections. For S waves, it is the verse verso.

There are many challenges coming along the way. First, the data volume is huge.  There are in total of 1480 earthquakes used in the inversion stage, added into the database step by step. Second, workflow management is crucial dealing with such a large project. One factor is coming from the complex workflow. There are 4 major building blocks, forward simulation, seismic data processing, adjoint simulation and post-processing. Each blocks contains several small blocks. The other factor is coming from the number of earthquakes and high demands of computation. In each iteration, we are doing 1480 forward and adjoint simulation, generating a few Petabyes of wavefiled files and consuming 16 million of CPU hours on the supercomputer at Oak Ridge National Lab. There are yet more in data processing stages. How to deal with hardware failures is very important and prevent containmination into our inversion results.

Here, we present our GLAD-M25 earth model, with significantly improvements on the plumes and subductions.

\section{Starting Model}

We used GLAD-M15 as our starting model. The GLAD-M15 is a 3D transverslty isotropic earth model which uses S362ani + CURST2.0 as its own starting model. It then uses 256 earthquakes and broad-band seismic data to do the 3D full-waveform inversion\cite{Ebru2015}. It uses 15 conjugate graident iterations to update the crust and mantle. The first 12 iterations of GLAD-M15 was performed under 27 secs and the last 3 under ~17 secs. In our inversion, we use the 17s resolution.

It provides 6 model parameters, mass density($\rho$), two compressional wavespeeds($\alpha_v$ and $\alpha_h$), tws shear wavespeeds($\beta_v$ and $\beta_h$) and a dimenionless parameter($\eta$). We will discuss the model parametrization in detail in the following sections.

\section{Earthquakes}
We selected 1040 earthquakes from Global CMT catalog. The mangitudes ranges from 5.5 to 7.0. The lower band is set to ensure the signal-to-noise ratio at the global scale. The upper bound of magnitude, 7.0, is set because the minimal period of waveform is 17s. We also constrain the duration of CMT sources to be smaller than 17s.

We carefully inverted the source mechanism using our starting model, GLAD-M15. The seismic data was filtered into 50-100s to select body wave windows and 60-100s to select surface wave windows\cite{globalCMT}. The inverted parameters includes moment tensors, longitude, latitude and depth. A grid search for the scalar moment and origin time correction was applied directly after the waveform-type of inversion to future calibrate the sources since the first stage inversion algorithm is not very sensitive to those two parameters.
On average, we observed ** km change in depth and ** km change in location. The moment tensor is not changed dramatically and the Global CMT provides good enough focal mechanism. The scalar moment, on the average, has **\% change.

In our 1st iteration, we used 520 earthquakes, as the first iteration is mainly to test our tools, to make sure software are robust and scalable. Starting from 2nd iteration, we double the number of earthquakes, further expanding our dataset to 1040 earthquakes. Starting from GLAD-M22, we added 440 earthquakes from GLobal CMT catelog, mainly in previously poorly covered regions. However, due to computational cost, we didn't implement the 1st stage source inversion in the newly added 440 earthquakes but only calibrate its origin time and scalar moment.

include the earthquake map here.

\begin{figure}
\includegraphics[width=\textwidth]{figures/events_1480.pdf}
\caption{1480 earthquakes used in this study. (a) Distribution of earthquakes The color of beach ball denotes the depth range of earthquakes from Global CMT Catalog \cite{GlobalCMT}. {\color{Blue}Blue} is for shallow earthquake which are above 50km, {\color{Green}Green} is between 50 and 300km and {\color{Red}Red} is below 300km.}
\centering
\end{figure}

\section{Seismic Data}

Seismic stations have been very carefully picked to ensure global converage and high data quality. There are global seismic networks which provides good global coverage, such as the Global Sesimic Netowork(GSN), GEOFON, GEOSCOPE. Regional networks, on the other hand, also becomes a significant part in our database and greatly improve the ray coverage at specific regions, such as US Array(TA), Africa Array(AF), Canadian National Seismograph Network (CN), Geoscience Australia (AU), Brazilian Lithospheric Seismic Project (BL), Antarctic Seismographic Argentinean Italian Network (AI), Caribbean Network (CU), the New Zealand National Seismograph Network (NZ) and etc. There are in total of *** seismic networks and 10,000 seismic stations used in our inversion.

The data, associated with the earhtquakes, was downloaed from several data centers, including IRIS, ORFEUS, INGV, IPGP, ETH, GEONET, RESIF, GFZ and BGR. We only include broad-band seimometers and there in total of 10,000 seismic stations occurred in our database.

include the station map here...

\begin{figure}
\includegraphics[width=\textwidth]{figures/station_map.pdf}
\caption{Locations of 1480 earthquakes used in this study.}
\centering
\end{figure}

\section{Misfit function and Model Parametrization}

\begin{table}[!htb]
\caption{Measurement Categories. Seismic waves are categorized in terms of complementary period bands on three components of motion.}
\label{tab:category}
\begin{tabular}{|c|c|c|c|}
\hline
~          &  Vertical & Radial &  Transverse \\
\hline
17--40~s   &   P-SV body waves          & P-SV body waves           & SH body waves   \\
40--100~s  &   P-SV body waves          & P-SV body waves           & SH body waves \\
40--100~s  &   Rayleigh mantle waves    & Rayleigh mantle waves     & Love mantle waves \\
90--250~s  &   Rayleigh surface waves   & Rayleigh surface waves    & Love surface waves \\
\hline
\end{tabular}\\
\label{table:categories}
\end{table}

\begin{table}[!htb]
\caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
\label{tab:category}
\begin{tabular}{|c|c|c|c|}
\hline
~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
\hline
17--40s                &   31.1    &       37.1 &       42.2 \\
40--100s body waves    &    31.3   &       40.2 &       42.0 \\
40--100s surface waves &   50.1    &       51.1 &       53.8 \\
90--250s               &    36.2   &       38.8 &       38.6 \\
\hline
\end{tabular}\\
\label{table:categories}
\end{table}

\begin{table}[!htb]
\caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
\label{tab:category}
\begin{tabular}{|c|c|c|c|}
\hline
~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
\hline
17--40s                &         29.2 &       33.7 &       43.4 \\
40--100s body waves    &         26.2 &       32.2 &       39.0 \\
40--100s surface waves &         49.1 &       49.4 &       51.2 \\
90--250s               &         30.9 &       34.8 &       34.9 \\
\hline
\end{tabular}\\
\label{table:categories}
\end{table}

\begin{table}[!htb]
\caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
\label{tab:category}
\begin{tabular}{|c|c|c|c|}
\hline
~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
\hline
17--40s                &   17.4   &       21.1 &       24.6 \\
40--100s body waves    &   16.8   &       21.3 &       21.7 \\
40--100s surface waves &   28.5   &       28.3 &       28.4 \\
90--250s               &     14.5 &       13.4 &       25.7 \\
\hline
\end{tabular}\\
\label{table:categories}
\end{table}

\begin{table}[!htb]
\caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
\label{tab:category}
\begin{tabular}{|c|c|c|c|}
\hline
~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
\hline
17--40s                &          11.8 &       14.1 &       21.5 \\
40--100s body waves    &          14.5 &       12.9 &       16.9 \\
40--100s surface waves &          29.3 &       28.1 &       23.7 \\
90--250s               &          10.9 &       14.3 &       24.0 \\
\hline
\end{tabular}\\
\label{table:categories}
\end{table}

The overall misfit, $\Phi$, is defined as follows:

\begin{align}
\label{eq:misfit}
\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{N_{scr}} \omega_{scrw}\, \chi_{scrw}
\quad ,
\end{align}\\
where~$S$ denotes the number of sources, $C$ the number of categories,
$R_{sc}$ the number of receivers for source~$s$ and category~$c$, and~$N_{scr}$ the number of measurements for source~$s$,
category~$c$ and receiver~$r$.
The misfit for source~$s$,
category~$c$, receiver~$r$, and window~$w$ is
\begin{align}
\chi_{scrw} = \left(\frac{\Delta m_{scrw}}{\sigma_{scrw}}\right)^2
\quad ,
\end{align}
where~$\Delta m_{scrw}$ denotes a measurement with associated standard deviation~$\sigma_{scrw}$.-

\subsection{Weightings}
Weighting is crucial to the global tompgraphy. Since most of the earthquakes happen in the in the plate boundaries and most of the seismic stations located in the continents(mostly in the northern hemisphere). Also, there are very dense seismic arrays, such as US array, deployed recently. All the factors mentioned above will lead to a really unevent distribution of ray paths. Our weighting strategy is developed to compensate such effects.

Our weighting algorithm is used to determine the $\omega_{scr}$ and $\omega_s$. $\omega_{scr}$ is the receiver weightings given one source and one category and $\omega_s$ is the source weighting based on it locations. Both problems can be simplied as: given the distrubtion of points in the space to determine the weighting asssociated with each point. Here we introduce the exponential weightings to describe the density of points and mimic the behavior of point correlations.

For more details for the weightings, please refer to the Appendix.

\subsection{Model parametrization}

Transversly isotropy model parametrization is used in our model, which is the same as GLAD-M15. Compared to a general anisotropic model which has 21 independent variables, our model could be described by 5 Love parameters,  A, C, L, N and F. In seismology, it is more straight forward to define the parameter with regarding to wavespeed. Instead of Love parameters, we have $\alpha_v$, $\alpha_h$, $\beta_v$, $\beta_h$ and $\eta$. The parameters can be further reduced to 4 assuming the radial anisotropy is due to shear anistropy, we introduced the buld sound speed, $c=\sqrt{\kappa/\rho}$. Our final parameters is:\\
\begin{align*}
c &= \sqrt{\kappa/\rho} \\
\beta_v &= \sqrt{L/\rho} \\
\beta_h &= \sqrt{N/\rho} \\
\eta & = F/(A-2L)
\end{align*}

The density is hard to contain in our study due to the period band we are working on. So it is constrained by isotropic shear wavespeed, $\beta = \sqrt{(2\beta_v^2 + \beta_h)/3}$,\\
\begin{equation*}
    \delta ln\rho = 0.33\delta ln\beta
\end{equation*}

Based on the parametrization described above, the perturbations in misfit functions would be:

\begin{equation*}
    \delta \chi = \int_V (K_c\delta lnc + K_{\beta_v}\delta ln\beta_v + K_{\beta_h}\delta ln\beta_h + K\eta \delta ln\eta) dV 
\end{equation*}

\section{Adjoint Tomography Workflow}

\subsection{Forward simulation}
The forward simulation takes the CMT sources, stations and Earth models as input. It will generate synthetic seismograms and forward wavefield snapshots. We used SPECFEM3D-GLOBE as the software to calculate the sysnthetic seismograms with GPU acceleration on Titan at the Oak Ridge Nation Lab.

We simulate 120min of seismigrams. It taks 384 Tesla K20 GPUs approximately 10 mins to do the simulation on Titan at the Oak Ridge National Lab for each earthquakes. To fully undo the attenuation, there is also forward wavefiled saved to the disk. In out current 17sec resolution and 120min simulation, for each earthquake, the forward wavefiled is about 1TB. Given the size the 1480 earthquakes, we have 1.5TB of wavefiled during about 10 hours's of simulation, which is huge volume of I/O happening during the calculation.

\subsection{Seismic Data Processing}

The seismic data processing takes the raw observed and synthetic data as input, and generate s the adjoint sources as the output. The preprocessing includes: 1) signal processing that  filter into different period bands and rotate the seismograms from East and North to Radial and transverse.; 2) window selection that pick the time window on a pair of observed and synthetic seismigrams; 3) frequency-dependent measurement that generate travel-time measurements inside the windows; 4) measurements quality checks that throw out bad windows and associated measurements and only keep good ones; 5) calcualte the adjoint sources; 6) for each window calculate its weightings that will be applied to the overall misfit function; 7) construct the final adjoint sources by combining the measurements in different period bands.

\subsection{Adjoint Simulation}
The adjoint simulation takes the adjoint sources as input, and calculate the Frechet derivatives as output. The computation cost is twice as the forward simulation since it is both calculating the adjoint wavefiled and reconstruct the forward wavefield. Other than the adjoint sources, the adjoint simulation also reads in the saved forward wave.

The Adjoint simulation nows takes about 20 mins for 17sec resolution and 120min simlulation, which about the twice the time of forwards simulation, since it needs to calculate both a forward and adjoint wavefield at the same time.

\subsection{Post-processing}
The post-processing takes the Frechet derivatives as the input and generate the model updates as the output. It contains: 1) summation of single event kernels; 2) smoothing the summed kernels; 3) Preconditions using pseudo-Hessian; 4) Numerical optimization to get serach direction; 5) calculate the step length on the search direction; 6) update the model using the search direction and step length.

Conjugated gradient methds was used from M00 to M21. Then L-BFGS was used afterwards. Here we will discuss the L-BFGS methods in details.

\subsubsection{L-BFGS}

Assuming the model is $m_i$ and gradient is $g_i$ at iteration i, we defined the change of model and gradient:\\
\begin{equation*}
    \Delta m_i = m_{i+1} - m_i \quad
    \Delta g_i = g_{i+1} - g_i
\end{equation*}

and \\
\begin{equation*}
     \rho_k = \frac{1}{\Delta g^{T} \Delta m}
\end{equation*}

The L-BFGS iteration could be described below, at iteration k \cite{NumericalOptimization}:

\begin{align*}
q = g_i \\
for \quad i = k -1, k-2, ..., k-n \\
\alpha_i = \rho_i \delta_m_i^{T}q \\
q = q - \alpha_i \delta g_i \\
end for\\
r = H_k^{0}q \\
for i = k-n, k-n+1, ..., k-1 \\
\beta = \rho_i \delta g_i^{T}r \\
    r = r + \delta m_i(\alpha_i - \beta) \\
end for \\
\end{align*}

The search direction for L-BFGS is:
$$d_i = -r$$

The step length is choosen based upon line search along the search direction of the overall misfit function.

\subsection{Adapative Seismic Data Format}

It will be a shame not to take the full advantage of high performance during the data processing stage. However, conventional data format, for example SAC, becomes the bottleneck on the I/O when processing millions of seismic traces since every trace is saved as single files. Not even to mention that it is very easy to make mistakes when processing the data since seismologists usually needs to use various files when processing the data, such as CMT files and station response files.

There are five key issues the new data format should resolve:
\begin{itemize}
    \item Robustness and stability: the container should be well developed and mantained to ensure the correctness of scientific results.
    \item Data Organization: the container should be self-describing. It is preferrable that data, including waveform, sources and station information, are orgainzed into certain structures.
    \item Reproducibility: the container should help scientist keep track of what has been done to the data and others can easily reproduce the results.
    \item Efficiently: providing users with easy mechanism to parallel computation.

\end{itemize}

The Adapative Seismic Data Format, ie ASDF, serves as a self-contained-and-explained data container while taking full adavantage of parallel computing. In our case, one ASDF file contained all the files need in data processing, including the seismic traces, quakeml files and station response files. The APIs were carefully designed for easy data extraction and parallel implementation. Each trace in the ASDF is associated with one speicific quakeml file and stationXML file, reducing the possibilities of making mistakes.

\cite{ASDF2016}
\cite{BookChapter}

\subsection{Workflow Management}

There are more than 10 of small blocks contained in our workflow. Each blocks contains thousands of mini-tasks. For the forward and adjoint simulation, we have 1480 simluations which is both computational and I/O intensive at the different stages of simulations. For the data processing stage, we have million of traces, windows and measurements. It is crucial to catch the hardware and softeware failures, preventing them from containating our results. Given such a complex workflow, it is easily for humans to make mistakes. So we bring in the workflow management tools.

After invesgating a few existing tools, we choose the RADICAL-SAGA and RADICAL-ENTK as our workflow mangement engines. Combine with domain applications, we developed the seismic tomography workflow tools. It can automatiically detected job failures both from the system and user-defined fucntions. So we can keep tracks of all the tasks and resubmit if necessary.

Based on our measurements, for the forward and adjoint simulation, the ENTK will have about 20 secs overhead on each simulation, which is about acceptable given it has the power to detect failures and relaunch jobs. Given the most of the time is waiting in the queue when using supercomputers, automatically failure detection and relaunch will greatly shorten our overall time since it will finish all the simluation in one single jobs.

\section{Misfit and Histogram Improvements}

\begin{figure}
\includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
\caption{Histogram of travel-time measurements from 1480 earthquakes.}
\centering
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
\caption{Histogram of travel-time measurements from 1480 earthquakes.}
\centering
\end{figure}

Also include the P arrival measurements here.

\begin{figure}
\includegraphics[width=\textwidth]{figures/misfit.pdf}
\caption{Misfit Changes from GLAD-M15 to GLAD-M25}
\centering
\end{figure}

\section{Models}

\subsection{Depth cross-section}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
\caption{Map views of global $V_s$ perturbations at various depths for out model GLAD-M25(left column), S362ANI+M(middle column)\cite{} and S40RTS\cite{}. The perturbations are calculated based on each model's own 1D profile. The values(upper-left corner of each figure) denotes the minimum/maximum perturbations for each model at the corresponding depth. The green circles denotes the locations of hotspots\cite{}. The range of the colorbar is the same for each row and the range value is labeled on the most left, right after the depth.}
\label{fig:global-vs}
\centering
\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
\caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3\cite{}. For LLNL-G3Dv3, the depths is labeled on the right bottom due to its specific mesh spacing. Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
\label{fig:global-vp}
\centering
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
\caption{Map views of $V_s$ variations of North America at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(US22 and SL2013NA) models. \ref{fig:global-vs}. Green circles denotes the locations of hotspots. For SL2013NA, we showed the 610km instead of 600km due to its own mesh grid.}
\label{fig:global-vp}

\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
\caption{Map views of $V_s$ variations of Europe at various depths for our model GLAD-M25(first column) and global(S362ANI+M and S40RTS) and regional(EU60) models. For EU60, the range of color bar is 4\% for all depths, which is labeled in the right bottom corner of the figures.}
\label{fig:global-vp}
\centering
\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
\caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(EARA2014) models.}
\label{fig:global-vp}
\centering
\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
\caption{Map views of $V_p$ variations of Europe at various depths for our model GLAD-M25(first column) and several global models, including S362ANI+M, LLNL-G3Dv3 and GAP-P4.}
\label{fig:global-vp}
\centering
\end{figure}

\subsection{Plumes}

\begin{figure}[h]
    \centering
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
\end{figure}

\begin{figure}[h]
    \centering
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
\end{figure}

\subsection{Subductions}

\section{Model Assesement}

\subsection{Out-of-Sample Test}

The goal is to picked unseen events and check the performance of our model using those events. We revisited the Global CMT catalogue, picked the events whose magnitude is between 6.3 and 7.0. There are in total of 360 earthquakes we choosed based. We calibrated the scalar moment and origin time in the GLAD-M25 and luanched forward simulations in variaous stage of GLAD models.

\begin{figure}
\includegraphics[width=\textwidth]{figures/events_360.pdf}
\caption{Locations of 360 out-of-sample earthquakes used in the model assessment stage.}
\centering
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
\caption{Histogram of travel-time measurements from out-of-sample earthquakes.}
\centering
\end{figure}

\subsection{Resolution Test}

\section{Conclusion}

\begin{acknowledgments}
thanks blabla...
\end{acknowledgments}

\newpage

\begin{thebibliography}{}  
  \bibitem[Butcher(1992)]{bu}  
    Butcher J. 1992. {\it Copy-editing: The Cambridge  
    Handbook}, 3rd edn, Cambridge Univ. Press, Cambridge.
  \bibitem[The Chicago Manual(1982)]{cm}  
    {\it The Chicago Manual of Style}, Univ.   
    Chicago Press, Chicago, 1982.
  \bibitem[Chao(1985)]{ch} 
    Chao, B. F., 1985. Normal mode study of the Earth's rigid 
     body motions, {\it Geophys. Res. Lett.}, {\bf 12}, 526-529.
  \bibitem[Hinderer(1986)]{hi}  
    Hinderer, J., 1986. Resonance effects of the earth's fluid
    core in earth rotation, in {\it Solved and Unsolved 
    Problems}, pp. 277-296, ed. Cazenave A., Reidel, 
    Dordrecht.
  \bibitem[Kopka \& Daly(1995)]{kd}  
    Kopka H. \& Daly P.W., 1995, \textit{A guide to} \LaTeX2e,
    Addison--Wesley, New York  
  \bibitem[Lamport(1986)]{la}  
    Lamport L., 1986,  \LaTeX: {\it A Document   
    Preparation System}, Addison--Wesley, New York  
  \bibitem[Lindberg (1986)]{bl}  
    Lindberg, C., 1986.  Multiple taper harmonic analysis of 
    terrestrial free oscillations, {\it PhD thesis}, 
    University of California.
  \bibitem[Maupin(1992)]{ma} 
    Maupin, V., 1992. Modelling of laterally trapped surface 
    waves with application to Rayleigh waves in the Hawaiian 
    swell, {\it Geophys. J. Int.}. {\bf 110}, 553-570.     	
  \bibitem[Rutherford \& Hawker(1981)]{rh}
      Rutherford, S. R. \& Hawker, K. E., 1981, 
    Consistent coupled mode theory of sound propagation for a 
    class of non-separable problems, 
   {\it J. acoust. Soc. Am.}, {\bf 71}, 554-564
\end{thebibliography}

\end{document}

### 2018-09-25 gji_extraguide.tex
refine upto misfit function section

@@
 \usepackage{amsmath}
-\usepackage{color}
+\usepackage[dvipsnames]{xcolor}
 \floatsetup[figure]{style=plain,subcapbesideposition=top}
@@
 
-\section{Starting Model}
+test1 (\cite{zhu2012structure}, \cite{zhu2012structure})
+test2 \citep{zhu2015seismic, ekstrom2012global}
+test3 \citet{ekstrom2012global}
 
-We used GLAD-M15 as our starting model.
-The GLAD-M15 is a 3D transverslty isotropic earth model which uses S362ani + CURST2.0 as its own starting model.
-It then uses 256 earthquakes and broad-band seismic data to do the 3D full-waveform inversion\cite{Ebru2015}.
-It uses 15 conjugate graident iterations to update the crust and mantle.
-The first 12 iterations of GLAD-M15 was performed under 27 secs and the last 3 under ~17 secs.
-In our inversion, we use the 17s resolution.
+\section{Starting Model GLAD--M15}
 
-It provides 6 model parameters, mass density($\rho$), two compressional wavespeeds($\alpha_v$ and $\alpha_h$), tws shear wavespeeds($\beta_v$ and $\beta_h$) and a dimenionless parameter($\eta$).
-We will discuss the model parametrization in detail in the following sections.
+As the continuation of our previous work, we used GLAD-M15 as our
+starting model\citep{bozdaug2016global}.
+The GLAD-M15 is a 3D transversly isotropic earth model. Its uses
+GLAD-M00, a combined 3-D mantle model S362ani \citep{kustowski2008anisotropic}
+with 3-D crust model CURST2.0 \citep{bassin2000current}, as its own starting model.
+Instead of relying to the "crust corrrection", SPECFEM mesher enables us to incoporate
+the 3D crustal model so we are able to update the crust and mantle structures at same
+time with any tradeoffs. Besides, the.
+
+GLAD-M15, same as  S362ANI, provides 6 model parameters, mass density($\rho$), two compressional
+wavespeeds($\alpha_v$ and $\alpha_h$), tws shear wavespeeds($\beta_v$
+and $\beta_h$) and a dimenionless parameter($\eta$). We will discuss
+the model parametrization in detail in the following sections.
+
+GLAD-M15 then uses 256 earthquakes and broad-band seismic data to do the 3D full-waveform
+inversion\citep{bozdaug2016global}. The first 12 iterations of GLAD-M15 was
+performed under 27 secs and the last 3 under 17 secs. We will keep our model
+resolution as 17s in our model. As shown in our later analysis,
+GLAD-M15 proven good enough improvements over S362ANI in both our inversion
+dataset and held-out test dataset. It also shows both significant misfit reduction
+in all measurement categories and and better behavior in statistic anlysis from distribution
+of the phase measurements, which will discussed in the following sections.
 
 \section{Earthquakes}
-We selected 1040 earthquakes from Global CMT catalog.
-The mangitudes ranges from 5.5 to 7.0.
-The lower band is set to ensure the signal-to-noise ratio at the global scale.
-The upper bound of magnitude, 7.0, is set because the minimal period of waveform is 17s.
-We also constrain the duration of CMT sources to be smaller than 17s.
+In addition to the 256 earthquakes used in the first generation model GLAD-M15, we
+carefully picked 784 more earthquakes from Global Centroid-Moment-Tensor catalog\citep{}
+and added them into our database, making the total number of earthquakes reach 1,040.
+The lower band of moment magnitude, is set at 5.5 to ensure the signal-to-noise ratio at
+the global scale. The upper bound of magnitude is set at 7.2 and duration of earthquakes
+is set at 9 secsince we can use point representation and gaussian source time function.
+We also constrain the duration of CMT sources to be smaller than 17s. The locations of 1040
+earthquakes is shown in fig.\ref{source_correction}a.
 
-We carefully inverted the source mechanism using our starting model, GLAD-M15.
-The seismic data was filtered into 50-100s to select body wave windows and 60-100s to select surface wave windows\cite{globalCMT}.
-The inverted parameters includes moment tensors, longitude, latitude and depth.
-A grid search for the scalar moment and origin time correction was applied directly after the waveform-type of inversion to future calibrate the sources since the first stage inversion algorithm is not very sensitive to those two parameters.
-On average, we observed ** km change in depth and ** km change in location.
-The moment tensor is not changed dramatically and the Global CMT provides good enough focal mechanism.
-The scalar moment, on the average, has **\% change.
+To ensure a even global coverage, we used the seismic stations mainly from serveral global
+seismic networks such as Global Seismic Network(II, IU, IC, US, CU and GT),
+GEOFON(GE), GEOSCOPE(G), and regional networks, such as MedNet(MN),
+, Brazilian Lithospheric Seismic Project(BL), Chilean National Seismic Network(C), Japan Meteorological
+Agency Seismic Network(JP) and etc. The number of seismic stations usuallay ranges
+from 150 to 500, denpending on the availablity of seismic stations when the earthquake
+happened. The distribution of seismic stations is in Fig.\ref{fig:source_correction}b and
+data is download from the Incorporated Research Institutions for Seismology(IRIS).
 
-In our 1st iteration, we used 520 earthquakes, as the first iteration is mainly to test our tools, to make sure software are robust and scalable.
-Starting from 2nd iteration, we double the number of earthquakes, further expanding our dataset to 1040 earthquakes.
-Starting from GLAD-M22, we added 440 earthquakes from GLobal CMT catelog, mainly in previously poorly covered regions.
-However, due to computational cost, we didn't implement the 1st stage source inversion in the newly added 440 earthquakes but only calibrate its origin time and scalar moment.
+We use the source inversion algorithm of \cite{liu2004spectral}. This algorithm set the
+target misfit function as the normalized waveform difference and envelope difference between
+observed data, \textbf{d} and synthetic data generated from GLAD-M15, \textbf{s}.
 
-include the earthquake map here.
+\begin{multline}
+  \chi = \sum\limits_{c=1}^{N_c} \omega_c \sum\limits_{r=1}^{N_r} \omega_{cr}
+       \sum\limits_{m=1}^{N_m} \omega_{crm}
+       \Big\{ \lambda {\frac
+              { \int \big[ \mathbf{d}_m(t) - \mathbf{s}_m(t - \Delta t, \mathbf{m}_{15}) \big]^2 dt }
+              {\int \big[ \mathbf{d}_m(t) \big]^2  dt } }\\
+         + (1 - \lambda) \frac
+              {\int \big[ e(\mathbf{d}_m(t)) - e(\mathbf{s}_m(t - \Delta t, \mathbf{m}_{15})) \big]^2 dt }
+              {\int \big[ e(\mathbf{d}_m(t)) \big]^2  dt} \Big\}
+\end{multline}
+
+Following \cite{ekstrom2012global}, seismograms were filtered into 50-100s
+to select 3-component body wave windows and 60-100s to select 3-component
+surface wave windows. Thus, the number of measurements categories $N_c$,
+is 6. To balance the contribution from each category, the weighting for each
+category $\omega_c$, is the reciprocal of the number of measurements in that
+category. The $N_r$ is the number of seismic stations in one category. $\omega_r$
+is the receiver weighting assigned to each individual stations, which we will discuss
+that in detail in the following sections. $N_m$ is the number of measurements for one
+seismic stations in one measurements category and $\omega_m$ is the measurements weightings
+, which is simply set to 1. The inverted parameters includes moment tensors, longitude,
+latitude and depth. In order to get the frechet derivatives for each parameter, there is
+one global-scale forward simulation needed to be done so the source inversion becomes a very expensive
+operation.
+
+Since we shifted the synthetic data based on the cross-correlation to its correspond observed
+data to the best match of the pair, our source inversion is not very sensitive to
+the origin time of earthquakes. In addition to prepare the future Q inversion,
+A grid search for the origin time and scalar moement correction was introduced
+directly to future calibrate the sources afterwards following \cite{zhu2012structure}.
+The grid-search calibration has a linear effect on the seismograms so it doesn't take extra
+simulation time.
+
+Fig.\ref{fig:source_correction} shows the source correction results.
+Most of the earthquakes shows a shallower depth after the source inversion
+(Fig.\ref{fig:source_correction}b and Fig.\ref{fig:source_correction}c),
+in consistent with \cite{hjorleifsdottir2010effects}.
+We observed $-2.62\pm2.49$km depth change compared with the global CMT solutions.
+The scalar moment, on the average, has $5.31\pm3.91$\% change and change of origin time
+is $-0.60\pm1.17$ sec.
+
+Starting from GLAD-M22, we added extra 440 earthquakes from GLobal CMT catelog,
+mainly in previously poorly covered regions. However, due to computational cost,
+we didn't implement the 1st stage source inversion in the newly added 440
+earthquakes but only calibrate its origin time and scalar moment.
 
 \begin{figure}
+  \centering
   \includegraphics[width=\textwidth]{figures/events_1480.pdf}
   \caption{1480 earthquakes used in this study.
-(a) Distribution of earthquakes The color of beach ball denotes the depth range of earthquakes from Global CMT Catalog \cite{GlobalCMT}.
-{\color{Blue}Blue} is for shallow earthquake which are above 50km, {\color{Green}Green} is between 50 and 300km and {\color{Red}Red} is below 300km.}
+(a) Distribution of earthquakes.
+Colors of beach balls indicate the depth range of earthquakes from Global CMT Catalog \citep{ekstrom2012global}.
+{\textbf{\color{Blue} Blue}} is for shallow earthquakes above 50km, \textbf{{\color{ForestGreen} Green}} is between 50 and 300km and \textbf{{\color{Red} Red}} is below 300km.
+(b) and (c) Histograms of earthquake moement magnitudes and depths.}
+  \label{fig:event_1480}
+\end{figure}
+
+\begin{figure}
   \centering
+  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
+  \caption{Source correction results for 1040 events used in the inversion.
+(a) Map views of depth changes.
+(b) Distribution of seismographic stations used in the source inversion stage.(c) depth change of CMT sources compared to its initial solution from the Global CMT Catalog.
+(d)-(f) Histograms of depth, origin time and scalar moment changes.}
+  \label{fig:source_correction}
 \end{figure}
@@
 Seismic stations have been very carefully picked to ensure global converage and high data quality.
-There are global seismic networks which provides good global coverage, such as the Global Sesimic Netowork(GSN), GEOFON, GEOSCOPE.
-Regional networks, on the other hand, also becomes a significant part in our database and greatly improve the ray coverage at specific regions, such as US Array(TA), Africa Array(AF), Canadian National Seismograph Network (CN), Geoscience Australia (AU), Brazilian Lithospheric Seismic Project (BL), Antarctic Seismographic Argentinean Italian Network (AI), Caribbean Network (CU), the New Zealand National Seismograph Network (NZ) and etc.
-There are in total of *** seismic networks and 10,000 seismic stations used in our inversion.
+Other than the networks we mentioned in the source inversion, we include all the data we can
+downloaded from IRIS data center. Regional and temporary networks has become a significant part
+in our database and greatly improve the ray coverage at specific regions, such as US Array(TA),
+Africa Array(AF), Canadian National Seismograph Network (CN), Geoscience Australia (AU),
+Brazilian Lithospheric Seismic Project (BL), Antarctic Seismographic Argentinean Italian Network (AI),
+the New Zealand National Seismograph Network (NZ) and etc.
 
-The data, associated with the earhtquakes, was downloaed from several data centers, including IRIS, ORFEUS, INGV, IPGP, ETH, GEONET, RESIF, GFZ and BGR.
-We only include broad-band seimometers and there in total of 10,000 seismic stations occurred in our database.
-
-include the station map here...
+The data, associated with the earthquakes, was downloaded from several data centers,
+including IRIS, ORFEUS, INGV, IPGP, ETH, GEONET, RESIF, GFZ and BGR.
+There are in total of 275 seismic networks (with individual network code) and 11,800
+seismic stations used in the strutrural inversion stage. Fig.\ref{fig:stations}
+shows the distribution of seismic stations.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{figures/station_map.pdf}
-\caption{Locations of 1480 earthquakes used in this study.}
+  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
+  \caption{Distribution of 11,800 seismographic stations on the globe.
+Colors denote the number of events which they contribute wavefroms to in the model inversion stage.
+Stations with event response < 400 are plotted in smaller size and they are usually temporary arrays which are deployed over a short period of time.}
+  \label{fig:stations}
   \centering
@@
 
-\section{Misfit function and Model Parametrization}
+\section{Misfit function and Model Parimetrization}
 
-\begin{table}[!htb]
-\caption{Measurement Categories. Seismic waves are categorized in terms of complementary period bands on three components of motion.}
-\label{tab:category}
-\begin{tabular}{|c|c|c|c|}
-\hline
-~          &  Vertical & Radial &  Transverse \\
-\hline
-17--40~s   &   P-SV body waves          & P-SV body waves           & SH body waves   \\
-40--100~s  &   P-SV body waves          & P-SV body waves           & SH body waves \\
-40--100~s  &   Rayleigh mantle waves    & Rayleigh mantle waves     & Love mantle waves \\
-90--250~s  &   Rayleigh surface waves   & Rayleigh surface waves    & Love surface waves \\
-\hline
-\end{tabular}\\
-\label{table:categories}
-\end{table}
-
-\begin{table}[!htb]
-\caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
-\label{tab:category}
-\begin{tabular}{|c|c|c|c|}
-\hline
-~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-\hline
-17--40s                &   31.1    &       37.1 &       42.2 \\
-40--100s body waves    &    31.3   &       40.2 &       42.0 \\
-40--100s surface waves &   50.1    &       51.1 &       53.8 \\
-90--250s               &    36.2   &       38.8 &       38.6 \\
-\hline
-\end{tabular}\\
-\label{table:categories}
-\end{table}
-
-\begin{table}[!htb]
-\caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
-\label{tab:category}
-\begin{tabular}{|c|c|c|c|}
-\hline
-~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-\hline
-17--40s                &         29.2 &       33.7 &       43.4 \\
-40--100s body waves    &         26.2 &       32.2 &       39.0 \\
-40--100s surface waves &         49.1 &       49.4 &       51.2 \\
-90--250s               &         30.9 &       34.8 &       34.9 \\
-\hline
-\end{tabular}\\
-\label{table:categories}
-\end{table}
-
-\begin{table}[!htb]
-\caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
-\label{tab:category}
-\begin{tabular}{|c|c|c|c|}
-\hline
-~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-\hline
-17--40s                &   17.4   &       21.1 &       24.6 \\
-40--100s body waves    &   16.8   &       21.3 &       21.7 \\
-40--100s surface waves &   28.5   &       28.3 &       28.4 \\
-90--250s               &     14.5 &       13.4 &       25.7 \\
-\hline
-\end{tabular}\\
-\label{table:categories}
-\end{table}
-
-\begin{table}[!htb]
-\caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
-\label{tab:category}
-\begin{tabular}{|c|c|c|c|}
-\hline
-~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-\hline
-17--40s                &          11.8 &       14.1 &       21.5 \\
-40--100s body waves    &          14.5 &       12.9 &       16.9 \\
-40--100s surface waves &          29.3 &       28.1 &       23.7 \\
-90--250s               &          10.9 &       14.3 &       24.0 \\
-\hline
-\end{tabular}\\
-\label{table:categories}
-\end{table}
-
+This sections will discuss how we define the the misfit fucntion and how we parametrize the model.
 The overall misfit, $\Phi$, is defined as follows:
@@
 where~$S$ denotes the number of sources, $C$ the number of categories,
-$R_{sc}$ the number of receivers for source~$s$ and category~$c$, and~$N_{scr}$ the number of measurements for source~$s$,
-category~$c$ and receiver~$r$.
-The misfit for source~$s$,
-category~$c$, receiver~$r$, and window~$w$ is
+$R_{sc}$ the number of receivers for source~$s$ and category~$c$,
+and~$N_{scr}$ the number of measurements for source~$s$, category~$c$
+and receiver~$r$.
+
+The misfit for source~$s$, category~$c$, receiver~$r$, and window~$w$ is
 \begin{align}
-\chi_{scrw} = \left(\frac{\Delta m_{scrw}}{\sigma_{scrw}}\right)^2
+  \chi_{scrw} = \int \Big[ \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big]^2 d\omega
 \quad ,
 \end{align}
-where~$\Delta m_{scrw}$ denotes a measurement with associated standard deviation~$\sigma_{scrw}$.-
+is a frequency-dependent phase measurements using then multitaper technique.
+where $\Delta m_{scrw}$ denotes a measurement with associated standard deviation~$\sigma_{scrw}$.-
 
 \subsection{Weightings}
-Weighting is crucial to the global tompgraphy.
-Since most of the earthquakes happen in the in the plate boundaries and most of the seismic stations located in the continents(mostly in the northern hemisphere).
-Also, there are very dense seismic arrays, such as US array, deployed recently.
-All the factors mentioned above will lead to a really unevent distribution of ray paths.
-Our weighting strategy is developed to compensate such effects.
+Weighting is crucial to the global tomography to compensate the uneven distribution
+of earthquakes and seismic stations. First, most of the earthquakes happen in the
+in the plate boundaries. There are also several seismic active zoens, such as Japan,
+Fiji Tonoga and South America, where there are a lot of earthquakes clustered near
+the subduction slabs.
+Second, most of the seismic stations located in the continents(futuremore located in
+the northern hemisphere). Besides, there are quite a few dense seismic arrays,
+for example US array, deployed recently, which has hundred or thousands of instrument deployed
+at the regional scale, which will has a very strong footprint on the misfit gradients if no weighting
+been applied.
 
-Our weighting algorithm is used to determine the $\omega_{scr}$ and $\omega_s$.
-$\omega_{scr}$ is the receiver weightings given one source and one category and $\omega_s$ is the source weighting based on it locations.
-Both problems can be simplied as: given the distrubtion of points in the space to determine the weighting asssociated with each point.
-Here we introduce the exponential weightings to describe the density of points and mimic the behavior of point correlations.
+All the factors mentioned above will lead to a uneven distribution of
+ray paths and thus uneven sampling of the earth structure. Our weighting strategy
+is developed to compensate such effects. There are two terms in the misfit function
+receiver weightings, $\omega_{scr}$, and source weightings $\omega_{s}$.
+The calculation of both terms can be abstracted as: given the distrubtion of
+points determine the weighting asssociated with each point.
+Here we introduce the exponential weightings to describe the density of points and
+determine the point weightings.
 
@@
 
-The L-BFGS iteration could be described below, at iteration k \cite{NumericalOptimization}:
+The L-BFGS iteration could be described below, at iteration k \citep{wright1999numerical}:
 
@@
 for \quad i = k -1, k-2, ..., k-n \\
-\alpha_i = \rho_i \delta_m_i^{T}q \\
+    \alpha_i = \rho_i \delta m_{i}^{T} q \\
     q = q - \alpha_i \delta g_i \\
@@
 
-\cite{ASDF2016}
-\cite{BookChapter}
+\citep{krischer2016adaptable}
+%\citep{BookChapter}
 
@@
 
+\begin{table}[!htb]
+  \centering
+  \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
+  \label{tab:category}
+  \begin{tabular}{|c|c|c|c|}
+    \hline
+     ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+    \hline
+    17--40s                &    31.1    &       37.1 &       42.2 \\
+    40--100s body waves    &    31.3    &       40.2 &       42.0 \\
+    40--100s surface waves &    50.1    &       51.1 &       53.8 \\
+    90--250s               &    36.2    &       38.8 &       38.6 \\
+    \hline
+  \end{tabular}\\
+  \label{table:categories}
+\end{table}
+
+\begin{table}[!htb]
+  \centering
+  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
+  \label{tab:category}
+  \begin{tabular}{|c|c|c|c|}
+    \hline
+    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+    \hline
+    17--40s                &         29.2 &       33.7 &       43.4 \\
+    40--100s body waves    &         26.2 &       32.2 &       39.0 \\
+    40--100s surface waves &         49.1 &       49.4 &       51.2 \\
+    90--250s               &         30.9 &       34.8 &       34.9 \\
+    \hline
+  \end{tabular}\\
+  \label{table:misfit_reduction_M00_M25_360}
+\end{table}
+
+\begin{table}[!htb]
+  \centering
+  \caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
+  \label{tab:category}
+  \begin{tabular}{|c|c|c|c|}
+    \hline
+    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+    \hline
+    17--40s                &   17.4   &       21.1 &       24.6 \\
+    40--100s body waves    &   16.8   &       21.3 &       21.7 \\
+    40--100s surface waves &   28.5   &       28.3 &       28.4 \\
+    90--250s               &   14.5   &       13.4 &       25.7 \\
+    \hline
+  \end{tabular}\\
+  \label{table:misfit_reduction_M15_M25}
+\end{table}
+
+\begin{table}[!htb]
+  \centering
+  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
+  \label{tab:category}
+  \begin{tabular}{|c|c|c|c|}
+  \hline
+  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+  \hline
+  17--40s                &          11.8 &       14.1 &       21.5 \\
+  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
+  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
+  90--250s               &          10.9 &       14.3 &       24.0 \\
+  \hline
+  \end{tabular}\\
+  \label{table:misfit_reduction_M15_M25_360}
+\end{table}
+
 \begin{figure}
+  \centering
   \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
-\caption{Histogram of travel-time measurements from 1480 earthquakes.}
-\centering
+  \caption{Histograms of phase measurements for S362ani(GLAD-M00, \textbf{Black}), GLAD-M15(\textbf{{\color{ForestGreen} Green}}) and GLAD-M25(\textbf{{\color{Red} Red}}) in the 12 measurement categories.
+Each columns is one comopnent and each row is one period band.
+The numbers on the top right is the number of measurements used in that category.
+The total number of measurements is around 18.2 million.
+Mean and standard deviations of phase measurements are also denoted in the top right of figures.}
+  \label{fig:phase_hist}
 \end{figure}
@@
 \begin{figure}
+  \centering
   \includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
-\caption{Histogram of travel-time measurements from 1480 earthquakes.}
-\centering
+  \caption{Same as Fig.\ref{fig:phase_hist} except for amplitude measurements.}
 \end{figure}
@@
 \begin{figure}
+  \centering
   \includegraphics[width=\textwidth]{figures/misfit.pdf}
-\caption{Misfit Changes from GLAD-M15 to GLAD-M25}
-\centering
+  \caption{Evolution of phase misfits from GLAD-M15 to GLAD-M25.
+Each color denotes the different stages of inversions, between which we make changes to the inversion by either tuning the weighting strategies or adding more data.
+(a) Evolution of the total phase misfit.
+(b) - (j) Misfit in each period band and component.
+(e) - {g} From GLAD-M18, we future split the 40-100 sec period band into two measurement  catgories: body waves and surface waves.}
 \end{figure}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
-\caption{Map views of global $V_s$ perturbations at various depths for out model GLAD-M25(left column), S362ANI+M(middle column)\cite{} and S40RTS\cite{}.
+  \caption{Map views of global $V_s$ perturbations at various depths for out model GLAD-M25(left column), S362ANI+M(middle column)\citep{moulik2014anisotropic} and S40RTS(right column)\citep{ritsema2011s40rts}.
 The perturbations are calculated based on each model's own 1D profile.
 The values(upper-left corner of each figure) denotes the minimum/maximum perturbations for each model at the corresponding depth.
-The green circles denotes the locations of hotspots\cite{}.
+The green circles denotes the locations of hotspots\citep{montelli2006catalogue}.
 The range of the colorbar is the same for each row and the range value is labeled on the most left, right after the depth.}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
-\caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3\cite{}.
-For LLNL-G3Dv3, the depths is labeled on the right bottom due to its specific mesh spacing.
+  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
+For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing.
 Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
-\caption{Map views of $V_s$ variations of North America at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(US22 and SL2013NA) models.
-\ref{fig:global-vs}.
+  \caption{Map views of $V_s$ variations of North America at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(US22\citep{zhu2017radial} and SL2013NA\citep{schaeffer2014imaging}) models.
 Green circles denotes the locations of hotspots.
-For SL2013NA, we showed the 610km instead of 600km due to its own mesh grid.}
+For SL2013NA, we showed the 610km instead of 600km due to its own mesh.}
 \label{fig:global-vp}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
-\caption{Map views of $V_s$ variations of Europe at various depths for our model GLAD-M25(first column) and global(S362ANI+M and S40RTS) and regional(EU60) models.
-For EU60, the range of color bar is 4\% for all depths, which is labeled in the right bottom corner of the figures.}
+  \caption{Map views of $V_s$ variations of Europe at various depths for our model GLAD-M25(first column) and global(S362ANI+M and S40RTS) and regional(EU60\citep{zhu2015seismic}) models.
+For EU60, the range of color bar is 4\% for all depths, which is labeled in the right bottom of the figures.}
 \label{fig:global-vp}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
-\caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(EARA2014) models.}
+  \caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(EARA2014\citep{chen2015multiparameter}) models.}
 \label{fig:global-vp}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
-\caption{Map views of $V_p$ variations of Europe at various depths for our model GLAD-M25(first column) and several global models, including S362ANI+M, LLNL-G3Dv3 and GAP-P4.}
+  \caption{Map views of $V_p$ variations of South America at various depths for our model GLAD-M25(first column) and several global models, including S362ANI+M, LLNL-G3Dv3 and GAP-P4\citep{fukao2013subducted}.}
 \label{fig:global-vp}
@@
     \centering
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
-    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
+%    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
 \end{figure}
@@
     \centering
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
-    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
+%    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
 \end{figure}
@@
 \includegraphics[width=\textwidth]{figures/events_360.pdf}
-\caption{Locations of 360 out-of-sample earthquakes used in the model assessment stage.}
+  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model asssessment stage.
+Theses events are not used in the structural inversion.
+(a) Beach balls of earthquakes.
+Same color conventions as used in the \ref{fig:} (b) and (c) Histograms of moment magnitude and depth.}
 \centering
@@
 \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
-\caption{Histogram of travel-time measurements from out-of-sample earthquakes.}
+  \caption{Histogram of phase measurements similar to \ref{fig:phase_hist} except for 360 held-out earthquakes.}
 \centering
@@
 \newpage
-
-\begin{thebibliography}{}  
-  \bibitem[Butcher(1992)]{bu}  
-    Butcher J. 1992. {\it Copy-editing: The Cambridge  
-    Handbook}, 3rd edn, Cambridge Univ. Press, Cambridge.
-  \bibitem[The Chicago Manual(1982)]{cm}  
-    {\it The Chicago Manual of Style}, Univ.   
-    Chicago Press, Chicago, 1982.
-  \bibitem[Chao(1985)]{ch} 
-    Chao, B. F., 1985. Normal mode study of the Earth's rigid 
-     body motions, {\it Geophys. Res. Lett.}, {\bf 12}, 526-529.
-  \bibitem[Hinderer(1986)]{hi}  
-    Hinderer, J., 1986. Resonance effects of the earth's fluid
-    core in earth rotation, in {\it Solved and Unsolved 
-    Problems}, pp. 277-296, ed. Cazenave A., Reidel, 
-    Dordrecht.
-  \bibitem[Kopka \& Daly(1995)]{kd}  
-    Kopka H. \& Daly P.W., 1995, \textit{A guide to} \LaTeX2e,
-    Addison--Wesley, New York  
-  \bibitem[Lamport(1986)]{la}  
-    Lamport L., 1986,  \LaTeX: {\it A Document   
-    Preparation System}, Addison--Wesley, New York  
-  \bibitem[Lindberg (1986)]{bl}  
-    Lindberg, C., 1986.  Multiple taper harmonic analysis of 
-    terrestrial free oscillations, {\it PhD thesis}, 
-    University of California.
-  \bibitem[Maupin(1992)]{ma} 
-    Maupin, V., 1992. Modelling of laterally trapped surface 
-    waves with application to Rayleigh waves in the Hawaiian 
-    swell, {\it Geophys. J. Int.}. {\bf 110}, 553-570.     	
-  \bibitem[Rutherford \& Hawker(1981)]{rh}
-      Rutherford, S. R. \& Hawker, K. E., 1981, 
-    Consistent coupled mode theory of sound propagation for a 
-    class of non-separable problems, 
-   {\it J. acoust. Soc. Am.}, {\bf 71}, 554-564
-\end{thebibliography}
+\bibliographystyle{gji}
+\bibliography{ref.bib}
 

### 2018-09-25 gji_extraguide.tex
Updates from ShareLaTeX

--- 2018-09-21 gji_extraguide.tex
@@
 
-\begin{figure}[h]
-    \centering
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
-    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
-\end{figure}
+%\begin{figure}[h]
+%    \centering
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
+%    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
+%\end{figure}
 
-\begin{figure}[h]
-    \centering
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
-    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
-\end{figure}
+%\begin{figure}[h]
+%    \centering
+%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
+%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
+%    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
+%\end{figure}
 
@@
 
+\cite{zhu2012structure}
+
 \newpage
 
-\begin{thebibliography}{}  
-  \bibitem[Butcher(1992)]{bu}  
-    Butcher J. 1992. {\it Copy-editing: The Cambridge  
-    Handbook}, 3rd edn, Cambridge Univ. Press, Cambridge.
-  \bibitem[The Chicago Manual(1982)]{cm}  
-    {\it The Chicago Manual of Style}, Univ.   
-    Chicago Press, Chicago, 1982.
-  \bibitem[Chao(1985)]{ch} 
-    Chao, B. F., 1985. Normal mode study of the Earth's rigid 
-     body motions, {\it Geophys. Res. Lett.}, {\bf 12}, 526-529.
-  \bibitem[Hinderer(1986)]{hi}  
-    Hinderer, J., 1986. Resonance effects of the earth's fluid
-    core in earth rotation, in {\it Solved and Unsolved 
-    Problems}, pp. 277-296, ed. Cazenave A., Reidel, 
-    Dordrecht.
-  \bibitem[Kopka \& Daly(1995)]{kd}  
-    Kopka H. \& Daly P.W., 1995, \textit{A guide to} \LaTeX2e,
-    Addison--Wesley, New York  
-  \bibitem[Lamport(1986)]{la}  
-    Lamport L., 1986,  \LaTeX: {\it A Document   
-    Preparation System}, Addison--Wesley, New York  
-  \bibitem[Lindberg (1986)]{bl}  
-    Lindberg, C., 1986.  Multiple taper harmonic analysis of 
-    terrestrial free oscillations, {\it PhD thesis}, 
-    University of California.
-  \bibitem[Maupin(1992)]{ma} 
-    Maupin, V., 1992. Modelling of laterally trapped surface 
-    waves with application to Rayleigh waves in the Hawaiian 
-    swell, {\it Geophys. J. Int.}. {\bf 110}, 553-570.     	
-  \bibitem[Rutherford \& Hawker(1981)]{rh}
-      Rutherford, S. R. \& Hawker, K. E., 1981, 
-    Consistent coupled mode theory of sound propagation for a 
-    class of non-separable problems, 
-   {\it J. acoust. Soc. Am.}, {\bf 71}, 554-564
-\end{thebibliography}
+\bibliographystyle{gji}
+\bibliography{ref.bib}
 

### 2018-09-25 gji_extraguide.tex
fix ref issues

--- 2018-09-25 gji_extraguide.tex
@@
 We also constrain the duration of CMT sources to be smaller than 17s. The locations of 1040
-earthquakes is shown in fig.\ref{source_correction}a.
+earthquakes is shown in fig.\ref{fig:source_correction}a.
 
@@
 
-Assuming the model is $m_i$ and gradient is $g_i$ at iteration i, we defined the change of model and gradient:\\
+Assuming the model is $m_i$ and gradient is $g_i$ at iteration i, we
+defined the change of model and gradient:
+
 \begin{equation*}
@@
 
-and \\
+and
 \begin{equation*}
@@
   \centering
-  \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
-  \label{tab:category}
+  %\label{tab:misfit_reduction_M00_M25}
   \begin{tabular}{|c|c|c|c|}
@@
   \end{tabular}\\
+  \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
   \label{table:categories}
@@
   \centering
-  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
-  \label{tab:category}
+  %\label{tag:misfit_reduction_M00_M25_360}
   \begin{tabular}{|c|c|c|c|}
@@
   \end{tabular}\\
+  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
   \label{table:misfit_reduction_M00_M25_360}
@@
   \centering
-  \caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
-  \label{tab:category}
+  %\label{tab:category}
   \begin{tabular}{|c|c|c|c|}
@@
   \label{table:misfit_reduction_M15_M25}
+  \caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
 \end{table}
@@
   \centering
-  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
-  \label{tab:category}
+  %\label{tab:category}
   \begin{tabular}{|c|c|c|c|}
@@
   \end{tabular}\\
+  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
   \label{table:misfit_reduction_M15_M25_360}
@@
 For SL2013NA, we showed the 610km instead of 600km due to its own mesh.}
-\label{fig:global-vp}
+\label{fig:america-vs}
 
@@
 For EU60, the range of color bar is 4\% for all depths, which is labeled in the right bottom of the figures.}
-\label{fig:global-vp}
+\label{fig:europe-vs}
 \centering
@@
   \caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(EARA2014\citep{chen2015multiparameter}) models.}
-\label{fig:global-vp}
+\label{fig:asia-vs}
 \centering
@@
   \caption{Map views of $V_p$ variations of South America at various depths for our model GLAD-M25(first column) and several global models, including S362ANI+M, LLNL-G3Dv3 and GAP-P4\citep{fukao2013subducted}.}
-\label{fig:global-vp}
+\label{fig:southamerica-vp}
 \centering
@@
 
-\begin{figure}[h]
-    \centering
+%\begin{figure}[h]
+%    \centering
 %    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
@@
 %    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
-\end{figure}
+%\end{figure}
 
-\begin{figure}[h]
-    \centering
+%\begin{figure}[h]
+%    \centering
 %    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
@@
 %    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
-\end{figure}
+%\end{figure}
 
@@
 (a) Beach balls of earthquakes.
-Same color conventions as used in the \ref{fig:} (b) and (c) Histograms of moment magnitude and depth.}
+Same color conventions as used in the \ref{fig:event_1480} (b) and (c) Histograms of moment magnitude and depth.}
 \centering

### 2018-09-25 gji_extraguide.tex
merge
Updates from ShareLaTeX

@@
 Those two kinds of models usually reveals very different parts of the earth.
-For example, for P wave, people used it the image the subduction slabs and it is not very good at image lower mantle structures, such as plumes and lower mantle convections.
+For example, for P wave, people used it the image the subduction slabs and it is not very good at image lower mantle structures, such as plumes and lower mantle convection.
 For S waves, it is the verse verso.
@@
 The other factor is coming from the number of earthquakes and high demands of computation.
-In each iteration, we are doing 1480 forward and adjoint simulation, generating a few Petabyes of wavefiled files and consuming 16 million of CPU hours on the supercomputer at Oak Ridge National Lab.
+In each iteration, we are doing 1480 forward and adjoint simulation, generating a few Petabytes of wavefield files and consuming 16 million of CPU hours on the supercomputer at Oak Ridge National Lab.
 There are yet more in data processing stages.
-How to deal with hardware failures is very important and prevent containmination into our inversion results.
+How to deal with hardware failures is very important and prevent contamination into our inversion results.
 
@@
 starting model\citep{bozdaug2016global}.
-The GLAD-M15 is a 3D transversly isotropic earth model. Its uses
-GLAD-M00, a combined 3-D mantle model S362ani \citep{kustowski2008anisotropic}
-with 3-D crust model CURST2.0 \citep{bassin2000current}, as its own starting model.
-Instead of relying to the "crust corrrection", SPECFEM mesher enables us to incoporate
+The GLAD-M15 is a 3D transversely isotropic earth model. Its uses
+GLAD-M00, a combined 3-D mantle model S362ANI \citep{kustowski2008anisotropic}
+with 3-D crust model CRUST2.0 \citep{bassin2000current}, as its own starting model.
+Instead of relying to the "crust correction", SPECFEM mesher enables us to incorporate
 the 3D crustal model so we are able to update the crust and mantle structures at same
-time with any tradeoffs. Besides, the.
+time with any trade-off. Besides, the.
 
 GLAD-M15, same as  S362ANI, provides 6 model parameters, mass density($\rho$), two compressional
-wavespeeds($\alpha_v$ and $\alpha_h$), tws shear wavespeeds($\beta_v$
+wavespeeds($\alpha_v$ and $\alpha_h$), two shear wavespeeds($\beta_v$
 and $\beta_h$) and a dimenionless parameter($\eta$). We will discuss
@@
 dataset and held-out test dataset. It also shows both significant misfit reduction
-in all measurement categories and and better behavior in statistic anlysis from distribution
+in all measurement categories and and better behavior in statistic analysis from distribution
 of the phase measurements, which will discussed in the following sections.
@@
 the global scale. The upper bound of magnitude is set at 7.2 and duration of earthquakes
-is set at 9 secsince we can use point representation and gaussian source time function.
-We also constrain the duration of CMT sources to be smaller than 17s. The locations of 1040
-earthquakes is shown in fig.\ref{fig:source_correction}a.
+is set at 9 sec since we can use point representation and Gaussian-type source
+time function.
+We also constrain the duration of CMT sources to be smaller than 17s.
+The locations of 1040 earthquakes is shown in fig.\ref{fig:source_correction}a.
 
-To ensure a even global coverage, we used the seismic stations mainly from serveral global
+To ensure a even global coverage, we used the seismic stations mainly from several global
 seismic networks such as Global Seismic Network(II, IU, IC, US, CU and GT),
@@
 , Brazilian Lithospheric Seismic Project(BL), Chilean National Seismic Network(C), Japan Meteorological
-Agency Seismic Network(JP) and etc. The number of seismic stations usuallay ranges
-from 150 to 500, denpending on the availablity of seismic stations when the earthquake
+Agency Seismic Network(JP) and etc. The number of seismic stations usually ranges
+from 150 to 500, depending on the availability of seismic stations when the earthquake
 happened. The distribution of seismic stations is in Fig.\ref{fig:source_correction}b and
@@
 the origin time of earthquakes. In addition to prepare the future Q inversion,
-A grid search for the origin time and scalar moement correction was introduced
+A grid search for the origin time and scalar moment correction was introduced
 directly to future calibrate the sources afterwards following \cite{zhu2012structure}.
@@
 
-Starting from GLAD-M22, we added extra 440 earthquakes from GLobal CMT catelog,
+Starting from GLAD-M22, we added extra 440 earthquakes from GLobal CMT catalog,
 mainly in previously poorly covered regions. However, due to computational cost,
@@
 {\textbf{\color{Blue} Blue}} is for shallow earthquakes above 50km, \textbf{{\color{ForestGreen} Green}} is between 50 and 300km and \textbf{{\color{Red} Red}} is below 300km.
-(b) and (c) Histograms of earthquake moement magnitudes and depths.}
+(b) and (c) Histograms of earthquake moment magnitudes and depths.}
   \label{fig:event_1480}
@@
 
-Seismic stations have been very carefully picked to ensure global converage and high data quality.
+Seismic stations have been very carefully picked to ensure global coverage and high data quality.
 Other than the networks we mentioned in the source inversion, we include all the data we can
@@
 Africa Array(AF), Canadian National Seismograph Network (CN), Geoscience Australia (AU),
-Brazilian Lithospheric Seismic Project (BL), Antarctic Seismographic Argentinean Italian Network (AI),
+Brazilian Lithospheric Seismic Project (BL),
+Antarctic Seismographic Argentinean Italian Network (AI),
 the New Zealand National Seismograph Network (NZ) and etc.
@@
 The data, associated with the earthquakes, was downloaded from several data centers,
-including IRIS, ORFEUS, INGV, IPGP, ETH, GEONET, RESIF, GFZ and BGR.
+including IRIS, ORFEUS, INGV, IPGP, ETH, GEONET and etc.
 There are in total of 275 seismic networks (with individual network code) and 11,800
-seismic stations used in the strutrural inversion stage. Fig.\ref{fig:stations}
+seismic stations used in the structural inversion stage. Fig.\ref{fig:stations}
 shows the distribution of seismic stations.
@@
   \caption{Distribution of 11,800 seismographic stations on the globe.
-Colors denote the number of events which they contribute wavefroms to in the model inversion stage.
+Colors denote the number of events which they contribute waveforms to in the model inversion stage.
 Stations with event response < 400 are plotted in smaller size and they are usually temporary arrays which are deployed over a short period of time.}
@@
 
-\section{Misfit function and Model Parimetrization}
+\section{Misfit function and Model Parametrization}
 
-This sections will discuss how we define the the misfit fucntion and how we parametrize the model.
+This sections will discuss how we define the the misfit function and how we parameterize the model.
 The overall misfit, $\Phi$, is defined as follows:
@@
 of earthquakes and seismic stations. First, most of the earthquakes happen in the
-in the plate boundaries. There are also several seismic active zoens, such as Japan,
-Fiji Tonoga and South America, where there are a lot of earthquakes clustered near
+in the plate boundaries. There are also several seismic active zones, such as Japan,
+Fiji Tonga and South America, where there are a lot of earthquakes clustered near
 the subduction slabs.
-Second, most of the seismic stations located in the continents(futuremore located in
-the northern hemisphere). Besides, there are quite a few dense seismic arrays,
+Second, most of the seismic stations located in the continents, especially located in
+the northern hemisphere. Besides, there are quite a few dense seismic arrays,
 for example US array, deployed recently, which has hundred or thousands of instrument deployed
@@
 receiver weightings, $\omega_{scr}$, and source weightings $\omega_{s}$.
-The calculation of both terms can be abstracted as: given the distrubtion of
-points determine the weighting asssociated with each point.
+The calculation of both terms can be abstracted as: given the distribution of
+points determine the weighting associated with each point.
 Here we introduce the exponential weightings to describe the density of points and
@@
 
-Transversly isotropy model parametrization is used in our model, which is the same as GLAD-M15.
+Transversely isotropy model parametrization is used in our model, which is the same as GLAD-M15.
 Compared to a general anisotropic model which has 21 independent variables, our model could be described by 5 Love parameters,  A, C, L, N and F.
@@
 Instead of Love parameters, we have $\alpha_v$, $\alpha_h$, $\beta_v$, $\beta_h$ and $\eta$.
-The parameters can be further reduced to 4 assuming the radial anisotropy is due to shear anistropy, we introduced the buld sound speed, $c=\sqrt{\kappa/\rho}$.
+The parameters can be further reduced to 4 assuming the radial anisotropy is due to shear anisotropy, we introduced the bulk sound speed, $c=\sqrt{\kappa/\rho}$.
 Our final parameters is:\\
@@
 It will generate synthetic seismograms and forward wavefield snapshots.
-We used SPECFEM3D-GLOBE as the software to calculate the sysnthetic seismograms with GPU acceleration on Titan at the Oak Ridge Nation Lab.
+We used SPECFEM3D-GLOBE as the software to calculate the synthetic seismograms with GPU acceleration on Titan at the Oak Ridge Nation Lab.
 
-We simulate 120min of seismigrams.
-It taks 384 Tesla K20 GPUs approximately 10 mins to do the simulation on Titan at the Oak Ridge National Lab for each earthquakes.
-To fully undo the attenuation, there is also forward wavefiled saved to the disk.
-In out current 17sec resolution and 120min simulation, for each earthquake, the forward wavefiled is about 1TB.
-Given the size the 1480 earthquakes, we have 1.5TB of wavefiled during about 10 hours's of simulation, which is huge volume of I/O happening during the calculation.
+We simulate 120min of seismograms.
+It takes 384 Tesla K20 GPUs approximately 10 mins to do the simulation on Titan at the Oak Ridge National Lab for each earthquakes.
+To fully undo the attenuation, there is also forward wavefield saved to the disk.
+In out current 17sec resolution and 120min simulation, for each earthquake, the forward wavefield is about 1TB.
+Given the size the 1480 earthquakes, we have 1.5TB of wavefield during about 10 hours of simulation, which is huge volume of I/O happening during the calculation.
 
@@
 The seismic data processing takes the raw observed and synthetic data as input, and generate s the adjoint sources as the output.
-The preprocessing includes: 1) signal processing that  filter into different period bands and rotate the seismograms from East and North to Radial and transverse.; 2) window selection that pick the time window on a pair of observed and synthetic seismigrams; 3) frequency-dependent measurement that generate travel-time measurements inside the windows; 4) measurements quality checks that throw out bad windows and associated measurements and only keep good ones; 5) calcualte the adjoint sources; 6) for each window calculate its weightings that will be applied to the overall misfit function; 7) construct the final adjoint sources by combining the measurements in different period bands.
+The preprocessing includes: 1) signal processing that  filter into different period bands and rotate the seismograms from East and North to Radial and transverse.; 2) window selection that pick the time window on a pair of observed and synthetic seismograms; 3) frequency-dependent measurement that generate travel-time measurements inside the windows; 4) measurements quality checks that throw out bad windows and associated measurements and only keep good ones; 5) calculate the adjoint sources; 6) for each window calculate its weightings that will be applied to the overall misfit function; 7) construct the final adjoint sources by combining the measurements in different period bands.
 
 \subsection{Adjoint Simulation}
-The adjoint simulation takes the adjoint sources as input, and calculate the Frechet derivatives as output.
+The adjoint simulation takes the adjoint sources as input, and calculate the frechet derivatives as output.
 The computation cost is twice as the forward simulation since it is both calculating the adjoint wavefiled and reconstruct the forward wavefield.
@@
 
-The Adjoint simulation nows takes about 20 mins for 17sec resolution and 120min simlulation, which about the twice the time of forwards simulation, since it needs to calculate both a forward and adjoint wavefield at the same time.
+The Adjoint simulation now takes about 20 mins for 17sec resolution and 120min simulation, which about the twice the time of forwards simulation, since it needs to calculate both a forward and adjoint wavefield at the same time.
 
 \subsection{Post-processing}
-The post-processing takes the Frechet derivatives as the input and generate the model updates as the output.
-It contains: 1) summation of single event kernels; 2) smoothing the summed kernels; 3) Preconditions using pseudo-Hessian; 4) Numerical optimization to get serach direction; 5) calculate the step length on the search direction; 6) update the model using the search direction and step length.
+The post-processing takes the frechet derivatives as the input and generate the model updates as the output.
+It contains: 1) summation of single event kernels; 2) smoothing the summed kernels; 3) Preconditions using pseudo-Hessian; 4) Numerical optimization to get search direction; 5) calculate the step length on the search direction; 6) update the model using the search direction and step length.
 
-Conjugated gradient methds was used from M00 to M21. Then L-BFGS was used afterwards. Here we will discuss the L-BFGS methods in details.
+Conjugated gradient methods was used from M00 to M21. Then L-BFGS was used afterwards. Here we will discuss the L-BFGS methods in details.
 
@@
 
-The step length is choosen based upon line search along the search direction of the overall misfit function.
+The step length is chosen based upon line search along the search direction of the overall misfit function.
 
-\subsection{Adapative Seismic Data Format}
+\subsection{Adaptable Seismic Data Format}
 
@@
 \begin{itemize}
-    \item Robustness and stability: the container should be well developed and mantained to ensure the correctness of scientific results.
-    \item Data Organization: the container should be self-describing. It is preferrable that data, including waveform, sources and station information, are orgainzed into certain structures.
+    \item Robustness and stability: the container should be well developed and maintained to ensure the correctness of scientific results.
+    \item Data Organization: the container should be self-describing. It is preferable that data, including waveform, sources and station information, are organized into certain structures.
     \item Reproducibility: the container should help scientist keep track of what has been done to the data and others can easily reproduce the results.
@@
 
-The Adapative Seismic Data Format, ie ASDF, serves as a self-contained-and-explained data container while taking full adavantage of parallel computing.
+The Adaptable Seismic Data Format, ASDF, serves as a self-contained-and-explained data container while taking full advantages of parallel computing.
 In our case, one ASDF file contained all the files need in data processing, including the seismic traces, quakeml files and station response files.
 The APIs were carefully designed for easy data extraction and parallel implementation.
-Each trace in the ASDF is associated with one speicific quakeml file and stationXML file, reducing the possibilities of making mistakes.
+Each trace in the ASDF is associated with one specific quakeml file and stationXML file, reducing the possibilities of making mistakes.
 
@@
 Each blocks contains thousands of mini-tasks.
-For the forward and adjoint simulation, we have 1480 simluations which is both computational and I/O intensive at the different stages of simulations.
+For the forward and adjoint simulation, we have 1480 simulations which is both computational and I/O intensive at the different stages of simulations.
 For the data processing stage, we have million of traces, windows and measurements.
-It is crucial to catch the hardware and softeware failures, preventing them from containating our results.
+It is crucial to catch the hardware and software failures, preventing them from contaminating our results.
 Given such a complex workflow, it is easily for humans to make mistakes.
@@
 
-After invesgating a few existing tools, we choose the RADICAL-SAGA and RADICAL-ENTK as our workflow mangement engines.
+After investigating a few existing tools, we choose the RADICAL-SAGA and RADICAL-ENTK as our workflow management engines.
 Combine with domain applications, we developed the seismic tomography workflow tools.
-It can automatiically detected job failures both from the system and user-defined fucntions.
+It can automatically detected job failures both from the system and user-defined functions.
 So we can keep tracks of all the tasks and resubmit if necessary.
@@
 Based on our measurements, for the forward and adjoint simulation, the ENTK will have about 20 secs overhead on each simulation, which is about acceptable given it has the power to detect failures and relaunch jobs.
-Given the most of the time is waiting in the queue when using supercomputers, automatically failure detection and relaunch will greatly shorten our overall time since it will finish all the simluation in one single jobs.
+Given the most of the time is waiting in the queue when using supercomputers, automatically failure detection and relaunch will greatly shorten our overall time since it will finish all the simulations in one single jobs.
 
@@
   \caption{Histograms of phase measurements for S362ani(GLAD-M00, \textbf{Black}), GLAD-M15(\textbf{{\color{ForestGreen} Green}}) and GLAD-M25(\textbf{{\color{Red} Red}}) in the 12 measurement categories.
-Each columns is one comopnent and each row is one period band.
+Each columns is one component and each row is one period band.
 The numbers on the top right is the number of measurements used in that category.
@@
 (b) - (j) Misfit in each period band and component.
-(e) - {g} From GLAD-M18, we future split the 40-100 sec period band into two measurement  catgories: body waves and surface waves.}
+(e) - {g} From GLAD-M18, we future split the 40-100 sec period band into two measurement categories: body waves and surface waves.}
 \end{figure}
@@
 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Comment out for speed-up compile of latex file
+% If not, the compilation will be slowed down quite a lot due
+% to the insertion of PNG files.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\begin{figure}[h]
@@
 
-\section{Model Assesement}
+\section{Model Assessment}
 
@@
 We revisited the Global CMT catalogue, picked the events whose magnitude is between 6.3 and 7.0.
-There are in total of 360 earthquakes we choosed based.
-We calibrated the scalar moment and origin time in the GLAD-M25 and luanched forward simulations in variaous stage of GLAD models.
+There are in total of 360 earthquakes we chooses.
+We calibrated the scalar moment and origin time in the GLAD-M25 and launched forward simulations in various stage of GLAD models.
 
@@
 \includegraphics[width=\textwidth]{figures/events_360.pdf}
-  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model asssessment stage.
+  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model assessment stage.
 Theses events are not used in the structural inversion.

### 2018-09-26 gji_extraguide.tex
add workflow diagram

@@
 Here we introduce the exponential weightings to describe the density of points and
-determine the point weightings.
+determine the point weightings. Given a set of points $p_i$, the distance between
+two is $r_{ij}$, the weightings associated with each point, $w_i$, could be obtained by:
 
-For more details for the weightings, please refer to the Appendix.
+\begin{equation}
+w_{i} = \frac{1}{A} \left(
+  \sum_{j=1}^N \exp \left[ \mbox{} - \left( \frac{r_{ij}} {r_{0}} \right)^2 \right] \right) ^{-1}
+\label{eq:spatial_weights}
+\end{equation}
+where $r_{0}$ is the sensitivity distance and $A$ is the normalization term.
+The reference distance will control ratios of weightings between dense and
+sparse regions. For more details for the weightings, please refer to the Appendix XXX.
 
-\subsection{Model parametrization}
-
-Transversely isotropy model parametrization is used in our model, which is the same as GLAD-M15.
-Compared to a general anisotropic model which has 21 independent variables, our model could be described by 5 Love parameters,  A, C, L, N and F.
-In seismology, it is more straight forward to define the parameter with regarding to wavespeed.
-Instead of Love parameters, we have $\alpha_v$, $\alpha_h$, $\beta_v$, $\beta_h$ and $\eta$.
-The parameters can be further reduced to 4 assuming the radial anisotropy is due to shear anisotropy, we introduced the bulk sound speed, $c=\sqrt{\kappa/\rho}$.
-Our final parameters is:\\
+\subsection{Model Parametrization}
+Transversely isotropy model parametrization is used in our model, same as S362ANI(GLAD-M00)
+and GLAD-M15. Comparing to a general anisotropic model which has 21 independent variables,
+our model could be described by 5 Love parameters, A, C, L, N and F\citep{love2013treatise}.
+Since it is more straight forward to use  wavespeed as model parameters in sesimology,
+we choose $\alpha_v$, $\alpha_h$, $\beta_v$, $\beta_h$ and $\eta$.
+Assuming the radial anisotropy is due to shear anisotropy, these 5 parameters
+can be further reduced to 4, we introduced the bulk sound speed,
+$c=\sqrt{\kappa/\rho}$. Our final parameters are:\\
 \begin{align*}
@@
 
-The density is hard to contain in our study due to the period band we are working on. So it is constrained by isotropic shear wavespeed, $\beta = \sqrt{(2\beta_v^2 + \beta_h)/3}$,\\
+Since density is hard to constrain due to the period band we are working on, the $\rho$ kernel is obtained by scaling the isotropic shear wavespeed kernel\citep{montagner1989petrological},\\
 \begin{equation*}
@@
 
+where $\beta$ is defined as the Voigt average of the raidally anisotropic shear wave speeds\citep{babuska1991seismic}
+$$\beta = \sqrt{(2\beta_v^2 + \beta_h)/3}$$
+
 Based on the parametrization described above, the perturbations in misfit functions would be:
@@
 \begin{equation*}
-    \delta \chi = \int_V (K_c\delta lnc + K_{\beta_v}\delta ln\beta_v + K_{\beta_h}\delta ln\beta_h + K\eta \delta ln\eta) dV
+    \delta \chi = \int_V
+      (K_c\delta lnc + K_{\beta_v}\delta ln\beta_v + K_{\beta_h}\delta ln\beta_h +
+      K_\eta \delta ln\eta) dV
 \end{equation*}
@@
 \section{Adjoint Tomography Workflow}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/adjoint_workflow.pdf}
+  \caption{Adjoint Tomography Workflow.}
+  \label{fig:phase_hist}
+\end{figure}
 

### 2018-09-28 main.tex
Updates from ShareLaTeX
update depth_slice figures
update till section: Comparison of Histograms

--- 2018-09-26 gji_extraguide.tex
@@
-%%gji_extra_guide.tex
-
 \documentclass[extra,mreferee]{gji}
@@
 \usepackage{floatrow}
+\usepackage{amssymb}
+\usepackage{commath}
 \usepackage{amsmath}
@@
 Colors denote the number of events which they contribute waveforms to in the model inversion stage.
-Stations with event response < 400 are plotted in smaller size and they are usually temporary arrays which are deployed over a short period of time.}
+Stations with event response < 400 are plotted in smaller size and they are usually temporary arrays which are deployed over a short period of time.
+The max event reponse comes from IU.ANMO, which contributeed to 1442 out of 1480 eartquakes in out dataset.}
   \label{fig:stations}
@@
 where $r_{0}$ is the sensitivity distance and $A$ is the normalization term.
-The reference distance will control ratios of weightings between dense and
+The reference distance $r_0$ will control ratios of weightings between dense and
 sparse regions. For more details for the weightings, please refer to the Appendix XXX.
@@
 
+The flow chart for adjoint tomography is shown in Fig.\ref{fig:adjoint_workflow}.
+The workflow starts with a certain number of earthquakes. Here, we used the
+inverted CMT sources from the Global CMT catalog. Based on the time
+of earthquakes, we downloaded observed data, including time series and StaionXML,
+from IRIS and other data centers. The we convert the sources, StationXML and time series
+into ASDF files. Each ASDF file usually contains a complete set of data from one
+earthquake. The data download and conversion need to be done only once. The raw observed data,
+storing in ASDF, could be reused afterwards.
+
 \begin{figure}
   \centering
-  \includegraphics[width=\textwidth]{figures/adjoint_workflow.pdf}
+  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
   \caption{Adjoint Tomography Workflow.}
-  \label{fig:phase_hist}
+  \label{fig:adjoint_workflow}
 \end{figure}
@@
 The forward simulation takes the CMT sources, stations and Earth models as input.
-It will generate synthetic seismograms and forward wavefield snapshots.
-We used SPECFEM3D-GLOBE as the software to calculate the synthetic seismograms with GPU acceleration on Titan at the Oak Ridge Nation Lab.
+We will first generate mesh based on the models. The CMT sources and station will
+be fed into the solver to generate synthetic seismograms and forward wavefield snapshots.
+SEPCFEM3D\_GLOBE with GPU acceleration is used on Titan at the Oak Ridge Nation Lab for
+both mesher and solver part.
 
-We simulate 120min of seismograms.
-It takes 384 Tesla K20 GPUs approximately 10 mins to do the simulation on Titan at the Oak Ridge National Lab for each earthquakes.
-To fully undo the attenuation, there is also forward wavefield saved to the disk.
-In out current 17sec resolution and 120min simulation, for each earthquake, the forward wavefield is about 1TB.
-Given the size the 1480 earthquakes, we have 1.5TB of wavefield during about 10 hours of simulation, which is huge volume of I/O happening during the calculation.
+To simulate 120min of seismograms at 17sec resolution, it takes 384 Tesla K20X
+GPUs approximately 10 mins to run on Titan. To precisly calculate the sensitivity
+kernels, there is forward wavefield saved to the disk and those will used in the
+adjoint simluation in the later stage. In the current resolution
+and simulation length, the forward wavefield saved is above 1 terabytes
+for each earthquake. Given the size the 1480 earthquakes, we have 1.5 petabytes of
+wavefield saved to disk using ADIOS\citep{liu2014hello} during about 10 hours
+of simulation using 15,360 GPUs.
+It is huge volume of data saved to distk in a relatively short period of time, in which case
+ADIOS really helped to relief the I/O bottleneck.
 
@@
 
-The seismic data processing takes the raw observed and synthetic data as input, and generate s the adjoint sources as the output.
-The preprocessing includes: 1) signal processing that  filter into different period bands and rotate the seismograms from East and North to Radial and transverse.; 2) window selection that pick the time window on a pair of observed and synthetic seismograms; 3) frequency-dependent measurement that generate travel-time measurements inside the windows; 4) measurements quality checks that throw out bad windows and associated measurements and only keep good ones; 5) calculate the adjoint sources; 6) for each window calculate its weightings that will be applied to the overall misfit function; 7) construct the final adjoint sources by combining the measurements in different period bands.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
+  \caption{Preprocessing Workflow for seismic data.}
+  \label{fig:preprocess_workflow}
+\end{figure}
+
+The seismic data processing takes the raw observed and synthetic data as input,
+and generate s the adjoint sources as the output. As shown
+in Fig.\ref{fig:preprocess_workflow}, preprocessing includes:
+\begin{enumerate}
+  \item Signal processing that remove the instrument response from observsed data
+    to recover the true ground motion. Both observed and synthetic data will be
+    filtered into a certain period band. Then the two horizontal components of the
+    sesimograms are roated from North, East to radial and transverse only if the
+    StationXML passed the sanity check.
+  \item Window selection that picks the time window on a pair of
+    observed and synthetic seismograms. Pyflex(python version
+    of FLEXWIN\citep{maggi2009automated}), is
+    such a tool that automatically generate windows where observed data and
+    synthetic data are close enough to make measurements based on user defined
+    criteria.
+  \item Multi-taper measurement that generates frequency-dependent travel-time
+    difference within the windows selected from the last step.
+    The output files contains both the measurements and misfit values.
+  \item Window cleaning that get rid of bad windows(and associated
+    measurements), only keeping good ones based on the statistical analysis of
+    measurements.
+  \item calculate the adjoint sources with the sorted windows.
+  \item For each window and associated measurement, calculate its weightings
+    that will be applied at the summation stage and calibrate its contribution
+    into the overall misfit function, using the methond we mentioned before.
+  \item Construct the final adjoint sources by summing the adjoint source from
+    different windows and measurement categories.
+\end{enumerate}
+
+Even though it is such a computational demanding process as the forward and adjoint
+simulation, only taking about $1\%$ CPU hours in the whole workflow, it is crucial
+that directly impact the inversion results. It decides which measurement
+will be taken into consideration and have a footprint in the final gradient.
+We are very careful at this stage, including a lot of checks, such as the Station and
+response integratity check, and also filtering out bad measurements to avoid big outliers.
+On the other hand, it is very process-demanding, which means it has complex data and
+control flows, that every seismograms will go through quite a few of processes
+before the final results is generated. We have millions of seismic traces and ten
+millions of windows, it is impossible to human-check every trace and measurements.
+I will go into more depth about this part in the following sections, discussing our
+efforts how to make the data and process safe and robust.
 
 \subsection{Adjoint Simulation}
-The adjoint simulation takes the adjoint sources as input, and calculate the frechet derivatives as output.
-The computation cost is twice as the forward simulation since it is both calculating the adjoint wavefiled and reconstruct the forward wavefield.
-Other than the adjoint sources, the adjoint simulation also reads in the saved forward wave.
-
-The Adjoint simulation now takes about 20 mins for 17sec resolution and 120min simulation, which about the twice the time of forwards simulation, since it needs to calculate both a forward and adjoint wavefield at the same time.
+The adjoint simulation takes the adjoint sources as input, and calculate the frechet
+derivatives as output. The computation cost is about twice as the forward simulation since
+it is both calculating the adjoint wavefiled and reconstruct the forward wavefield.
+Other than the adjoint sources, the adjoint simulation also reads in the saved forward
+wave, to fully incorporate attenuation and more exactly calculate the anelastic
+sensitivity kernels.
+After the adjoint simulation is done, the save wavefield could be deleted and disk
+space would be freed.
+One Adjoint simulation takes about 25 mins for 17sec resolution for 120min simulation
+at 17s resolution.
 
 \subsection{Post-processing}
-The post-processing takes the frechet derivatives as the input and generate the model updates as the output.
-It contains: 1) summation of single event kernels; 2) smoothing the summed kernels; 3) Preconditions using pseudo-Hessian; 4) Numerical optimization to get search direction; 5) calculate the step length on the search direction; 6) update the model using the search direction and step length.
 
-Conjugated gradient methods was used from M00 to M21. Then L-BFGS was used afterwards. Here we will discuss the L-BFGS methods in details.
+The post-processing takes the frechet derivatives as the input and generate
+the model updates as the output. It contains:
+\begin{enumerate}
+  \item Summation of each kernel for each earthquake to obtain one
+    gradient for the overall misfit function. The number of kernel
+    files will reduce from 1480 to 1 after summing them up. Also,
+    there will source weightings applied at this stage, to balance
+    the uneven distribution of earthquakes.
+  \item Smoothing the misfit gradient using 3D gaussian function, which
+    serves as a regularization procedure. Instead of using a changing
+    smooth radius based upon the "ray density"\citep{bozdaug2016global},
+    we used the fixed value in the same iteration, following\cite{hu2012structure}.
+  \item Precondition the smoothed kernels. Following
+    \citep{luo2013strategies, zhu2012structure, bozdaug2016global},
+    the preconditioner we used is:
+    \begin{equation}
+      P(\mathbf{x}) = 1 / \int \partial_t^2 \mathbf{s}(\mathbf{x}, t) \cdot \partial_t^2 \mathbf{s}^\dagger(\mathbf{x}, T-t) dt
+    \end{equation}
+\end{enumerate}
 
-\subsubsection{L-BFGS}
+Search direction is calculated based on the misfit gradient from the
+post-processsing stage. Search direction is calculated using nonlinear conjugate
+gradient methods\citep{tape2007finite} and L-BFGS(starting from GLAD-M22),
+Here, we used a slightly modified version of conjugate gradient methods,
+adding a restart condition\citep{wright1999numerical} to iterations by checking
+if the current and previous gradient are far from orthogonal:
 
-Assuming the model is $m_i$ and gradient is $g_i$ at iteration i, we
-defined the change of model and gradient:
+\begin{equation}
+  \frac { \abs{g_i \cdot g_{i-1}} }  {\norm{g_{i-1}}^2} \geqslant v
+\end{equation}
 
-\begin{equation*}
-    \Delta m_i = m_{i+1} - m_i \quad
-    \Delta g_i = g_{i+1} - g_i
-\end{equation*}
+where the $v$ is set to $0.1$ in out case.
 
-and
-\begin{equation*}
-     \rho_k = \frac{1}{\Delta g^{T} \Delta m}
-\end{equation*}
-
-The L-BFGS iteration could be described below, at iteration k \citep{wright1999numerical}:
-
-\begin{align*}
-q = g_i \\
-for \quad i = k -1, k-2, ..., k-n \\
-    \alpha_i = \rho_i \delta m_{i}^{T} q \\
-    q = q - \alpha_i \delta g_i \\
-end for\\
-r = H_k^{0}q \\
-for i = k-n, k-n+1, ..., k-1 \\
-    \beta = \rho_i \delta g_i^{T}r \\
-    r = r + \delta m_i(\alpha_i - \beta) \\
-end for \\
-\end{align*}
-
-The search direction for L-BFGS is:
-$$d_i = -r$$
-
-The step length is chosen based upon line search along the search direction of the overall misfit function.
+Based upon the misfit gradient obtained from the post-processing stage.
+Line search is then used to determine the step length for model update
+along the search direction. Forward simulations were run for a subset
+of 120 earthquakes with different step length and the one with
+the max misfit reudction was picked as the model update step length.
 
@@
 
+\subsection{Misfit Evolution}
+
+The inversion went through a few stages, mainly due to adding more data
+and measurement categories and fine tunning the weighting strategies.
+
+\subsubsection{Stage I: M15 - M17}
+
+In the GLAD-M15, we started with 520 events, mainly to validate the test our
+software and workflow, making sure things are working properly.
+In GLAD-M16, we increase our dataset to 1040 earthquakes.
+
+For iterations at this stage, seismograms are filtered into 3 period bands,
+17-40sec, 40-100sec, 90-250 sec. In the 17-40s, we selected body wave windows. For the
+other two, we used all the phases available on the seismograms. Conjugate
+gradient method is used to calculate the model update.
+
+The misfit values increase a bit at M16 due to increase of earthquakes.
+
+\subsubsection{Stage II: M18-M21}
+
+The major change at stage II is we split the 40-100 sec period band into two: one with
+body wave and the other with only surface wave measurements. Since body waves and
+surfaces are sensitive to the different parts of the earth, by splitting these two
+phases, we have more controls over spatical distribution of the model update.
+Table.\ref{table:measurement_category} shows the measurement categories we used starting
+from M18 and we will stick to it till M25.
+
+**Not sure if we need to mention the change of weighting strategy in such a detail here**
+
+Since surface waves are mostly sensitive to shallow
+structures and for shallow structures our model performs quite good
+already given current dataset, we don't expect to see large misfit
+reduction from in those long period surface wave category.
+To better bring out the deep structure, We tune
+down the weightings of 40-100 sec surface wave, thus reduce their
+contribution in the overal misfit function. That explained why we see the
+misfit jum(decrease) from M17 to M18 in Fig.\ref{fig:misfit}(h) - (j) and
+increase Fig.\ref{fig:misfit}(b)-(d). We are using the same data but
+redistribution the contribution from each category by changing the measurements
+weight in the overall misfit function.
+
 \begin{table}[!htb]
   \centering
-  %\label{tab:misfit_reduction_M00_M25}
   \begin{tabular}{|c|c|c|c|}
@@
     \hline
-    17--40s                &    31.1    &       37.1 &       42.2 \\
+    17--40~s   &   P-SV body waves          & P-SV body waves           & SH body waves   \\
+    40--100~s  &   P-SV body waves          & P-SV body waves           & SH body waves \\
+    40--100~s  &   Rayleigh surface waves   & Rayleigh surface waves    & Love surface waves \\
+    90--250~s  &   All waves                & All waves                 & All waves \\
+    \hline
+  \end{tabular}\\
+  \caption{12 measurement categories starting from M18 till M25. Before M15, the 40--100 body and surface waves are combined into one in each component.}
+  \label{table:measurement_category}
+\end{table}
+
+The misfit values for 17-40sec and 40-100s body wavess are decreasing fast at
+the first few iterations, and flattens gradually, which may indicate that we are
+approaching the model resolution limits given current dataset.
+
+\subsubsection{Stage III: M22 - M25}
+
+We added an extra set of 440 earthquakes into our inversion database. Thus, the total
+number of earthquakes increased from 1,040 to 1480. We also bring back weightings
+of 40-100sec surface wave as stage I since the newly added 440 was mostly located
+in poorly covered regions in our previous dataset and those surface wave meansurements
+will help to better constrain the shallow structures at those regions.
+
+The misit jumps, from M21 to M22, is mostly due to the redistribution of weights
+and new earthquakes being added to the dataset. Optimization method is changed
+from conjugate gradient to L-BFGS. Overall misift values is steadily reducing,
+as well as those in each category.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/misfit.pdf}
+  \caption{Evolution of phase misfits from GLAD-M15 to GLAD-M25.
+  Each color denotes the different stages of inversions, between
+  which we make changes to the inversion by either tuning the
+  weighting strategies or adding more data.
+  (a) Evolution of the total phase misfit. (b) - (j) Misfit in
+  each period band and component. (e) - (g) From GLAD-M18,
+  we future split the 40-100 sec period band into two
+  measurement categories: body(red dimond) waves and surface waves
+  (red square).}
+  \label{fig:misfit}
+\end{figure}
+
+\subsection{Misfit Assessment}
+
+In the last setion, we discussed how the misfit evolves in iterations. However, since
+we changed our dataset and misfit functions(mainly weightings) between different stages,
+it might not be clear that how much did we improve our model. To precisely measure
+our model performance, we calculate synthetic data using the same source using M00, M15
+and M25. Windows and weightings are also identical across different iterations.
+
+Table.\ref{table:misfit_reduction_M15_M25} shows the misfit reduction from M15 to M25
+for 12 categories. For all categories, there is a significant misfit reduction. Among
+the three components, transverse have the largest misfit recution. For the 4 period bands,
+40-100s surface waves have the largest misfit reduction which may indicate the 40-100 sec
+surface wave might not have good fit between synthetic and observed data compared to
+other period band and our inversion is improving it a lot.
+
+Table.\ref{table:misfit_reduction_M00_M25} shows M00 to M25. It is very similar to
+Table.\ref{table:misfit_reduction_M15_M25} but with larger values since it also
+counts the model improvements from M00 to M15. The best improved category is
+the transverse component in 40-100s surface waves, with misfit reduction at
+53.8\%. The minimum misfit reudction, on the other hand, is the vertical component
+in 17-40s body waves, with 31.1\% misfit reduction.
+
+\begin{table}[!htb]
+  \centering
+  \begin{tabular}{|c|c|c|c|}
+    \hline
+    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+    \hline
+    17--40s  body waves    &   17.4   &       21.1 &       24.6 \\
+    40--100s body waves    &   16.8   &       21.3 &       21.7 \\
+    40--100s surface waves &   28.5   &       28.3 &       28.4 \\
+    90--250s               &   14.5   &       13.4 &       25.7 \\
+    \hline
+  \end{tabular}\\
+  \caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
+  \label{table:misfit_reduction_M15_M25}
+\end{table}
+
+\begin{table}[!htb]
+  \centering
+  \begin{tabular}{|c|c|c|c|}
+    \hline
+     ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+    \hline
+    17--40s body waves     &    31.1    &       37.1 &       42.2 \\
     40--100s body waves    &    31.3    &       40.2 &       42.0 \\
@@
   \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
-  \label{table:categories}
+  \label{table:misfit_reduction_M00_M25}
 \end{table}
 
-\begin{table}[!htb]
-  \centering
-  %\label{tag:misfit_reduction_M00_M25_360}
-  \begin{tabular}{|c|c|c|c|}
-    \hline
-    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-    \hline
-    17--40s                &         29.2 &       33.7 &       43.4 \\
-    40--100s body waves    &         26.2 &       32.2 &       39.0 \\
-    40--100s surface waves &         49.1 &       49.4 &       51.2 \\
-    90--250s               &         30.9 &       34.8 &       34.9 \\
-    \hline
-  \end{tabular}\\
-  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
-  \label{table:misfit_reduction_M00_M25_360}
-\end{table}
-
-\begin{table}[!htb]
-  \centering
-  %\label{tab:category}
-  \begin{tabular}{|c|c|c|c|}
-    \hline
-    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-    \hline
-    17--40s                &   17.4   &       21.1 &       24.6 \\
-    40--100s body waves    &   16.8   &       21.3 &       21.7 \\
-    40--100s surface waves &   28.5   &       28.3 &       28.4 \\
-    90--250s               &   14.5   &       13.4 &       25.7 \\
-    \hline
-  \end{tabular}\\
-  \label{table:misfit_reduction_M15_M25}
-  \caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
-\end{table}
-
-\begin{table}[!htb]
-  \centering
-  %\label{tab:category}
-  \begin{tabular}{|c|c|c|c|}
-  \hline
-  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-  \hline
-  17--40s                &          11.8 &       14.1 &       21.5 \\
-  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
-  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
-  90--250s               &          10.9 &       14.3 &       24.0 \\
-  \hline
-  \end{tabular}\\
-  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
-  \label{table:misfit_reduction_M15_M25_360}
-\end{table}
+\subsection{Comparison of Histograms}
 
@@
 
-Also include the P arrival measurements here.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/misfit.pdf}
-  \caption{Evolution of phase misfits from GLAD-M15 to GLAD-M25.
-Each color denotes the different stages of inversions, between which we make changes to the inversion by either tuning the weighting strategies or adding more data.
-(a) Evolution of the total phase misfit.
-(b) - (j) Misfit in each period band and component.
-(e) - {g} From GLAD-M18, we future split the 40-100 sec period band into two measurement categories: body waves and surface waves.}
-\end{figure}
+**Also include the P arrival measurements here.**
 
@@
 
+%\begin{figure}
+%\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
+%  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
+For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing.
+Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
+%\label{fig:global-vp}
+%\centering
+%\end{figure
+
 \begin{figure}
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
+\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
   \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
@@
 
+\newpage
+
 \section{Model Assessment}
@@
 We calibrated the scalar moment and origin time in the GLAD-M25 and launched forward simulations in various stage of GLAD models.
+
+\begin{table}[!htb]
+  \centering
+  %\label{tag:misfit_reduction_M00_M25_360}
+  \begin{tabular}{|c|c|c|c|}
+    \hline
+    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+    \hline
+    17--40s                &         29.2 &       33.7 &       43.4 \\
+    40--100s body waves    &         26.2 &       32.2 &       39.0 \\
+    40--100s surface waves &         49.1 &       49.4 &       51.2 \\
+    90--250s               &         30.9 &       34.8 &       34.9 \\
+    \hline
+  \end{tabular}\\
+  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
+  \label{table:misfit_reduction_M00_M25_360}
+\end{table}
+
+\begin{table}[!htb]
+  \centering
+  %\label{tab:category}
+  \begin{tabular}{|c|c|c|c|}
+  \hline
+  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+  \hline
+  17--40s                &          11.8 &       14.1 &       21.5 \\
+  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
+  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
+  90--250s               &          10.9 &       14.3 &       24.0 \\
+  \hline
+  \end{tabular}\\
+  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
+  \label{table:misfit_reduction_M15_M25_360}
+\end{table}
 

### 2018-09-28 main.tex
Updates from ShareLaTeX

--- 2018-09-26 gji_extraguide.tex
@@
 
-\title[\texttt{gji\_extra.sty} ]
-  {\texttt{GLAD-M25} - global adjoint tomography model}
+\title[Global Adjoint Tomography -- Model GLAD-M25]
+  {Global adjoint tomography -- Model GLAD-M25}
 
-\author[]  {Wenjie lei, Jeroen Tromp, ...}
+\author[Lei et al.]
+  {Wenjie Lei$^1$, Youyi Ruan$^{1.2}$, Ebru Bozda\u g$^3$, Daniel Peter$^4$, Matthieu Lefebvre$^1$, \\{\LARGE \rm Dimitri Komatitsch$^5$, Jeroen Tromp$^{1,6}$, Judith Hill$^7$, Norbert Podhorszki$^7$}, \\ {\LARGE \rm and David Pugmire$^7$} \\
+  $^1$ Department of Geosciences, Princeton University, Princeton, NJ 08544, USA\\
+  $^2$ Nanjing University, Nanjing, China\\
+  $^3$ Department of Geophysics, Colorado School of Mines, Colden, CO 80401, USA\\
+  $^4$ Extreme Computing Research Center, King Abdullah University of Science and Technology, \\Thuwal 23955-6900, Kingdom of Saudi Arabia\\
+  $^5$ LMA, CNRS UPR 7051, Aix-Marseille University, Centrale Marseille, 13453 Marseille Cedex 13, France\\
+  $^6$ Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ 08544, USA\\
+  $^7$ Oak Ridge National Laboratory, Oak Ridge, TN 37831, USA\\
+  }
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/adjoint_workflow.pdf}
+  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
   \caption{Adjoint Tomography Workflow.}
@@
 \subsection{Seismic Data Processing}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
+  \caption{Adjoint Tomography Workflow.}
+  \label{fig:phase_hist}
+\end{figure}
 
@@
 
+%\begin{figure}
+%\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
+%  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
+For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing.
+Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
+%\label{fig:global-vp}
+%\centering
+%\end{figure}
+
 \begin{figure}
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
+\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
   \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
@@
 \begin{acknowledgments}
-thanks blabla...
+This research used resources of the Oak Ridge Leadership Computing Facility, which is a DOE Office of Science User Facility supported under contract DE-AC05-00OR22725.
+Additional computational resources were provided by the Princeton Institute for Computational Science \& Engineering (PICSciE).
+We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for providing the data used in this study.
+We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
+The open source spectral-element software package SPECFEM3D\_GLOBE and the seismic measurement software package FLEXWIN used for this article are freely available via the Computational Infrastructure for Geodynamics (CIG; {\tt geodynamics.org}).
+This research was supported by NSF grant~1644826.
 \end{acknowledgments}

### 2018-09-28 main.tex
add conclusion section

--- 2018-09-28 main.tex
@@
 
+Another way to evaluate the model performance by checking the distribution
+of measurements. Fig.\ref{fig:phase_hist} shows the histograms of phase
+measurements. We use identical windows to make measurements using 1,480
+earthquakes on the all the three models, our starting model
+GLAD-M00(362ANI+CRUST2.0), first generation model GLAD-M15,
+and lastest model GLAD-M25. The total number of selected windows is over
+18 million. The standard deviations values of phase measurements has
+significant improvments on all the categories over iterations.
+The means values, has also improved expecially in the long period categories,
+such as the 40-100 surface waves and 90-250 all waves. In some categories,
+you may see slight shift of mean values, mainly due to the trade off among
+different compnents and period bands. To summarize, the improvements in
+the phase measurements histogram is consistent as we observed in the
+misfit reduction.
+
+Fig.\ref{fig:amp_hist} shows the histogram of amplitude measurements. We do
+observed variance reductions in all the categories, but the difference is
+not significant and the variance is still relatively large.
+It is because now we only assimilate phase measurements to
+constrain the elastic model parameters. To better constrain the amplitude
+anomalies, shear attenuation has to been include in our inversion, which is
+next step of our work.
+
 \begin{figure}
@@
   \caption{Same as Fig.\ref{fig:phase_hist} except for amplitude measurements.}
+  \label{fig:amp_hist}
 \end{figure}
@@
 
-\section{Model Assessment}
+\section{Model Evaluation}
 
-\subsection{Out-of-Sample Test}
+Here, we present two ways that used to evaluate the quality of our model:
+resolution analysis and held-out data test.
 
-The goal is to picked unseen events and check the performance of our model using those events.
-We revisited the Global CMT catalogue, picked the events whose magnitude is between 6.3 and 7.0.
-There are in total of 360 earthquakes we chooses.
-We calibrated the scalar moment and origin time in the GLAD-M25 and launched forward simulations in various stage of GLAD models.
+\subsection{Resolution Analysis}
+Checkboard test was commonly used a resolution test method but it is at the
+same cost of inversion of GLAD-M25, which will cost millions of CPU hours.
+Due to the very demanding computational requirements, we used the 'point
+spread function to assess the imaging quality in models GLAD-M25.
+
+\subsection{Held-out Dataset Test}
+Following the approch by \cite{tape2009adjoint}, \cite{bozdaug2016global},
+unseen events are used to check the performance of our
+model. We revisited the Global CMT catalogue,
+picked all the events whose magnitude is between 6.3 and 7.0, which hasn't
+been used in our inversion. The reason why we set the lower bound to 6.3
+instead of 5.5, is those earthquakes have good enough data and generates
+more measurements at the global scale.
+We calibrated the scalar moment and origin time in the GLAD-M25, and there
+are 360 events left that has enough windows. Fig.\ref{fig:events_360} shows
+the ditribution of 360 earthquake that we used as held-out dataset
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/events_360.pdf}
+  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model assessment stage.
+Theses events are not used in the structural inversion.
+(a) Beach balls of earthquakes.
+Same color conventions as used in the \ref{fig:event_1480} (b) and (c) Histograms of moment magnitude and depth.}
+  \label{fig:events_360}
+\end{figure}
+
+First, we evaluate the model performance by misfit reduction. Same windows and
+weightings are used across models. Table.\ref{table:misfit_reduction_M00_M25_360}
+shows the misfit reduction from M15 to M25 and Table.\ref{table:misfit_reduction_M00_M25_360}
+is from M00 to M25. It agains shows misfit reduction in all categories in
+our held-out dataset, simliar to what we observed from the inversion dataset.
+The reduction are slightly smaller, partly due to the reason that we didn't
+do waveform-type inversion as we mentioned in the source inversion stage but
+only did a grid search to calibrate the scalar moment and origin time.
+
+\begin{table}[!htb]
+  \centering
+  %\label{tab:category}
+  \begin{tabular}{|c|c|c|c|}
+  \hline
+  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+  \hline
+  17--40s                &          11.8 &       14.1 &       21.5 \\
+  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
+  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
+  90--250s               &          10.9 &       14.3 &       24.0 \\
+  \hline
+  \end{tabular}\\
+  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
+  \label{table:misfit_reduction_M15_M25_360}
+\end{table}
 
@@
 
-\begin{table}[!htb]
-  \centering
-  %\label{tab:category}
-  \begin{tabular}{|c|c|c|c|}
-  \hline
-  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-  \hline
-  17--40s                &          11.8 &       14.1 &       21.5 \\
-  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
-  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
-  90--250s               &          10.9 &       14.3 &       24.0 \\
-  \hline
-  \end{tabular}\\
-  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
-  \label{table:misfit_reduction_M15_M25_360}
-\end{table}
+Second, we also plotted the histograms of phase measurements in Fig.\ref{fig:phase_hist_360}. We also observed clear variance reduction in all the 12 categories from GLAD--M00 to GLAD--M25.
+
+To summarize, both the misfit reduction and histogram improvements indicates that our model performs good with data that hasn't been used in our inversion.
+We expect to see similar behavior for the future earthquakes.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{figures/events_360.pdf}
-  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model assessment stage.
-Theses events are not used in the structural inversion.
-(a) Beach balls of earthquakes.
-Same color conventions as used in the \ref{fig:event_1480} (b) and (c) Histograms of moment magnitude and depth.}
   \centering
-\end{figure}
-
-\begin{figure}
   \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
   \caption{Histogram of phase measurements similar to \ref{fig:phase_hist} except for 360 held-out earthquakes.}
-\centering
+  \label{fig:phase_hist_360}
 \end{figure}
-
-\subsection{Resolution Test}
 
@@
 
+Seismology is driven by data. Back into time, seismolgist would look at
+single seimograms and pick valuable information out the them. Now, we have
+ten thousands of seismograms deployed globallay and it will be a pity not
+to take all the information we have. Eventhough GLAD-M25 is following-up
+of GLAD-M15. It has many superior advantages and improvements. We increase
+the dataset from 253 to 1480 earthquaks, with carefully inverted sources
+in the 3D earth structures. We have 360 earthquakes used in the test
+dataset, which is already larger than the most of the dataset other people used
+for their inversion. We culled every seismograms from various data centers,
+thanks to the open environment and data sharing spirit of our seimology community.
+With very careful checks by assessing the integrity of instrument response
+and deployment, evaluating the singal-to-noise ratios, picking the time windows
+using over 20 criterias, cleaning windows by their statistical behavior, and
+calculating weights to balance the uneven distribution of earthquakes and
+seismic stations, we really have done a lot to ensure the cleaness of the
+data assimilated into our inversion and make sure every piece of value infomation
+will be used but rejecting the crap data.
+
+There are also quite a lot of technique challenges on the way but we are seeking
+the most cutting-edge technologies to solve them. ADIOS was introduced to save mesh
+and kernel related data, since we are saving petabyes of wavefiled snapshots
+in a few hours of simulation and it is critical even for the most advanced
+supercomputers in the world. ASDF is developed by us to store the seismograms
+since we have ten millions of time series data from thousands of earthquakes.
+We have to get access and process them in a very efficient manner that most of
+the existing data format just won't meet our requirements. To handle the complex
+inversion workflow, we are working RADICAL group to develop the workflow mangement
+tools that will help manage every piece of task and make the user aware if there
+is anything bad happened during the computation. Those tools that help the
+automation of the workflow, is the "guard" that stand there and monitor things
+to make sure our scientific results away from contaminations. Besides, the
+developer of SPECFEM packages, they dedicate more than ten years of work,
+to develop the software and make it fast, efficient and robust for global scale of simulation.
+They are working closly with hardware vendors such as Cray, IBM and NVIDIA to adapt
+the code to architecture of the most advanced supercomputers. We are soon
+moving our simulation to Summit, the world No.1 supercomputer at the Oak Ridge
+National Lab.
+
 \begin{acknowledgments}
-thanks blabla...
+
+  We want to give thanks to the Oak Ridge National Lab, for providing
+  excellent support and computational resource that facilitate our research.
+  We want to thanks IRIS and ORFEUS for providing seismic datas used in this
+  study. We want to acknowledge Hejun Zhu, Min Chen, Carl Tape and Qinya Liu,
+  for providing usefull tools and great suggetions these years.
+  We want to thanks Ebru Bozdag, for providing GLAD-M15, data and software
+  she used in the first generation model.
+
 \end{acknowledgments}

### 2018-09-28 main.tex

@@
 
-  We want to give thanks to the Oak Ridge National Lab, for providing
-  excellent support and computational resource that facilitate our research.
-  We want to thanks IRIS and ORFEUS for providing seismic datas used in this
-  study. We want to acknowledge Hejun Zhu, Min Chen, Carl Tape and Qinya Liu,
-  for providing usefull tools and great suggetions these years.
-  We want to thanks Ebru Bozdag, for providing GLAD-M15, data and software
-  she used in the first generation model.
+%We want to give thanks to the Oak Ridge National Lab, for providing
+%  excellent support and computational resource that facilitate our research.
+%  We want to thanks IRIS and ORFEUS for providing seismic datas used in this
+%  study. We want to acknowledge Hejun Zhu, Min Chen, Carl Tape and Qinya Liu,
+%  for providing usefull tools and great suggetions these years.
+%  We want to thanks Ebru Bozdag, for providing GLAD-M15, data and software
+%  she used in the first generation model.
+
+This research used resources of the Oak Ridge Leadership Computing Facility, which is a DOE Office of Science User Facility supported under contract DE-AC05-00OR22725.
+Additional computational resources were provided by the Princeton Institute for Computational Science \& Engineering (PICSciE).
+We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for providing the data used in this study.
+We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
+The open source spectral-element software package SPECFEM3D\_GLOBE and the seismic measurement software package FLEXWIN used for this article are freely available via the Computational Infrastructure for Geodynamics (CIG; {\tt geodynamics.org}).
+This research was supported by NSF grant~1644826.
 

### 2018-10-09 main.tex
add North America section

@@
     smooth radius based upon the "ray density"\citep{bozdaug2016global},
-    we used the fixed value in the same iteration, following\cite{hu2012structure}.
+    we used the fixed value in the same iteration, following\cite{zhu2012structure}.
   \item Precondition the smoothed kernels. Following
@@
 
-\subsection{Depth cross-section}
+\subsection{Global Velocity Structure}
+In Fig.\ref{fig:global-vs}, the global map of isotropic $V_s$ is plotted at certain depths.
+As comparisons, we also plotted two other models, S362ANI+M{\citep{moulik2014anisotropic},
+which is the updated version of our starting model but with mode data added
+into the inversion, and S40RTS\citep{ritsema2011s40rts}. At the first glance,
+you may notice that all the models agree at the long wavelength structures.
+At 2800km depth, our model is very close to S362ANI+M, with more extended
+features at the LLSVP.
+
+The value ranges are labeled on the top left on each figure. It is obvious the
+value ranges in our model is generally larger than other two models, which is
+consistent with \cite{french2014whole}.
 
 \begin{figure}
+  \centering
   \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
-  \caption{Map views of global $V_s$ perturbations at various depths for out model GLAD-M25(left column), S362ANI+M(middle column)\citep{moulik2014anisotropic} and S40RTS(right column)\citep{ritsema2011s40rts}.
-The perturbations are calculated based on each model's own 1D profile.
-The values(upper-left corner of each figure) denotes the minimum/maximum perturbations for each model at the corresponding depth.
-The green circles denotes the locations of hotspots\citep{montelli2006catalogue}.
-The range of the colorbar is the same for each row and the range value is labeled on the most left, right after the depth.}
+  \caption{Map views of global $V_s$ perturbations at various depths for out model
+  GLAD-M25(left column), S362ANI+M(middle column)\citep{moulik2014anisotropic}
+  and S40RTS(right column)\citep{ritsema2011s40rts}. The perturbations are
+  calculated based on each model's own 1D profile. The values(upper-left corner
+  of each figure) denotes the minimum/maximum perturbations for each model at
+  the corresponding depth. The green circles denotes the locations of
+  hotspots\citep{montelli2006catalogue}. The range of the colorbar is the same
+  for each row and the range value is labeled on the most left, right after
+  the depth.}
   \label{fig:global-vs}
-\centering
 \end{figure}
@@
 
+The other prominent feature of our models is that we can also constrain $V_p$ as an
+independent model parameters. Fig.\ref{fig:global-vp} shows our isotropic $V_p$
+structures at serveal depths. As comparisons, we also showed two more global
+$V_p$ models, LLNL-G3Dv3\citep{simmons2012llnl}} and GAP-P4\citep{fukao2013subducted}.
+
+At 100km depth, our model shows prominent ocean ridges at the realm of pacific
+oceans, which are relatively slow velocity regions, compared to other two vp models.
+On the other hand, the continent slabs, such as Australia, South Africa,
+North America and Europe, is more prominent in our model.
+
+For upper mantle, the LLNL-G3Dv3 shows the largest variations. For example,
+the 500km, the LLNL model shows very strong slow velocity anomalies at
+Hawaii and other pacific hotspots, such as Samoa and Tahiti.
+For middle mantle at about 1000km, all them models all shows a few major
+subduction zones, such as the south america, Fiji and Sumatra regions.
+At lower mantle, such as 2000km and 2800km, LLNL-G3Dv3 and GAP-P4 tends to
+fade out, even though the patterns are very similar among them, such as
+the LLSVP regions.
+
+** Note: add sphereical hormonica analysis later **
+
 \begin{figure}
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
-  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
-For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing.
-Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
+  \caption{Map views of global $V_p$ variations at various depths for our model
+  GLAD-M25(left column), LLNL-G3Dv3(middle column) \citep{simmons2012llnl} and
+  GAP-P4(\citep{fukao2013subducted}).
+  For LLNL-G3Dv3, the depths is labeled on the right
+  bottom based on its own mesh spacing. Other plotting conventions are used
+  similar as in Figure \ref{fig:global-vs}.}
 \label{fig:global-vp}
@@
 
+For the following sections, we will discuss the velocity structures in regional
+areas.
+
+\subsubsection{North America}
+The deployment of USArray has dramatically incresed the data overage on the
+continental United States. In this section, we compare our GLAD-M25 with
+together with two global models, S362ANI+M, S40RTS, and two regional models,
+US22\citep{zhu2017radial}, SL2013NA\citep{schaeffer2014imaging}.
+
+US22 is radially anosotropic model build based on adjoint tomography using
+USArray data from 180 regional earthquakes using 15-50sec short-period
+body waves and 25-150sec long-period surface waves.
+SL2013NA is an uppe-matnle global shear wave speed model using multimode
+surface wavefrom tomography and primally focused on the north american
+region.
+
+The North American region is featured by a large, high-velocity cartonic
+lithosphere, bounded by the Rocky Mountain Front to the west and continental
+margein to the east. For both sides the lithosphere has been deformed by
+low velocity structures thus form a sharp boundary.
+
+At 100km, our model shows a much sharpened boundary between the carton
+and surrounding low veclocity strcutures, especially compared with
+two global models, S362ANI+M and S40RTS, yet stay very similar to
+two regional models, US22 and SL2014NA. At such depth,
+we are observed a very strong expression of the Snake River Plain(
+with YellowStone) and Raton hotspot, with their depth extending to 200km.
+The very high-velocity caraton extend to 200km, with its very core part to
+300 km, similiar to US22 while SL2013NA shows it almost disappeared at such depth.
+Again, the Wyonming craton and Mecicine Hat Block shows a very strong lithospheric
+root from the very shallow depth to 400km, which is also smiliar to US22 but
+hard to observe in SL2013NA. Similiar case is the craton at Yavapai and
+Mazatzal Blocks, which define the souther bound of the large craton.
+
+At such depth, we also observed high velocity
+features within the Gulf of Mexico, which conincides spatially with the deepest
+bathymetry and corresponds to a portion of anciet oceanic
+Lithosphere\citep{muller2008}. The remanant of Juan de Fuca subudction
+plates, with its high velocity footprint, is presented in our model at
+300km and 400km, though the SL2013NA shows a much stronger anomaly.
+
+At the North, our models shows a extended high veloicty craton beneath the 
+Greenland, though clearly seperated with the North America Craton,
+bounded at the relativly low velcoity strcture at Barffin Bay and Labrador
+Sea, with North American Craton followed nicely with the coastline. In the
+north west region, our models shows the most clear picture of
+Aleutian subduction zones, with it high velocity feature down to 400km.
+In the nort easter part, the Iceland hotspot has been greatly enhanced,
+especially at 300km and 400km compared to S362ANI+M.
+
+In the Easter part, our models shows a high-velocity structure at the western
+Atlantic, starting from the tip of Florica to the New York,
+seperated from the major part the north america craton,
+though it stays very thin that the depth only extend to above 200km.
+This feature is associated with some of the oldest oceanic crust and lithosphere
+within the Atlantic\citep{muller2008, schaeffer2014imaging}.
+All the models is showing a high velocity anomaly at Nova Scotia and Newfoundland
+with its high-velocity core to 300km.
+Bermuda hotspot is nicely perserved from our starting
+model, yet get sharpened and stronger at 200km and 300km. Besides, the
+Carribean suduction, which is relatively young subduction systems, is clearly
+observable in our model, starting from 200km to 300km.
+
+For even deeper depth, our models shows a very clear picture of the Farallon
+subductions, but it goes beyond the range of this comparison since the two
+region models are really upper-mantle models which don't extend to the very
+deep depth. We will show some vertical cross-sections of Farallon slabs in
+the later sections.
+
 \begin{figure}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
-  \caption{Map views of $V_s$ variations of North America at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(US22\citep{zhu2017radial} and SL2013NA\citep{schaeffer2014imaging}) models.
-Green circles denotes the locations of hotspots.
-For SL2013NA, we showed the 610km instead of 600km due to its own mesh.}
+  \caption{Map views of $V_s$ variations of North America at various depths
+  for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS)
+  and regional(US22\citep{zhu2017radial} and SL2013NA\citep{schaeffer2014imaging})
+  models. Green circles denotes the locations of hotspots. For SL2013NA, we
+  showed the 610km instead of 600km due to its own mesh.}
 \label{fig:america-vs}
@@
 
+\subsubsection{Europe}
+Fig.\ref{fig:europe-vs} shows the isotropic $V_s$ structures at Europe. As
+comparisons, we also showed S362ANI+M, S40RTS and one regional model EU60
+\citep{zhu2015seismic}. Compared to two global models, it is clear that
+our model is much sharper at few locations. At 100 and 200km, Eifel
+hotspot is clearly seen in our models, as well as in EU60. At 400km
+and 600km, the subduction is very consistent between GLAD-M25 and EU60,
+with the curved shape at the lower bottom of the figure,
+while S362ANI+M shows very smooth shape and S40RTS shows much smaller 
+perturbation values. Besides, at 400km, GLAD-M25 is enhancing Iceland
+compared to S362ANI+M.
+
 \begin{figure}
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
-  \caption{Map views of $V_s$ variations of Europe at various depths for our model GLAD-M25(first column) and global(S362ANI+M and S40RTS) and regional(EU60\citep{zhu2015seismic}) models.
-For EU60, the range of color bar is 4\% for all depths, which is labeled in the right bottom of the figures.}
+  \caption{Map views of $V_s$ variations of Europe at various depths for our
+  model GLAD-M25(first column) and global(S362ANI+M and S40RTS) and
+  regional(EU60\citep{zhu2015seismic}) models. For EU60, the range of color
+  bar is 4\% for all depths, which is labeled in the right bottom of the figures.}
 \label{fig:europe-vs}
@@
 \end{figure}
+
+\subsubsection{Asia}
+
+We presented our model GLAD-M25, with S362ANI+M, S40RTS and EARA2014.
+At 100km depth, our model shows sharpening at the Himalayas subductions
+zones. At 250km, our models shows the subudction in the east part.
+At 400km, our models shows the subduction at sumartra.
 
@@
 \end{figure}
+
+\subsubsection{South America}
 
@@
 \subsection{Plumes}
+
+In this section, we will visit the plumes systems on the earth.
 
@@
 \subsection{Subductions}
+
+In this sections, we will visit some of the well-known subduction zones.
 

### 2018-10-09 main.tex
Updates from ShareLaTeX

@@
 Stations with event response < 400 are plotted in smaller size and they are usually temporary arrays which are deployed over a short period of time.
-The max event reponse comes from IU.ANMO, which contributeed to 1442 out of 1480 eartquakes in out dataset.}
+The max event response comes from IU.ANMO, which contribute ed to 1442 out of 1480 earthquakes in out dataset.}
   \label{fig:stations}
@@
 \end{align}
-is a frequency-dependent phase measurements using then multitaper technique.
+is a frequency-dependent phase measurements using then multi-taper technique.
 where $\Delta m_{scrw}$ denotes a measurement with associated standard deviation~$\sigma_{scrw}$.-
@@
 our model could be described by 5 Love parameters, A, C, L, N and F\citep{love2013treatise}.
-Since it is more straight forward to use  wavespeed as model parameters in sesimology,
+Since it is more straight forward to use  wavespeed as model parameters in seismology,
 we choose $\alpha_v$, $\alpha_h$, $\beta_v$, $\beta_h$ and $\eta$.
@@
 
-where $\beta$ is defined as the Voigt average of the raidally anisotropic shear wave speeds\citep{babuska1991seismic}
+where $\beta$ is defined as the Voigt average of the radially anisotropic shear wave speeds\citep{babuska1991seismic}
 $$\beta = \sqrt{(2\beta_v^2 + \beta_h)/3}$$
@@
 inverted CMT sources from the Global CMT catalog. Based on the time
-of earthquakes, we downloaded observed data, including time series and StaionXML,
+of earthquakes, we downloaded observed data, including time series and StationXML,
 from IRIS and other data centers. The we convert the sources, StationXML and time series
@@
 To simulate 120min of seismograms at 17sec resolution, it takes 384 Tesla K20X
-GPUs approximately 10 mins to run on Titan. To precisly calculate the sensitivity
+GPUs approximately 10 mins to run on Titan. To precisely calculate the sensitivity
 kernels, there is forward wavefield saved to the disk and those will used in the
-adjoint simluation in the later stage. In the current resolution
+adjoint simulation in the later stage. In the current resolution
 and simulation length, the forward wavefield saved is above 1 terabytes
@@
 of simulation using 15,360 GPUs.
-It is huge volume of data saved to distk in a relatively short period of time, in which case
+It is huge volume of data saved to disk in a relatively short period of time, in which case
 ADIOS really helped to relief the I/O bottleneck.
@@
 \begin{enumerate}
-  \item Signal processing that remove the instrument response from observsed data
+  \item Signal processing that remove the instrument response from observed data
     to recover the true ground motion. Both observed and synthetic data will be
     filtered into a certain period band. Then the two horizontal components of the
-    sesimograms are roated from North, East to radial and transverse only if the
+    seismograms are rotated from North, East to radial and transverse only if the
     StationXML passed the sanity check.
@@
     that will be applied at the summation stage and calibrate its contribution
-    into the overall misfit function, using the methond we mentioned before.
+    into the overall misfit function, using the method we mentioned before.
   \item Construct the final adjoint sources by summing the adjoint source from
@@
 We are very careful at this stage, including a lot of checks, such as the Station and
-response integratity check, and also filtering out bad measurements to avoid big outliers.
+response integrity check, and also filtering out bad measurements to avoid big outliers.
 On the other hand, it is very process-demanding, which means it has complex data and
@@
     the uneven distribution of earthquakes.
-  \item Smoothing the misfit gradient using 3D gaussian function, which
+  \item Smoothing the misfit gradient using 3D Gaussian function, which
     serves as a regularization procedure. Instead of using a changing
@@
 of 120 earthquakes with different step length and the one with
-the max misfit reudction was picked as the model update step length.
+the max misfit reduction was picked as the model update step length.
 
@@
 The Adaptable Seismic Data Format, ASDF, serves as a self-contained-and-explained data container while taking full advantages of parallel computing.
-In our case, one ASDF file contained all the files need in data processing, including the seismic traces, quakeml files and station response files.
+In our case, one ASDF file contained all the files need in data processing, including the seismic traces, Quakeml files and station response files.
 The APIs were carefully designed for easy data extraction and parallel implementation.
-Each trace in the ASDF is associated with one specific quakeml file and stationXML file, reducing the possibilities of making mistakes.
+Each trace in the ASDF is associated with one specific Quakeml file and StationXML file, reducing the possibilities of making mistakes.
 
@@
 The inversion went through a few stages, mainly due to adding more data
-and measurement categories and fine tunning the weighting strategies.
+and measurement categories and fine tuning the weighting strategies.
 
@@
 surfaces are sensitive to the different parts of the earth, by splitting these two
-phases, we have more controls over spatical distribution of the model update.
+phases, we have more controls over spatial distribution of the model update.
 Table.\ref{table:measurement_category} shows the measurement categories we used starting
@@
 down the weightings of 40-100 sec surface wave, thus reduce their
-contribution in the overal misfit function. That explained why we see the
-misfit jum(decrease) from M17 to M18 in Fig.\ref{fig:misfit}(h) - (j) and
+contribution in the overall misfit function. That explained why we see the
+misfit jump(decrease) from M17 to M18 in Fig.\ref{fig:misfit}(h) - (j) and
 increase Fig.\ref{fig:misfit}(b)-(d). We are using the same data but
@@
 
-The misfit values for 17-40sec and 40-100s body wavess are decreasing fast at
+The misfit values for 17-40sec and 40-100s body waves are decreasing fast at
 the first few iterations, and flattens gradually, which may indicate that we are
@@
 of 40-100sec surface wave as stage I since the newly added 440 was mostly located
-in poorly covered regions in our previous dataset and those surface wave meansurements
+in poorly covered regions in our previous dataset and those surface wave measurements
 will help to better constrain the shallow structures at those regions.
 
-The misit jumps, from M21 to M22, is mostly due to the redistribution of weights
+The misfit jumps, from M21 to M22, is mostly due to the redistribution of weights
 and new earthquakes being added to the dataset. Optimization method is changed
-from conjugate gradient to L-BFGS. Overall misift values is steadily reducing,
+from conjugate gradient to L-BFGS. Overall misfit values is steadily reducing,
 as well as those in each category.
@@
   we future split the 40-100 sec period band into two
-  measurement categories: body(red dimond) waves and surface waves
+  measurement categories: body(red diamond) waves and surface waves
   (red square).}
@@
 
-In the last setion, we discussed how the misfit evolves in iterations. However, since
+In the last section, we discussed how the misfit evolves in iterations. However, since
 we changed our dataset and misfit functions(mainly weightings) between different stages,
@@
 for 12 categories. For all categories, there is a significant misfit reduction. Among
-the three components, transverse have the largest misfit recution. For the 4 period bands,
+the three components, transverse have the largest misfit reduction. For the 4 period bands,
 40-100s surface waves have the largest misfit reduction which may indicate the 40-100 sec
@@
 the transverse component in 40-100s surface waves, with misfit reduction at
-53.8\%. The minimum misfit reudction, on the other hand, is the vertical component
+53.8\%. The minimum misfit reduction, on the other hand, is the vertical component
 in 17-40s body waves, with 31.1\% misfit reduction.
@@
 18 million. The standard deviations values of phase measurements has
-significant improvments on all the categories over iterations.
-The means values, has also improved expecially in the long period categories,
+significant improvements on all the categories over iterations.
+The means values, has also improved especially in the long period categories,
 such as the 40-100 surface waves and 90-250 all waves. In some categories,
 you may see slight shift of mean values, mainly due to the trade off among
-different compnents and period bands. To summarize, the improvements in
+different components and period bands. To summarize, the improvements in
 the phase measurements histogram is consistent as we observed in the
@@
 independent model parameters. Fig.\ref{fig:global-vp} shows our isotropic $V_p$
-structures at serveal depths. As comparisons, we also showed two more global
+structures at several depths. As comparisons, we also showed two more global
 $V_p$ models, LLNL-G3Dv3\citep{simmons2012llnl}} and GAP-P4\citep{fukao2013subducted}.
@@
 For middle mantle at about 1000km, all them models all shows a few major
-subduction zones, such as the south america, Fiji and Sumatra regions.
+subduction zones, such as the South America, Fiji and Sumatra regions.
 At lower mantle, such as 2000km and 2800km, LLNL-G3Dv3 and GAP-P4 tends to
@@
 
-** Note: add sphereical hormonica analysis later **
+** Note: add spherical harmonic analysis later **
 
@@
 \subsubsection{North America}
-The deployment of USArray has dramatically incresed the data overage on the
+The deployment of USArray has dramatically increased the data overage on the
 continental United States. In this section, we compare our GLAD-M25 with
@@
 
-US22 is radially anosotropic model build based on adjoint tomography using
+US22 is radially anisotropic model build based on adjoint tomography using
 USArray data from 180 regional earthquakes using 15-50sec short-period
 body waves and 25-150sec long-period surface waves.
-SL2013NA is an uppe-matnle global shear wave speed model using multimode
-surface wavefrom tomography and primally focused on the north american
+SL2013NA is an upper-mantle global shear wave speed model using multimode
+surface waveform tomography and primarily focused on the north American
 region.
 
-The North American region is featured by a large, high-velocity cartonic
+The North American region is featured by a large, high-velocity cratonic
 lithosphere, bounded by the Rocky Mountain Front to the west and continental
-margein to the east. For both sides the lithosphere has been deformed by
+margin to the east. For both sides the lithosphere has been deformed by
 low velocity structures thus form a sharp boundary.
@@
 At 100km, our model shows a much sharpened boundary between the carton
-and surrounding low veclocity strcutures, especially compared with
+and surrounding low velocity structures, especially compared with
 two global models, S362ANI+M and S40RTS, yet stay very similar to
@@
 we are observed a very strong expression of the Snake River Plain(
-with YellowStone) and Raton hotspot, with their depth extending to 200km.
-The very high-velocity caraton extend to 200km, with its very core part to
-300 km, similiar to US22 while SL2013NA shows it almost disappeared at such depth.
-Again, the Wyonming craton and Mecicine Hat Block shows a very strong lithospheric
-root from the very shallow depth to 400km, which is also smiliar to US22 but
-hard to observe in SL2013NA. Similiar case is the craton at Yavapai and
-Mazatzal Blocks, which define the souther bound of the large craton.
+with Yellowstone) and Raton hotspot, with their depth extending to 200km.
+The very high-velocity craton extend to 200km, with its very core part to
+300 km, similar to US22 while SL2013NA shows it almost disappeared at such depth.
+Again, the Wyoming craton and Medicine Hat Block shows a very strong lithosphere
+root from the very shallow depth to 400km, which is also similar to US22 but
+hard to observe in SL2013NA. Similar case is the craton at Yavapai and
+Mazatzal Blocks, which define the southern bound of the large craton.
 
 At such depth, we also observed high velocity
-features within the Gulf of Mexico, which conincides spatially with the deepest
-bathymetry and corresponds to a portion of anciet oceanic
-Lithosphere\citep{muller2008}. The remanant of Juan de Fuca subudction
+features within the Gulf of Mexico, which coincides spatially with the deepest
+bathymetry and corresponds to a portion of ancient oceanic
+Lithosphere\citep{muller2008}. The remnant of Juan de Fuca subduction
 plates, with its high velocity footprint, is presented in our model at
@@
 
-At the North, our models shows a extended high veloicty craton beneath the 
-Greenland, though clearly seperated with the North America Craton,
-bounded at the relativly low velcoity strcture at Barffin Bay and Labrador
+At the North, our models shows a extended high velocity craton beneath the 
+Greenland, though clearly separated with the North America Craton,
+bounded at the relatively low velocity structure at Barffin Bay and Labrador
 Sea, with North American Craton followed nicely with the coastline. In the
@@
 Aleutian subduction zones, with it high velocity feature down to 400km.
-In the nort easter part, the Iceland hotspot has been greatly enhanced,
+In the northeastern part, the Iceland hotspot has been greatly enhanced,
 especially at 300km and 400km compared to S362ANI+M.
@@
 In the Easter part, our models shows a high-velocity structure at the western
-Atlantic, starting from the tip of Florica to the New York,
-seperated from the major part the north america craton,
+Atlantic, starting from the tip of Florida to the New York,
+separated from the major part the north America craton,
 though it stays very thin that the depth only extend to above 200km.
@@
 with its high-velocity core to 300km.
-Bermuda hotspot is nicely perserved from our starting
+Bermuda hotspot is nicely preserved from our starting
 model, yet get sharpened and stronger at 200km and 300km. Besides, the
-Carribean suduction, which is relatively young subduction systems, is clearly
+Caribbean suduction, which is relatively young subduction systems, is clearly
 observable in our model, starting from 200km to 300km.
@@
 \subsubsection{Europe}
+
+...to be done...
 Fig.\ref{fig:europe-vs} shows the isotropic $V_s$ structures at Europe. As
@@
 
+...to be done...
 We presented our model GLAD-M25, with S362ANI+M, S40RTS and EARA2014.
 At 100km depth, our model shows sharpening at the Himalayas subductions
-zones. At 250km, our models shows the subudction in the east part.
+zones. At 250km, our models shows the subduction in the east part.
 At 400km, our models shows the subduction at sumartra.
@@
 \subsubsection{South America}
+...to be done...
 
@@
 \subsection{Held-out Dataset Test}
-Following the approch by \cite{tape2009adjoint}, \cite{bozdaug2016global},
+Following the approach by \cite{tape2009adjoint}, \cite{bozdaug2016global},
 unseen events are used to check the performance of our
@@
 are 360 events left that has enough windows. Fig.\ref{fig:events_360} shows
-the ditribution of 360 earthquake that we used as held-out dataset
+the distribution of 360 earthquake that we used as held-out dataset
 
@@
 shows the misfit reduction from M15 to M25 and Table.\ref{table:misfit_reduction_M00_M25_360}
-is from M00 to M25. It agains shows misfit reduction in all categories in
-our held-out dataset, simliar to what we observed from the inversion dataset.
+is from M00 to M25. It again shows misfit reduction in all categories in
+our held-out dataset, similar to what we observed from the inversion dataset.
 The reduction are slightly smaller, partly due to the reason that we didn't
@@
 
-Seismology is driven by data. Back into time, seismolgist would look at
-single seimograms and pick valuable information out the them. Now, we have
-ten thousands of seismograms deployed globallay and it will be a pity not
-to take all the information we have. Eventhough GLAD-M25 is following-up
+Seismology is driven by data. Back into time, seismologists would look at
+single seismograms and pick valuable information out the them. Now, we have
+ten thousands of seismograms deployed globally and it will be a pity not
+to take all the information we have. Even though GLAD-M25 is following-up
 of GLAD-M15. It has many superior advantages and improvements. We increase
-the dataset from 253 to 1480 earthquaks, with carefully inverted sources
+the dataset from 253 to 1480 earthquakes, with carefully inverted sources
 in the 3D earth structures. We have 360 earthquakes used in the test
@@
 for their inversion. We culled every seismograms from various data centers,
-thanks to the open environment and data sharing spirit of our seimology community.
+thanks to the open environment and data sharing spirit of our seismology community.
 With very careful checks by assessing the integrity of instrument response
-and deployment, evaluating the singal-to-noise ratios, picking the time windows
-using over 20 criterias, cleaning windows by their statistical behavior, and
+and deployment, evaluating the signal-to-noise ratios, picking the time windows
+using over 20 criteria, cleaning windows by their statistical behavior, and
 calculating weights to balance the uneven distribution of earthquakes and
-seismic stations, we really have done a lot to ensure the cleaness of the
-data assimilated into our inversion and make sure every piece of value infomation
+seismic stations, we really have done a lot to ensure the cleanness of the
+data assimilated into our inversion and make sure every piece of value information
 will be used but rejecting the crap data.
@@
 the most cutting-edge technologies to solve them. ADIOS was introduced to save mesh
-and kernel related data, since we are saving petabyes of wavefiled snapshots
+and kernel related data, since we are saving petabytes of wavefiled snapshots
 in a few hours of simulation and it is critical even for the most advanced
@@
 the existing data format just won't meet our requirements. To handle the complex
-inversion workflow, we are working RADICAL group to develop the workflow mangement
+inversion workflow, we are working RADICAL group to develop the workflow management
 tools that will help manage every piece of task and make the user aware if there
@@
 automation of the workflow, is the "guard" that stand there and monitor things
-to make sure our scientific results away from contaminations. Besides, the
+to make sure our scientific results away from contamination. Besides, the
 developer of SPECFEM packages, they dedicate more than ten years of work,
 to develop the software and make it fast, efficient and robust for global scale of simulation.
-They are working closly with hardware vendors such as Cray, IBM and NVIDIA to adapt
+They are working closely with hardware vendors such as Cray, IBM and NVidia to adapt
 the code to architecture of the most advanced supercomputers. We are soon

### 2018-10-12 main.tex
highlight Jeroen's edit section

@@
 \section{Introduction}
+
+{\color{Red} Wenjie: I want to leave this part to the end, when I finished reading all the papers.}
+
 With the development of high performance computing and numerical methods, it is now possible to using adjoint method to image the interior the globe using thousands of earthquakes.
@@
 
+{\color{Red} Wenjie: Read for Jeroen to edit}
+
 As the continuation of our previous work, we used GLAD-M15 as our
@@
 \section{Earthquakes}
+
+{\color{Red} Wenjie: Read for Jeroen to edit}
+
 In addition to the 256 earthquakes used in the first generation model GLAD-M15, we
@@
 
+{\color{Red} Wenjie: Read for Jeroen to edit}
+
 Seismic stations have been very carefully picked to ensure global coverage and high data quality.
@@
 \section{Misfit function and Model Parametrization}
+
+{\color{Red} Wenjie: Read for Jeroen to edit}
 
@@
 
+{\color{Red} Wenjie: Read for Jeroen to edit}
+
 The flow chart for adjoint tomography is shown in Fig.\ref{fig:adjoint_workflow}.
@@
 \subsection{Forward simulation}
+
+{\color{Red} Wenjie: Read for Jeroen to edit}
+
 The forward simulation takes the CMT sources, stations and Earth models as input.
@@
 \subsection{Seismic Data Processing}
+
+{\color{Red} Wenjie: Read for Jeroen to edit}
 
@@
 \subsection{Adjoint Simulation}
+
+{\color{Red} Wenjie: Read for Jeroen to edit}
+
 The adjoint simulation takes the adjoint sources as input, and calculate the frechet
@@
 \subsection{Post-processing}
+
+{\color{Red} Wenjie: Read for Jeroen to edit}
 
@@
 
+{\color{Red} Wenjie: Read for Jeroen to edit}
+
 The inversion went through a few stages, mainly due to adding more data
@@
 
+{\color{Red} Wenjie: Read for Jeroen to edit}
+
 In the last section, we discussed how the misfit evolves in iterations. However, since
@@
 \subsection{Comparison of Histograms}
+
+{\color{Red} Wenjie: Read for Jeroen to edit}
 
@@
 
+\section{Model Evaluation}
+
+Here, we present two ways that used to evaluate the quality of our model:
+resolution analysis and held-out data test.
+
+\subsection{Resolution Analysis}
+Checkboard test was commonly used a resolution test method but it is at the
+same cost of inversion of GLAD-M25, which will cost millions of CPU hours.
+Due to the very demanding computational requirements, we used the 'point
+spread function to assess the imaging quality in models GLAD-M25.
+
+\subsection{Held-out Dataset Test}
+Following the approach by \cite{tape2009adjoint}, \cite{bozdaug2016global},
+unseen events are used to check the performance of our
+model. We revisited the Global CMT catalogue,
+picked all the events whose magnitude is between 6.3 and 7.0, which hasn't
+been used in our inversion. The reason why we set the lower bound to 6.3
+instead of 5.5, is those earthquakes have good enough data and generates
+more measurements at the global scale.
+We calibrated the scalar moment and origin time in the GLAD-M25, and there
+are 360 events left that has enough windows. Fig.\ref{fig:events_360} shows
+the distribution of 360 earthquake that we used as held-out dataset
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/events_360.pdf}
+  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model assessment stage.
+Theses events are not used in the structural inversion.
+(a) Beach balls of earthquakes.
+Same color conventions as used in the \ref{fig:event_1480} (b) and (c) Histograms of moment magnitude and depth.}
+  \label{fig:events_360}
+\end{figure}
+
+First, we evaluate the model performance by misfit reduction. Same windows and
+weightings are used across models. Table.\ref{table:misfit_reduction_M00_M25_360}
+shows the misfit reduction from M15 to M25 and Table.\ref{table:misfit_reduction_M00_M25_360}
+is from M00 to M25. It again shows misfit reduction in all categories in
+our held-out dataset, similar to what we observed from the inversion dataset.
+The reduction are slightly smaller, partly due to the reason that we didn't
+do waveform-type inversion as we mentioned in the source inversion stage but
+only did a grid search to calibrate the scalar moment and origin time.
+
+\begin{table}[!htb]
+  \centering
+  %\label{tab:category}
+  \begin{tabular}{|c|c|c|c|}
+  \hline
+  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+  \hline
+  17--40s                &          11.8 &       14.1 &       21.5 \\
+  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
+  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
+  90--250s               &          10.9 &       14.3 &       24.0 \\
+  \hline
+  \end{tabular}\\
+  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
+  \label{table:misfit_reduction_M15_M25_360}
+\end{table}
+
+\begin{table}[!htb]
+  \centering
+  %\label{tag:misfit_reduction_M00_M25_360}
+  \begin{tabular}{|c|c|c|c|}
+    \hline
+    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+    \hline
+    17--40s                &         29.2 &       33.7 &       43.4 \\
+    40--100s body waves    &         26.2 &       32.2 &       39.0 \\
+    40--100s surface waves &         49.1 &       49.4 &       51.2 \\
+    90--250s               &         30.9 &       34.8 &       34.9 \\
+    \hline
+  \end{tabular}\\
+  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
+  \label{table:misfit_reduction_M00_M25_360}
+\end{table}
+
+Second, we also plotted the histograms of phase measurements in Fig.\ref{fig:phase_hist_360}. We also observed clear variance reduction in all the 12 categories from GLAD--M00 to GLAD--M25.
+
+To summarize, both the misfit reduction and histogram improvements indicates that our model performs good with data that hasn't been used in our inversion.
+We expect to see similar behavior for the future earthquakes.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
+  \caption{Histogram of phase measurements similar to \ref{fig:phase_hist} except for 360 held-out earthquakes.}
+  \label{fig:phase_hist_360}
+\end{figure}
+
 \section{Models}
@@
 \subsection{Global Velocity Structure}
+
+{\color{Red} Wenjie: Plan to work more on this part. But do you any suggestion what things should I talk about?}
+
 In Fig.\ref{fig:global-vs}, the global map of isotropic $V_s$ is plotted at certain depths.
@@
 \subsubsection{North America}
+
+{\color{Red} Wenjie: Read for Jeroen to edit}
+
 The deployment of USArray has dramatically increased the data overage on the
@@
 \newpage
-
-\section{Model Evaluation}
-
-Here, we present two ways that used to evaluate the quality of our model:
-resolution analysis and held-out data test.
-
-\subsection{Resolution Analysis}
-Checkboard test was commonly used a resolution test method but it is at the
-same cost of inversion of GLAD-M25, which will cost millions of CPU hours.
-Due to the very demanding computational requirements, we used the 'point
-spread function to assess the imaging quality in models GLAD-M25.
-
-\subsection{Held-out Dataset Test}
-Following the approach by \cite{tape2009adjoint}, \cite{bozdaug2016global},
-unseen events are used to check the performance of our
-model. We revisited the Global CMT catalogue,
-picked all the events whose magnitude is between 6.3 and 7.0, which hasn't
-been used in our inversion. The reason why we set the lower bound to 6.3
-instead of 5.5, is those earthquakes have good enough data and generates
-more measurements at the global scale.
-We calibrated the scalar moment and origin time in the GLAD-M25, and there
-are 360 events left that has enough windows. Fig.\ref{fig:events_360} shows
-the distribution of 360 earthquake that we used as held-out dataset
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/events_360.pdf}
-  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model assessment stage.
-Theses events are not used in the structural inversion.
-(a) Beach balls of earthquakes.
-Same color conventions as used in the \ref{fig:event_1480} (b) and (c) Histograms of moment magnitude and depth.}
-  \label{fig:events_360}
-\end{figure}
-
-First, we evaluate the model performance by misfit reduction. Same windows and
-weightings are used across models. Table.\ref{table:misfit_reduction_M00_M25_360}
-shows the misfit reduction from M15 to M25 and Table.\ref{table:misfit_reduction_M00_M25_360}
-is from M00 to M25. It again shows misfit reduction in all categories in
-our held-out dataset, similar to what we observed from the inversion dataset.
-The reduction are slightly smaller, partly due to the reason that we didn't
-do waveform-type inversion as we mentioned in the source inversion stage but
-only did a grid search to calibrate the scalar moment and origin time.
-
-\begin{table}[!htb]
-  \centering
-  %\label{tab:category}
-  \begin{tabular}{|c|c|c|c|}
-  \hline
-  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-  \hline
-  17--40s                &          11.8 &       14.1 &       21.5 \\
-  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
-  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
-  90--250s               &          10.9 &       14.3 &       24.0 \\
-  \hline
-  \end{tabular}\\
-  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
-  \label{table:misfit_reduction_M15_M25_360}
-\end{table}
-
-\begin{table}[!htb]
-  \centering
-  %\label{tag:misfit_reduction_M00_M25_360}
-  \begin{tabular}{|c|c|c|c|}
-    \hline
-    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-    \hline
-    17--40s                &         29.2 &       33.7 &       43.4 \\
-    40--100s body waves    &         26.2 &       32.2 &       39.0 \\
-    40--100s surface waves &         49.1 &       49.4 &       51.2 \\
-    90--250s               &         30.9 &       34.8 &       34.9 \\
-    \hline
-  \end{tabular}\\
-  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
-  \label{table:misfit_reduction_M00_M25_360}
-\end{table}
-
-Second, we also plotted the histograms of phase measurements in Fig.\ref{fig:phase_hist_360}. We also observed clear variance reduction in all the 12 categories from GLAD--M00 to GLAD--M25.
-
-To summarize, both the misfit reduction and histogram improvements indicates that our model performs good with data that hasn't been used in our inversion.
-We expect to see similar behavior for the future earthquakes.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
-  \caption{Histogram of phase measurements similar to \ref{fig:phase_hist} except for 360 held-out earthquakes.}
-  \label{fig:phase_hist_360}
-\end{figure}
 

### 2018-10-15 main.tex
fix typo
add asia section

@@
 
-{\color{Red} Wenjie: Read for Jeroen to edit}
+{\color{Red} Wenjie: Ready for Jeroen to edit}
 
@@
 
-...to be done...
-We presented our model GLAD-M25, with S362ANI+M, S40RTS and EARA2014.
-At 100km depth, our model shows sharpening at the Himalayas subductions
-zones. At 250km, our models shows the subduction in the east part.
-At 400km, our models shows the subduction at sumartra.
+Asia has a very compliated tectonic settings, which mainly contains the interaction
+among India, Euroasia, Australia, Pacific and Phillipine plates. Even though we don't
+have a significant large number of high event-response stations at this region(compared
+to Europe and North America), our inversion is compsentated by the large number of
+temporary arrays and earthquakes.
+
+The southwestern part of china is featured by the Himalayas mountain, which is 
+a shallow expression of the collission between India and Euroasian plate. Our
+models shows a strong high-velocity anomalies near the plate boundary, and this
+anomaly has all the way extending from 100km to 600km depth. With the increase
+of depth, the high-velcity regions get sharper, indicating the narrowing
+root of subduction plate. The high-elevation Tibetan platuea, residenting to
+the north of Himalaya monuntains, shows a relatively low velocity
+comparing to its surroundings, including the Himalayas at its south and Titanshan
+Mountain at is North.
+
+The southern part of Asia sees the majority tectonic activity between the Phillipine
+, EuroAsia and Australia plate. The Summatra and Java trench, shown as sharp high-velocity
+anomaly in our models below 200km, nicely follows the boundary between Euroasia
+and Australia plates. This feature stays still very sharp at the 600km and extend
+down to 1000km. We will have more detailed discussion about it in the follwing sections.
+The Malina and Philippine Trench is also much sharper in our model between 200km and
+600km.
+The eastern part has a series of trenchs, including Japan Trench, Izu-Bonin Trench,
+Mariana Trench from North to the Sounth. All those features follows perfectly with
+the plate boundary, from 200km to 400km depth, as emerging features
+compared the two global models. At the north, our models shows low-velocity structures
+, which could be associated with the Altay-Sayan and Baikai rift systems.
+
+Other than the boundaries, our models also show much more details at the intra-plate
+tectonic activities. Our models shows good correlation of low-velocity regions with
+the Hainan spot and Changbai Volcanoes. Those low-velocity features is prominent at shallow
+depth, but gradually reduce its magnitude down with the increase of depth, indicating
+that those features might be lithospherical acticity rather than deep mantle's. The Sichuan
+basin, shows as a very locolized high-velocity structures, is extended below 250km.
+At 600, most of the models shows a large regions of high-velocities near the Phillipine
+plate, which may indicate the pounding of ancient subucted plates.
 

### 2018-10-15 main.tex
Updates from ShareLaTeX

--- 2018-10-12 main.tex
@@
 
-\section{Starting Model GLAD--M15}
-
-{\color{Red} Wenjie: Read for Jeroen to edit}
+\section{Starting Model GLAD-M15}
+
+{\color{Red} Wenjie: Ready for Jeroen to edit}
 
@@
 
-...to be done...
-We presented our model GLAD-M25, with S362ANI+M, S40RTS and EARA2014.
-At 100km depth, our model shows sharpening at the Himalayas subductions
-zones. At 250km, our models shows the subduction in the east part.
-At 400km, our models shows the subduction at sumartra.
+Asia has a very complicated tectonic settings, containing
+the interaction among Indian, Euroasian, Australia, Pacific and Philippine
+plates. Even though we don't have a significant large number of high
+event-response stations at this region(compared to Europe and North
+America), our inversion is compensated by the large number of temporary
+arrays and earthquakes.
+
+The southwestern part of china is featured by the Himalayas mountain, which is 
+a shallow expression of the collision between India and Euroasian plate. Our
+models shows a strong high-velocity anomalies near the plate boundary, and this
+anomaly has all the way extending from 100km to 600km depth. With the increase
+of depth, the high-velocity regions get sharper, indicating the narrowing
+root of subduction plate. The high-elevation Tibetan plateau, sitting to
+the north of Himalaya mountains, shows a relatively low velocity
+comparing to its surroundings, including the Himalayas at its south and
+Tianshan Mountain at is North, which is consistent with other global
+and regional studies.
+
+The southern part of Asia sees the majority tectonic activity between the Philippine
+, EuroAsian and Australia plate. The Sumatra and Java trench, shown as sharp high-velocity
+anomaly in our models below 200km, nicely follows the boundary between Euroasian
+and Australia plates. This feature stays still very sharp at the 600km and extend
+down to 1000km. We will have more detailed discussion about it in the following sections.
+The Malina and Philippine Trench is also much sharper in our model between 200km and
+600km.
+The eastern part has a series of trenches, including Japan Trench, Izu-Bonin Trench,
+Mariana Trench from North to the South. All those features follows perfectly with
+the plate boundary, as emerging features compared the two global models from 200km
+to 400km depth. At 100km depth, our model is strengthening the low-velocity structures
+in the east of Philippine Plate and the anomaly gradually moved to the west at 200km
+depth. In the north, our models shows low-velocity structures associated
+with the Altay-Sayan and Baikai rift systems.
+
+Other than the boundaries, our models also show much more details at the
+intra-plate tectonic activities. It has good correlation of low-velocity regions with
+the Hainan spot and Changbai Volcanoes. Those low-velocity features is prominent at
+shallow depth, but gradually reduce its magnitude down with the increase of
+depth, indicating that those features might be lithosphere's activity rather
+than deep mantle's.
+The Sichuan basin, a very localized high-velocity structures, is extending below
+250km depth. At 600km, most of the models shows a large regions of high-velocities
+near the Philippine plate, indicating the pounding of ancient subducted plates.
 

### 2018-10-18 main.tex
Updates from ShareLaTeX

@@
 
-\section{Starting Model GLAD-M15}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-As the continuation of our previous work, we used GLAD-M15 as our
-starting model\citep{bozdaug2016global}.
-The GLAD-M15 is a 3D transversely isotropic earth model. Its uses
-GLAD-M00, a combined 3-D mantle model S362ANI \citep{kustowski2008anisotropic}
-with 3-D crust model CRUST2.0 \citep{bassin2000current}, as its own starting model.
-Instead of relying to the "crust correction", SPECFEM mesher enables us to incorporate
-the 3D crustal model so we are able to update the crust and mantle structures at same
-time with any trade-off. Besides, the.
-
-GLAD-M15, same as  S362ANI, provides 6 model parameters, mass density($\rho$), two compressional
-wavespeeds($\alpha_v$ and $\alpha_h$), two shear wavespeeds($\beta_v$
-and $\beta_h$) and a dimenionless parameter($\eta$). We will discuss
-the model parametrization in detail in the following sections.
-
-GLAD-M15 then uses 256 earthquakes and broad-band seismic data to do the 3D full-waveform
-inversion\citep{bozdaug2016global}. The first 12 iterations of GLAD-M15 was
-performed under 27 secs and the last 3 under 17 secs. We will keep our model
-resolution as 17s in our model. As shown in our later analysis,
-GLAD-M15 proven good enough improvements over S362ANI in both our inversion
-dataset and held-out test dataset. It also shows both significant misfit reduction
-in all measurement categories and and better behavior in statistic analysis from distribution
-of the phase measurements, which will discussed in the following sections.
+\section{Starting model GLAD-M15}
+
+As a continuation of our previous work~\citep{bozdaug2016global},
+we used ``first generation'' model GLAD-M15 as our
+starting model.
+GLAD-M15 is a 3D transversely isotropic earth model, which combined
+3D mantle model S362ANI~\citep{kustowski2008anisotropic}
+with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
+In this study,
+we continue to use the same transversely isotropic model parametrization.
+Instead of relying on ubiquitous ``crustal corrections'',
+the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us accurately accommodate topography and bathymetry as well as variations in the Moho.
+GLAD-M15 was constructed using a global data base of 256 earthquakes.
+The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
+and the final 3 iterations reduced this further to 17~s.
+In this study we also used three-component seismograms with a shortest period of 17~s.
 
 \section{Earthquakes}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-In addition to the 256 earthquakes used in the first generation model GLAD-M15, we
-carefully picked 784 more earthquakes from Global Centroid-Moment-Tensor catalog\citep{}
-and added them into our database, making the total number of earthquakes reach 1,040.
-The lower band of moment magnitude, is set at 5.5 to ensure the signal-to-noise ratio at
-the global scale. The upper bound of magnitude is set at 7.2 and duration of earthquakes
-is set at 9 sec since we can use point representation and Gaussian-type source
-time function.
-We also constrain the duration of CMT sources to be smaller than 17s.
-The locations of 1040 earthquakes is shown in fig.\ref{fig:source_correction}a.
-
-To ensure a even global coverage, we used the seismic stations mainly from several global
-seismic networks such as Global Seismic Network(II, IU, IC, US, CU and GT),
-GEOFON(GE), GEOSCOPE(G), and regional networks, such as MedNet(MN),
-, Brazilian Lithospheric Seismic Project(BL), Chilean National Seismic Network(C), Japan Meteorological
-Agency Seismic Network(JP) and etc. The number of seismic stations usually ranges
-from 150 to 500, depending on the availability of seismic stations when the earthquake
-happened. The distribution of seismic stations is in Fig.\ref{fig:source_correction}b and
-data is download from the Incorporated Research Institutions for Seismology(IRIS).
-
-We use the source inversion algorithm of \cite{liu2004spectral}. This algorithm set the
-target misfit function as the normalized waveform difference and envelope difference between
-observed data, \textbf{d} and synthetic data generated from GLAD-M15, \textbf{s}.
-
-\begin{multline}
-  \chi = \sum\limits_{c=1}^{N_c} \omega_c \sum\limits_{r=1}^{N_r} \omega_{cr}
-       \sum\limits_{m=1}^{N_m} \omega_{crm}
-       \Big\{ \lambda {\frac
-              { \int \big[ \mathbf{d}_m(t) - \mathbf{s}_m(t - \Delta t, \mathbf{m}_{15}) \big]^2 dt }
-              {\int \big[ \mathbf{d}_m(t) \big]^2  dt } }\\
-         + (1 - \lambda) \frac
-              {\int \big[ e(\mathbf{d}_m(t)) - e(\mathbf{s}_m(t - \Delta t, \mathbf{m}_{15})) \big]^2 dt }
-              {\int \big[ e(\mathbf{d}_m(t)) \big]^2  dt} \Big\}
-\end{multline}
-
-Following \cite{ekstrom2012global}, seismograms were filtered into 50-100s
-to select 3-component body wave windows and 60-100s to select 3-component
-surface wave windows. Thus, the number of measurements categories $N_c$,
-is 6. To balance the contribution from each category, the weighting for each
-category $\omega_c$, is the reciprocal of the number of measurements in that
-category. The $N_r$ is the number of seismic stations in one category. $\omega_r$
-is the receiver weighting assigned to each individual stations, which we will discuss
-that in detail in the following sections. $N_m$ is the number of measurements for one
-seismic stations in one measurements category and $\omega_m$ is the measurements weightings
-, which is simply set to 1. The inverted parameters includes moment tensors, longitude,
-latitude and depth. In order to get the frechet derivatives for each parameter, there is
-one global-scale forward simulation needed to be done so the source inversion becomes a very expensive
-operation.
-
-Since we shifted the synthetic data based on the cross-correlation to its correspond observed
-data to the best match of the pair, our source inversion is not very sensitive to
-the origin time of earthquakes. In addition to prepare the future Q inversion,
-A grid search for the origin time and scalar moment correction was introduced
-directly to future calibrate the sources afterwards following \cite{zhu2012structure}.
-The grid-search calibration has a linear effect on the seismograms so it doesn't take extra
-simulation time.
-
-Fig.\ref{fig:source_correction} shows the source correction results.
-Most of the earthquakes shows a shallower depth after the source inversion
-(Fig.\ref{fig:source_correction}b and Fig.\ref{fig:source_correction}c),
-in consistent with \cite{hjorleifsdottir2010effects}.
-We observed $-2.62\pm2.49$km depth change compared with the global CMT solutions.
-The scalar moment, on the average, has $5.31\pm3.91$\% change and change of origin time
-is $-0.60\pm1.17$ sec.
-
-Starting from GLAD-M22, we added extra 440 earthquakes from GLobal CMT catalog,
-mainly in previously poorly covered regions. However, due to computational cost,
-we didn't implement the 1st stage source inversion in the newly added 440
-earthquakes but only calibrate its origin time and scalar moment.
+\label{section:earthquakes}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
+  \caption{Source corrections for 1,040 out of 1,480 events used in the structural inversion.
+(a) Map view of depth changes.
+(b) Distribution of seismographic stations used for source inversions.
+(c) Depth change relative to the original global CMT Catalog depth.
+(d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
+  {\color{red} Wenjie: please put a space between ``depth'' and ``km'' in the x-axis labels of figures C and D.}
+  }
+  \label{fig:source_correction}
+\end{figure}
+
+In addition to the 256 earthquakes used for the construction of first generation model GLAD-M15, we initially selected 784 carefully chosen additional earthquakes from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{Ekstrom12},
+and added them to our database, resulting in a total number of 1,040 earthquakes.
+To ensure a good signal-to-noise ratio on a global scale,
+the smallest moment magnitude in the database is set to~5.5,
+and to avoid complications associated with source size,
+the largest moment magnitude is set to~7.2.
+
+Before using the 1,040 earthquakes in our structural inversion,
+we performed CMT inversions in model GLAD-M15,
+the results of which are summarized in Fig.~\ref{fig:source_correction}.
+To ensure even global coverage,
+we used seismographic stations from the  Global Seismic Network (II, IU, IC, US, CU, and GT),
+GEOFON~(GE), GEOSCOPE~(G), and several regional networks, such as MedNet~(MN),
+the Brazilian Lithospheric Seismic Project~(BL), the Chilean National Seismic Network~(C),
+and the Japan Meteorological Agency Seismic Network~(JP) (Fig.~\ref{fig:source_correction}b).
+The number of stations used for CMT inversion usually ranges
+from~150 to~500.
+
+To determine the source parameters in the starting model,
+we used the CMT inversion algorithm of \cite{liu2004spectral}.
+This algorithm combines a normalized waveform difference misfit with an envelope difference misfit.
+Specifically, the algorithm minimizes the misfit function
+\begin{equation}
+   \begin{split}
+      \Phi =  \sum\limits_{c=1}^{C} \omega_c \sum\limits_{r=1}^{R_c} \omega_{cr}
+       \sum\limits_{w=1}^{W_{cr}} \omega_{crw}\,
+          & \left\{ \lambda\, \frac
+              { \int \big[ d_w(t) - s_w(t - \Delta t) \big]^2 \mathrm{d}t}
+              {\int \big[ d_w(t) \big]^2  \mathrm{d}t} \right.
+       \\ & \quad \left. \mbox{} + (1 - \lambda)\, \frac
+              {\int \big[ e(d_w(t)) - e(s_w(t - \Delta t)) \big]^2 \mathrm{d}t}
+              {\int \big[ e(d_w(t)) \big]^2\mathrm{d}t} \right\}
+              \quad ,
+   \end{split}
+\end{equation}
+where~$d_w(t)$ denotes data in time window~$w$\,,
+and~$s_w(t - \Delta t)$ the corresponding synthetic for model~GLAD-M15.
+We allow the synthetics to shift relative to the data by an amount~$\Delta t$
+--- effectively a station correction --- determined by cross correlation.
+The envelope function is denoted by~$e(\,\cdot\,)$\,,
+and the parameter~$\lambda$ determines the balance between fitting waveforms versus fitting envelopes.
+The number of measurement categories is denoted by~$C$\,.
+Following~\cite{ekstrom2012global},
+seismograms were filtered between 50~s and 100~s
+to select three-component body-wave windows,
+and between 60~s and 100~s to select three-component
+surface-wave windows,
+resulting in six measurement categories, $c=1,\ldots,C$\,.
+To balance their contributions,
+each category is weighted by the reciprocal of the number of measurements in that
+category, $\omega_c$\,.
+The number of windows for a given receiver~$r$ in a given measurement category~$c$ is~$W_{cr}$\,.
+Each such window is weighted equally, i.e.,~$\omega_{crw}=1$\,.
+The number of receivers that records data in category~$c$ is denoted by~$R_c$\,.
+As shown in Fig.~\ref{fig:source_correction}b,
+the receivers are unevenly distributed across the globe,
+with several dense arrays in the Northern Hemisphere and poor coverage in the Southern Hemisphere.
+To balance the coverage,
+we assign receiver weights~$\omega_{cr}$ based on the expression
+\begin{equation}
+\omega_{cr}^{-1} = N_c\,\sum_{r'=1}^{R_c} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_c}\right)^2\right]
+\quad ,
+\label{eq:spatial_weights}
+\end{equation}
+{\color{Red} Wenjie: is it $\omega_{cr}^{-2}$ or $\omega_{cr}^{-1}$? And does the normalization factor~$N_c$ depend on~$c$?\\ }
+where~$N_c$ is a normalization factor,
+and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
+The reference angular distance~$\Delta_c$ needs to be chosen such that the condition 
+number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
+The calculation of the weights may be abstracted as: given a spatial distribution of
+points on the unit sphere, determine a weighting associated with each point.
+
+The algorithm inverts for the six elements of the moment tensor
+and the centroid location~(latitude, longitude, and depth).
+The calculation of each associated Fr\'echet derivative requires one full 3D forward simulation,
+so, considering we have more than one thousand events,
+these source inversions are computationally very expensive.
+
+Because we allow the synthetics to shift by an amount~$\Delta t$ relative to the data,
+the CMT inversion has unreliable sensitivity to the centroid time.
+To alleviate this problem,
+following~\cite{zhu2012structure},
+we perform a subsequent grid search for the centroid time and the scalar moment.
+The grid-search calibration involves simple shift and multiply operations on seismograms
+and, unlike the CMT inversion, requires minimal simulation time.
+
+Most earthquakes show a shallower depth after inversion
+(Fig.~\ref{fig:source_correction}c),
+consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}.
+We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
+an average scalar moment change of~$5.31\pm3.91$\%,
+and an average centroid time shift of~$-0.60\pm1.17$~s.
+These are relatively minor corrections, especially in view of the significant expense of the source inversions.
+For this reason, when we added another 440 earthquakes during iteration~22,
+thereby bringing the total to~1,480 events,
+we only performed a grid search to calibrate the centroid times and scalar moments.
+Fig.~\ref{fig:event_1480} summarizes the characteristics of all 1,480 earthquakes used in this study.
 
@@
   \includegraphics[width=\textwidth]{figures/events_1480.pdf}
-  \caption{1480 earthquakes used in this study.
+  \caption{1,480 earthquakes used in this study.
 (a) Distribution of earthquakes.
-Colors of beach balls indicate the depth range of earthquakes from Global CMT Catalog \citep{ekstrom2012global}.
-{\textbf{\color{Blue} Blue}} is for shallow earthquakes above 50km, \textbf{{\color{ForestGreen} Green}} is between 50 and 300km and \textbf{{\color{Red} Red}} is below 300km.
+The color of each beach ball reflects its depth range, where blue designate events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
 (b) and (c) Histograms of earthquake moment magnitudes and depths.}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
-  \caption{Source correction results for 1040 events used in the inversion.
-(a) Map views of depth changes.
-(b) Distribution of seismographic stations used in the source inversion stage.(c) depth change of CMT sources compared to its initial solution from the Global CMT Catalog.
-(d)-(f) Histograms of depth, origin time and scalar moment changes.}
-  \label{fig:source_correction}
-\end{figure}
-
-\section{Seismic Data}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-Seismic stations have been very carefully picked to ensure global coverage and high data quality.
-Other than the networks we mentioned in the source inversion, we include all the data we can
-downloaded from IRIS data center. Regional and temporary networks has become a significant part
-in our database and greatly improve the ray coverage at specific regions, such as US Array(TA),
-Africa Array(AF), Canadian National Seismograph Network (CN), Geoscience Australia (AU),
-Brazilian Lithospheric Seismic Project (BL),
-Antarctic Seismographic Argentinean Italian Network (AI),
-the New Zealand National Seismograph Network (NZ) and etc.
-
-The data, associated with the earthquakes, was downloaded from several data centers,
-including IRIS, ORFEUS, INGV, IPGP, ETH, GEONET and etc.
-There are in total of 275 seismic networks (with individual network code) and 11,800
-seismic stations used in the structural inversion stage. Fig.\ref{fig:stations}
-shows the distribution of seismic stations.
+\section{Seismic data}
+\label{section:data}
+
+The seismographic stations used in this study were carefully selected to ensure global coverage and high data quality (Fig.~\ref{fig:stations}).
+In addition to the seismic stations used for the source inversions,
+we included all available data for our 1,480 event earthquake database from many data centers,
+including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
+Regional and temporary networks,
+such as US Array~(TA),
+Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
+the Antarctic Seismographic Argentinean Italian Network~(AI),
+and the New Zealand National Seismograph Network~(NZ),
+constitute a significant part
+of our database and greatly improve coverage in certain regions.
 
@@
   \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
-  \caption{Distribution of 11,800 seismographic stations on the globe.
-Colors denote the number of events which they contribute waveforms to in the model inversion stage.
-Stations with event response < 400 are plotted in smaller size and they are usually temporary arrays which are deployed over a short period of time.
-The max event response comes from IU.ANMO, which contribute ed to 1442 out of 1480 earthquakes in out dataset.}
+  \caption{Distribution of 11,800 seismographic stations used in this study.
+Colors denote the number of events for which a given station contributes waveforms to the structural inversion.
+Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers.
+The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}
   \label{fig:stations}
@@
 
-\section{Misfit function and Model Parametrization}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-This sections will discuss how we define the the misfit function and how we parameterize the model.
-The overall misfit, $\Phi$, is defined as follows:
-
-\begin{align}
+\subsection{Adaptable Seismic Data Format}
+\label{section:ASDF}
+
+Conventional seismic data formats, such as SAC, involve one file per time series plus related files with instrument response and event information.
+Since every earthquake in the database is typically recorded by thousands of instruments, I/O during the preprocessing stage of the adjoint tomography workflow quickly cripples the file system.
+The Adaptable Seismic Data Format (ASDF)~\citep[][ \texttt{https://seismic-data.org/ }]{krischer2016adaptable} was developed with complete reproducibility and fast parallel processing in mind.
+
+In this context, there are four key issues ASDF resolves.
+\begin{itemize}
+    \item Robustness and stability: the data container is developed and maintained to ensure accuracy of scientific results.
+    \item Data organization: the container is self-describing. Data, including waveform, source, and station information, are organized into well-defined structures.
+    \item Reproducibility: the container enables scientists to keep track of what has been done to data so that results can be reproduced.
+    \item Efficiency: the format provides easy mechanisms for parallel processing.
+\end{itemize}
+ASDF serves as a self-contained-and-explained data container while taking full advantages of parallel computing.
+In our workflow,
+one ASDF file contains all the information needed for data processing, including the seismic traces, event information files, and station response files.
+The related APIs are carefully designed for easy data extraction and parallel implementation.
+
+\section{Misfit function}
+\label{section:misfit}
+
+The misfit function to be minimized during the iterative inversion process must be carefully constructed.
+It will typically involve cross-correlation traveltimes for body waves and frequency-dependent multitaper phase measurements for surface waves.
+Measurements are made in several passbands of three-component seismograms rotated into vertical, radial, and transverse components, resulting in a number of measurement categories.
+In this study, we consider four passbands,
+namely, a 17--40~s passband targeting body waves,
+two 40--100~s passbands separately targeting body and surface waves,
+and a 90--250~s passband targeting longer-period surface waves.
+Each passband involves measurements on all three components,
+which results in a total of twelve measurement categories.
+Although the inversion is designed to minimize the overall misfit,
+we will be tracking the misfit reduction in each of the categories to ensure that the model is improving the fit to the data roughly equally across the board.
+One of the biggest challenges in the construction of the misfit function is the highly uneven distribution of earthquakes and seismographic stations,
+which must be counterbalanced by geographically weighting the data.
+This issue is discussed in detail by~\cite{Ruanetal2018};
+in this section we present a brief synopsis.
+
+With these considerations in mind,
+the overall misfit, $\Phi$, is defined as follows:
+\begin{equation}
 \label{eq:misfit}
-\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{N_{scr}} \omega_{scrw}\, \chi_{scrw}
+\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{W_{scr}} \omega_{scrw}\, \chi_{scrw}
 \quad ,
-\end{align}\\
+\end{equation}
 where~$S$ denotes the number of sources, $C$ the number of categories,
-$R_{sc}$ the number of receivers for source~$s$ and category~$c$,
-and~$N_{scr}$ the number of measurements for source~$s$, category~$c$
+$R_{sc}$ the number of receivers recording source~$s$ in category~$c$,
+and~$W_{scr}$ the number of measurement windows for source~$s$, category~$c$
 and receiver~$r$.
-
-The misfit for source~$s$, category~$c$, receiver~$r$, and window~$w$ is
-\begin{align}
-  \chi_{scrw} = \int \Big[ \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big]^2 d\omega
+The misfit for a specific source~$s$, category~$c$, receiver~$r$, and window~$w$ is
+\begin{equation}
+  \chi_{scrw} = \frac{1}{\Delta\omega}\int_{\omega_1}^{\omega_2} \Big( \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big)^2\, \mathrm{d}\omega
 \quad ,
-\end{align}
-is a frequency-dependent phase measurements using then multi-taper technique.
-where $\Delta m_{scrw}$ denotes a measurement with associated standard deviation~$\sigma_{scrw}$.-
-
-\subsection{Weightings}
-Weighting is crucial to the global tomography to compensate the uneven distribution
-of earthquakes and seismic stations. First, most of the earthquakes happen in the
-in the plate boundaries. There are also several seismic active zones, such as Japan,
-Fiji Tonga and South America, where there are a lot of earthquakes clustered near
-the subduction slabs.
-Second, most of the seismic stations located in the continents, especially located in
-the northern hemisphere. Besides, there are quite a few dense seismic arrays,
-for example US array, deployed recently, which has hundred or thousands of instrument deployed
-at the regional scale, which will has a very strong footprint on the misfit gradients if no weighting
-been applied.
-
-All the factors mentioned above will lead to a uneven distribution of
-ray paths and thus uneven sampling of the earth structure. Our weighting strategy
-is developed to compensate such effects. There are two terms in the misfit function
-receiver weightings, $\omega_{scr}$, and source weightings $\omega_{s}$.
-The calculation of both terms can be abstracted as: given the distribution of
-points determine the weighting associated with each point.
-Here we introduce the exponential weightings to describe the density of points and
-determine the point weightings. Given a set of points $p_i$, the distance between
-two is $r_{ij}$, the weightings associated with each point, $w_i$, could be obtained by:
-
+\end{equation}
+where~$\Delta \tau_{scrw}$ denotes a multi-taper frequency-dependent phase measurement over the frequency interval~$\Delta\omega=\omega_2-\omega_1$\,,
+with associated standard deviation~$\sigma_{scrw}$\,.
+For body waves, the window misfit is simply the cross-correlation traveltime anomaly,
+$\Delta T_{scrw}$\,, weighted by its standard deviation, i.e., $\chi_{scrw}=(\Delta T_{scrw}/\sigma_{scrw})^2$\,.
+As in the source inversions,
+the window weights are equal, $\omega_{scrw}=1$\,,
+and the category weight, $\omega_c$\,, is the reciprocal of the number of measurements in that
+category.
+Earthquakes are mainly confined to plate boundaries,
+and most seismic stations are confined to the continents,
+which leads to a very uneven distribution of sources and stations,
+as illustrated in Figs.~\ref{fig:event_1480} and~\ref{fig:stations}.
+Therefore, weighting is crucial in global tomography to balance this uneven sampling
+of Earth's interior.
+Our source and receiver weighting strategy,
+encapsulated by the weights~$\omega_s$ and $\omega_{scr}$\,,
+is developed to compensate for uneven spatial sampling.
+Following the same strategy as for the receiver weights in the source inversions,
+we define the source and receiver weights as
 \begin{equation}
-w_{i} = \frac{1}{A} \left(
-  \sum_{j=1}^N \exp \left[ \mbox{} - \left( \frac{r_{ij}} {r_{0}} \right)^2 \right] \right) ^{-1}
-\label{eq:spatial_weights}
+\omega_{s}^{-1} = N\,\sum_{s'=1}^{S} \exp\left[\mbox{}-\left(\frac{\Delta_{ss'}}{\Delta}\right)^2\right]
+\quad ,
+\label{eq:source_weights}
 \end{equation}
-where $r_{0}$ is the sensitivity distance and $A$ is the normalization term.
-The reference distance $r_0$ will control ratios of weightings between dense and
-sparse regions. For more details for the weightings, please refer to the Appendix XXX.
-
-\subsection{Model Parametrization}
-Transversely isotropy model parametrization is used in our model, same as S362ANI(GLAD-M00)
-and GLAD-M15. Comparing to a general anisotropic model which has 21 independent variables,
-our model could be described by 5 Love parameters, A, C, L, N and F\citep{love2013treatise}.
-Since it is more straight forward to use  wavespeed as model parameters in seismology,
-we choose $\alpha_v$, $\alpha_h$, $\beta_v$, $\beta_h$ and $\eta$.
-Assuming the radial anisotropy is due to shear anisotropy, these 5 parameters
-can be further reduced to 4, we introduced the bulk sound speed,
-$c=\sqrt{\kappa/\rho}$. Our final parameters are:\\
-\begin{align*}
-      c &= \sqrt{\kappa/\rho} \\
-\beta_v &= \sqrt{L/\rho} \\
-\beta_h &= \sqrt{N/\rho} \\
-\eta & = F/(A-2L)
-\end{align*}
-
-Since density is hard to constrain due to the period band we are working on, the $\rho$ kernel is obtained by scaling the isotropic shear wavespeed kernel\citep{montagner1989petrological},\\
-\begin{equation*}
-    \delta ln\rho = 0.33\delta ln\beta
-\end{equation*}
-
-where $\beta$ is defined as the Voigt average of the radially anisotropic shear wave speeds\citep{babuska1991seismic}
-$$\beta = \sqrt{(2\beta_v^2 + \beta_h)/3}$$
-
-Based on the parametrization described above, the perturbations in misfit functions would be:
-
-\begin{equation*}
-    \delta \chi = \int_V
-      (K_c\delta lnc + K_{\beta_v}\delta ln\beta_v + K_{\beta_h}\delta ln\beta_h +
-      K_\eta \delta ln\eta) dV
-\end{equation*}
-
-\section{Adjoint Tomography Workflow}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-The flow chart for adjoint tomography is shown in Fig.\ref{fig:adjoint_workflow}.
-The workflow starts with a certain number of earthquakes. Here, we used the
-inverted CMT sources from the Global CMT catalog. Based on the time
-of earthquakes, we downloaded observed data, including time series and StationXML,
-from IRIS and other data centers. The we convert the sources, StationXML and time series
-into ASDF files. Each ASDF file usually contains a complete set of data from one
-earthquake. The data download and conversion need to be done only once. The raw observed data,
-storing in ASDF, could be reused afterwards.
+and
+\begin{equation}
+\omega_{scr}^{-1} = N_{sc}\,\sum_{r'=1}^{R_{sc}} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_{sc}}\right)^2\right]
+\quad ,
+\label{eq:receiver_weights}
+\end{equation}
+respectively.
+Here~$N$ and~$N_{sc}$ are a normalization factors,
+and~$\Delta_{ss'}$ and~$\Delta_{rr'}$ denote angular distances between source and receiver pairs~$\{s,s'\}$ and~$\{r,r'\}$\,.
+The reference angular distances~$\Delta$ and~$\Delta_{sc}$ need to be chosen based on the condition 
+numbers of the diagonal weighting matrices defined by Eqns.~(\ref{eq:source_weights}) and~(\ref{eq:receiver_weights}).
+
+{\color{red} Wenjie: is there just one $\Delta$, or are there different ones for sources, receivers and categories? And is there just one normalization constant~$N$, or are there multiple ones?}
+
+\section{Model parametrization}
+
+We use the same transversely isotropic model parametrization as starting model GLAD-M15.
+Such a model is described by the five Love parameters $A$, $C$, $L$, $N$, and $F$~\citep{Love27},
+or, alternatively, using the mass density~$\rho$, in terms of the wavespeeds~$\alpha_v=\sqrt{C/\rho}$, $\alpha_h=\sqrt{A/\rho}$, $\beta_v=\sqrt{L/\rho}$, $\beta_h=\sqrt{N/\rho}$ and the dimensionless parameter $\eta=F/(A-2L)$~\citep{PREM,DT98}.
+Assuming the radial anisotropy is due to shear anisotropy, these five parameters
+may be further reduced to four by introducing the bulk sound speed,
+$c=\sqrt{\kappa/\rho}$\,.
+Therefore, the final four parameters are $c$, $\beta_v$, $\beta_h$, and $\eta$.
+
+Since density is difficult to constrain with seismic data,
+density perturbations are scaled to isotropic (Voigt averaged) shear wavespeed perturbations based on the relationship~$\delta\ln\rho = 0.33\,\delta\ln\beta$~\citep{montagner1989petrological}.
+
+Based on this parametrization,
+the variation in the misfit function~(\ref{eq:misfit}) may be expressed as~\citep{zhu2015seismic,bozdaug2016global}
+\begin{equation}
+    \delta \Phi = \int_V
+      (\delta \ln c\,K_c + \delta \ln\beta_v\,K_{\beta_v} + \delta \ln\beta_h\,K_{\beta_h} +
+      \delta\ln\eta\,K_\eta) \mathrm{d}V
+      \quad ,
+\end{equation}
+where~$K_c$, $K_{\beta_v}$, $K_{\beta_h}$, and $K_\eta$ denote the four Fr\'echet derivatives,
+which are calculated based on an adjoint-state method~\citep[e.g.,][]{Plessix_2006_RAS,Tromp2005}.
+
+\section{Adjoint tomography workflow}
+
+The adjoint tomography workflow is shown in Fig.~\ref{fig:adjoint_workflow}.
+It starts with the selection of earthquakes, as discussed in Section~\ref{section:earthquakes}.
+Given the earthquake selection,
+observed seismographic data and related response information are acquired,
+as discussed in Section~\ref{section:data}.
+For a given earthquake,
+the corresponding seismograms and related response information are combined in a single ASDF file,
+described in Section~\ref{section:ASDF}.
+For a given earthquake dataset, the conversion to ASDF needs to be performed once and for all.
+In the following sections we highlight several important aspects of the workflow.
 
@@
   \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
-  \caption{Adjoint Tomography Workflow.}
+  \caption{Adjoint tomography workflow.}
   \label{fig:adjoint_workflow}
@@
 
-\subsection{Forward simulation}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-The forward simulation takes the CMT sources, stations and Earth models as input.
-We will first generate mesh based on the models. The CMT sources and station will
-be fed into the solver to generate synthetic seismograms and forward wavefield snapshots.
-SEPCFEM3D\_GLOBE with GPU acceleration is used on Titan at the Oak Ridge Nation Lab for
-both mesher and solver part.
-
-To simulate 120min of seismograms at 17sec resolution, it takes 384 Tesla K20X
-GPUs approximately 10 mins to run on Titan. To precisely calculate the sensitivity
-kernels, there is forward wavefield saved to the disk and those will used in the
-adjoint simulation in the later stage. In the current resolution
-and simulation length, the forward wavefield saved is above 1 terabytes
-for each earthquake. Given the size the 1480 earthquakes, we have 1.5 petabytes of
-wavefield saved to disk using ADIOS\citep{liu2014hello} during about 10 hours
-of simulation using 15,360 GPUs.
-It is huge volume of data saved to disk in a relatively short period of time, in which case
-ADIOS really helped to relief the I/O bottleneck.
-
-\subsection{Seismic Data Processing}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
+\subsection{Forward simulations}
+
+The observed seismograms need to be compared to corresponding synthetic seismograms
+for the purpose of making measurements.
+The forward simulations are based on the global spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a},
+and take a CMT solution, a relevant list of stations, and the current earth model as input.
+The solver is GPU accelerated, and the simulations are performed on the Cray `Titan' at the Oak Ridge Leadership Computing Facility.
+To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA Tesla K20X GPUs takes approximately 10~min of wall clock time.
+The calculation of Fr\'echet derivatives at a later stage of the workflow requires access to snapshots of the forward wavefield as part of the parsimonious storage algorithm developed by~\cite{KoXiBoPeSaLiTr16},
+with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
+For the current simulation setup,
+this requires about 1~TB of storage per earthquake,
+so for 1,480 earthquakes this amounts to 1.5~PB of storage.
+
+\subsection{Seismic data processing}
 
@@
   \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
-  \caption{Preprocessing Workflow for seismic data.}
+  \caption{Preprocessing workflow for seismic data.}
   \label{fig:preprocess_workflow}
@@
 
-The seismic data processing takes the raw observed and synthetic data as input,
-and generate s the adjoint sources as the output. As shown
-in Fig.\ref{fig:preprocess_workflow}, preprocessing includes:
+The seismic data preprocessing workflow takes raw observed and synthetic data as input,
+and generates adjoint sources for data assimilation as output.
+From a computational perspective, the preprocessing workflow consumes only~1\% of the overall computational requirements.
+But from the perspective of the tomographic inversion, this is by far the most important stage of the adjoint tomography workflow,
+directly and fundamentally impacting the outcome.
+Any ``bad data'' assimilated at this stage may contaminate the gradient and ultimately the final model.
+
+We use millions of seismograms generating tens of millions of measurement windows,
+making data selection through human interaction impossible.
+The preprocessing workflow automates this task,
+most importantly via the time window selection tool FLEXWIN~\citep{maggi2009automated}.
+Every seismogram and potential measurement goes through multiple checks and and balances before acceptance or rejection.
+
+As illustrated in Fig.~\ref{fig:preprocess_workflow}, the preprocessing workflow includes the following phases.
 \begin{enumerate}
-  \item Signal processing that remove the instrument response from observed data
-    to recover the true ground motion. Both observed and synthetic data will be
-    filtered into a certain period band. Then the two horizontal components of the
-    seismograms are rotated from North, East to radial and transverse only if the
-    StationXML passed the sanity check.
-  \item Window selection that picks the time window on a pair of
-    observed and synthetic seismograms. Pyflex(python version
-    of FLEXWIN\citep{maggi2009automated}), is
-    such a tool that automatically generate windows where observed data and
-    synthetic data are close enough to make measurements based on user defined
+  \item Signal processing to remove the instrument response from observed data
+    to recover ground displacement. Both observed and synthetic data are bandpass
+    filtered, and the horizontal components are rotated to obtain the radial and transverse components of motion.
+  \item Window selection on a pair of
+    observed and synthetic seismograms. Pyflex (a Python version
+    of FLEXWIN) is
+    used to automatically generate windows where observed and
+    synthetic data are sufficiently close to make measurements based on user defined
     criteria.
-  \item Multi-taper measurement that generates frequency-dependent travel-time
-    difference within the windows selected from the last step.
-    The output files contains both the measurements and misfit values.
-  \item Window cleaning that get rid of bad windows(and associated
-    measurements), only keeping good ones based on the statistical analysis of
-    measurements.
-  \item calculate the adjoint sources with the sorted windows.
-  \item For each window and associated measurement, calculate its weightings
-    that will be applied at the summation stage and calibrate its contribution
-    into the overall misfit function, using the method we mentioned before.
-  \item Construct the final adjoint sources by summing the adjoint source from
-    different windows and measurement categories.
+  \item Cross-correlation traveltime or multi-taper phase measurements in selected windows.
+  \item Window sorting and cleaning based on statistical analyses of all measurements to eliminate outliers.
+  \item Preliminary adjoint source construction based on the sorted windows.
+  \item Calculation and assignment of weights, as discussed in Section~\ref{section:misfit}.
+  \item Construction of the final, properly weighted, adjoint sources.
 \end{enumerate}
 
-Even though it is such a computational demanding process as the forward and adjoint
-simulation, only taking about $1\%$ CPU hours in the whole workflow, it is crucial
-that directly impact the inversion results. It decides which measurement
-will be taken into consideration and have a footprint in the final gradient.
-We are very careful at this stage, including a lot of checks, such as the Station and
-response integrity check, and also filtering out bad measurements to avoid big outliers.
-On the other hand, it is very process-demanding, which means it has complex data and
-control flows, that every seismograms will go through quite a few of processes
-before the final results is generated. We have millions of seismic traces and ten
-millions of windows, it is impossible to human-check every trace and measurements.
-I will go into more depth about this part in the following sections, discussing our
-efforts how to make the data and process safe and robust.
-
-\subsection{Adjoint Simulation}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-The adjoint simulation takes the adjoint sources as input, and calculate the frechet
-derivatives as output. The computation cost is about twice as the forward simulation since
-it is both calculating the adjoint wavefiled and reconstruct the forward wavefield.
-Other than the adjoint sources, the adjoint simulation also reads in the saved forward
-wave, to fully incorporate attenuation and more exactly calculate the anelastic
-sensitivity kernels.
-After the adjoint simulation is done, the save wavefield could be deleted and disk
-space would be freed.
-One Adjoint simulation takes about 25 mins for 17sec resolution for 120min simulation
-at 17s resolution.
-
-\subsection{Post-processing}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-The post-processing takes the frechet derivatives as the input and generate
-the model updates as the output. It contains:
+\subsection{Adjoint Simulations}
+
+Collectively,
+the adjoint simulations are the most expensive stage of the adjoint tomography workflow. 
+Adjoint simulations take the adjoint sources as input, and generate Fr\'echet
+derivatives of the four model parameters as output.
+The computational cost of one adjoint simulation is roughly twice ($\sim25$~min) that of a forward simulation,
+since the forward wavefield is recalculated for convolution with the adjoint wavefield during the adjoint simulation,
+as discussed in~\cite{KoXiBoPeSaLiTr16}.
+Using this procedure,
+both the forward and adjoint wavefield are calculated in forward time,
+and attenuation is accurately taken into account in both simulations.
+
+\subsection{Postprocessing}
+
+The postprocessing stage of the workflow takes Fr\'echet derivatives as input and
+generates a model update as output.
+It involves the follow steps.
 \begin{enumerate}
-  \item Summation of each kernel for each earthquake to obtain one
-    gradient for the overall misfit function. The number of kernel
-    files will reduce from 1480 to 1 after summing them up. Also,
-    there will source weightings applied at this stage, to balance
-    the uneven distribution of earthquakes.
-  \item Smoothing the misfit gradient using 3D Gaussian function, which
+  \item Summation of the individual Fr\'echet derivatives for each earthquake to obtain the overall gradient of the misfit function. The contribution of each source is weighted to balance
+    the uneven distribution of earthquakes based on the weighting strategy discussed in Section~\ref{section:misfit} .
+  \item Smoothing of the raw misfit gradient using a 3D Gaussian, which
     serves as a regularization procedure. Instead of using a changing
-    smooth radius based upon the "ray density"\citep{bozdaug2016global},
-    we used the fixed value in the same iteration, following\cite{zhu2012structure}.
-  \item Precondition the smoothed kernels. Following
-    \citep{luo2013strategies, zhu2012structure, bozdaug2016global},
-    the preconditioner we used is:
-    \begin{equation}
-      P(\mathbf{x}) = 1 / \int \partial_t^2 \mathbf{s}(\mathbf{x}, t) \cdot \partial_t^2 \mathbf{s}^\dagger(\mathbf{x}, T-t) dt
-    \end{equation}
+    smoothing radius based upon the ``ray density''~\citep{bozdaug2016global},
+    we used a fixed value at a given iteration, following~\cite{zhu2012structure}.
+  \item Preconditioning of the smoothed gradient based on a technique proposed by~\cite{luo2013strategies}.
+  \item Line search to determine the magnitude of the model update.
+  The search direction is determined using a nonlinear conjugate gradient method~\citep{wright1999numerical} (iterations 16--21) or an L-BFGS quasi-Newton method (iterations 22--25).
+  We used a subset of 120 earthquakes to conduct the line search and determine the step length.
 \end{enumerate}
 
-Search direction is calculated based on the misfit gradient from the
-post-processsing stage. Search direction is calculated using nonlinear conjugate
-gradient methods\citep{tape2007finite} and L-BFGS(starting from GLAD-M22),
-Here, we used a slightly modified version of conjugate gradient methods,
-adding a restart condition\citep{wright1999numerical} to iterations by checking
-if the current and previous gradient are far from orthogonal:
-
-\begin{equation}
-  \frac { \abs{g_i \cdot g_{i-1}} }  {\norm{g_{i-1}}^2} \geqslant v
-\end{equation}
-
-where the $v$ is set to $0.1$ in out case.
-
-Based upon the misfit gradient obtained from the post-processing stage.
-Line search is then used to determine the step length for model update
-along the search direction. Forward simulations were run for a subset
-of 120 earthquakes with different step length and the one with
-the max misfit reduction was picked as the model update step length.
-
-\subsection{Adaptable Seismic Data Format}
-
-It will be a shame not to take the full advantage of high performance during the data processing stage.
-However, conventional data format, for example SAC, becomes the bottleneck on the I/O when processing millions of seismic traces since every trace is saved as single files.
-Not even to mention that it is very easy to make mistakes when processing the data since seismologists usually needs to use various files when processing the data, such as CMT files and station response files.
-
-There are five key issues the new data format should resolve:
-\begin{itemize}
-    \item Robustness and stability: the container should be well developed and maintained to ensure the correctness of scientific results.
-    \item Data Organization: the container should be self-describing. It is preferable that data, including waveform, sources and station information, are organized into certain structures.
-    \item Reproducibility: the container should help scientist keep track of what has been done to the data and others can easily reproduce the results.
-    \item Efficiently: providing users with easy mechanism to parallel computation.
-
-\end{itemize}
-
-The Adaptable Seismic Data Format, ASDF, serves as a self-contained-and-explained data container while taking full advantages of parallel computing.
-In our case, one ASDF file contained all the files need in data processing, including the seismic traces, Quakeml files and station response files.
-The APIs were carefully designed for easy data extraction and parallel implementation.
-Each trace in the ASDF is associated with one specific Quakeml file and StationXML file, reducing the possibilities of making mistakes.
-
-\citep{krischer2016adaptable}
-%\citep{BookChapter}
-
-\subsection{Workflow Management}
-
-There are more than 10 of small blocks contained in our workflow.
-Each blocks contains thousands of mini-tasks.
-For the forward and adjoint simulation, we have 1480 simulations which is both computational and I/O intensive at the different stages of simulations.
-For the data processing stage, we have million of traces, windows and measurements.
-It is crucial to catch the hardware and software failures, preventing them from contaminating our results.
-Given such a complex workflow, it is easily for humans to make mistakes.
-So we bring in the workflow management tools.
-
-After investigating a few existing tools, we choose the RADICAL-SAGA and RADICAL-ENTK as our workflow management engines.
-Combine with domain applications, we developed the seismic tomography workflow tools.
-It can automatically detected job failures both from the system and user-defined functions.
-So we can keep tracks of all the tasks and resubmit if necessary.
-
-Based on our measurements, for the forward and adjoint simulation, the ENTK will have about 20 secs overhead on each simulation, which is about acceptable given it has the power to detect failures and relaunch jobs.
-Given the most of the time is waiting in the queue when using supercomputers, automatically failure detection and relaunch will greatly shorten our overall time since it will finish all the simulations in one single jobs.
-
-\section{Misfit and Histogram Improvements}
-
-\subsection{Misfit Evolution}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-The inversion went through a few stages, mainly due to adding more data
-and measurement categories and fine tuning the weighting strategies.
-
-\subsubsection{Stage I: M15 - M17}
-
-In the GLAD-M15, we started with 520 events, mainly to validate the test our
-software and workflow, making sure things are working properly.
-In GLAD-M16, we increase our dataset to 1040 earthquakes.
-
-For iterations at this stage, seismograms are filtered into 3 period bands,
-17-40sec, 40-100sec, 90-250 sec. In the 17-40s, we selected body wave windows. For the
-other two, we used all the phases available on the seismograms. Conjugate
-gradient method is used to calculate the model update.
-
-The misfit values increase a bit at M16 due to increase of earthquakes.
-
-\subsubsection{Stage II: M18-M21}
-
-The major change at stage II is we split the 40-100 sec period band into two: one with
-body wave and the other with only surface wave measurements. Since body waves and
-surfaces are sensitive to the different parts of the earth, by splitting these two
-phases, we have more controls over spatial distribution of the model update.
-Table.\ref{table:measurement_category} shows the measurement categories we used starting
-from M18 and we will stick to it till M25.
-
-**Not sure if we need to mention the change of weighting strategy in such a detail here**
-
-Since surface waves are mostly sensitive to shallow
-structures and for shallow structures our model performs quite good
-already given current dataset, we don't expect to see large misfit
-reduction from in those long period surface wave category.
-To better bring out the deep structure, We tune
-down the weightings of 40-100 sec surface wave, thus reduce their
-contribution in the overall misfit function. That explained why we see the
-misfit jump(decrease) from M17 to M18 in Fig.\ref{fig:misfit}(h) - (j) and
-increase Fig.\ref{fig:misfit}(b)-(d). We are using the same data but
-redistribution the contribution from each category by changing the measurements
-weight in the overall misfit function.
-
-\begin{table}[!htb]
-  \centering
-  \begin{tabular}{|c|c|c|c|}
-    \hline
-    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-    \hline
-    17--40~s   &   P-SV body waves          & P-SV body waves           & SH body waves   \\
-    40--100~s  &   P-SV body waves          & P-SV body waves           & SH body waves \\
-    40--100~s  &   Rayleigh surface waves   & Rayleigh surface waves    & Love surface waves \\
-    90--250~s  &   All waves                & All waves                 & All waves \\
-    \hline
-  \end{tabular}\\
-  \caption{12 measurement categories starting from M18 till M25. Before M15, the 40--100 body and surface waves are combined into one in each component.}
-  \label{table:measurement_category}
-\end{table}
-
-The misfit values for 17-40sec and 40-100s body waves are decreasing fast at
-the first few iterations, and flattens gradually, which may indicate that we are
-approaching the model resolution limits given current dataset.
-
-\subsubsection{Stage III: M22 - M25}
-
-We added an extra set of 440 earthquakes into our inversion database. Thus, the total
-number of earthquakes increased from 1,040 to 1480. We also bring back weightings
-of 40-100sec surface wave as stage I since the newly added 440 was mostly located
-in poorly covered regions in our previous dataset and those surface wave measurements
-will help to better constrain the shallow structures at those regions.
-
-The misfit jumps, from M21 to M22, is mostly due to the redistribution of weights
-and new earthquakes being added to the dataset. Optimization method is changed
-from conjugate gradient to L-BFGS. Overall misfit values is steadily reducing,
-as well as those in each category.
+\subsection{Workflow management}
+
+There are more than ten stages in the adjoint tomography workflow,
+and each stage involves thousands of small tasks.
+For every model iteration,
+we perform 1,480 forward and adjoint simulations, each involving hundreds of compute cores and graphics cards, as well as heavy I/O.
+The workflow is prone to human error and hardware failure, making it fragile.
+For these reasons, we wish to harden the worflow by taking advantage of modern workflow management software.
+With this goal in mind, we selected RADICAL-SAGA and RADICAL-EnTK as our workflow management engines, and developed complementary seismic tomography workflow tools~\citep{EnTK2017}.
+The workflow engine can automatically detected job failures both from the HPC system and via user-defined functions.
+This enables us to keep track of all tasks and semi-automatically resubmit jobs if necessary.
+Given that most HPC system time is spent waiting in the job queue, automatic failure detection and relaunching greatly shortens the overall time to solution.
+
+\section{Misfit evolution}
+
+The inversion went through ten iterations in a number of stages, as documented in this section.
+The behavior of the overall misfit function~(\ref{eq:misfit}) as well as its behavior in the various measurement categories is shown in Fig.~\ref{fig:misfit}.
 
@@
   measurement categories: body(red diamond) waves and surface waves
-  (red square).}
+  (red square).
+  {\color{red} Wenjie, why do the graphs overlap at iteration 22, but not at iteration 18?Shouldn't 22 look like 18, i.e., no overlapping points?}
+  }
   \label{fig:misfit}
@@
 
-\subsection{Misfit Assessment}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-In the last section, we discussed how the misfit evolves in iterations. However, since
-we changed our dataset and misfit functions(mainly weightings) between different stages,
-it might not be clear that how much did we improve our model. To precisely measure
-our model performance, we calculate synthetic data using the same source using M00, M15
-and M25. Windows and weightings are also identical across different iterations.
-
-Table.\ref{table:misfit_reduction_M15_M25} shows the misfit reduction from M15 to M25
-for 12 categories. For all categories, there is a significant misfit reduction. Among
-the three components, transverse have the largest misfit reduction. For the 4 period bands,
-40-100s surface waves have the largest misfit reduction which may indicate the 40-100 sec
-surface wave might not have good fit between synthetic and observed data compared to
-other period band and our inversion is improving it a lot.
-
-Table.\ref{table:misfit_reduction_M00_M25} shows M00 to M25. It is very similar to
-Table.\ref{table:misfit_reduction_M15_M25} but with larger values since it also
-counts the model improvements from M00 to M15. The best improved category is
-the transverse component in 40-100s surface waves, with misfit reduction at
-53.8\%. The minimum misfit reduction, on the other hand, is the vertical component
-in 17-40s body waves, with 31.1\% misfit reduction.
+\subsubsection{Stage~I: Iterations 15--17}
+
+Starting model GLAD-M15 was constructed using a database of 256 earthquakes.
+For iterations 15--17 of the inversion we used an expanded database of 520 events.
+Our focus was to validate and test our software and workflow before scaling up
+to a larger database of 1,040 events.
+For these iterations we used three period bands, namely,
+17--40~s, 40--100~s, and 90--250~s,
+and we used a nonlinear conjugate
+gradient method to update the model.
+
+\subsubsection{Stage~II: Iterations 18--21}
+
+We see an abrupt change in the value of the misfit function at iteration 18
+in Fig.~\ref{fig:misfit},
+reflecting the addition of 520 events to the inversion database,
+and a change in the weighting strategy for 40--100~s surface waves.
+For iterations 18--21 we split the 40--100~s period band into two, separating the body and surface waves (Figs.~\ref{fig:misfit}e--g).
+Since body and surface waves sample different parts of the mantle,
+this split facilitated more control over the spatial distribution of the model update.
+Because the 17th iteration model explains 40--100~s surface wave data relatively well,
+we reduced their weight on all three components for iterations 18--21,
+as indicated by the lower red curves in Figs.~\ref{fig:misfit}e--g.
+
+The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by iteration 21, prompting us to add more earthquakes and change the weighting strategy again.
+
+% Table~\ref{table:measurement_category} shows the four passbands we used in Stage~II, tabulating misfit reductions in all four passbands on three components,
+% that is, in twelve measurement categories.
+
+% \begin{table}[!htb]
+%   \centering
+%   \begin{tabular}{|c|c|c|c|}
+%     \hline
+%     ~          &  Vertical & Radial &  Transverse \\
+%     \hline
+%     17--40~s   &   P-SV          & P-SV           & SH   \\
+%     40--100~s  &   P-SV          & P-SV            & SH \\
+%     40--100~s  &   Rayleigh   & Rayleigh    & Love \\
+%     90--250~s  &   All                 & All                  & All  \\
+%     \hline
+%   \end{tabular}\\
+%   \caption{Twelve measurement categories used for iterations 18--25.
+%   Before iteration~18, the 40--100~s body and surface waves categories were combined into a single category on each component, resulting in nine categories.}
+%   \label{table:measurement_category}
+% \end{table}
+
+\subsubsection{Stage~III: Iterations 22--25}
+
+At iteration~22 we added another 440 earthquakes to the database,
+bringing the total to 1,480 event,
+and we changed the 40--100~s surface wave weights back to their setting during Stage~I.
+During this stage we also switched from a nonlinear conjugate gradient optimization algorithm to an L-BFGS quasi-Newton method.
+
+\subsection{Misfit assessment}
+
+In the previous section we discussed the evolution of the misfit through the three key stages of the inversion.
+It is important to note that ``the misfit function'' is, in fact, a continually moving target, because at every iteration the number of measurements increases as the model improves,
+and the number of earthquakes increases at iterations~18 and~22.
+In this section we calculate specific changes in misfit using all 1,480 earthquakes and an identical set of weightings and windows for three models, namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
+Table~\ref{table:misfit_reduction_M15_M25} summarizes the changes in fit in the twelve measurement categories
+between the new model, GLAD-M25, and its starting model, GLAD-M15, and between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.
+In all categories we observe significant misfit reductions,
+with dispersive 40--100~s surface waves exhibiting the largest misfit reduction.
+The improvements in fit per component are comparable in all period bands,
+indicating that the various categories are reasonably well balanced in the assessment of misfit.
 
@@
     \hline
-    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+    ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
     \hline
-    17--40s  body waves    &   17.4   &       21.1 &       24.6 \\
-    40--100s body waves    &   16.8   &       21.3 &       21.7 \\
-    40--100s surface waves &   28.5   &       28.3 &       28.4 \\
-    90--250s               &   14.5   &       13.4 &       25.7 \\
+    17--40~s  body waves    &   17.4 (31.1)   &       21.1 (37.1) &       24.6 (42.2) \\
+    40--100~s body waves    &   16.8 (31.3)  &       21.3 (40.2)  &       21.7 (42.0) \\
+    40--100~s surface waves &   28.5 (50.1)  &       28.3 (51.1) &       28.4 (53.8)  \\
+    90--250~s surface waves &   14.5 (36.2)  &       13.4 (38.8) &       25.7 (38.6) \\
     \hline
   \end{tabular}\\
-  \caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
+  \caption{Changes in fit in the twelve measurement categories
+between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
   \label{table:misfit_reduction_M15_M25}
@@
 
-\begin{table}[!htb]
-  \centering
-  \begin{tabular}{|c|c|c|c|}
-    \hline
-     ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-    \hline
-    17--40s body waves     &    31.1    &       37.1 &       42.2 \\
-    40--100s body waves    &    31.3    &       40.2 &       42.0 \\
-    40--100s surface waves &    50.1    &       51.1 &       53.8 \\
-    90--250s               &    36.2    &       38.8 &       38.6 \\
-    \hline
-  \end{tabular}\\
-  \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
-  \label{table:misfit_reduction_M00_M25}
-\end{table}
-
-\subsection{Comparison of Histograms}
-
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-Another way to evaluate the model performance by checking the distribution
-of measurements. Fig.\ref{fig:phase_hist} shows the histograms of phase
-measurements. We use identical windows to make measurements using 1,480
-earthquakes on the all the three models, our starting model
-GLAD-M00(362ANI+CRUST2.0), first generation model GLAD-M15,
-and lastest model GLAD-M25. The total number of selected windows is over
-18 million. The standard deviations values of phase measurements has
-significant improvements on all the categories over iterations.
-The means values, has also improved especially in the long period categories,
-such as the 40-100 surface waves and 90-250 all waves. In some categories,
-you may see slight shift of mean values, mainly due to the trade off among
-different components and period bands. To summarize, the improvements in
-the phase measurements histogram is consistent as we observed in the
-misfit reduction.
-
-Fig.\ref{fig:amp_hist} shows the histogram of amplitude measurements. We do
-observed variance reductions in all the categories, but the difference is
-not significant and the variance is still relatively large.
-It is because now we only assimilate phase measurements to
-constrain the elastic model parameters. To better constrain the amplitude
-anomalies, shear attenuation has to been include in our inversion, which is
-next step of our work.
+% \begin{table}[!htb]
+%   \centering
+%   \begin{tabular}{|c|c|c|c|}
+%     \hline
+%      ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+%     \hline
+%     17--40s body waves     &    31.1    &       37.1 &       42.2 \\
+%     40--100s body waves    &    31.3    &       40.2 &       42.0 \\
+%     40--100s surface waves &    50.1    &       51.1 &       53.8 \\
+%     90--250s               &    36.2    &       38.8 &       38.6 \\
+%     \hline
+%   \end{tabular}\\
+%   \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
+%   \label{table:misfit_reduction_M00_M25}
+% \end{table}
+
+\subsection{Histogram comparisons}
+
+Another way to evaluate model performance is by assessing the distribution
+of measurements in the various categories.
+Again we use all 1,480 events and a set of identical windows on all three components
+to assess GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
+The total number of selected windows exceeds 18~million.
+Fig~\ref{fig:phase_hist} shows histograms of the resulting phase
+measurements in all twelve measurement categories.
+We observed that the distributions generally become better centered on zero,
+and that the standard deviations are steadily reduced.
+Again we note that the inversion is aimned at reducing the overall misfit,
+so there are small tradeoffs between different measurement categories.
+
+Fig~\ref{fig:amp_hist} shows histograms of the amplitude
+measurements for all twelve measurement categories,
+which are not used in the current inversion.
+Despite this,
+we observe modest reductions in the standard deviations of the histograms.
+The histograms are nicely centered, indicating that the moment magnitudes are suitably selected.
+In the next phase of our ongoing inversion we plan to begin assimilating these amplitude measurements,
+while simultaneously adding shear attenuation as a new model parameter.
 
@@
   \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
-  \caption{Histograms of phase measurements for S362ani(GLAD-M00, \textbf{Black}), GLAD-M15(\textbf{{\color{ForestGreen} Green}}) and GLAD-M25(\textbf{{\color{Red} Red}}) in the 12 measurement categories.
-Each columns is one component and each row is one period band.
-The numbers on the top right is the number of measurements used in that category.
-The total number of measurements is around 18.2 million.
-Mean and standard deviations of phase measurements are also denoted in the top right of figures.}
+  \caption{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, \textbf{Black}), GLAD-M15 (M15, \textbf{{\color{ForestGreen} Green}}) and GLAD-M25 (M25, \textbf{{\color{Red} Red}}).
+  Each column represents one component, and each row corresponds to a period band.
+  The numbers above the top right of each panel denote the number of measurements in the corresponding category.
+  The total number of measurements is 18.2 million.
+  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}
   \label{fig:phase_hist}
@@
   \includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
-  \caption{Same as Fig.\ref{fig:phase_hist} except for amplitude measurements.}
+  \caption{Same as Fig.~\ref{fig:phase_hist} except for amplitude measurements. These measurements are currently not used in the inversion.}
   \label{fig:amp_hist}
@@
 
-**Also include the P arrival measurements here.**
+{\color{red} Wenjie: Also include the P arrival measurements here.}
 
@@
   \hline
-  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+  ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
   \hline
-  17--40s                &          11.8 &       14.1 &       21.5 \\
-  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
-  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
-  90--250s               &          10.9 &       14.3 &       24.0 \\
+  17--40~s                &          11.8 (29.2) &       14.1 (33.7) &       21.5 (43.4) \\
+  40--100~s body waves    &          14.5 (26.2) &       12.9 (32.2)  &       16.9 (39.0) \\
+  40--100~s surface waves &          29.3 (49.1) &       28.1 (49.4) &       23.7 (51.2) \\
+  90--250~s               &          10.9 (30.9) &       14.3 (34.8)  &       24.0 (34.9) \\
   \hline
   \end{tabular}\\
-  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
+  \caption{Changes in fit for 360 earthquakes not used in the inversion in the twelve measurement categories
+between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
   \label{table:misfit_reduction_M15_M25_360}
@@
 
-\begin{table}[!htb]
-  \centering
-  %\label{tag:misfit_reduction_M00_M25_360}
-  \begin{tabular}{|c|c|c|c|}
-    \hline
-    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-    \hline
-    17--40s                &         29.2 &       33.7 &       43.4 \\
-    40--100s body waves    &         26.2 &       32.2 &       39.0 \\
-    40--100s surface waves &         49.1 &       49.4 &       51.2 \\
-    90--250s               &         30.9 &       34.8 &       34.9 \\
-    \hline
-  \end{tabular}\\
-  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
-  \label{table:misfit_reduction_M00_M25_360}
-\end{table}
+% \begin{table}[!htb]
+%   \centering
+%   %\label{tag:misfit_reduction_M00_M25_360}
+%   \begin{tabular}{|c|c|c|c|}
+%     \hline
+%     ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
+%     \hline
+%     17--40s                &         29.2 &       33.7 &       43.4 \\
+%     40--100s body waves    &         26.2 &       32.2 &       39.0 \\
+%     40--100s surface waves &         49.1 &       49.4 &       51.2 \\
+%     90--250s               &         30.9 &       34.8 &       34.9 \\
+%     \hline
+%   \end{tabular}\\
+%   \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
+%   \label{table:misfit_reduction_M00_M25_360}
+% \end{table}
 
@@
 
-...to be done...
 Fig.\ref{fig:europe-vs} shows the isotropic $V_s$ structures at Europe. As
@@
 
-The southwestern part of china is featured by the Himalayas mountain, which is 
+Our model at Asian region is plotted on Fig.\ref{fig:asia-vs},
+together with S362ANI+M, S40RTS and EARA2014\cite{chen2015multiparameter}.
+EARA2014 is a regional 3D anisotropic tomographic model using adjoint
+methods, comprising 1.7million frequency-dependent traveltime
+measurements from 227 earthquakes recorded by 1869 seismic stations.
+It has superior data coverage, mainly by incorporating the China
+Seismic Array in this area.
+
+The southwestern part of China is featured by the Himalayas mountain,
+which is 
 a shallow expression of the collision between India and Euroasian plate. Our

### 2018-10-19 main.tex
fix space in figure
Updates from ShareLaTeX

@@
 (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
-  {\color{red} Wenjie: please put a space between ``depth'' and ``km'' in the x-axis labels of figures C and D.}
   }
@@
 The inversion went through ten iterations in a number of stages, as documented in this section.
-The behavior of the overall misfit function~(\ref{eq:misfit}) as well as its behavior in the various measurement categories is shown in Fig.~\ref{fig:misfit}.
+The evolution of the overall misfit function~(\ref{eq:misfit}) as well as its behavior in the various measurement categories is summarized in Fig.~\ref{fig:misfit}.
 
@@
   (red square).
-  {\color{red} Wenjie, why do the graphs overlap at iteration 22, but not at iteration 18?Shouldn't 22 look like 18, i.e., no overlapping points?}
+  {\color{red} Wenjie, why do the graphs overlap at iteration 22, but not at iteration 18? Shouldn't 22 look like 18, i.e., no overlapping points?}
   }
@@
 
-The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by iteration 21, prompting us to add more earthquakes and change the weighting strategy again.
+The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by iteration 21, prompting us to add more earthquakes and change the weighting strategy again by reintroducing the 17--40~s surface waves.
 
@@
 bringing the total to 1,480 event,
-and we changed the 40--100~s surface wave weights back to their setting during Stage~I.
-During this stage we also switched from a nonlinear conjugate gradient optimization algorithm to an L-BFGS quasi-Newton method.
+and we changed the 40--100~s surface wave weights back to their setting in Stage~I.
+During this stage we switched from a nonlinear conjugate gradient optimization algorithm to an L-BFGS quasi-Newton method.
 
 \subsection{Misfit assessment}
-
-In the previous section we discussed the evolution of the misfit through the three key stages of the inversion.
+\label{section:Misfit assessment}
+
+In the previous sections we discussed the evolution of the misfit through three key stages of the inversion.
 It is important to note that ``the misfit function'' is, in fact, a continually moving target, because at every iteration the number of measurements increases as the model improves,
 and the number of earthquakes increases at iterations~18 and~22.
+
 In this section we calculate specific changes in misfit using all 1,480 earthquakes and an identical set of weightings and windows for three models, namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
@@
 In all categories we observe significant misfit reductions,
-with dispersive 40--100~s surface waves exhibiting the largest misfit reduction.
+with dispersive 40--100~s surface waves exhibiting the largest improvements.
 The improvements in fit per component are comparable in all period bands,
 indicating that the various categories are reasonably well balanced in the assessment of misfit.
+
+{\color{red} Wenjie: Make sure the variance reductions are calculated as ln (Phi\_M25 / Phi\_M15).}
 
@@
 \subsection{Histogram comparisons}
+\label{section:Histogram comparisons}
 
@@
 measurements in all twelve measurement categories.
-We observed that the distributions generally become better centered on zero,
-and that the standard deviations are steadily reduced.
-Again we note that the inversion is aimned at reducing the overall misfit,
+We observe that the distributions generally become better centered on zero,
+and that all standard deviations are steadily reduced.
+Again we note that the inversion is aimed at reducing the overall misfit,
 so there are small tradeoffs between different measurement categories.
@@
 measurements for all twelve measurement categories,
-which are not used in the current inversion.
+which were not used in the current inversion.
 Despite this,
-we observe modest reductions in the standard deviations of the histograms.
-The histograms are nicely centered, indicating that the moment magnitudes are suitably selected.
-In the next phase of our ongoing inversion we plan to begin assimilating these amplitude measurements,
+we observe modest reductions in all standard deviations of the histograms.
+The histograms are nicely centered, indicating that the moment magnitudes are suitably selected, because the scalar moment affects all measurement categories equally.
+In the next phase of our ongoing inversion we plan to begin assimilating amplitude measurements,
 while simultaneously adding shear attenuation as a new model parameter.
@@
 
-\section{Model Evaluation}
-
-Here, we present two ways that used to evaluate the quality of our model:
-resolution analysis and held-out data test.
-
-\subsection{Resolution Analysis}
-Checkboard test was commonly used a resolution test method but it is at the
-same cost of inversion of GLAD-M25, which will cost millions of CPU hours.
-Due to the very demanding computational requirements, we used the 'point
-spread function to assess the imaging quality in models GLAD-M25.
-
-\subsection{Held-out Dataset Test}
-Following the approach by \cite{tape2009adjoint}, \cite{bozdaug2016global},
-unseen events are used to check the performance of our
-model. We revisited the Global CMT catalogue,
-picked all the events whose magnitude is between 6.3 and 7.0, which hasn't
-been used in our inversion. The reason why we set the lower bound to 6.3
-instead of 5.5, is those earthquakes have good enough data and generates
-more measurements at the global scale.
-We calibrated the scalar moment and origin time in the GLAD-M25, and there
-are 360 events left that has enough windows. Fig.\ref{fig:events_360} shows
-the distribution of 360 earthquake that we used as held-out dataset
+\section{Model evaluation}
+
+In this section we evaluate model GLAD-M25 further based on a point-spread function resolution analysis as well as a ``held-out'' dataset, that is, a set of data not used in the actual structural inversion.
+
+\subsection{Point-spread function analysis}
+
+Checkboard tests or tests involving a chosen known structure, e.g., a plume or slab,
+are frequently used to evaluate resolution in a tomographic inversion.
+Such tests are extremely expensive in FWI and adjoint tomography, because they require roughly the same computational resources as the actual inversion.
+In lieu of such tests,
+we performed two point-spread function analyses~\citep{fichtner2011resolution,zhu2015seismic,bozdaug2016global}.
+
+\subsection{Held-out dataset}
+
+Following the approach of \cite{tape2009adjoint}, \cite{chen2015multiparameter}, and \cite{bozdaug2016global},
+we selected 360 earthquakes that were not used in the actual inversion.
+This held-out dataset consists of all magnitude 6.3--7.0 earthquakes in the global CMT catalog that were not used in the inversion.
+We chose larger events to generate as many measurements as possible.
+We calibrated the centroid time and scalar moment using a grid search based on 3D synthetics calculated in GLAD-M25.
+Fig.~\ref{fig:events_360} summarizes the properties of the held-out database.
 
@@
   \includegraphics[width=\textwidth]{figures/events_360.pdf}
-  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model assessment stage.
-Theses events are not used in the structural inversion.
-(a) Beach balls of earthquakes.
-Same color conventions as used in the \ref{fig:event_1480} (b) and (c) Histograms of moment magnitude and depth.}
+  \caption{Summary of the held-out database containing 360 earthquakes.
+Theses events were not used in the structural inversion.
+(a) Distribution of events, color coded by depth range as in Fig.~\ref{fig:event_1480}.
+(b) \& (c) Histograms of moment magnitude and depth.}
   \label{fig:events_360}
@@
 
-First, we evaluate the model performance by misfit reduction. Same windows and
-weightings are used across models. Table.\ref{table:misfit_reduction_M00_M25_360}
-shows the misfit reduction from M15 to M25 and Table.\ref{table:misfit_reduction_M00_M25_360}
-is from M00 to M25. It again shows misfit reduction in all categories in
-our held-out dataset, similar to what we observed from the inversion dataset.
-The reduction are slightly smaller, partly due to the reason that we didn't
-do waveform-type inversion as we mentioned in the source inversion stage but
-only did a grid search to calibrate the scalar moment and origin time.
+First, we repeated the misfit assessment discussed in Section~\ref{section:Misfit assessment} for the held-out database.
+Table~\ref{table:misfit_reduction_M15_M25_360} summarizes the reductions in misfit for the held-out database for model GLAD-M25 compared to GLAD-M15 as well a S362ANI combined with CRUST2.0.
+It is comforting to see that the reductions are comparable to the
+values tabulated in Table~\ref{table:misfit_reduction_M15_M25} for the actual inversion.
+Overall the reductions are slightly smaller, partly due to the fact that we did not conduct full CMT inversions for the held-out database.
 
@@
 
-Second, we also plotted the histograms of phase measurements in Fig.\ref{fig:phase_hist_360}. We also observed clear variance reduction in all the 12 categories from GLAD--M00 to GLAD--M25.
-
-To summarize, both the misfit reduction and histogram improvements indicates that our model performs good with data that hasn't been used in our inversion.
-We expect to see similar behavior for the future earthquakes.
+Second, we repeated the histogram comparisons discussed in Section~\ref{section:Histogram comparisons} for the held-out database.
+We used a set of identical windows on all three components to assess
+phase and amplitude anomalies in models GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
+Fig.~\ref{fig:phase_hist_360} shows histograms of the resulting phase
+measurements in all twelve measurement categories.
+The total number of measurements exceeds 7.8~million.
+As in the actual inversion,
+we observe systematic decreases in all standard deviations in all twelve categories,
+and we note a sharpening of the distributions centered around zero.
 
@@
   \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
-  \caption{Histogram of phase measurements similar to \ref{fig:phase_hist} except for 360 held-out earthquakes.}
+  \caption{Histogram of phase measurements for the 360 events in the held-out database.}
   \label{fig:phase_hist_360}
@@
 
-\section{Models}
-
-\subsection{Global Velocity Structure}
-
-{\color{Red} Wenjie: Plan to work more on this part. But do you any suggestion what things should I talk about?}
-
-In Fig.\ref{fig:global-vs}, the global map of isotropic $V_s$ is plotted at certain depths.
-As comparisons, we also plotted two other models, S362ANI+M{\citep{moulik2014anisotropic},
-which is the updated version of our starting model but with mode data added
-into the inversion, and S40RTS\citep{ritsema2011s40rts}. At the first glance,
-you may notice that all the models agree at the long wavelength structures.
-At 2800km depth, our model is very close to S362ANI+M, with more extended
-features at the LLSVP.
-
-The value ranges are labeled on the top left on each figure. It is obvious the
-value ranges in our model is generally larger than other two models, which is
-consistent with \cite{french2014whole}.
+\section{Model GLAD-M25}
+
+In this section we discuss model GLAD-M25 in some detail.
+We begin with a global overview of the model before concentrating on specific geographical regions.
+We conclude by highlighting various slabs and plumes in the model.
+
+\subsection{Global structure}
+
+We first examine model GLAD-M25 in the context of existing global tomographic models.
+In Fig.~\ref{fig:global-vs} we compare global maps of the isotropic part of our shear wavespeed model with model S362ANI$+$M~\citep{moulik2014anisotropic},
+which is an updated version of the starting model for the GLAD-M15 inversion,
+and model S40RTS~\citep{ritsema2011s40rts}.
+The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
+Overall these models are in good agreement at the longest wavelengths, especially Glad-M25 and S362ANI$+$M.
+The perturbations in GLAD-M15 tend to be larger than in the other models,
+consistent with observations by~\cite{french2014whole},
+whose model is also based on a form of waveform inversion.
 
@@
   \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
-  \caption{Map views of global $V_s$ perturbations at various depths for out model
-  GLAD-M25(left column), S362ANI+M(middle column)\citep{moulik2014anisotropic}
-  and S40RTS(right column)\citep{ritsema2011s40rts}. The perturbations are
-  calculated based on each model's own 1D profile. The values(upper-left corner
-  of each figure) denotes the minimum/maximum perturbations for each model at
-  the corresponding depth. The green circles denotes the locations of
-  hotspots\citep{montelli2006catalogue}. The range of the colorbar is the same
-  for each row and the range value is labeled on the most left, right after
+  \caption{Map views of global shear wavespeed perturbations at various depths for  model
+  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic}
+  and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
+  At a given radius,
+  perturbations are calculated relative to each model's average.
+  The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
+  The green circles denote locations of various
+  hotspots~\citep{montelli2006catalogue}.
+  The range of the colorbar is the same for each row,
+  and its maximum value is indicated in parentheses on the left, after
   the depth.}
@@
 %\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
-%  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
+%  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI$+$M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
 For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing.
@@
 
-The other prominent feature of our models is that we can also constrain $V_p$ as an
-independent model parameters. Fig.\ref{fig:global-vp} shows our isotropic $V_p$
-structures at several depths. As comparisons, we also showed two more global
-$V_p$ models, LLNL-G3Dv3\citep{simmons2012llnl}} and GAP-P4\citep{fukao2013subducted}.
-
-At 100km depth, our model shows prominent ocean ridges at the realm of pacific
-oceans, which are relatively slow velocity regions, compared to other two vp models.
-On the other hand, the continent slabs, such as Australia, South Africa,
-North America and Europe, is more prominent in our model.
-
-For upper mantle, the LLNL-G3Dv3 shows the largest variations. For example,
-the 500km, the LLNL model shows very strong slow velocity anomalies at
-Hawaii and other pacific hotspots, such as Samoa and Tahiti.
-For middle mantle at about 1000km, all them models all shows a few major
-subduction zones, such as the South America, Fiji and Sumatra regions.
-At lower mantle, such as 2000km and 2800km, LLNL-G3Dv3 and GAP-P4 tends to
-fade out, even though the patterns are very similar among them, such as
-the LLSVP regions.
-
-** Note: add spherical harmonic analysis later **
+An important aspect of our inversion is that constrain shear and compressional waves simultaneously.
+In Fig.~\ref{fig:global-vs} we compare global maps of our compressional wavespeed model with P models LLNL-G3Dv3~\citep{simmons2012llnl} and GAP-P4~\citep{fukao2013subducted}.
+At a depth of 100~km,
+GLAD-M25 shows prominent mid-oceanic ridges, cooling of the Pacific lithosphere, and the roots of numerous continental cratons.
+In the upper mantle, LLNL-G3Dv3 exhibits the largest lateral variations,
+e.g., very slow compressional wavespeeds at 500~km depth below Hawaii, Samoa, and Tahiti.
+In the midmantle we can see remnants of subduction beneath South America, Indonesia,
+and Tonga-Kermadec.
+In the deep mantle, LLNL-G3Dv3 and GAP-P4 begin to fade out, but the long-wavelength patterns,
+in particular the lowerparts of the Africa and Pacific superplumes, are very similar.
+
+{\color{red} Wenjie: Note: add spherical harmonic analysis later.}
 
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
-  \caption{Map views of global $V_p$ variations at various depths for our model
-  GLAD-M25(left column), LLNL-G3Dv3(middle column) \citep{simmons2012llnl} and
-  GAP-P4(\citep{fukao2013subducted}).
-  For LLNL-G3Dv3, the depths is labeled on the right
-  bottom based on its own mesh spacing. Other plotting conventions are used
-  similar as in Figure \ref{fig:global-vs}.}
+  \caption{Map views of global compressional wavespeed variations at various depths for model
+  GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl} and
+  GAP-P4~[right column;][](\citep{fukao2013subducted}).
+  For LLNL-G3Dv3, depth ranges are labeled on the bottom right
+  bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}
 \label{fig:global-vp}
@@
 
-For the following sections, we will discuss the velocity structures in regional
-areas.
-
 \subsubsection{North America}
 
-{\color{Red} Wenjie: Ready for Jeroen to edit}
-
-The deployment of USArray has dramatically increased the data overage on the
-continental United States. In this section, we compare our GLAD-M25 with
-together with two global models, S362ANI+M, S40RTS, and two regional models,
-US22\citep{zhu2017radial}, SL2013NA\citep{schaeffer2014imaging}.
-
-US22 is radially anisotropic model build based on adjoint tomography using
-USArray data from 180 regional earthquakes using 15-50sec short-period
-body waves and 25-150sec long-period surface waves.
-SL2013NA is an upper-mantle global shear wave speed model using multimode
-surface waveform tomography and primarily focused on the north American
-region.
-
-The North American region is featured by a large, high-velocity cratonic
-lithosphere, bounded by the Rocky Mountain Front to the west and continental
-margin to the east. For both sides the lithosphere has been deformed by
-low velocity structures thus form a sharp boundary.
+The deployment of USArray has dramatically increased data overage underneath the
+continental United States.
+In this section, we compare GLAD-M25 with
+with two global models, S362ANI$+$M and S40RTS, and two regional models,
+US22~\citep{zhu2017radial} and SL2013NA~\citep{schaeffer2014imaging}.
+US22 is a radially anisotropic model based on adjoint tomography using
+USArray data from 180 regional earthquakes using 15--50~s
+body waves and 25--150~s surface waves.
+SL2013NA is a global upper-mantle shear wavespeed model based on multimode
+surface waveform tomography primarily focused on North America.
+
+North America is characterized by a large, high-wavespeed cratonic
+lithosphere, bounded by the Rocky Mountain Front to the West and continental
+margin to the East. On both sides the lithosphere has been deformed by
+low wavespeed structures, thus forming sharp boundaries.
 
@@
 and surrounding low velocity structures, especially compared with
-two global models, S362ANI+M and S40RTS, yet stay very similar to
+two global models, S362ANI$+$M and S40RTS, yet stay very similar to
 two regional models, US22 and SL2014NA. At such depth,
@@
 In the northeastern part, the Iceland hotspot has been greatly enhanced,
-especially at 300km and 400km compared to S362ANI+M.
+especially at 300km and 400km compared to S362ANI$+$M.
 
@@
   \caption{Map views of $V_s$ variations of North America at various depths
-  for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS)
+  for our model GLAD-M25(first column) and several global(S362ANI$+$M and S40RTS)
   and regional(US22\citep{zhu2017radial} and SL2013NA\citep{schaeffer2014imaging})
@@
 Fig.\ref{fig:europe-vs} shows the isotropic $V_s$ structures at Europe. As
-comparisons, we also showed S362ANI+M, S40RTS and one regional model EU60
+comparisons, we also showed S362ANI$+$M, S40RTS and one regional model EU60
 \citep{zhu2015seismic}. Compared to two global models, it is clear that
@@
 with the curved shape at the lower bottom of the figure,
-while S362ANI+M shows very smooth shape and S40RTS shows much smaller 
+while S362ANI$+$M shows very smooth shape and S40RTS shows much smaller 
 perturbation values. Besides, at 400km, GLAD-M25 is enhancing Iceland
-compared to S362ANI+M.
+compared to S362ANI$+$M.
 
@@
   \caption{Map views of $V_s$ variations of Europe at various depths for our
-  model GLAD-M25(first column) and global(S362ANI+M and S40RTS) and
+  model GLAD-M25(first column) and global(S362ANI$+$M and S40RTS) and
   regional(EU60\citep{zhu2015seismic}) models. For EU60, the range of color
@@
 Our model at Asian region is plotted on Fig.\ref{fig:asia-vs},
-together with S362ANI+M, S40RTS and EARA2014\cite{chen2015multiparameter}.
+together with S362ANI$+$M, S40RTS and EARA2014\cite{chen2015multiparameter}.
 EARA2014 is a regional 3D anisotropic tomographic model using adjoint
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
-  \caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(EARA2014\citep{chen2015multiparameter}) models.}
+  \caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI$+$M and S40RTS) and regional(EARA2014\citep{chen2015multiparameter}) models.}
 \label{fig:asia-vs}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
-  \caption{Map views of $V_p$ variations of South America at various depths for our model GLAD-M25(first column) and several global models, including S362ANI+M, LLNL-G3Dv3 and GAP-P4\citep{fukao2013subducted}.}
+  \caption{Map views of $V_p$ variations of South America at various depths for our model GLAD-M25(first column) and several global models, including S362ANI$+$M, LLNL-G3Dv3 and GAP-P4\citep{fukao2013subducted}.}
 \label{fig:southamerica-vp}
@@
 \section{Conclusion}
+
+In summary,
+the new model performs well for the held-out dataset, both in terms of misfit reductions and measurement distributions in all twelve measurement categories.
+We expect to see similar behavior for any future earthquakes.
 
@@
 We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for providing the data used in this study.
-We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
+{\color{red} Wenjie: Please add all relevant data centers.} We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
 The open source spectral-element software package SPECFEM3D\_GLOBE and the seismic measurement software package FLEXWIN used for this article are freely available via the Computational Infrastructure for Geodynamics (CIG; {\tt geodynamics.org}).

### 2018-10-19 main.tex
Q&A

@@
 \end{equation}
+
 {\color{Red} Wenjie: is it $\omega_{cr}^{-2}$ or $\omega_{cr}^{-1}$? And does the normalization factor~$N_c$ depend on~$c$?\\ }
+{\color{Red} To Jeroen: I checked the code. we are using $\omega_{cr}^{-1}$. The normalization factor depends on c.}
+
 where~$N_c$ is a normalization factor,
@@
 
+{\color{red} To Jeroen: You are right.
+$\Delta$ is different for a given source and category.
+Actually, we don't directly control $\Delta$.
+Instead, we control the condition number of weights.
+So the $\Delta$ will vary with receiver distributions.
+}
+
 \section{Model parametrization}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/misfit.pdf}
+  \includegraphics[width=0.8\textwidth]{figures/misfit.pdf}
   \caption{Evolution of phase misfits from GLAD-M15 to GLAD-M25.
@@
   (red square).
-  {\color{red} Wenjie, why do the graphs overlap at iteration 22, but not at iteration 18? Shouldn't 22 look like 18, i.e., no overlapping points?}
+  {\color{red} Wenjie, why do the graphs overlap at iteration 22, but not at iteration 18?
+Shouldn't 22 look like 18, i.e., no overlapping points?
+\textbf{To Jeroen}: overlap means I calculate the misfit twice using the same mode.
+For example, in iteration M22, I caculated the misfit using the 1040 earthquakes and 1480 earthquakes, respectively.
+In M18, I haven't done so.
+If you want, I can calculate the misfit values and adding the overlap misfit point.}
   }
@@
 {\color{red} Wenjie: Make sure the variance reductions are calculated as ln (Phi\_M25 / Phi\_M15).}
-
+{\color{red} Wenjie: I was using (Phi\_M25 - Phi\_M15) / Phi\_M15. So let me modify it?}
 \begin{table}[!htb]

### 2018-10-20 main.tex
Updates from ShareLaTeX

@@
 \end{equation}
-
-{\color{Red} Wenjie: is it $\omega_{cr}^{-2}$ or $\omega_{cr}^{-1}$? And does the normalization factor~$N_c$ depend on~$c$?\\ }
-{\color{Red} To Jeroen: I checked the code. we are using $\omega_{cr}^{-1}$. The normalization factor depends on c.}
-
-where~$N_c$ is a normalization factor,
+where~$N_c$ is a normalization factor for category~$c$,
 and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
-The reference angular distance~$\Delta_c$ needs to be chosen such that the condition 
+The reference angular distance~$\Delta_c$ for each category~$c$ needs to be chosen such that the condition 
 number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
@@
 The color of each beach ball reflects its depth range, where blue designate events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
-(b) and (c) Histograms of earthquake moment magnitudes and depths.}
+(b) \& (c) Histograms of earthquake moment magnitudes and depths.}
   \label{fig:event_1480}
@@
 
-{\color{red} Wenjie: is there just one $\Delta$, or are there different ones for sources, receivers and categories? And is there just one normalization constant~$N$, or are there multiple ones?}
-
-{\color{red} To Jeroen: You are right.
-$\Delta$ is different for a given source and category.
-Actually, we don't directly control $\Delta$.
-Instead, we control the condition number of weights.
-So the $\Delta$ will vary with receiver distributions.
-}
-
 \section{Model parametrization}
@@
 If you want, I can calculate the misfit values and adding the overlap misfit point.}
+  {\color{blue}Wenjie: OK, then let's be consistent in what we do. I would prefer no overlap.}
   }
@@
 {\color{red} Wenjie: I was using (Phi\_M25 - Phi\_M15) / Phi\_M15. So let me modify it?}
+{\color{blue} Wenjie: yes please. It will only change things slightly, if at all. You need to do the same for Table~\ref{table:misfit_reduction_M15_M25_360}.}
 \begin{table}[!htb]
@@
 values tabulated in Table~\ref{table:misfit_reduction_M15_M25} for the actual inversion.
-Overall the reductions are slightly smaller, partly due to the fact that we did not conduct full CMT inversions for the held-out database.
+Overall, the reductions are slightly smaller, partly due to the fact that we did not conduct full CMT inversions for the held-out database.
 
@@
 We used a set of identical windows on all three components to assess
-phase and amplitude anomalies in models GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
+phase anomalies in models GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
 Fig.~\ref{fig:phase_hist_360} shows histograms of the resulting phase
@@
   \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
-  \caption{Histogram of phase measurements for the 360 events in the held-out database.}
+  \caption{Histograms of phase measurements for the 360 events in the held-out database.}
   \label{fig:phase_hist_360}
@@
 The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
-Overall these models are in good agreement at the longest wavelengths, especially Glad-M25 and S362ANI$+$M.
+Overall, these models are in good agreement at the longest wavelengths, especially Glad-M25 and S362ANI$+$M.
 The perturbations in GLAD-M15 tend to be larger than in the other models,
@@
 
-An important aspect of our inversion is that constrain shear and compressional waves simultaneously.
+An important aspect of our inversion is that it constrains shear and compressional waves simultaneously.
 In Fig.~\ref{fig:global-vs} we compare global maps of our compressional wavespeed model with P models LLNL-G3Dv3~\citep{simmons2012llnl} and GAP-P4~\citep{fukao2013subducted}.
@@
   GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl} and
-  GAP-P4~[right column;][](\citep{fukao2013subducted}).
-  For LLNL-G3Dv3, depth ranges are labeled on the bottom right
+  GAP-P4~\citep[right column;][]{fukao2013subducted}.
+  For LLNL-G3Dv3, depth ranges are labeled in the bottom right
   bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}
@@
 
-The deployment of USArray has dramatically increased data overage underneath the
+The deployment of USArray has dramatically increased data overage across the
 continental United States.
-In this section, we compare GLAD-M25 with
+In this section, we compare GLAD-M25 in this region with
 with two global models, S362ANI$+$M and S40RTS, and two regional models,
@@
 
-North America is characterized by a large, high-wavespeed cratonic
-lithosphere, bounded by the Rocky Mountain Front to the West and continental
+North America is characterized by a large, high-wavespeed lithospheric craton,
+bounded by the Rocky Mountain Front to the West and continental
 margin to the East. On both sides the lithosphere has been deformed by
-low wavespeed structures, thus forming sharp boundaries.
-
-At 100km, our model shows a much sharpened boundary between the carton
-and surrounding low velocity structures, especially compared with
-two global models, S362ANI$+$M and S40RTS, yet stay very similar to
-two regional models, US22 and SL2014NA. At such depth,
-we are observed a very strong expression of the Snake River Plain(
-with Yellowstone) and Raton hotspot, with their depth extending to 200km.
-The very high-velocity craton extend to 200km, with its very core part to
-300 km, similar to US22 while SL2013NA shows it almost disappeared at such depth.
-Again, the Wyoming craton and Medicine Hat Block shows a very strong lithosphere
-root from the very shallow depth to 400km, which is also similar to US22 but
-hard to observe in SL2013NA. Similar case is the craton at Yavapai and
-Mazatzal Blocks, which define the southern bound of the large craton.
-
-At such depth, we also observed high velocity
-features within the Gulf of Mexico, which coincides spatially with the deepest
+low wavespeed structures, thus forming sharp tectonic boundaries.
+
+At a depth of 100~km, we observed that the edges of the craton are sharper in
+GLAD-M15 than in the other two global models,
+and quite similar in shape and sharpness to the two regional models.
+We can clearly see impressions of the Snake River Plain (with Yellowstone)
+and the Raton hotspot, which also have distinct slow expressions at depths of 200~km.
+The core of the craton exhibits fast wavespeeds at depths reaching 300~km Northwest of
+Hudson Bay.
+In the regional models the craton has basically faded away at these depths.
+The Wyoming and Medicine Hat Blocks show a very strong and thick lithospheric
+root from shallow depths to $\sim$400~km, similar to US22 but
+difficult to discern in SL2013NA.
+Similar observations can be made for the Yavapai and
+Mazatzal Blocks, which define the southern boundary of the large craton.
+
+In the 200--400~km depth range, we observe a high wavespeed
+anomaly within the Gulf of Mexico, which coincides spatially with the deepest
 bathymetry and corresponds to a portion of ancient oceanic
-Lithosphere\citep{muller2008}. The remnant of Juan de Fuca subduction
-plates, with its high velocity footprint, is presented in our model at
-300km and 400km, though the SL2013NA shows a much stronger anomaly.
-
-At the North, our models shows a extended high velocity craton beneath the 
-Greenland, though clearly separated with the North America Craton,
-bounded at the relatively low velocity structure at Barffin Bay and Labrador
-Sea, with North American Craton followed nicely with the coastline. In the
-north west region, our models shows the most clear picture of
-Aleutian subduction zones, with it high velocity feature down to 400km.
-In the northeastern part, the Iceland hotspot has been greatly enhanced,
-especially at 300km and 400km compared to S362ANI$+$M.
-
-In the Easter part, our models shows a high-velocity structure at the western
-Atlantic, starting from the tip of Florida to the New York,
-separated from the major part the north America craton,
-though it stays very thin that the depth only extend to above 200km.
-This feature is associated with some of the oldest oceanic crust and lithosphere
-within the Atlantic\citep{muller2008, schaeffer2014imaging}.
-All the models is showing a high velocity anomaly at Nova Scotia and Newfoundland
-with its high-velocity core to 300km.
-Bermuda hotspot is nicely preserved from our starting
-model, yet get sharpened and stronger at 200km and 300km. Besides, the
-Caribbean suduction, which is relatively young subduction systems, is clearly
-observable in our model, starting from 200km to 300km.
-
-For even deeper depth, our models shows a very clear picture of the Farallon
-subductions, but it goes beyond the range of this comparison since the two
-region models are really upper-mantle models which don't extend to the very
-deep depth. We will show some vertical cross-sections of Farallon slabs in
-the later sections.
+Lithosphere~\citep{muller2008}.
+A remnant of the Juan de Fuca plate,
+with a high wavespeed footprint, is visible at depths of 300~km and 400~km,
+where SL2013NA shows a much stronger anomaly.
+
+In the North,
+we see a high wavespeed craton beneath Greenland which is partly separated from the
+North American craton by low wavespeed structures beneath Baffin Bay and the Labrador Sea,
+where the North American craton nicely follows the coastline.
+In the Northeast corner of the maps we see that the Iceland hotspot is very prominent in GLAD-M25 in all depth ranges, similar to S40RTS but largely missing in S362ANI$+$M.
+In the Northwest we see a clear imprint of the Aleutian subduction zone in the 200--400~km depth range, comparable to SL2013NA bu absent in the other global models.
+
+In the East, at 100~km depth,
+we see ageing of the Atlantic lithosphere, comparable to the other global models~\citep{muller2008, schaeffer2014imaging}.
+All models show fast anomalies beneath Newfoundland and Nova Scotia extending to depths of 300~km.
+The Bermuda hotspot shows a very nice slow wavespeed impression,
+getting sharper and stronger at depths of 200~km and 300~km (note differences in the scales of the maps).
+The Caribbean slab, a relatively young subduction zone, is clearly
+visible in our model in the 200--400~km depth range.
+At greater depths,
+GLAD-M25 shows a very distinct image of the Farallon slab,
+but since it goes well beyond the depth range of this comparison,
+we return to this feature in Section~\ref{section:slabs}.
 
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
-  \caption{Map views of $V_s$ variations of North America at various depths
-  for our model GLAD-M25(first column) and several global(S362ANI$+$M and S40RTS)
-  and regional(US22\citep{zhu2017radial} and SL2013NA\citep{schaeffer2014imaging})
-  models. Green circles denotes the locations of hotspots. For SL2013NA, we
-  showed the 610km instead of 600km due to its own mesh.}
+  \caption{Map views of isotropic shear wavespeed variations beneath North America 
+  for model GLAD-M25 (first column) and several global (S362ANI$+$M and S40RTS)
+  and regional~\citep[US22;][]{zhu2017radial} and~\citep[SL2013NA;][]{schaeffer2014imaging}
+  models. Green circles denote the locations of hotspots. For SL2013NA, we
+  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}
 \label{fig:america-vs}
@@
 
-Fig.\ref{fig:europe-vs} shows the isotropic $V_s$ structures at Europe. As
-comparisons, we also showed S362ANI$+$M, S40RTS and one regional model EU60
-\citep{zhu2015seismic}. Compared to two global models, it is clear that
-our model is much sharper at few locations. At 100 and 200km, Eifel
-hotspot is clearly seen in our models, as well as in EU60. At 400km
-and 600km, the subduction is very consistent between GLAD-M25 and EU60,
-with the curved shape at the lower bottom of the figure,
-while S362ANI$+$M shows very smooth shape and S40RTS shows much smaller 
-perturbation values. Besides, at 400km, GLAD-M25 is enhancing Iceland
-compared to S362ANI$+$M.
+Fig.~\ref{fig:europe-vs} shows isotropic shear wavespeed perturbations beneath Europe.
+For comparison,
+we again include the two global models S362ANI$+$M and S40RTS,
+as well as regional model EU60~\citep{zhu2015seismic},
+which is based on adjoint tomography.
+Again there is good agreemment with the two global models with regards to the longer wavelength structure,
+although the Iceland hotspot is less prominent in S362ANI$+$M.
+In the 100--200~km depth range we see the Massif Central, the Eiffel hotspot,
+and the Central Slovakia Volcanic Field as distinctly slow anomalies,
+in agreement with EU60.
+In the 400--600~km depth range,
+GLAD-M25 is again in good agreement with~EU60,
+featuring past subduction in the Mediterranean,
+including the present-day Aegean slab.
 
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
-  \caption{Map views of $V_s$ variations of Europe at various depths for our
-  model GLAD-M25(first column) and global(S362ANI$+$M and S40RTS) and
-  regional(EU60\citep{zhu2015seismic}) models. For EU60, the range of color
-  bar is 4\% for all depths, which is labeled in the right bottom of the figures.}
+  \caption{Map views of isotropic shear wavespeed variations beneath Europe for   
+  model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
+  one regional model~\citep[EU60;][]{zhu2015seismic}. For EU60, the range of the color
+  bar is 4\% at all depths, as indicated in the bottom right bottom of the panels.}
 \label{fig:europe-vs}
@@
 
-Asia has a very complicated tectonic settings, containing
-the interaction among Indian, Euroasian, Australia, Pacific and Philippine
-plates. Even though we don't have a significant large number of high
-event-response stations at this region(compared to Europe and North
-America), our inversion is compensated by the large number of temporary
-arrays and earthquakes.
-
-Our model at Asian region is plotted on Fig.\ref{fig:asia-vs},
-together with S362ANI$+$M, S40RTS and EARA2014\cite{chen2015multiparameter}.
-EARA2014 is a regional 3D anisotropic tomographic model using adjoint
-methods, comprising 1.7million frequency-dependent traveltime
-measurements from 227 earthquakes recorded by 1869 seismic stations.
-It has superior data coverage, mainly by incorporating the China
-Seismic Array in this area.
-
-The southwestern part of China is featured by the Himalayas mountain,
-which is 
-a shallow expression of the collision between India and Euroasian plate. Our
-models shows a strong high-velocity anomalies near the plate boundary, and this
-anomaly has all the way extending from 100km to 600km depth. With the increase
-of depth, the high-velocity regions get sharper, indicating the narrowing
-root of subduction plate. The high-elevation Tibetan plateau, sitting to
-the north of Himalaya mountains, shows a relatively low velocity
-comparing to its surroundings, including the Himalayas at its south and
-Tianshan Mountain at is North, which is consistent with other global
+Asia, like Europe, has a complicated tectonic history, involving
+interactions among the Indian, Eurasian, Australian, Pacific, and Philippine
+plates.
+Map views of GLAD-M15 centered on Asia are plotted in Fig.~\ref{fig:asia-vs},
+together with S362ANI$+$M, S40RTS, and regional model EARA2014~\citep{chen2015multiparameter}.
+EARA2014 is a transversely isotropic model based on adjoint
+tomography, assimilating 1.7~million frequency-dependent traveltime
+measurements from 227 earthquakes recorded by 1,869 seismic stations.
+It has superior data coverage, mainly by incorporating data from the China Array.
+
+The Southwestern part of China is dominated by the Himalayas,
+expressing the collision between India and Eurasia.
+GLAD-M25 exhibits strong high wavespeed anomalies in this area, which extend all the way from 100~km to 600~km, narrowing and sharpening with depth,
+in good agreement with EARA2014.
+The Tibetan plateau shows relatively low wavespeeds
+compared to its surroundings, including the Himalayas to its South and
+the Tianshan Mountains to its North, consistent with the other global
 and regional studies.
 
-The southern part of Asia sees the majority tectonic activity between the Philippine
-, EuroAsian and Australia plate. The Sumatra and Java trench, shown as sharp high-velocity
-anomaly in our models below 200km, nicely follows the boundary between Euroasian
-and Australia plates. This feature stays still very sharp at the 600km and extend
-down to 1000km. We will have more detailed discussion about it in the following sections.
-The Malina and Philippine Trench is also much sharper in our model between 200km and
-600km.
-The eastern part has a series of trenches, including Japan Trench, Izu-Bonin Trench,
-Mariana Trench from North to the South. All those features follows perfectly with
-the plate boundary, as emerging features compared the two global models from 200km
-to 400km depth. At 100km depth, our model is strengthening the low-velocity structures
-in the east of Philippine Plate and the anomaly gradually moved to the west at 200km
-depth. In the north, our models shows low-velocity structures associated
-with the Altay-Sayan and Baikai rift systems.
-
-Other than the boundaries, our models also show much more details at the
-intra-plate tectonic activities. It has good correlation of low-velocity regions with
-the Hainan spot and Changbai Volcanoes. Those low-velocity features is prominent at
-shallow depth, but gradually reduce its magnitude down with the increase of
-depth, indicating that those features might be lithosphere's activity rather
-than deep mantle's.
-The Sichuan basin, a very localized high-velocity structures, is extending below
-250km depth. At 600km, most of the models shows a large regions of high-velocities
-near the Philippine plate, indicating the pounding of ancient subducted plates.
+The southern part of Asia shows major tectonic activity between the
+Philippine, Eurasian, and Australia plates.
+The Sunda trench is visible as a distinct high wavespeed anomaly below 200~km,
+nicely following the plate boundary.
+This feature remains very sharp at 600~km and extends
+down to 1000~km.
+We discuss this subducting slab further in Section~\ref{section:slabs}.
+The Manila and Philippine trenches are also much sharper in our model between 200~km and
+600~km than in the other global models, and comparable to EARA2014.
+The eastern edge of the map features a series of trenches following plate boundaries,
+including Japan, Izu-Bonin, and Mariana.
+These slabs are absent in the other global model,
+but feature more prominently in EARA2014.
+Along the northern edge we see low wavespeeds associated with the
+Altai-Sayan and Baikal rift systems.
+In terms of intra-plate activities,
+at shallow depths we see clear low wavespeed impressions of the Hainan and Changbai volcanoes,
+suggesting a lithospheric rather than deeper mantle origin.
+The Sichuan basin, a very localized high-wavespeed structure, extends below
+250~km depth. At 600~km, most models shows a large region of high wavespeed
+beneath the Philippine plate, indicating ponding of ancient subducted plates.
 
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
-  \caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI$+$M and S40RTS) and regional(EARA2014\citep{chen2015multiparameter}) models.}
+  \caption{Map views of shear wavespeed variations beneath Asia for GLAD-M25~(first column),
+  global models S362ANI$+$M (second column) and S40RTS (third column), and regional model EARA2014~\citep[last column;][]{chen2015multiparameter}.}
 \label{fig:asia-vs}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
-  \caption{Map views of $V_p$ variations of South America at various depths for our model GLAD-M25(first column) and several global models, including S362ANI$+$M, LLNL-G3Dv3 and GAP-P4\citep{fukao2013subducted}.}
+  \caption{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M (second column), LLNL-G3Dv3~(third column), and GAP-P4~\citep[last column;][]{fukao2013subducted}.}
 \label{fig:southamerica-vp}
@@
 \subsection{Plumes}
+\label{section:plumes}
 
@@
 
-\subsection{Subductions}
+\subsection{Slabs}
+\label{section:slabs}
 
@@
 
+\appendix
+
+\section{Spherical harmonic model expansion}
+
+{\color{red} Wenjie, to save space, this appendix could also go in the supplementary online material.}
+
+In this appendix we express model GLAD-M25 in a spherical harmonic basis
+to facilitate easy plotting, analysis, and comparisons with other models.
+The resulting spherical harmonic model should only be used for these purposes, not for numerical simulations, which should always be based on the fully 3D spectral-element mesh.
+
+To accomplish the transformation,
+we first need to transform our 3D mesh --- which includes ellipticity, topography \& bathymetry, and undulations on internal boundaries --- into a spherical volume.
+After these adjustments, we obtain a spectral element mesh for a perfect sphere,
+that is, the sort of mesh we use for spherically symmetric earth models, such as PREM~\citep{PREM}.
+
+In the spherical mesh, the model may be expressed in the form
+\begin{equation}
+    m(\mathbf{x})=\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}m^{\alpha\beta\gamma}\,h_{\alpha}(\xi)\,h_{\beta}(\eta)\,h_{\gamma}(\zeta)\,
+    \quad ,
+\end{equation}
+where~$h_\alpha$ denotes a Lagrange polynomial, and where we have used the invertible mapping
+\begin{equation}
+    \mathbf{x}=\mathbf{x}(\xi,\eta,\zeta)
+    \label{eq:map}
+\end{equation}
+between spatial points~$\mathbf{x}=\{x,y,z\}$ and Gauss-Lobatto-Legendre (GLL) points in the reference element~$\{\xi,\eta,\zeta\}$~\citep{KoTr99}.
+
+Our goal is to expand our spectral-element model in a spherical harmonic basis, i.e.,
+\begin{equation}
+    m(\mathbf{x})=\sum_{n=0}^N\sum_{\ell = 0}^L\sum_{m=-\ell}^\ell {}_nC_{\ell m}\,R_n(r)\,Y_{\ell m}(\theta,\phi)
+    \quad ,
+    \label{eq:m}
+\end{equation}
+where~$r$ denotes the radius, $\theta$ colatitude, and~$\phi$ longitude.
+We choose a radial basis of the form~$R_n(r)$\,, $n=0,\ldots,N$\,,
+e.g., layers or B-splines.
+These radial basis functions need to be chosen sufficiently dense to mimic the density of the radial spectral element mesh.
+The radial basis may or may not be orthogonal,
+i.e.,
+\begin{equation}
+    \int_b^a R_{n'}(r)\,R_{n}(r)\,r^2\mathrm{d}r = A_{n'n}
+    \quad ,
+    \label{eq:R}
+\end{equation}
+where~$b$ denotes the radius of the CMB and~$a$ the free surface.
+The matrix elements~$A_{n'n}$ define a positive definite matrix which is invertible.
+As lateral basis functions we use fully normalized spherical harmonics~$Y_{\ell m}(\theta,\phi)$\,, $\ell=0,\ldots,L$ and $m=\mbox{}-\ell,\ldots,\ell$\,, i.e.,~\citep{DT98}
+\begin{equation}
+    \int_0^{2\pi}\int_0^\pi Y^*_{\ell'm'}(\theta,\phi)\,Y_{\ell m}(\theta,\phi)\,\sin\theta\,\mathrm{d}\theta\,\mathrm{d}\phi = \delta_{\ell' \ell}\,\delta_{m'm}
+    \quad ,
+    \label{eq:Y}
+\end{equation}
+where an asterisk denotes complex conjugation.
+The maximum degree~$L$ needs to be chosen to resolve the spectral-element mesh laterally.
+
+To obtain the expansion coefficients~${}_nC_{\ell m}$\,, we multiply Eqn.~(\ref{eq:m}) by
+$R_{n'}(r)\,Y^*_{\ell' m'}(\theta,\phi)$ and integrate over the volume of the mantle and crust,~$V$\,, using Eqns.~(\ref{eq:R} and~(\ref{eq:Y}):
+\begin{equation}
+    \int_V m(\mathbf{x})\,R_{n'}(r)\,Y^*_{\ell' m'}(\theta,\phi)\,\mathrm{d}^3\mathrm{x}=\sum_{n=0}^N {}_nC_{\ell' m'}\,A_{n'n}
+    \quad ,
+\end{equation}
+We evaluate the integral on the left using GLL quadrature~\citep{KoTr99}:
+\begin{equation}
+    \sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,Y_{\ell'm'}^{*\,\alpha\beta\gamma}
+    =\sum_{n=0}^N {}_nC_{\ell' m'}\,A_{n'n}
+    \quad .
+\end{equation}
+Here~$\omega_\alpha$ denotes a GLL quadrature weight,
+$J_{\alpha\beta\gamma}$ the Jacobian of the mapping~(\ref{eq:map}) evaluated on the GLL points,
+and $R_{n'}^{\alpha\beta\gamma}$ and $Y_{\ell'm'}^{*\,\alpha\beta\gamma}$ the values of the radial and spherical harmonic basis functions at a GLL point.
+
+Finally, the desired model coefficients may be obtained ---one combination of $n$\,, $\ell$\,, and $m$ at a time--- via
+\begin{equation}
+    {}_nC_{\ell m}=\sum_{n'}A^{-1}_{nn'}\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,Y_{\ell m}^{*\,\alpha\beta\gamma}
+    \quad ,
+    \label{eq:Cnlm}
+\end{equation}
+where~$A^{-1}$ denotes the inverse of the~$N\times N$ matrix~$A$.
+Expressions of the form~(\ref{eq:Cnlm}) are commonplace in spectral-element simulations,
+and thus easily calculated.
+The power per degree~$\ell$ may be calculated via~\citep[][Eqn.~B.95]{DT98}
+\begin{equation}
+    \sigma_\ell^2=\frac{1}{2\ell+1}\,\sum_{n=0}^N\sum_{m=-\ell}^\ell|{}_nC_{\ell m}|^2
+    \quad .
+\end{equation}
+
+Instead of the complex spherical harmonic model expansion~(\ref{eq:m}),
+we may wish to use a real spherical harmonic expansion of the form~\citep[][Section~B.8, Eqn.~B.99]{DT98}
+\begin{equation}
+\begin{split}
+    m(\mathbf{x}) \ = & \ \sum_{n=0}^N\sum_{\ell = 0}^L \left[ {}_na_{\ell 0}\,R_n(r)\,X_{\ell 0}(\theta)
+   +\sqrt{2}\sum_{m=1}^\ell R_n(r)\,({}_na_{\ell m}\,\cos m\phi+{}_nb_{\ell m}\,\sin m\phi)\,X_{\ell m}(\theta)\right]
+    \quad ,
+\end{split}
+    \label{eq:mreal}
+\end{equation}
+where~\citep[][Eqn.~B.30]{DT98}
+\begin{equation}
+    Y_{\ell m}(\theta,\phi)=X_{\ell m}(\theta)\exp(i m\phi)
+    \quad ,
+\end{equation}
+and where
+\begin{equation}
+    {}_na_{\ell 0}=\sum_{n'}A^{-1}_{nn'}\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,X_{\ell m}^{\alpha\beta\gamma}
+    \quad ,
+\end{equation}
+and for~$1\le m\le \ell$
+\begin{equation}
+    {}_na_{\ell m}=\sqrt{2}\,\sum_{n'}A^{-1}_{nn'}\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,X_{\ell m}^{\alpha\beta\gamma}\,(\cos m \phi)^{\alpha\beta\gamma}
+    \quad ,
+\end{equation}
+\begin{equation}
+    {}_nb_{\ell m}=\sqrt{2}\,\sum_{n'}A^{-1}_{nn'}\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,X_{\ell m}^{\alpha\beta\gamma}\,(\sin m \phi)^{\alpha\beta\gamma}
+    \quad .
+\end{equation}
+The power per degree~$\ell$ may then be calculated via~\citep[][Eqn.~B.104]{DT98}
+\begin{equation}
+    \sigma_\ell^2=\frac{1}{2\ell+1}\,\sum_{n=0}^N\left[{}_na_{\ell 0}^2+\sum_{m=1}^\ell({}_na_{\ell m}^2+{}_nb_{\ell m}^2)\right]
+    \quad .
+\end{equation}
+
 \newpage
+
 \bibliographystyle{gji}

### 2018-10-21 main.tex
add Europe setion

@@
 
-{\color{red} Wenjie: Make sure the variance reductions are calculated as ln (Phi\_M25 / Phi\_M15).}
-{\color{red} Wenjie: I was using (Phi\_M25 - Phi\_M15) / Phi\_M15. So let me modify it?}
-{\color{blue} Wenjie: yes please. It will only change things slightly, if at all. You need to do the same for Table~\ref{table:misfit_reduction_M15_M25_360}.}
+%{\color{red} Wenjie: Make sure the variance reductions are calculated as ln (Phi\_M25 / Phi\_M15).}
+%{\color{red} Wenjie: I was using (Phi\_M25 - Phi\_M15) / Phi\_M15. So let me modify it?}
+%{\color{blue} Wenjie: yes please. It will only change things slightly, if at all. You need to do the same for Table~\ref{table:misfit_reduction_M15_M25_360}.}
+
 \begin{table}[!htb]
@@
     \hline
-    17--40~s  body waves    &   17.4 (31.1)   &       21.1 (37.1) &       24.6 (42.2) \\
-    40--100~s body waves    &   16.8 (31.3)  &       21.3 (40.2)  &       21.7 (42.0) \\
-    40--100~s surface waves &   28.5 (50.1)  &       28.3 (51.1) &       28.4 (53.8)  \\
-    90--250~s surface waves &   14.5 (36.2)  &       13.4 (38.8) &       25.7 (38.6) \\
+    %17--40~s  body waves    &   17.4 (31.1)   &       21.1 (37.1) &       24.6 (42.2) \\
+    %40--100~s body waves    &   16.8 (31.3)  &       21.3 (40.2)  &       21.7 (42.0) \\
+    %40--100~s surface waves &   28.5 (50.1)  &       28.3 (51.1) &       28.4 (53.8)  \\
+    %90--250~s surface waves &   14.5 (36.2)  &       13.4 (38.8) &       25.7 (38.6) \\
+    17--40~s  body waves    &   19.1 (37.3)   &       23.7 (46.3) &       28.2 (54.8) \\
+    40--100~s body waves    &   18.3 (37.5)   &       24.0 (51.4) &       24.5 (54.5) \\
+    40--100~s surface waves &   33.6 (69.6)   &       33.3 (71.5) &       33.5 (77.2) \\
+    90--250~s all waves &   15.7 (44.9)   &       14.4 (49.1) &       29.6 (48.7) \\
     \hline
@@
   \caption{Changes in fit in the twelve measurement categories
-between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
+  between the new model, GLAD-M25, and its starting model, GLAD-M15,
+  and, in parentheses, between GLAD-M25 and model S362ANI combined with
+  CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
   \label{table:misfit_reduction_M15_M25}
@@
 For comparison,
-we again include the two global models S362ANI$+$M and S40RTS,
-as well as regional model EU60~\citep{zhu2015seismic},
-which is based on adjoint tomography.
-Again there is good agreemment with the two global models with regards to the longer wavelength structure,
-although the Iceland hotspot is less prominent in S362ANI$+$M.
-In the 100--200~km depth range we see the Massif Central, the Eiffel hotspot,
-and the Central Slovakia Volcanic Field as distinctly slow anomalies,
-in agreement with EU60.
-In the 400--600~km depth range,
-GLAD-M25 is again in good agreement with~EU60,
-featuring past subduction in the Mediterranean,
-including the present-day Aegean slab.
+
+In addition to our model GLAD-M25, S362ANI+M and S40RTS, we included a regional
+tomography model EU60\citep{zhu2015seismic} into our comparison. The EU60 uses
+adjoint methods to iteratively inverse the crust and upper mantle strcuture
+beneath the European continent and North Atlantic Ocean, by assimilating
+190 earthquakes and 745 seismic station.
+
+Europe is featured by the Trans-European Suture Zone(TESZ), seperating the
+Precambrian East Europen Craton(EEC) in the northeast and the Phanerozoic
+europe in the southwest.  The TESZ is very consistent across all the models,
+even though is much sharper in GLAD-M25 and EU60.
+
+In the north, we observed the high velocity anomaly beneath Central Graben in the
+North Sea, and clearly seperated from the EEC bounded at the western north, which is
+explained as the lithospheric drip with delamination, as explained in
+\cite{zhu2015seismic}.
+
+In the south at the Mediterranean region, the tectonic settings is complex with the
+existence of several regional plates. In the west of Mediterranean ocean, there is
+Appennines-Maghrebides subductions, with the subduction retreat direction from South
+(older, >30Ma)to North(younger, present), with its western border of back-arc basin
+following along the coastline of East Spain and South France
+\citep{Giordano2017Magmatic}. In our model, this is shown as fast velocity starting
+from 400km and extend all the way to the mantle transition zones at 600km beneath the
+Mediterranean Ocean, nicely following its west and east boundaries. At shallower depth
+such as 100km, we observe low velocity structures, which is explained as the
+back-arc extension associated with the roll-back. Compared to S362ANI+M and S40RTS,
+our model shows much sharper features for the tectonic structures mentioned above.
+
+Moving furture to the east, at about 400km, there is clearlyfast anomaly lie beneath
+the Dinarides Mountains,
+sepating the Adria plate and Pannonian Basin and indicating the subudction of Adria
+plate into the Euroasian plate. This anomaly get sharper at 600km. The southern
+part of it interacts with the Hellenic Arc subductions, which penetrate the mantle
+trasition zones and extend below 1,000 kms in our model. We will discuss the Hellenic
+Arc in details in the later sections. The Pannonia Basin is featured by low velocity
+anomaly at the depth from 100 to 250km, then gradually transferred to high velocity
+due to the subduction of Adria plate. The Anatolia plate is shown as slow velocity
+anomaly in our model, sharpened from two other global models.
+
+In the Central Europe, there is Cenozoic Ridge System, featured by the low velocity
+anomaly, starting from Massif Central and extending to Eifel. Both the EU60 and
+GLAD-M25 found slow anomaly lying beneath the northern par of Rhine Graben, explained
+as the reservoir that fuels the Eifel hotspot, from 100km to 250km.
+
+In the north of Atlantic Ocean, our model strengthed the slow anlomaly near the
+Atlantic Ocean Ridge, especially at the Iceland and Azores. The Iceland, becomes
+much strong in our model in the upper mantle from 250km to 400km, compared to
+S362ANI+M, extending all the way to the mantle-transition zone. On the other hand,
+Azores, is a much shallower hotspot, with the slow anomaly extend at about 250km.
 

### 2018-10-21 main.tex
Updates from ShareLaTeX

@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
+  \caption{Map views of isotropic shear wavespeed variations beneath North America 
+  for model GLAD-M25 (first column) and several global (S362ANI$+$M and S40RTS)
+  and regional~\citep[US22;][]{zhu2017radial} and~\citep[SL2013NA;][]{schaeffer2014imaging}
+  models. Green circles denote the locations of hotspots. For SL2013NA, we
+  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}
+\label{fig:america-vs}
+\end{figure}
+
 The deployment of USArray has dramatically increased data overage across the
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
-  \caption{Map views of isotropic shear wavespeed variations beneath North America 
-  for model GLAD-M25 (first column) and several global (S362ANI$+$M and S40RTS)
-  and regional~\citep[US22;][]{zhu2017radial} and~\citep[SL2013NA;][]{schaeffer2014imaging}
-  models. Green circles denote the locations of hotspots. For SL2013NA, we
-  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}
-\label{fig:america-vs}
-
-\end{figure}
-
 \subsubsection{Europe}
@@
 Fig.~\ref{fig:europe-vs} shows isotropic shear wavespeed perturbations beneath Europe.
-For comparison,
-
 In addition to our model GLAD-M25, S362ANI+M and S40RTS, we included a regional
 tomography model EU60\citep{zhu2015seismic} into our comparison. The EU60 uses
-adjoint methods to iteratively inverse the crust and upper mantle strcuture
+adjoint methods to iteratively inverse the crust and upper mantle structure
 beneath the European continent and North Atlantic Ocean, by assimilating
@@
 
-Europe is featured by the Trans-European Suture Zone(TESZ), seperating the
-Precambrian East Europen Craton(EEC) in the northeast and the Phanerozoic
-europe in the southwest.  The TESZ is very consistent across all the models,
+Europe is featured by the Trans-European Suture Zone(TESZ), separating the
+Precambrian East European Craton(EEC) in the northeast and the Phanerozoic
+Europe in the southwest.  The TESZ is very consistent across all the models,
 even though is much sharper in GLAD-M25 and EU60.
@@
 In the north, we observed the high velocity anomaly beneath Central Graben in the
-North Sea, and clearly seperated from the EEC bounded at the western north, which is
+North Sea, and clearly separated from the EEC bounded at the western north, which is
 explained as the lithospheric drip with delamination, as explained in
@@
 
-Moving furture to the east, at about 400km, there is clearlyfast anomaly lie beneath
-the Dinarides Mountains,
-sepating the Adria plate and Pannonian Basin and indicating the subudction of Adria
-plate into the Euroasian plate. This anomaly get sharper at 600km. The southern
+Moving further to the east, at about 400km, there is clear fast anomaly lie
+beneath the Dinarides Mountains, separating the Adria plate and Pannonian Basin, indicating the subduction of Adria plate into the Euroasian plate.
+This anomaly get sharper at 600km. The southern
 part of it interacts with the Hellenic Arc subductions, which penetrate the mantle
-trasition zones and extend below 1,000 kms in our model. We will discuss the Hellenic
-Arc in details in the later sections. The Pannonia Basin is featured by low velocity
+transition zones and extend below 1,000 km in our model. We will discuss the Hellenic
+Arc in details in the later sections. The Pannonian Basin is featured by low velocity
 anomaly at the depth from 100 to 250km, then gradually transferred to high velocity
@@
 
-In the north of Atlantic Ocean, our model strengthed the slow anlomaly near the
+In the north of Atlantic Ocean, our model strengthened the slow anomaly near the
 Atlantic Ocean Ridge, especially at the Iceland and Azores. The Iceland, becomes

### 2018-10-22 main.tex
add south america section

@@
 
-In the North,
-we see a high wavespeed craton beneath Greenland which is partly separated from the
-North American craton by low wavespeed structures beneath Baffin Bay and the Labrador Sea,
-where the North American craton nicely follows the coastline.
-In the Northeast corner of the maps we see that the Iceland hotspot is very prominent in GLAD-M25 in all depth ranges, similar to S40RTS but largely missing in S362ANI$+$M.
-In the Northwest we see a clear imprint of the Aleutian subduction zone in the 200--400~km depth range, comparable to SL2013NA bu absent in the other global models.
+In the North, we see a high wavespeed craton beneath Greenland which is partly
+separated from the North American craton by low wavespeed structures beneath
+Baffin Bay and the Labrador Sea, where the North American craton nicely follows
+the coastline.
+In the Northeast corner of the maps we see that the Iceland hotspot is very
+prominent in GLAD-M25 in all depth ranges, similar to S40RTS but largely missing
+in S362ANI$+$M. In the Northwest we see a clear imprint of the Aleutian
+subduction zone in the 200--400~km depth range, comparable to SL2013NA but absent
+in the other global models.
 
 In the East, at 100~km depth,
-we see ageing of the Atlantic lithosphere, comparable to the other global models~\citep{muller2008, schaeffer2014imaging}.
-All models show fast anomalies beneath Newfoundland and Nova Scotia extending to depths of 300~km.
-The Bermuda hotspot shows a very nice slow wavespeed impression,
-getting sharper and stronger at depths of 200~km and 300~km (note differences in the scales of the maps).
+we see ageing of the Atlantic lithosphere, comparable to the other global models
+~\citep{muller2008, schaeffer2014imaging}.
+All models show fast anomalies beneath Newfoundland and Nova Scotia extending to
+depths of 300~km. The Bermuda hotspot shows a very nice slow wavespeed impression,
+getting sharper and stronger at depths of 200~km and 300~km (note differences in
+the scales of the maps).
 The Caribbean slab, a relatively young subduction zone, is clearly
@@
 Moving further to the east, at about 400km, there is clear fast anomaly lie
-beneath the Dinarides Mountains, separating the Adria plate and Pannonian Basin, indicating the subduction of Adria plate into the Euroasian plate.
+beneath the Dinarides Mountains, separating the Adria plate and Pannonian Basin,
+indicating the subduction of Adria plate into the Euroasian plate.
 This anomaly get sharper at 600km. The southern
@@
 expressing the collision between India and Eurasia.
-GLAD-M25 exhibits strong high wavespeed anomalies in this area, which extend all the way from 100~km to 600~km, narrowing and sharpening with depth,
+GLAD-M25 exhibits strong high wavespeed anomalies in this area,
+which extend all the way from 100~km to 600~km, narrowing and sharpening with depth,
 in good agreement with EARA2014.
@@
 \subsubsection{South America}
-...to be done...
 
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
-  \caption{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M (second column), LLNL-G3Dv3~(third column), and GAP-P4~\citep[last column;][]{fukao2013subducted}.}
+  \caption{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M, LLNL-G3Dv3~\citep{}, and GAP-P4~\citep{fukao2013subducted}.}
 \label{fig:southamerica-vp}
@@
 \end{figure}
+
+Fig.\ref{fig:southamerica-vp} shows the $V_p$ velocity in our model, togthere with 3 global models,
+S362ANI+M, LLNL-G3Dv3\citep{}, GAP-P4\citep{fukao2013subducted}, while the latter two are
+global $V_p$ models.
+
+At 100km depth, the northern part of South America is covered by large area
+of lithosphere craton, showing fast wave anomaly except GAP-P4. The fast anomaly
+stays strong in LLNL-G3Dv3 while for GLAD-M25
+and S362ANI+M it disappear at such depth.
+At 300km, we are see a sharpened fast anomaly in the south subduction area
+in GLAD-M25 compared to S372ANI+M. However, the shape and strength are very close
+between GLAD-M25 and LLNL-G3Dv3 models. Moving to even larger depth, the features of
+subcutions becomes divergent between the north Peruvian slab and south Chilean slab.
+At 600km, we observed a large chunck of fast anomaly in the Chilean slab,
+indicating the slab is trapped and stagnant in the mantle transition zone. However,
+the Peruvian slabs has penertrated the mantle transition zone and extend till 1000,
+reaching the uppermost part of lower mantle, which is consistent with GAP-P4
+\citep{fukao2013subducted}.
+
+Besides, in the Pacific and Nazca plate, our models is sharpening the Galapagos,
+San Felix and Juan Fernandez hotspot. In the Scotia plate, our models shows a very
+strong expression of Scotia Arc subduciton till 1000km, which is barely observable
+in other models. In the Carribean plate, we also observed fast anomaly, indicating
+the carribean subduction.
 
@@
 
+\newpage
+
 \appendix

### 2018-10-22 main.tex
Updates from ShareLaTeX

@@
 
-Fig.\ref{fig:southamerica-vp} shows the $V_p$ velocity in our model, togthere with 3 global models,
-S362ANI+M, LLNL-G3Dv3\citep{}, GAP-P4\citep{fukao2013subducted}, while the latter two are
-global $V_p$ models.
+Fig.\ref{fig:southamerica-vp} shows the $V_p$ velocity in our model, together with 3
+global models, S362ANI+M, LLNL-G3Dv3\citep{}, GAP-P4\citep{fukao2013subducted},
+while the latter two are global $V_p$ models.
 
@@
 between GLAD-M25 and LLNL-G3Dv3 models. Moving to even larger depth, the features of
-subcutions becomes divergent between the north Peruvian slab and south Chilean slab.
-At 600km, we observed a large chunck of fast anomaly in the Chilean slab,
+subductions becomes divergent between the north Peruvian slab and south Chilean slab.
+At 600km, we observed a large chunk of fast anomaly in the Chilean slab,
 indicating the slab is trapped and stagnant in the mantle transition zone. However,
-the Peruvian slabs has penertrated the mantle transition zone and extend till 1000,
+the Peruvian slabs has penetrated the mantle transition zone and extend till 1000,
 reaching the uppermost part of lower mantle, which is consistent with GAP-P4
@@
 San Felix and Juan Fernandez hotspot. In the Scotia plate, our models shows a very
-strong expression of Scotia Arc subduciton till 1000km, which is barely observable
-in other models. In the Carribean plate, we also observed fast anomaly, indicating
-the carribean subduction.
+strong expression of Scotia Arc subduction till 1000km, which is barely observable
+in other models. In the Caribbean plate, we also observed fast anomaly, indicating
+the Caribbean subduction.
 

### 2018-10-28 main.tex
Updates from ShareLaTeX

@@
 continental United States.
-In this section, we compare GLAD-M25 in this region with
+In this section, we compare GLAD-M25 in this region 
 with two global models, S362ANI$+$M and S40RTS, and two regional models,
@@
 
-At a depth of 100~km, we observed that the edges of the craton are sharper in
+At a depth of 100~km, we observe that the edges of the craton are sharper in
 GLAD-M15 than in the other two global models,
@@
 Fig.~\ref{fig:europe-vs} shows isotropic shear wavespeed perturbations beneath Europe.
-In addition to our model GLAD-M25, S362ANI+M and S40RTS, we included a regional
-tomography model EU60\citep{zhu2015seismic} into our comparison. The EU60 uses
-adjoint methods to iteratively inverse the crust and upper mantle structure
-beneath the European continent and North Atlantic Ocean, by assimilating
-190 earthquakes and 745 seismic station.
-
-Europe is featured by the Trans-European Suture Zone(TESZ), separating the
-Precambrian East European Craton(EEC) in the northeast and the Phanerozoic
-Europe in the southwest.  The TESZ is very consistent across all the models,
+In addition to models GLAD-M25, S362ANI$+$M, and S40RTS, we included regional
+model EU60~\citep{zhu2015seismic} for comparison.
+EU60 is the result of adjoint tomography of the crust and upper mantle
+beneath the European continent and the North Atlantic based on the assimilation of data from
+190 earthquakes recorded by 745 seismographic station.
+
+A defining tectonic feature of Europe is the Trans-European Suture Zone~(TESZ),
+also known as the Tornquist-Teisseyre Zone,
+separating the  Precambrian East European Craton~(EEC) in the Northeast from Phanerozoic Europe in the Southwest.
+The TESZ is very consistent across all models,
 even though is much sharper in GLAD-M25 and EU60.
 
-In the north, we observed the high velocity anomaly beneath Central Graben in the
-North Sea, and clearly separated from the EEC bounded at the western north, which is
-explained as the lithospheric drip with delamination, as explained in
-\cite{zhu2015seismic}.
-
-In the south at the Mediterranean region, the tectonic settings is complex with the
-existence of several regional plates. In the west of Mediterranean ocean, there is
-Appennines-Maghrebides subductions, with the subduction retreat direction from South
-(older, >30Ma)to North(younger, present), with its western border of back-arc basin
-following along the coastline of East Spain and South France
-\citep{Giordano2017Magmatic}. In our model, this is shown as fast velocity starting
-from 400km and extend all the way to the mantle transition zones at 600km beneath the
-Mediterranean Ocean, nicely following its west and east boundaries. At shallower depth
-such as 100km, we observe low velocity structures, which is explained as the
-back-arc extension associated with the roll-back. Compared to S362ANI+M and S40RTS,
-our model shows much sharper features for the tectonic structures mentioned above.
-
-Moving further to the east, at about 400km, there is clear fast anomaly lie
-beneath the Dinarides Mountains, separating the Adria plate and Pannonian Basin,
-indicating the subduction of Adria plate into the Euroasian plate.
-This anomaly get sharper at 600km. The southern
-part of it interacts with the Hellenic Arc subductions, which penetrate the mantle
-transition zones and extend below 1,000 km in our model. We will discuss the Hellenic
-Arc in details in the later sections. The Pannonian Basin is featured by low velocity
-anomaly at the depth from 100 to 250km, then gradually transferred to high velocity
-due to the subduction of Adria plate. The Anatolia plate is shown as slow velocity
-anomaly in our model, sharpened from two other global models.
-
-In the Central Europe, there is Cenozoic Ridge System, featured by the low velocity
-anomaly, starting from Massif Central and extending to Eifel. Both the EU60 and
-GLAD-M25 found slow anomaly lying beneath the northern par of Rhine Graben, explained
-as the reservoir that fuels the Eifel hotspot, from 100km to 250km.
-
-In the north of Atlantic Ocean, our model strengthened the slow anomaly near the
-Atlantic Ocean Ridge, especially at the Iceland and Azores. The Iceland, becomes
-much strong in our model in the upper mantle from 250km to 400km, compared to
-S362ANI+M, extending all the way to the mantle-transition zone. On the other hand,
-Azores, is a much shallower hotspot, with the slow anomaly extend at about 250km.
+At depths of 100---250~km we observe high wavespeeds beneath the Central Graben in the North Sea, which is clearly separated from the EEC.
+The tectonic history of the Mediterranean is complex,
+involving several regional plates and multiple past and present subduction zones.
+We see slab ponding in the transition zone beneath the western Mediterranean associated with slab roll-back of the Appennines-Maghrebides subduction zone~\citep{Giordano2017Magmatic}.
+At shallower depths, we see low wavespeeds along its western border,
+which are interpreted as back-arc extension associated with the roll-back. Compared to S362ANI$+$M and S40RTS,
+our model shows much sharper features for these tectonic structures.
+
+In the Eastern Mediterranean, there is a distinct fast anomaly beneath the 
+Dinarides Mountains, separating the Adria plate from the Pannonian Basin,
+indicating subduction of the Adria plate beneath the Eurasian plate.
+This anomaly gets sharper at 600~km depth.
+Its southern part interacts with the Hellenic slab, which penetrates the mantle transition zone and extends below 1,000~km in our model.
+We discuss the Hellenic Arc further in Section~\ref{section:slabs}.
+The Pannonian Basin is characterized by a low wavespeed
+anomaly at depths from 100~km to 250~km.
+In this depth range we also see slow wavespeeds beneath Anatolia,
+stronger than in the two other global models.
+
+In Central Europe we note the Cenozoic Ridge System, characterized by low  wavespeeds from the Massif Central to the Eifel. Both EU60 and
+GLAD-M25 exhibit a slow anomaly beneath the northern part of the Rhine Graben, which is interpreted as the reservoir that fuels the Eifel hotspot.
+
+Beneath the Atlantic Ocean, our model strengthens slow anomalies beneath the ridges, especially underneath Iceland and the Azores.
+Compared to S362ANI$+$M, Iceland becomes
+much stronger in the upper mantle at depths from 250~km to 400~km, extending all the way to the mantle-transition zone.
+The Azores represent a much shallower hotspot, with a maximum depth of about 250~km.
 
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
-  \caption{Map views of isotropic shear wavespeed variations beneath Europe for   
-  model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
+  \caption{Map views of isotropic shear wavespeed variations beneath Europe for model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
   one regional model~\citep[EU60;][]{zhu2015seismic}. For EU60, the range of the color
@@
 Fig.\ref{fig:southamerica-vp} shows the $V_p$ velocity in our model, together with 3
-global models, S362ANI+M, LLNL-G3Dv3\citep{}, GAP-P4\citep{fukao2013subducted},
+global models, S362ANI$+$M, LLNL-G3Dv3\citep{}, GAP-P4\citep{fukao2013subducted},
 while the latter two are global $V_p$ models.
@@
 stays strong in LLNL-G3Dv3 while for GLAD-M25
-and S362ANI+M it disappear at such depth.
+and S362ANI$+$M it disappear at such depth.
 At 300km, we are see a sharpened fast anomaly in the south subduction area

### 2018-12-04 main.tex
update figures
Updates from ShareLaTeX

@@
 
+\section{Spherically symmetric average model}
+
+In this appendix we determine the spherically symmetric (radial) average of model GLAD-M25.
+To accomplish this,
+we first need to transform the 3D spectral-element mesh --- which includes ellipticity, topography \& bathymetry, and undulations on internal boundaries --- into a spherical volume.
+After these adjustments, we obtain a spectral-element mesh for a perfect cubed sphere~\citep{KoTr02a}.
+
+In the spherical mesh, the model may be expressed in the form
+\begin{equation}
+    m(\mathbf{x})=\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}m^{\alpha\beta\gamma}\,h_{\alpha}(\xi)\,h_{\beta}(\eta)\,h_{\gamma}(\zeta)\,
+    \quad ,
+\end{equation}
+where~$h_\alpha$ denotes a Lagrange polynomial, and where we have used the invertible mapping
+\begin{equation}
+    \mathbf{x}=\mathbf{x}(\xi,\eta,\zeta)
+\end{equation}
+between spatial points~$\mathbf{x}=\{x,y,z\}$ and Gauss-Lobatto-Legendre (GLL) points in the reference element~$\{\xi,\eta,\zeta\}$~\citep{KoTr99}.
+
+The spherically symmetric part of the model is defined as
+\begin{equation}
+    \overline{m}(r)=\frac{1}{4\pi}\,\int_\Omega m(\mathbf{x})\,\mathrm{d} \Omega
+    \quad,
+\end{equation}
+where~$r$ denotes the radius and~$\Omega$ the unit sphere.
+
+Using 2D GLL quadrature~\citep{KoTr99} in the unit sphere,
+the radial average may be determined numerically via GLL quadrature:
+\begin{equation}
+    \overline{m}(r)=\frac{1}{4\pi\,r^2}\,\sum_{\alpha,\beta}\omega_\alpha\omega_\beta\,m^{\alpha\beta}(r)\,J^{\alpha\beta}(r)
+    \quad.
+    \label{eq:radial_average}
+\end{equation}
+Here~$\alpha$ and~$\beta$ denote GLL points in the sphere with radius~$r$\,,
+$\omega_\alpha$ denotes a GLL quadrature weight, and $J^{\alpha\beta}(r)$ is the 2D Jacobian of the mapping to the sphere.
+It is important to carry out the summations in~(\ref{eq:radial_average}) at the elemental level to ensure that first-order discontinuities are honored in the process.
+
+Figure~\ref{fig:global-average} shows the resulting radial averages of the isotropic shear and compressional wavespeeds for model~GLAD-M25
+compared to 1D starting model~STW105~\citep{kustowski2008anisotropic} and PREM~\citep{PREM}.
+The radial average of~GLAD-M25 remains very close to the radial starting model~STW105.
+The main difference between these two models and~PREM
+is the absence of the 220~km discontinuity and a lower~$V_p/V_s$ ratio in the top 200~km.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/1d_profile.pdf}
+  \caption{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
+  The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}
+  \label{fig:global-average}
+\end{figure}
+
 \section{Spherical harmonic model expansion}
@@
 To accomplish the transformation,
-we first need to transform our 3D mesh --- which includes ellipticity, topography \& bathymetry, and undulations on internal boundaries --- into a spherical volume.
+we first need to transform the 3D mesh --- which includes ellipticity, topography \& bathymetry, and undulations on internal boundaries --- into a spherical volume.
 After these adjustments, we obtain a spectral element mesh for a perfect sphere,
-that is, the sort of mesh we use for spherically symmetric earth models, such as PREM~\citep{PREM}.
+that is, the sort of mesh used for spherically symmetric earth models, such as PREM~\citep{PREM}.
 

### 2018-12-04 main.tex
add plumes and subduction figures

@@
 
-%\begin{figure}[h]
-%    \centering
-%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
-%    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
-%\end{figure}
+\begin{figure}[h]
+    \centering
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
+    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.}
+\end{figure}
 
@@
 
-\subsection{Slabs}
+\subsection{Subduction Slabs}
 \label{section:slabs}
@@
 In this sections, we will visit some of the well-known subduction zones.
+
+\begin{figure}[h]
+    \centering
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Aeg.png}\label{fig:a}}\\[-4pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Br.png}\label{fig:b}}\\[-4pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Ha.png}\label{fig:c}}\\[-4pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Ne.png}\label{fig:d}}\\[-4pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Wc.png}\label{fig:a}}\\[-4pt]
+    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.}
+\end{figure}
 

### 2018-12-05 main.tex
update plumes and subductions figures

@@
     \centering
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Aeg.png}\label{fig:a}}\\[-4pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Br.png}\label{fig:b}}\\[-4pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Ha.png}\label{fig:c}}\\[-4pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Ne.png}\label{fig:d}}\\[-4pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Wc.png}\label{fig:a}}\\[-4pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Aeg.png}\label{fig:a}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Br.png}\label{fig:b}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:c}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:d}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:a}}\\[-1pt]
     \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.}

### 2019-01-16 main.tex
Updates from ShareLaTeX

@@
 \begin{equation}
-    \int_V m(\mathbf{x})\,R_{n'}(r)\,Y^*_{\ell' m'}(\theta,\phi)\,\mathrm{d}^3\mathrm{x}=\sum_{n=0}^N {}_nC_{\ell' m'}\,A_{n'n}
+    \int_V m(\mathbf{x})\,R_{n'}(r)\,Y^*_{\ell' m'}(\theta,\phi)\,\mathrm{d}^3\mathbf{x}=\sum_{n=0}^N {}_nC_{\ell' m'}\,A_{n'n}
     \quad ,
@@
 and thus easily calculated.
-The power per degree~$\ell$ may be calculated via~\citep[][Eqn.~B.95]{DT98}
-\begin{equation}
-    \sigma_\ell^2=\frac{1}{2\ell+1}\,\sum_{n=0}^N\sum_{m=-\ell}^\ell|{}_nC_{\ell m}|^2
+The normalized power per degree~$\ell$ may be calculated via
+\begin{equation}
+    \sigma_\ell^2=\frac{1}{2\ell+1}\,
+    \sum_{n' = 0}^N\sum_{n = 0}^N\sum_{m = -\ell}^\ell{}_{n'}C^*_{\ell m}\,A_{n'n}\,{}_{n}C_{\ell m}
     \quad .
@@
 \end{equation}
-The power per degree~$\ell$ may then be calculated via~\citep[][Eqn.~B.104]{DT98}
-\begin{equation}
-    \sigma_\ell^2=\frac{1}{2\ell+1}\,\sum_{n=0}^N\left[{}_na_{\ell 0}^2+\sum_{m=1}^\ell({}_na_{\ell m}^2+{}_nb_{\ell m}^2)\right]
+The normalized power per degree~$\ell$ may then be calculated via
+\begin{equation}
+    \sigma_\ell^2=\frac{1}{2\ell+1}\,\sum_{n'=0}^N\,\sum_{n=0}^N\,A_{n'n}\,\left[{}_{n'}a_{\ell 0}\,{}_{n}a_{\ell 0}+\sum_{m=1}^\ell({}_{n'}a_{\ell m}\,{}_na_{\ell m}+{}_{n'}b_{\ell m}\,{}_nb_{\ell m})\right]
+    \quad .
+\end{equation}
+
+To assess the accuracy of the expansion,
+we calculate the model norm in the GLL basis,
+\begin{equation}
+    ||m_\text{\,GLL}||^2=\int_V m_\text{\,GLL}^2(\mathbf{x})\,\mathrm{d}^3\mathbf{x}=
+    \sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,(m^{\alpha\beta\gamma})^2\,J^{\alpha\beta\gamma}
+    \quad ,
+\end{equation}
+and compare it to the model norm in the spherical harmonic basis,
+\begin{equation}
+    ||m_\text{\,SH}||^2=\int_V m_\text{\,SH}^2(\mathbf{x})\,\mathrm{d}^3\mathbf{x}=
+    \sum_{\ell = 0}^L(2\ell+1)\,\sigma_\ell^2
+    \quad ,
+\end{equation}
+by calculating the error
+\begin{equation}
+    \epsilon = \log\,\frac{||m_\text{\,SH}||^2}{||m_\text{\,GLL}||^2}
     \quad .

### 2019-01-16 main.tex
update

--- 2018-12-05 main.tex
@@
 \section{Introduction}
-
-{\color{Red} Wenjie: I want to leave this part to the end, when I finished reading all the papers.}
 
@@
 
-In addition to the 256 earthquakes used for the construction of first generation model GLAD-M15, we initially selected 784 carefully chosen additional earthquakes from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{Ekstrom12},
+In addition to the 256 earthquakes used for the construction of first generation
+model GLAD-M15, we initially selected 784 carefully chosen additional earthquakes
+from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{Ekstrom12},
 and added them to our database, resulting in a total number of 1,040 earthquakes.
@@
 
-The seismographic stations used in this study were carefully selected to ensure global coverage and high data quality (Fig.~\ref{fig:stations}).
+The seismographic stations used in this study were carefully selected to ensure global coverage
+and high data quality (Fig.~\ref{fig:stations}).
 In addition to the seismic stations used for the source inversions,
@@
 
-Conventional seismic data formats, such as SAC, involve one file per time series plus related files with instrument response and event information.
-Since every earthquake in the database is typically recorded by thousands of instruments, I/O during the preprocessing stage of the adjoint tomography workflow quickly cripples the file system.
-The Adaptable Seismic Data Format (ASDF)~\citep[][ \texttt{https://seismic-data.org/ }]{krischer2016adaptable} was developed with complete reproducibility and fast parallel processing in mind.
+Conventional seismic data formats, such as SAC, involve one file per time series
+plus related files with instrument response and event information.
+Since every earthquake in the database is typically recorded by thousands of
+instruments, I/O during the preprocessing stage of the adjoint tomography workflow
+quickly cripples the file system. The Adaptable Seismic Data Format
+(ASDF)~\citep[][ \texttt{https://seismic-data.org/ }]{krischer2016adaptable}
+was developed with complete reproducibility and fast parallel processing in mind.
 
@@
 \end{itemize}
-ASDF serves as a self-contained-and-explained data container while taking full advantages of parallel computing.
-In our workflow,
-one ASDF file contains all the information needed for data processing, including the seismic traces, event information files, and station response files.
+
+ASDF serves as a self-contained-and-explained data container while taking
+full advantages of parallel computing. In our workflow,
+one ASDF file contains all the information needed for data processing,
+including the seismic traces, event information files, and station response files.
 The related APIs are carefully designed for easy data extraction and parallel implementation.
@@
 
-The misfit function to be minimized during the iterative inversion process must be carefully constructed.
-It will typically involve cross-correlation traveltimes for body waves and frequency-dependent multitaper phase measurements for surface waves.
-Measurements are made in several passbands of three-component seismograms rotated into vertical, radial, and transverse components, resulting in a number of measurement categories.
-In this study, we consider four passbands,
-namely, a 17--40~s passband targeting body waves,
+The misfit function to be minimized during the iterative inversion process must
+be carefully constructed. It will typically involve cross-correlation traveltimes
+for body waves and frequency-dependent multitaper phase measurements for surface waves.
+Measurements are made in several passbands of three-component seismograms rotated
+into vertical, radial, and transverse components, resulting in a number of measurement
+categories.
+In this study, we consider four passbands, namely, a 17--40~s passband targeting body waves,
 two 40--100~s passbands separately targeting body and surface waves,
@@
 Although the inversion is designed to minimize the overall misfit,
-we will be tracking the misfit reduction in each of the categories to ensure that the model is improving the fit to the data roughly equally across the board.
-One of the biggest challenges in the construction of the misfit function is the highly uneven distribution of earthquakes and seismographic stations,
+we will be tracking the misfit reduction in each of the categories to ensure that
+the model is improving the fit to the data roughly equally across the board.
+One of the biggest challenges in the construction of the misfit function is the
+highly uneven distribution of earthquakes and seismographic stations,
 which must be counterbalanced by geographically weighting the data.
@@
 for the purpose of making measurements.
-The forward simulations are based on the global spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a},
-and take a CMT solution, a relevant list of stations, and the current earth model as input.
-The solver is GPU accelerated, and the simulations are performed on the Cray `Titan' at the Oak Ridge Leadership Computing Facility.
-To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA Tesla K20X GPUs takes approximately 10~min of wall clock time.
-The calculation of Fr\'echet derivatives at a later stage of the workflow requires access to snapshots of the forward wavefield as part of the parsimonious storage algorithm developed by~\cite{KoXiBoPeSaLiTr16},
+The forward simulations are based on the global spectral-element solver
+SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a}, and take a CMT solution, a relevant list
+of stations, and the current earth model as input.
+The solver is GPU accelerated, and the simulations are performed on the Cray `Titan'
+at the Oak Ridge Leadership Computing Facility.
+To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA
+Tesla K20X GPUs takes approximately 10~min of wall clock time.
+The calculation of Fr\'echet derivatives at a later stage of the workflow requires
+access to snapshots of the forward wavefield as part of the parsimonious storage
+algorithm developed by~\cite{KoXiBoPeSaLiTr16},
 with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
@@
 and generates adjoint sources for data assimilation as output.
-From a computational perspective, the preprocessing workflow consumes only~1\% of the overall computational requirements.
-But from the perspective of the tomographic inversion, this is by far the most important stage of the adjoint tomography workflow,
+From a computational perspective, the preprocessing workflow consumes only~1\%
+of the overall computational requirements.
+But from the perspective of the tomographic inversion, this is by far the most
+important stage of the adjoint tomography workflow,
 directly and fundamentally impacting the outcome.
-Any ``bad data'' assimilated at this stage may contaminate the gradient and ultimately the final model.
+Any ``bad data'' assimilated at this stage may contaminate the gradient and
+ultimately the final model.
 
@@
 most importantly via the time window selection tool FLEXWIN~\citep{maggi2009automated}.
-Every seismogram and potential measurement goes through multiple checks and and balances before acceptance or rejection.
-
-As illustrated in Fig.~\ref{fig:preprocess_workflow}, the preprocessing workflow includes the following phases.
+Every seismogram and potential measurement goes through multiple checks and and
+balances before acceptance or rejection.
+
+As illustrated in Fig.~\ref{fig:preprocess_workflow}, the preprocessing workflow
+includes the following phases.
 \begin{enumerate}
@@
 derivatives of the four model parameters as output.
-The computational cost of one adjoint simulation is roughly twice ($\sim25$~min) that of a forward simulation,
-since the forward wavefield is recalculated for convolution with the adjoint wavefield during the adjoint simulation,
+The computational cost of one adjoint simulation is roughly twice ($\sim25$~min) that of
+a forward simulation, since the forward wavefield is recalculated for convolution with
+the adjoint wavefield during the adjoint simulation,
 as discussed in~\cite{KoXiBoPeSaLiTr16}.
@@
 For every model iteration,
-we perform 1,480 forward and adjoint simulations, each involving hundreds of compute cores and graphics cards, as well as heavy I/O.
+we perform 1,480 forward and adjoint simulations, each involving hundreds of
+compute cores and graphics cards, as well as heavy I/O.
 The workflow is prone to human error and hardware failure, making it fragile.
-For these reasons, we wish to harden the worflow by taking advantage of modern workflow management software.
-With this goal in mind, we selected RADICAL-SAGA and RADICAL-EnTK as our workflow management engines, and developed complementary seismic tomography workflow tools~\citep{EnTK2017}.
-The workflow engine can automatically detected job failures both from the HPC system and via user-defined functions.
-This enables us to keep track of all tasks and semi-automatically resubmit jobs if necessary.
-Given that most HPC system time is spent waiting in the job queue, automatic failure detection and relaunching greatly shortens the overall time to solution.
+For these reasons, we wish to harden the worflow by taking advantage of modern
+workflow management software.
+With this goal in mind, we selected RADICAL-SAGA and RADICAL-EnTK as our
+workflow management engines, and developed complementary seismic tomography
+workflow tools~\citep{EnTK2017}.
+The workflow engine can automatically detected job failures both from the
+HPC system and via user-defined functions. This enables us to keep track of
+all tasks and semi-automatically resubmit jobs if necessary.
+Given that most HPC system time is spent waiting in the job queue, automatic
+failure detection and relaunching greatly shortens the overall time to solution.
 
@@
 
-The inversion went through ten iterations in a number of stages, as documented in this section.
-The evolution of the overall misfit function~(\ref{eq:misfit}) as well as its behavior in the various measurement categories is summarized in Fig.~\ref{fig:misfit}.
+The inversion went through ten iterations in a number of stages, as documented
+in this section. The evolution of the overall misfit function~(\ref{eq:misfit})
+as well as its behavior in the various measurement categories is summarized
+in Fig.~\ref{fig:misfit}.
 
@@
 and a change in the weighting strategy for 40--100~s surface waves.
-For iterations 18--21 we split the 40--100~s period band into two, separating the body and surface waves (Figs.~\ref{fig:misfit}e--g).
+For iterations 18--21 we split the 40--100~s period band into two, separating the
+body and surface waves (Figs.~\ref{fig:misfit}e--g).
 Since body and surface waves sample different parts of the mantle,
@@
 
-The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by iteration 21, prompting us to add more earthquakes and change the weighting strategy again by reintroducing the 17--40~s surface waves.
+The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by
+iteration 21, prompting us to add more earthquakes and change the weighting strategy
+again by reintroducing the 17--40~s surface waves.
 
@@
 \subsubsection{Stage~III: Iterations 22--25}
-
 At iteration~22 we added another 440 earthquakes to the database,
 bringing the total to 1,480 event,
-and we changed the 40--100~s surface wave weights back to their setting in Stage~I.
-During this stage we switched from a nonlinear conjugate gradient optimization algorithm to an L-BFGS quasi-Newton method.
+and we changed the 40--100~s surface wave weights back to their
+setting in Stage~I. During this stage we switched from a nonlinear
+conjugate gradient optimization algorithm to an L-BFGS quasi-Newton method.
 
@@
 
-In the previous sections we discussed the evolution of the misfit through three key stages of the inversion.
-It is important to note that ``the misfit function'' is, in fact, a continually moving target, because at every iteration the number of measurements increases as the model improves,
+In the previous sections we discussed the evolution of the misfit through
+three key stages of the inversion.
+It is important to note that ``the misfit function'' is, in fact, a
+continually moving target, because at every iteration the number of
+measurements increases as the model improves,
 and the number of earthquakes increases at iterations~18 and~22.
 
-In this section we calculate specific changes in misfit using all 1,480 earthquakes and an identical set of weightings and windows for three models, namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
-Table~\ref{table:misfit_reduction_M15_M25} summarizes the changes in fit in the twelve measurement categories
-between the new model, GLAD-M25, and its starting model, GLAD-M15, and between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.
+In this section we calculate specific changes in misfit using all 1,480
+earthquakes and an identical set of weightings and windows for three models,
+namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
+Table~\ref{table:misfit_reduction_M15_M25} summarizes the changes in fit in
+the twelve measurement categories between the new model, GLAD-M25, and its
+starting model, GLAD-M15, and between GLAD-M25 and model S362ANI combined
+with CRUST2.0, which was the starting model for the GLAD-M15 inversion.
+
 In all categories we observe significant misfit reductions,
@@
 The improvements in fit per component are comparable in all period bands,
-indicating that the various categories are reasonably well balanced in the assessment of misfit.
+indicating that the various categories are reasonably well balanced in the
+assessment of misfit.
 
@@
 we observe modest reductions in all standard deviations of the histograms.
-The histograms are nicely centered, indicating that the moment magnitudes are suitably selected, because the scalar moment affects all measurement categories equally.
+The histograms are nicely centered, indicating that the moment magnitudes are
+suitably selected, because the scalar moment affects all measurement categories equally.
 In the next phase of our ongoing inversion we plan to begin assimilating amplitude measurements,
@@
 
-In this section we evaluate model GLAD-M25 further based on a point-spread function resolution analysis as well as a ``held-out'' dataset, that is, a set of data not used in the actual structural inversion.
+In this section we evaluate model GLAD-M25 further based on a point-spread
+function resolution analysis as well as a ``held-out'' dataset, that is,
+a set of data not used in the actual structural inversion.
 
@@
 are frequently used to evaluate resolution in a tomographic inversion.
-Such tests are extremely expensive in FWI and adjoint tomography, because they require roughly the same computational resources as the actual inversion.
-In lieu of such tests,
-we performed two point-spread function analyses~\citep{fichtner2011resolution,zhu2015seismic,bozdaug2016global}.
+Such tests are extremely expensive in FWI and adjoint tomography, because they
+require roughly the same computational resources as the actual inversion.
+In lieu of such tests, we performed two point-spread function analyses~
+\citep{fichtner2011resolution,zhu2015seismic,bozdaug2016global}.
 
@@
 
-Following the approach of \cite{tape2009adjoint}, \cite{chen2015multiparameter}, and \cite{bozdaug2016global},
-we selected 360 earthquakes that were not used in the actual inversion.
-This held-out dataset consists of all magnitude 6.3--7.0 earthquakes in the global CMT catalog that were not used in the inversion.
+Following the approach of \cite{tape2009adjoint}, \cite{chen2015multiparameter},
+and \cite{bozdaug2016global}, we selected 360 earthquakes that were not used
+in the actual inversion. This held-out dataset consists of all magnitude 6.3--7.0
+earthquakes in the global CMT catalog that were not used in the inversion.
 We chose larger events to generate as many measurements as possible.
-We calibrated the centroid time and scalar moment using a grid search based on 3D synthetics calculated in GLAD-M25.
+We calibrated the centroid time and scalar moment using a grid search based on
+3D synthetics calculated in GLAD-M25.
 Fig.~\ref{fig:events_360} summarizes the properties of the held-out database.
@@
 
-First, we repeated the misfit assessment discussed in Section~\ref{section:Misfit assessment} for the held-out database.
-Table~\ref{table:misfit_reduction_M15_M25_360} summarizes the reductions in misfit for the held-out database for model GLAD-M25 compared to GLAD-M15 as well a S362ANI combined with CRUST2.0.
+First, we repeated the misfit assessment discussed in
+Section~\ref{section:Misfit assessment} for the held-out database.
+Table~\ref{table:misfit_reduction_M15_M25_360} summarizes the reductions
+in misfit for the held-out database for model GLAD-M25 compared to GLAD-M15
+as well a S362ANI combined with CRUST2.0.
 It is comforting to see that the reductions are comparable to the
 values tabulated in Table~\ref{table:misfit_reduction_M15_M25} for the actual inversion.
-Overall, the reductions are slightly smaller, partly due to the fact that we did not conduct full CMT inversions for the held-out database.
+Overall, the reductions are slightly smaller, partly due to the fact that we did not
+conduct full CMT inversions for the held-out database.
 
@@
 
-Second, we repeated the histogram comparisons discussed in Section~\ref{section:Histogram comparisons} for the held-out database.
+Second, we repeated the histogram comparisons discussed in
+Section~\ref{section:Histogram comparisons} for the held-out database.
 We used a set of identical windows on all three components to assess
@@
 In this section we discuss model GLAD-M25 in some detail.
-We begin with a global overview of the model before concentrating on specific geographical regions.
+We begin with a global overview of the model before concentrating on
+specific geographical regions.
 We conclude by highlighting various slabs and plumes in the model.
@@
 We first examine model GLAD-M25 in the context of existing global tomographic models.
-In Fig.~\ref{fig:global-vs} we compare global maps of the isotropic part of our shear wavespeed model with model S362ANI$+$M~\citep{moulik2014anisotropic},
+In Fig.~\ref{fig:global-vs} we compare global maps of the isotropic part of our
+shear wavespeed model with model S362ANI$+$M~\citep{moulik2014anisotropic},
 which is an updated version of the starting model for the GLAD-M15 inversion,
 and model S40RTS~\citep{ritsema2011s40rts}.
-The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
-Overall, these models are in good agreement at the longest wavelengths, especially Glad-M25 and S362ANI$+$M.
+The range of perturbations in shear wavespeed varies from map to map,
+as indicated in the top left of each panel. Overall, these models are in good agreement
+at the longest wavelengths, especially Glad-M25 and S362ANI$+$M.
 The perturbations in GLAD-M15 tend to be larger than in the other models,
@@
 
-An important aspect of our inversion is that it constrains shear and compressional waves simultaneously.
-In Fig.~\ref{fig:global-vs} we compare global maps of our compressional wavespeed model with P models LLNL-G3Dv3~\citep{simmons2012llnl} and GAP-P4~\citep{fukao2013subducted}.
+An important aspect of our inversion is that it constrains shear and
+compressional waves simultaneously. In Fig.~\ref{fig:global-vs} we
+compare global maps of our compressional wavespeed model with P models
+LLNL-G3Dv3~\citep{simmons2012llnl} and GAP-P4~\citep{fukao2013subducted}.
 At a depth of 100~km,
-GLAD-M25 shows prominent mid-oceanic ridges, cooling of the Pacific lithosphere, and the roots of numerous continental cratons.
-In the upper mantle, LLNL-G3Dv3 exhibits the largest lateral variations,
+
+GLAD-M25 shows prominent mid-oceanic ridges, cooling of the Pacific lithosphere,
+and the roots of numerous continental cratons. In the upper mantle, LLNL-G3Dv3
+exhibits the largest lateral variations,
 e.g., very slow compressional wavespeeds at 500~km depth below Hawaii, Samoa, and Tahiti.
@@
 also known as the Tornquist-Teisseyre Zone,
-separating the  Precambrian East European Craton~(EEC) in the Northeast from Phanerozoic Europe in the Southwest.
+separating the  Precambrian East European Craton~(EEC) in the Northeast from
+Phanerozoic Europe in the Southwest.
 The TESZ is very consistent across all models,
@@
 
-At depths of 100---250~km we observe high wavespeeds beneath the Central Graben in the North Sea, which is clearly separated from the EEC.
+At depths of 100---250~km we observe high wavespeeds beneath the Central Graben
+in the North Sea, which is clearly separated from the EEC.
 The tectonic history of the Mediterranean is complex,
 involving several regional plates and multiple past and present subduction zones.
-We see slab ponding in the transition zone beneath the western Mediterranean associated with slab roll-back of the Appennines-Maghrebides subduction zone~\citep{Giordano2017Magmatic}.
+We see slab ponding in the transition zone beneath the western Mediterranean
+associated with slab roll-back of the Appennines-Maghrebides subduction zone
+~\citep{Giordano2017Magmatic}.
 At shallower depths, we see low wavespeeds along its western border,
-which are interpreted as back-arc extension associated with the roll-back. Compared to S362ANI$+$M and S40RTS,
+which are interpreted as back-arc extension associated with the roll-back.
+Compared to S362ANI$+$M and S40RTS,
 our model shows much sharper features for these tectonic structures.
@@
 This anomaly gets sharper at 600~km depth.
-Its southern part interacts with the Hellenic slab, which penetrates the mantle transition zone and extends below 1,000~km in our model.
+Its southern part interacts with the Hellenic slab, which penetrates the mantle
+transition zone and extends below 1,000~km in our model.
 We discuss the Hellenic Arc further in Section~\ref{section:slabs}.
@@
 
-In Central Europe we note the Cenozoic Ridge System, characterized by low  wavespeeds from the Massif Central to the Eifel. Both EU60 and
-GLAD-M25 exhibit a slow anomaly beneath the northern part of the Rhine Graben, which is interpreted as the reservoir that fuels the Eifel hotspot.
-
-Beneath the Atlantic Ocean, our model strengthens slow anomalies beneath the ridges, especially underneath Iceland and the Azores.
-Compared to S362ANI$+$M, Iceland becomes
-much stronger in the upper mantle at depths from 250~km to 400~km, extending all the way to the mantle-transition zone.
+In Central Europe we note the Cenozoic Ridge System, characterized by low 
+wavespeeds from the Massif Central to the Eifel. Both EU60 and
+GLAD-M25 exhibit a slow anomaly beneath the northern part of the Rhine Graben,
+which is interpreted as the reservoir that fuels the Eifel hotspot.
+
+Beneath the Atlantic Ocean, our model strengthens slow anomalies beneath the
+ridges, especially underneath Iceland and the Azores.
+Compared to S362ANI$+$M, Iceland becomes much stronger in the upper mantle at
+depths from 250~km to 400~km, extending all the way to the mantle-transition zone.
 The Azores represent a much shallower hotspot, with a maximum depth of about 250~km.
@@
 
-In this section, we will visit the plumes systems on the earth.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Comment out for speed-up compile of latex file
-% If not, the compilation will be slowed down quite a lot due
-% to the insertion of PNG files.
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this section, we will visit the plumes systems on the earth. Fig.\ref{fig:plumes}
+shows the cross section on several plumes. In addition, we also shows TX2015 model here.
+
+Some of the plumes origins from the CMB and extend till the surface of the Earth,
+even though their formation is still under heated discussion. Even though most of
+the models tends to agree near the CMB, its rising shape diffs quite a lot in the
+lower and upper mantle, thus dramatically changes the dynamics of the mantle
+convections. Here, we present our model together with TX2015 and SEMUCB-WM1.
+
+Our model shows that Afar plumes orignates from the CMB, narrows its diameter
+in the middle mantle and broadens again above 660km discontinuity. It behaves
+very similar to TX2015 while differs a lot with SEMUCB-WM1. Despite the similarity
+with TX2015, our models shows stronger slow velocity anomaly around 660km
+discontinuity, possibly indicating a enhanced partial melting at that depth.
+
+In fig.\ref{fig:plumes_b}, from left to right, we can see: 1) the Farallon
+subduction slabs showing as fast anomaly; 2) the bermuda hotspot that stays
+above 660km discontinuity; 3) Canary hotspot that originates from the CMT and
+rise all the way up the the surface of the earth; 4) the Afar hotspot from another
+angle of view.
+
+In fig.\ref{fig:plumes_c}, from left to right, we can see: 1) the subduction slab
+in South America showings as a big block of fast anomaly; 2) Cape Verde hotspot
+that originates from the CMT and rise all the way up to the surface; 3) Hoggar hotspot
+that has strong slow anomaly from 660km to the very surface. It is very interesting
+to compare the image of Hoggar in our model with the other two, while the TX2015 only
+shows slow anomaly around 660km and SEMUCB-WM1 only in the very surface.
+
+In fig.\ref{fig:plumes_d}, plumes rises right below Icleland, reaches 660km and amplifies
+its anomaly and rise to the surface. Here it may indicates another place where anmaly gets
+much stronger above 660, possibly indicating the partial melting below 600km.
+
+In fig.\ref{fig:plumes_e}, from left to right: 1) the Easter hotspot; 2) the Galapogos
+hotspot; 3) the Central America subduction slabs showing as fast anomaly. It is interesting
+seeing that the Easter and Galapagos may originates from the same underlying plumes, which
+lies in the middle of both hotspots. The underlying plumes near the CMB belongs to the
+a east extension arm of the Pacific super plume.
+
+If fig.\ref{fig:plumes:f}, we are seeing Marion and Kerguelen hotspot, which might related
+the Afar at its lower mantle part. Those hotspots and plumes are very hard to recover due
+to the poor data coverage at the south hemisphere.
 
@@
     \centering
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
-    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.}
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:plumes_a}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:plumes_b}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:plumes_c}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:plumes_d}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:plumes_a}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:plumes_g}}\\
+    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.
+(a) Afar; (b) Bermuda (left) and Canary (mid); (c) Cape Verde (mid) and Hoggar (right); (d) Iceland (mid) and Eifel (right); (e) Easter (left) and Galapagos (right); (f) Marion (mid) and Kerguelen (right).
+}
+    \label{fig:plumes}
 \end{figure}
@@
 
-In this sections, we will visit some of the well-known subduction zones.
+In this section, we visit another kind of geological systems on the earth,
+subduction zones. In \cite{fukao2013subducted} and \cite{van2018atlas},
+they both presented the subductions systems in the details. In
+figure.\ref{fig:subd} we plotted our model, GLAD-M25, together with
+GAP-P4 and UU-P07.
+
+In general, all the models are in good agreement with each other, despite
+the fact that our model use waveform measurements and the other two
+uses travel-time. However, there are still difference when comparing those
+models in details. At shallow depth, our models shows more consistent
+structure in the continental crust and craton, across all the figures we
+listed in fig.\ref{fig:subd}. When it comes to the upper and middle mantle,
+all the models shares a a lot in common. Difference becomes obvious at depth,
+especially for subductions below 1000km. For example, in fig.\ref{fig:subd_c},
+it shows the Frallon subductions. Our models shows a more continous subductions
+that goes all the way the lower mantle, while the other two travel-time models
+only shows the subduction slab vaguely. This comes from two factors. Our model
+incorporates more data, including the whole US-Array data for this region
+specifically. Second, the finite-frequency kernels have more sensitivity in
+depth, when compared to the classical ray-theory based inversions.
+
+Also, as mentioned in the previous sections, we showed our model in Vp
+perturbations, since in our inverison, Vp is treated as independant
+parameters, while in previous waveform models, they usually fixed the
+Vp and Vs ratios.
 
@@
     \centering
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Aeg.png}\label{fig:a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Br.png}\label{fig:b}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:c}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:a}}\\[-1pt]
-    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.}
-\end{figure}
-
-\newpage
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Aeg.png}\label{fig:subd_a}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Br.png}\label{fig:subd_b}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:subd_c}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:subd_d}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:subd_e}}\\[-1pt]
+    \caption{Vertical cross sections of perturbations of Vp in subduction regions.
+(a) the Aegean anomaly; (b) South American Subduction; (c) the Hatteras anomaly; (d) the Nepal Anomaly; (e) the Wichita anomaly.}
+    \label{fig:subd}
+\end{figure}
 
@@
 
-In summary,
-the new model performs well for the held-out dataset, both in terms of misfit reductions and measurement distributions in all twelve measurement categories.
-We expect to see similar behavior for any future earthquakes.
+In summary, the new model performs well for the held-out dataset,
+both in terms of misfit reductions and measurement distributions
+in all twelve measurement categories. We expect to see similar
+behavior for any future earthquakes.
 
@@
 
+\newpage
 \begin{acknowledgments}
-
 %We want to give thanks to the Oak Ridge National Lab, for providing

### 2019-01-16 main.tex
add more figures

@@
 
-With the development of high performance computing and numerical methods, it is now possible to using adjoint method to image the interior the globe using thousands of earthquakes.
-
-There are few agreements about the earth model and yet many unknown to be resolved. There are quite a lot of global models exits however there is no such con-sense.
+With the development of high performance computing and numerical methods,
+it is now possible to using adjoint method to image the interior the globe
+using thousands of earthquakes.
+
+There are few agreements about the earth model and yet many unknown to be
+resolved. There are quite a lot of global models exits however there is no such con-sense.
 
@@
 is the absence of the 220~km discontinuity and a lower~$V_p/V_s$ ratio in the top 200~km.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/1d_profile.pdf}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/1d_profile.pdf}
   \caption{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
@@
   \label{fig:global-average}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/1d_profile_ra.pdf}
+  \caption{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}
+  \label{fig:global-ra-average}
+\end{figure}
+
+\section{Window distributions}
+
+Fig.\ref{fig:window_density} shows the window density map on the
+vertical component for 17-40 sec period band. In this category,
+we picked in total of 4,363,719 time windows. The color denotes the
+density of windows. X axis is the time and y axis is the epicenter
+distance. Windows are discretized into 1 degree in epicenter distance
+domain and 1 second in time domain.
+
+The max density value of windows is 9,931, located at 134-135 epicenter
+distance bin and 1375-1376 time bin.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
+  \caption{The window density map.}
+  \label{fig:window_density}
 \end{figure}

### 2019-01-18 main.tex
Updates from ShareLaTeX

--- 2019-01-16 main.tex
@@
 As a continuation of our previous work~\citep{bozdaug2016global},
-we used ``first generation'' model GLAD-M15 as our
+we used ``first-generation'' model GLAD-M15 as our
 starting model.
@@
 Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers.
-The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}
+The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the dataset.}
   \label{fig:stations}
@@
 ASDF serves as a self-contained-and-explained data container while taking
-full advantages of parallel computing. In our workflow,
+full advantage of parallel computing. In our workflow,
 one ASDF file contains all the information needed for data processing,
-including the seismic traces, event information files, and station response files.
+including the seismic traces, event information files (QuakeML), and station response files (StationXML).
 The related APIs are carefully designed for easy data extraction and parallel implementation.
@@
 respectively.
-Here~$N$ and~$N_{sc}$ are a normalization factors,
+Here~$N$ and~$N_{sc}$ are normalization factors,
 and~$\Delta_{ss'}$ and~$\Delta_{rr'}$ denote angular distances between source and receiver pairs~$\{s,s'\}$ and~$\{r,r'\}$\,.
@@
 
+Fig.~\ref{fig:window_density} shows a time-distance plot
+for vertical component 17--40~s body waves in which the Pyflex window count is used to identify parts of seismograms being assimilated.
+A total of 4,363,719 time windows were picked in this category.
+The figure nicely highlights all the well known body traveltime branches.
+The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1376~s time bin.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
+  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
+  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
+  }
+  \label{fig:window_density}
+\end{figure}
+
 \subsection{Adjoint Simulations}
@@
   \includegraphics[width=0.8\textwidth]{figures/misfit.pdf}
-  \caption{Evolution of phase misfits from GLAD-M15 to GLAD-M25.
-  Each color denotes the different stages of inversions, between
-  which we make changes to the inversion by either tuning the
-  weighting strategies or adding more data.
-  (a) Evolution of the total phase misfit. (b) - (j) Misfit in
-  each period band and component. (e) - (g) From GLAD-M18,
-  we future split the 40-100 sec period band into two
-  measurement categories: body(red diamond) waves and surface waves
-  (red square).
-  {\color{red} Wenjie, why do the graphs overlap at iteration 22, but not at iteration 18?
-Shouldn't 22 look like 18, i.e., no overlapping points?
-\textbf{To Jeroen}: overlap means I calculate the misfit twice using the same mode.
-For example, in iteration M22, I caculated the misfit using the 1040 earthquakes and 1480 earthquakes, respectively.
-In M18, I haven't done so.
-If you want, I can calculate the misfit values and adding the overlap misfit point.}
-  {\color{blue}Wenjie: OK, then let's be consistent in what we do. I would prefer no overlap.}
+  \caption{Evolution of the misfit function from GLAD-M15 to GLAD-M25.
+  Each color denotes different stages of the inversion, as discussed in Sections~\ref{sec:I}--\ref{sec:III}.
+  (a) Evolution of the total misfit. (b)--(j) Misfit in
+  each period band (rows) on three components (columns). (e)--(g) From GLAD-M18,
+  we  split the 40--100~s period band into two
+  measurement categories: body waves (red diamonds) and surface waves
+  (red squares).
   }
@@
 
-\subsubsection{Stage~I: Iterations 15--17}
+\subsection{Stage~I: Iterations 15--17}
+\label{sec:I}
 
@@
 
-\subsubsection{Stage~II: Iterations 18--21}
-
-We see an abrupt change in the value of the misfit function at iteration 18
+\subsection{Stage~II: Iterations 18--21}
+
+We see an abrupt change in the value of the misfit function at iteration~18
 in Fig.~\ref{fig:misfit},
-reflecting the addition of 520 events to the inversion database,
+reflecting the addition of 520~events to the inversion database,
 and a change in the weighting strategy for 40--100~s surface waves.
@@
 The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by
-iteration 21, prompting us to add more earthquakes and change the weighting strategy
-again by reintroducing the 17--40~s surface waves.
+iteration~21, prompting us to add more earthquakes and change the weighting strategy again by reintroducing 17--40~s surface waves.
 
@@
 
-\subsubsection{Stage~III: Iterations 22--25}
+\subsection{Stage~III: Iterations 22--25}
+\label{sec:III}
+
 At iteration~22 we added another 440 earthquakes to the database,
-bringing the total to 1,480 event,
+bringing the total to 1,480 events,
 and we changed the 40--100~s surface wave weights back to their
@@
 In this section we calculate specific changes in misfit using all 1,480
-earthquakes and an identical set of weightings and windows for three models,
+earthquakes and an identical set of weights and windows for three models,
 namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
@@
 
-In this section we discuss model GLAD-M25 in some detail.
+In this section we discuss model GLAD-M25 in detail.
 We begin with a global overview of the model before concentrating on
@@
 and model S40RTS~\citep{ritsema2011s40rts}.
-The range of perturbations in shear wavespeed varies from map to map,
-as indicated in the top left of each panel. Overall, these models are in good agreement
+Overall, these models are in good agreement
 at the longest wavelengths, especially Glad-M25 and S362ANI$+$M.
-The perturbations in GLAD-M15 tend to be larger than in the other models,
+The perturbations in GLAD-M25 tend to be larger than in the other models,
 consistent with observations by~\cite{french2014whole},
@@
 %\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
-%  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI$+$M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
+%  \caption{Map views of global $V_\textrm{P}$ variations at various depths for our model GLAD-M25(left column), S362ANI$+$M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
 For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing.
@@
 At a depth of 100~km,
-
 GLAD-M25 shows prominent mid-oceanic ridges, cooling of the Pacific lithosphere,
@@
 At a depth of 100~km, we observe that the edges of the craton are sharper in
-GLAD-M15 than in the other two global models,
+GLAD-M25 than in the other two global models,
 and quite similar in shape and sharpness to the two regional models.
@@
 At shallower depths, we see low wavespeeds along its western border,
-which are interpreted as back-arc extension associated with the roll-back.
+which are interpreted as back-arc extension associated with  roll-back.
 Compared to S362ANI$+$M and S40RTS,
@@
 Its southern part interacts with the Hellenic slab, which penetrates the mantle
-transition zone and extends below 1,000~km in our model.
+transition zone and extends below 1000km in our model.
 We discuss the Hellenic Arc further in Section~\ref{section:slabs}.
@@
 
-Asia, like Europe, has a complicated tectonic history, involving
+Asia, like Europe, has a complex tectonic history, involving
 interactions among the Indian, Eurasian, Australian, Pacific, and Philippine
 plates.
-Map views of GLAD-M15 centered on Asia are plotted in Fig.~\ref{fig:asia-vs},
+Map views of GLAD-M25 centered on Asia are plotted in Fig.~\ref{fig:asia-vs},
 together with S362ANI$+$M, S40RTS, and regional model EARA2014~\citep{chen2015multiparameter}.
@@
   \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
-  \caption{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M, LLNL-G3Dv3~\citep{}, and GAP-P4~\citep{fukao2013subducted}.}
+  \caption{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).}
   \label{fig:southamerica-vp}
@@
 
-Fig.\ref{fig:southamerica-vp} shows the $V_p$ velocity in our model, together with 3
-global models, S362ANI$+$M, LLNL-G3Dv3\citep{}, GAP-P4\citep{fukao2013subducted},
-while the latter two are global $V_p$ models.
-
-At 100km depth, the northern part of South America is covered by large area
-of lithosphere craton, showing fast wave anomaly except GAP-P4. The fast anomaly
-stays strong in LLNL-G3Dv3 while for GLAD-M25
-and S362ANI$+$M it disappear at such depth.
-At 300km, we are see a sharpened fast anomaly in the south subduction area
-in GLAD-M25 compared to S372ANI+M. However, the shape and strength are very close
-between GLAD-M25 and LLNL-G3Dv3 models. Moving to even larger depth, the features of
-subductions becomes divergent between the north Peruvian slab and south Chilean slab.
-At 600km, we observed a large chunk of fast anomaly in the Chilean slab,
-indicating the slab is trapped and stagnant in the mantle transition zone. However,
-the Peruvian slabs has penetrated the mantle transition zone and extend till 1000,
-reaching the uppermost part of lower mantle, which is consistent with GAP-P4
+Fig.~\ref{fig:southamerica-vp} shows compressional wavespeed anomalies in model GLAD-M25 in comparison with three
+global models, namely, S362ANI$+$M~\citep{moulik2014anisotropic}, LLNL-G3Dv3~\citep{simmons2012llnl}, and GAP-P4~\citep{fukao2013subducted};
+the latter two are $V_\textrm{P}$ models.
+
+At 150~km depth, the northern half of South America is covered by a large lithospheric craton, exhibiting fast anomalies in all models except GAP-P4.
+The Galapagos,
+San Felix, and Juan Fernandez hotspots are associated with distinct low wavespeed anomalies in GLAD-M25,
+but not in the other models.
+At 300~km depth, we see sharpened subduction of the Nazca plate
+in GLAD-M25 compared to S372ANI+M, similar in shape to  model LLNL-G3Dv3.
+Moving to greater depths,
+we see distinct Peru and Chile slabs in GLAD-M25,
+with the Chile slab ponding in the transition zone
+and the Peru slab penetrating into the lower mantle and still clearly visible at 1000km depth.
+These differences in behavior are consistent with GAP-P4
 \citep{fukao2013subducted}.
 
-Besides, in the Pacific and Nazca plate, our models is sharpening the Galapagos,
-San Felix and Juan Fernandez hotspot. In the Scotia plate, our models shows a very
-strong expression of Scotia Arc subduction till 1000km, which is barely observable
-in other models. In the Caribbean plate, we also observed fast anomaly, indicating
-the Caribbean subduction.
+In the south,
+Scotia Arc subduction is very distinct in GLAD-M25 at all depths,
+but barely observable in other models.
+To the north,
+Caribbean subduction is clearly discernible in model GLAD-M25 and the two $V_\textrm{P}$ models.
 
@@
 
-In this section, we will visit the plumes systems on the earth. Fig.\ref{fig:plumes}
-shows the cross section on several plumes. In addition, we also shows TX2015 model here.
-
-Some of the plumes origins from the CMB and extend till the surface of the Earth,
-even though their formation is still under heated discussion. Even though most of
-the models tends to agree near the CMB, its rising shape diffs quite a lot in the
-lower and upper mantle, thus dramatically changes the dynamics of the mantle
-convections. Here, we present our model together with TX2015 and SEMUCB-WM1.
-
-Our model shows that Afar plumes orignates from the CMB, narrows its diameter
-in the middle mantle and broadens again above 660km discontinuity. It behaves
-very similar to TX2015 while differs a lot with SEMUCB-WM1. Despite the similarity
-with TX2015, our models shows stronger slow velocity anomaly around 660km
-discontinuity, possibly indicating a enhanced partial melting at that depth.
-
-In fig.\ref{fig:plumes_b}, from left to right, we can see: 1) the Farallon
-subduction slabs showing as fast anomaly; 2) the bermuda hotspot that stays
-above 660km discontinuity; 3) Canary hotspot that originates from the CMT and
-rise all the way up the the surface of the earth; 4) the Afar hotspot from another
-angle of view.
-
-In fig.\ref{fig:plumes_c}, from left to right, we can see: 1) the subduction slab
-in South America showings as a big block of fast anomaly; 2) Cape Verde hotspot
-that originates from the CMT and rise all the way up to the surface; 3) Hoggar hotspot
-that has strong slow anomaly from 660km to the very surface. It is very interesting
-to compare the image of Hoggar in our model with the other two, while the TX2015 only
-shows slow anomaly around 660km and SEMUCB-WM1 only in the very surface.
-
-In fig.\ref{fig:plumes_d}, plumes rises right below Icleland, reaches 660km and amplifies
-its anomaly and rise to the surface. Here it may indicates another place where anmaly gets
-much stronger above 660, possibly indicating the partial melting below 600km.
-
-In fig.\ref{fig:plumes_e}, from left to right: 1) the Easter hotspot; 2) the Galapogos
-hotspot; 3) the Central America subduction slabs showing as fast anomaly. It is interesting
-seeing that the Easter and Galapagos may originates from the same underlying plumes, which
-lies in the middle of both hotspots. The underlying plumes near the CMB belongs to the
-a east extension arm of the Pacific super plume.
-
-If fig.\ref{fig:plumes:f}, we are seeing Marion and Kerguelen hotspot, which might related
-the Afar at its lower mantle part. Those hotspots and plumes are very hard to recover due
-to the poor data coverage at the south hemisphere.
+In this section we highlight various plume systems on Earth. Fig.~\ref{fig:plumes}
+shows cross sections of several plumes, comparing models GLAD-M25 ($V_\textrm{P}$),
+TX2015~\citep[$V_\textrm{S}$;][]{TX2015}, and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad}.
+
+Some plumes originate from the CMB and extend all the way to the Earth's surface.
+The three models tend to agree near the CMB,
+and there is overall good agreement between GLAD-M25 and TX2015,
+but the models can differ substantially in the mid and upper mantle,
+with profoundly different implications for mantle
+convection.
+
+In Fig.~\ref{fig:plumes}(a),
+we see that the Afar plume in model GLAD-M25 originates from the CMB, narrows its diameter
+in the mid mantle, and broadens again above the 660~km discontinuity.
+It exhibits
+very similar behavior in TX2015 but differs significantly in SEMUCB-WM1.
+
+In Fig.~\ref{fig:plumes}(b), from left to right, we see in model GLAD-M25 1) the Farallon
+slab; 2) the Bermuda hotspot above the 660~km discontinuity; 3) the Canary hotspot originating from the CMT and
+rising all the way up the Earth's surface; 4) the Afar hotspot from another angle.
+
+Fig.~\ref{fig:plumes}(c) features 1) South America subduction; 2) the Cape Verde hotspot extending from the CMB all the way to the surface; 3) the Hoggar hotspot from 660~km to the surface.
+
+Fig.~\ref{fig:plumes}(d) shows a plume which rises from the CMB right below Iceland, reaches 660~km, amplifies,
+and ascends to the surface.
+The intensification above 660~km may be an indication of partial melting.
+
+Fig.~\ref{fig:plumes}(e) contains 1) the Easter hotspot; 2) the Galapagos
+hotspot; 3) the Central America slab.
+In models GLAD-M25 and TX2015,
+the Easter and Galapagos hotspots appear to originate from the same underlying plume in the deep mantle,
+which is the eastern arm of the Pacific superplume.
+
+Finally,
+in Fig.~\ref{fig:plumes}(f) we see the Marion and Kerguelen hotspots, which might be connected to Afar in the lower mantle.
+Recovering these plumes is challenging due to poor data coverage in the southern hemisphere.
 
@@
     \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:plumes_g}}\\
-    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.
-(a) Afar; (b) Bermuda (left) and Canary (mid); (c) Cape Verde (mid) and Hoggar (right); (d) Iceland (mid) and Eifel (right); (e) Easter (left) and Galapagos (right); (f) Marion (mid) and Kerguelen (right).
+    \caption{Vertical cross sections for various plumes for models GLAD-M25 ($V_\textrm{P}$; left column), TX2015~\citep[$V_\textrm{S}$;][]{TX2015} (center column), and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad} (right column).
+    The map in the top left corner of each row shows the cross section with color-coded red, green, and white dots for geographical reference;
+    hotspots are denoted by red triangles.
+    The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
+    (a) Afar; (b) Bermuda (left) and Canary (middle); (c) Cape Verde (middle) and Hoggar (right); (d) Iceland (middle) and Eifel (right); (e) Easter (left) and Galapagos (right); (f) Marion (middle), and Kerguelen (right).
 }
@@
 
-\subsection{Subduction Slabs}
+\subsection{Subduction zones}
 \label{section:slabs}
 
-In this section, we visit another kind of geological systems on the earth,
-subduction zones. In \cite{fukao2013subducted} and \cite{van2018atlas},
-they both presented the subductions systems in the details. In
-figure.\ref{fig:subd} we plotted our model, GLAD-M25, together with
-GAP-P4 and UU-P07.
-
-In general, all the models are in good agreement with each other, despite
-the fact that our model use waveform measurements and the other two
-uses travel-time. However, there are still difference when comparing those
-models in details. At shallow depth, our models shows more consistent
-structure in the continental crust and craton, across all the figures we
-listed in fig.\ref{fig:subd}. When it comes to the upper and middle mantle,
-all the models shares a a lot in common. Difference becomes obvious at depth,
-especially for subductions below 1000km. For example, in fig.\ref{fig:subd_c},
-it shows the Frallon subductions. Our models shows a more continous subductions
-that goes all the way the lower mantle, while the other two travel-time models
-only shows the subduction slab vaguely. This comes from two factors. Our model
-incorporates more data, including the whole US-Array data for this region
-specifically. Second, the finite-frequency kernels have more sensitivity in
-depth, when compared to the classical ray-theory based inversions.
-
-Also, as mentioned in the previous sections, we showed our model in Vp
-perturbations, since in our inverison, Vp is treated as independant
-parameters, while in previous waveform models, they usually fixed the
-Vp and Vs ratios.
+In this section we highlight various subduction systems on Earth.
+In Fig.~\ref{fig:subd} we compare GLAD-M25~($V_\textrm{P}$) with two compressional wavespeed models,
+namely, GAP-P4~\citep{fukao2013subducted} and UU-P07~\citep{van2018atlas}.
+
+Overall, the three models are in reasonably good agreement.
+At shallow depths, model GLAD-M25 shows more distinct continental crust and cratons, thanks to the inclusion of surface waves.
+In the upper and mid mantle,
+the models share very similar features.
+At depth greater than 1000km, 
+we see a very strong expression of the ancient Farallon slab in model Glad-M25, which is much weaker in the two P models.
+The difference may be attributed to increased data coverage thanks to USArray, as well as the use of finite-frequency Fr\'echet derivatives.
 
@@
     \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:subd_e}}\\[-1pt]
-    \caption{Vertical cross sections of perturbations of Vp in subduction regions.
-(a) the Aegean anomaly; (b) South American Subduction; (c) the Hatteras anomaly; (d) the Nepal Anomaly; (e) the Wichita anomaly.}
+    \caption{Vertical cross sections of compressional wavespeed perturbations in various subduction zones
+    for models GLAD-M25 ($V_\textrm{P}$; left column), GAP-P4~\citep{fukao2013subducted} (middle column) and UU-P07~\citep{van2018atlas} (right column).
+    The map in the top left corner of each row shows the cross section with color-coded red, green, and white dots for geographical reference.
+    The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
+    (a) Aegean; (b) South America; (c) Hatteras; (d) Nepal; (e)  Wichita.}
     \label{fig:subd}
@@
 $\omega_\alpha$ denotes a GLL quadrature weight, and $J^{\alpha\beta}(r)$ is the 2D Jacobian of the mapping to the sphere.
-It is important to carry out the summations in~(\ref{eq:radial_average}) at the elemental level to ensure that first-order discontinuities are honored in the process.
+%It is important to carry out the summations in~(\ref{eq:radial_average}) at the elemental level to ensure that first-order discontinuities are honored in the process.
 
@@
 The main difference between these two models and~PREM
-is the absence of the 220~km discontinuity and a lower~$V_p/V_s$ ratio in the top 200~km.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/1d_profile.pdf}
+is the absence of the 220~km discontinuity and a lower~$V_P/V_S$ ratio in the top 200~km.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/1d_profile.pdf}
   \caption{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
@@
   \label{fig:global-average}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/1d_profile_ra.pdf}
+  \caption{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}
+  \label{fig:global-ra-average}
 \end{figure}

### 2019-01-23 main.tex
update window plots

@@
 
-With the development of high performance computing and numerical methods,
-it is now possible to using adjoint method to image the interior the globe
-using thousands of earthquakes.
-
-There are few agreements about the earth model and yet many unknown to be
-resolved. There are quite a lot of global models exits however there is no such con-sense.
-
-The GLAD-M25 is the first earth model that incorporate the P and S wave speed using full waveform inversion.
-Also, people are using specific set of phases in their inversion.
-For P models, people are using P phase and other body wave phases and for S models, people are using mostly S wave phases and surface waves to constrain the structure.
-Those two kinds of models usually reveals very different parts of the earth.
-For example, for P wave, people used it the image the subduction slabs and it is not very good at image lower mantle structures, such as plumes and lower mantle convection.
-For S waves, it is the verse verso.
-
-There are many challenges coming along the way.
-First, the data volume is huge.
-There are in total of 1480 earthquakes used in the inversion stage, added into the database step by step.
-Second, workflow management is crucial dealing with such a large project.
-One factor is coming from the complex workflow.
-There are 4 major building blocks, forward simulation, seismic data processing, adjoint simulation and post-processing.
-Each blocks contains several small blocks.
-The other factor is coming from the number of earthquakes and high demands of computation.
-In each iteration, we are doing 1480 forward and adjoint simulation, generating a few Petabytes of wavefield files and consuming 16 million of CPU hours on the supercomputer at Oak Ridge National Lab.
-There are yet more in data processing stages.
-How to deal with hardware failures is very important and prevent contamination into our inversion results.
-
-Here, we present our GLAD-M25 earth model, with significantly improvements on the plumes and subductions.
+In the last few decades, we have witnessed great improvments in the global
+seismic imaging. There are different types of earth models published using
+various data types and methodologies\citep{}. The theory of Finite-frequcy
+was brought up in the early 1980\citep{}, overcomes very limitations
+in the ray-based theory. However, it is still the very recent
+decade that people are able to use it in the global scale inverison, 
+thanks to the advance in the high-performance computing and numerical methods.
+
+There are gaps between the global and regional models. Regional models, tends to
+resolve structures at shorter period bands such as 10 - 15 seconds\citep{},
+but lacks of resolution in depth. 
+On the other hand, global models, resolved structures as deep as 
+the core-mantle boundary, but only starting from ~60 seconds period bands
+at most, mainly due to the high computational cost\citep{}. Recent years
+we have seen models moves to 30 seconds in waveform-type inversion but
+there is still a clear gap between the global and regional inversions.
+Owing to the recent advances in high-performance computing and numerical
+methods, it is possible to simulate seismic waves in an unprecendental
+resolution at global scale, to close the gap between regional and global
+studies.
+
+In our previous model paper\citep{}, advantanges of spetral-element methods
+and adjoint tomography has been thoroughly discussed. Crust and discontinuity
+is honored in our mesh. Thus, there is no crust correction needed in our
+inversion procedures. Adjoint methods, can fully take the 3D earth structure
+an attenuation into account, for both forward simulation and adjoint simulation,
+calculating the frechet direvative in a more precise way.
+However, when pushing for high frequecy, it soon becomes very
+demanding on computational resourse.
+
+Other than the simulation part, the data assimilation has been another key factor
+to the success of tomography. Ray-based travel-time inversion has accumulated
+huge amount of data along it way. However, they usually focused on certain type of phases.
+relying on both open and customized travel time database.
+Models, such as GAP-P4 and UU-P07, used millions of travel time measurements, but only
+used P related phases. 
+The finite frequcy methods is developed recently so there are less consense of the dataset
+used in the research. On the other hand, the methods also gives more freedom when it comes
+to data assimilation. It then become a critial question for which part of the data should
+be assimilated into the inverison. 
+Recent years have seen a lot of good quality seismic networks deployed, such as US array.
+However, there is few global model that take the advantage of network yet. It would be
+a pity not to utlized it, but data assimilation should be handled very carefully since it
+will directly impact the image in a few ways. First, it is the data quality. only good
+seismograms and phases should be including into the inversion. Second, the high density
+distribution of regional networks would skew the inversion so proper weightings should be
+taken care of.
+
+There are many challenges coming along the way. First, the data volume is huge.
+There are in total of 1480 earthquakes used in the inversion stage, added into
+the database step by step. Second, workflow management is crucial dealing with
+such a large project. One factor is coming from the complex workflow. There are
+4 major building blocks, forward simulation, seismic data processing, adjoint
+simulation and post-processing. Each blocks contains several small blocks.
+The other factor is coming from the number of earthquakes and high demands of
+computation. In each iteration, we are doing 1480 forward and adjoint simulation,
+generating a few Petabytes of wavefield files and consuming 16 million of CPU
+hours on the supercomputer at Oak Ridge National Lab. There are yet more in
+data processing stages. How to deal with hardware failures is very important
+and prevent contamination into our inversion results.
+
+In the following sections, we will present the GLAD-M25 earth model in details.
+From section 2 - 4, we will focus on the data, including the starting model,
+earthquakes and seismic data used in this study.  In section 5 and 6, we will
+discuss the model parametrization and the choice of misfit function we made.
+Section 7 and 8 describes the adjoint tomography workflow and the evolution
+of inversion, and the improvments we made with the iterations. Section 9 will
+focus on model evaluation part, which we used a few techniques to assess the
+quality of inverison. Section 10 will address on presenting images of our model,
+together with whole bunch of other models, global and regional. We conclude in 
+section 10, summarizing our model and diretion of future works.
 
@@
 
+\section{Discussion}
+
+Here, we presented our GLAD-M25 models. Starting from GLAD-M25, we
+conducted 10 more iterations, with significantly more earthquakes
+(up to 1480 earthquakes)and seismic data(up to 18.2 million time
+windows) added in the inversion in a progressive way. It is the first
+global transerse isotropoic model that brings the resolution down to
+17 secs, but also invert the $V_p$ and $V_s$ indenpendently. Due to the
+nature of spetral-element methos, our model meshes the crust and mantal
+, without introducing the "crustal correction". Our solver also enables
+us the take the full-attenuation into accout, both in forward and adjoint
+simulations, using undo attenuation at the cost of more computation
+hours and disk space.
+
+GLAD-M25 is evaluated in many ways. First, it shows significant misfit
+reduction in all measurements categories, but also in the variance
+reduction in travel-time measurements. For the 360 held-out earthquakes,
+the behavior is similar to what we have in our inversion dataset. We
+presented our global $V_s$ and $V_p$, together with other well-known global
+models and at large scale they agree with each other. However, when we focus
+on regional studies and compare with regional models, our model shows superior
+more detailed structures compared to other global models, staying at the 
+same resolution of regional models. Our models shows great resolution in both
+plumes and suduction zones, using the independently inverted $V_p$ and $V_s$
+velocity models.
+
 \section{Conclusion}
-
-In summary, the new model performs well for the held-out dataset,
-both in terms of misfit reductions and measurement distributions
-in all twelve measurement categories. We expect to see similar
-behavior for any future earthquakes.
 
@@
 to take all the information we have. Even though GLAD-M25 is following-up
-of GLAD-M15. It has many superior advantages and improvements. We increase
+of GLAD-M15, It has many superior advantages and improvements. We increase
 the dataset from 253 to 1480 earthquakes, with carefully inverted sources
@@
 dataset, which is already larger than the most of the dataset other people used
-for their inversion. We culled every seismograms from various data centers,
+for their inversion. We culled seismograms from various data centers,
 thanks to the open environment and data sharing spirit of our seismology community.
@@
 data assimilated into our inversion and make sure every piece of value information
-will be used but rejecting the crap data.
-
-There are also quite a lot of technique challenges on the way but we are seeking
-the most cutting-edge technologies to solve them. ADIOS was introduced to save mesh
-and kernel related data, since we are saving petabytes of wavefiled snapshots
-in a few hours of simulation and it is critical even for the most advanced
-supercomputers in the world. ASDF is developed by us to store the seismograms
-since we have ten millions of time series data from thousands of earthquakes.
-We have to get access and process them in a very efficient manner that most of
-the existing data format just won't meet our requirements. To handle the complex
-inversion workflow, we are working RADICAL group to develop the workflow management
-tools that will help manage every piece of task and make the user aware if there
-is anything bad happened during the computation. Those tools that help the
+will be used but rejecting crap data.
+
+However, global tomography research has progressed to a stage that not only relying
+on the data and methodology, but also involving a lot of technique challenges
+under the hood.
+It has driven us to seek for the most cutting-edge technologies to solve them.
+ADIOS was introduced to save mesh and kernel related data, since we are saving
+petabytes of wavefiled snapshots in a few hours of simulation and it is critical
+even for the most advanced supercomputers in the world.
+ASDF is developed by us to store the seismograms since we have ten millions of
+time series data from thousands of earthquakes. We have to get access and process
+them in a very efficient manner that most of the existing data format just won't
+meet our requirements.
+To handle the complex inversion workflow, we are working RADICAL group to develop
+the workflow management tools that will help manage every piece of task and make
+the user aware if there is anything bad happened during the computation. Those tools that help the
 automation of the workflow, is the "guard" that stand there and monitor things
@@
 
+For the future work, inversion for azimuthal anisotropy and attenuation is on the way.
+The methodolody has already be demonstrated in a few regional studies, such as
+\citep{}. We will start with our current dataset but increase our earthquakes to
+more than $6,000$ in a progressive way , which will covered most of the
+earthquakes in Global CMT project. We also plan to push our model resolution to
+9 secs, with the Summit supercomputer available at Oak Ridge national lab. It will be
+unprecedental in sesimology that pushes global tomography to such resolution, meanwhile
+it will pose new chanllenges. Ensuring the reliability and stability on such a large machine
+and associated file system, for example, will be one of those challenges. Even though the
+computing powers has grown significantly, the storage has not. Our 17 sec has already
+generated a few petabytes of wavefields files and 9 sec will generate at least one order
+of magnitudes more files.
+
+There are certains things that we would like to address on in the near future. First is the
+the seismic data distribtuion. As we know, most of the seismic stations are distributed on
+the continents, while the oceans are most left blank, with only a few stations on a few
+islands. Floating arrays\citep{} might be promising in the future but it all comes down to the 
+data processing and data quality. Second, harnessing such a large data set is difficult.
+Artifical intelligence may be introduced and help us to make decisions when assimilating
+measurements\citep{}.
+
 \newpage
+
 \begin{acknowledgments}
@@
 
-This research used resources of the Oak Ridge Leadership Computing Facility, which is a DOE Office of Science User Facility supported under contract DE-AC05-00OR22725.
-Additional computational resources were provided by the Princeton Institute for Computational Science \& Engineering (PICSciE).
-We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for providing the data used in this study.
-{\color{red} Wenjie: Please add all relevant data centers.} We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
-The open source spectral-element software package SPECFEM3D\_GLOBE and the seismic measurement software package FLEXWIN used for this article are freely available via the Computational Infrastructure for Geodynamics (CIG; {\tt geodynamics.org}).
-This research was supported by NSF grant~1644826.
+This research used resources of the Oak Ridge Leadership Computing Facility,
+which is a DOE Office of Science User Facility supported under contract DE-AC05-00OR22725.
+Additional computational resources were provided by the Princeton Institute
+for Computational Science \& Engineering (PICSciE).
+We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for
+providing the data used in this study.
+{\color{red} Wenjie: Please add all relevant data centers.}
+We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
+The open source spectral-element software package SPECFEM3D\_GLOBE and
+the seismic measurement software package FLEXWIN used for this article are
+  freely available via the Computational Infrastructure for Geodynamics
+  (CIG; {\tt geodynamics.org}). This research was supported by NSF grant~1644826.
 

### 2019-01-25 main.tex
remove unused lines
Updates from ShareLaTeX

--- 2019-01-18 main.tex
@@
 
-\newcommand{\btx}{\textsc{BibTeX}}
+%\newcommand{\btx}{\textsc{BibTeX}}
 
@@
 
+%%---------------------------------------------
+%
+%   Summary
+%
+%%---------------------------------------------
+\begin{summary}
+Building on our first-generation global adjoint tomography model,
+GLAD-M15, we present our second-generation transversely isotropic global model,
+named GLAD-M25, which is the result of ten quasi-Newton tomographic iterations with an
+earthquake database consisting of 1,480 events in the magnitude range $5.8\le M_w \le 7.0$,
+an almost six-fold increase over the previous generation model.
+We calculated fully 3D synthetic seismograms with a shortest period of 17~s based on a GPU-accelerated spectral-element wave
+propagation solver which accommodates effects due to 3-D anelastic crust \& mantle structure, topography \& bathymetry, the ocean load, ellipticity, rotation, and self-gravitation.
+We used an adjoint-state method to calculate Fr\'echet derivatives in 3D anelastic earth models
+facilitated by a parsimonious storage algorithm.
+The simulations were performed on the Cray XK7 ``Titan'' at the Oak Ridge Leadership Computing Facility.
+We quantitatively evaluated GLAD-M25 by assessing misfit reductions and traveltime \& amplitude anomaly histograms in twelve measurement
+categories.
+We performed similar assessments for a held-out dataset consisting of 380 earthquakes,
+with results comparable to the actual inversion.
+We compare GLAD-M25 with numerous other global and regional models,
+and highlight a variety of plumes and subduction zones.
+\end{summary}
+
+\begin{keywords}
+Body waves, Surface waves and free oscillations, Seismic anisotropy, Seismic tomography, Computational seismology, Wave propagation, Waveform inversion
+\end{keywords}
+
 \section{Introduction}
 
-With the development of high performance computing and numerical methods,
-it is now possible to using adjoint method to image the interior the globe
-using thousands of earthquakes.
-
-There are few agreements about the earth model and yet many unknown to be
-resolved. There are quite a lot of global models exits however there is no such con-sense.
-
-The GLAD-M25 is the first earth model that incorporate the P and S wave speed using full waveform inversion.
-Also, people are using specific set of phases in their inversion.
-For P models, people are using P phase and other body wave phases and for S models, people are using mostly S wave phases and surface waves to constrain the structure.
-Those two kinds of models usually reveals very different parts of the earth.
-For example, for P wave, people used it the image the subduction slabs and it is not very good at image lower mantle structures, such as plumes and lower mantle convection.
-For S waves, it is the verse verso.
-
-There are many challenges coming along the way.
-First, the data volume is huge.
-There are in total of 1480 earthquakes used in the inversion stage, added into the database step by step.
-Second, workflow management is crucial dealing with such a large project.
-One factor is coming from the complex workflow.
-There are 4 major building blocks, forward simulation, seismic data processing, adjoint simulation and post-processing.
-Each blocks contains several small blocks.
-The other factor is coming from the number of earthquakes and high demands of computation.
-In each iteration, we are doing 1480 forward and adjoint simulation, generating a few Petabytes of wavefield files and consuming 16 million of CPU hours on the supercomputer at Oak Ridge National Lab.
-There are yet more in data processing stages.
-How to deal with hardware failures is very important and prevent contamination into our inversion results.
-
-Here, we present our GLAD-M25 earth model, with significantly improvements on the plumes and subductions.
-
-test1 (\cite{zhu2012structure}, \cite{zhu2012structure})
-test2 \citep{zhu2015seismic, ekstrom2012global}
-test3 \citet{ekstrom2012global}
+Construction of the first seismic tomographic models of the Earth dates back to the late 1970s~\citep{Aki77,Dziewonski77,SenTok77} and early 1980s~\citep[e.g.,][]{WD84,Nataf1984}.
+Around the same time,
+\cite{BaChLa77}, \cite{Lailly1983}, and~\cite{Tar84} formulated and adapted the theory of adjoint-state methods~\citep{Chavent1974} for exploration seismology with the goal of capturing the full physics of seismic wave propagation.
+Mainly due to computational challenges,
+it took until the late 2000s to see the first applications of adjoint-state methods in regional- and continental-scale earthquake seismology~\citep{tape2009adjoint,Fichtner09,zhu2012structure}.
+The first global ``adjoint tomography'' model of the Earth's mantle was published in 2016~\citep{bozdaug2016global}, more than 30 years after the development of the original ``full waveform inversion'' (FWI) theory.
+
+Current global models are in general agreement regardless of data type and inversion strategy in terms of long-wavelength heterogeneity \citep{ritzwollerlavely1995,TW01,beckerboschi2002}.
+However, discrepancies between models become noticeable as resolution increases.
+Using accurate 3D simulations of seismic wave propagation and the computation of data sensitivities in 3D background models are key requirements for improving resolution in tomographic images on all scales.
+Such detailed images are essential for understanding mantle dynamics and related surface tectonic processes
+---for example the origin of hotspots and the forces behind plate motions and earthquakes.
+Higher resolution wavespeed models are also important for accurately locating earthquakes, and are required from an engineering point of view to assess seismic hazard in earthquake prone regions and to detect nuclear explosions.
+
+With these goals in mind,
+in this study we use a GPU-accelerated version of the 3D spectral-element solver
+SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the Cray ``Titan'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
+These simulations accommodate the full 3D complexity of global Earth models,
+including 3D anelastic crust and mantle structure, self-gravitation, rotation, ellipticity, topography \& bathymetry, and the load of the oceans.
+No compromises are made with regards to resolving the Earth's crust,
+which is explicitly captured by the spectral-element mesh~\citep{tromp2010a},
+thereby eschewing the need for ubiquitous ``crustal corrections''.
+The ultimate goal is to use anything and everything in seismograms,
+a task made partly feasible based on the automated window selection tool FLEXWIN~\citep{maggi2009automated}.
+
+Global adjoint tomography has a well-defined but complex workflow with multiple
+stages involving numerical simulations of synthetic seismograms (forward simulations),
+pre-processing of seismic data, making measurements, data assimilation, and Fr\'echet derivative
+calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
+updates.
+It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
+For each iteration,
+1,480 forward and adjoint simulations need to be performed,
+generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
+How to deal with hardware failures during this process is critical
+to prevent contamination of the inversion results.
+For these reasons, we use RADICAL-SAGA and RADICAL-EnTK as our
+workflow management engines~\citep{EnTK2017}.
+These workflow engines can automatically detected job failures,
+both from the high-performance computing (HPC) system and via user-defined functions.
+This facilitates tracking of tasks and semi-automatic job resubmission if necessary.
+
+In this article we compare the results of our inversion with a number of previous tomographic models.
+On a global scale, we present comparisons with model S362ANI$+$M~\citep{moulik2014anisotropic},
+which is an updated version of model S362ANI~\citep{s362ani},
+the starting model for the GLAD-M15 inversion.
+We also consider global shear wavespeed models S40RTS~\citep{ritsema2011s40rts},
+TX2015~\citep{TX2015}, SEMUCB-WM1~\citep{french2015broad},
+and SL2013sv~\citep{SchaefferLebedev13},
+as well as compressional wavespeed models LLNL-G3Dv3 \citep{simmons2012llnl}, GAP-P4~\citep{fukao2013subducted}, and UU-P07~\citep{van2018atlas}.
+On the scale of North America,
+we make comparisons with models US22~\citep{zhu2017radial},
+a radially anisotropic model based on adjoint tomography using USArray data from 180 regional earthquakes,
+and SL2013NA~\citep{schaeffer2014imaging},
+a modification of global model SL2013sv focused on North America.
+In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison.
+EU60 is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
+Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227 earthquakes recorded by more than 1,800 stations.
+
+This article is organized as follows.
+Sections~\ref{section:start}--\ref{section:data} describe the starting model,
+earthquake database, and the seismographic data set. 
+Sections~\ref{section:misfit} and~\ref{section:parameterization} describe the misfit function minimized during the inversion process
+and the related model parameterization.
+In Section~\ref{section:workflow} we describe the adjoint tomography workflow in some detail.
+Sections~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 320 earthquakes.
+Finally, in Section~\ref{section:model}, we describe the model in detail,
+offering many comparisons with various global and regional models, as described in the proceeding paragraph.
+We conclude with a discussion of future opportunities and directions.
 
 \section{Starting model GLAD-M15}
+\label{section:start}
 
 As a continuation of our previous work~\citep{bozdaug2016global},
-we used ``first-generation'' model GLAD-M15 as our
+we used first-generation model GLAD-M15 as our
 starting model.
@@
 model GLAD-M15, we initially selected 784 carefully chosen additional earthquakes
-from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{Ekstrom12},
+from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global},
 and added them to our database, resulting in a total number of 1,040 earthquakes.
@@
 Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers.
-The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the dataset.}
+The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}
   \label{fig:stations}
@@
 including the seismic traces, event information files (QuakeML), and station response files (StationXML).
-The related APIs are carefully designed for easy data extraction and parallel implementation.
+The related Application Programming Interfaces (API)s are carefully designed for easy data extraction and parallel implementation.
 
@@
 
-\section{Model parametrization}
+\section{Model parameterization}
+\label{section:parameterization}
 
@@
 \section{Adjoint tomography workflow}
+\label{section:workflow}
 
@@
 described in Section~\ref{section:ASDF}.
-For a given earthquake dataset, the conversion to ASDF needs to be performed once and for all.
+For a given earthquake data set, the conversion to ASDF needs to be performed once and for all.
 In the following sections we highlight several important aspects of the workflow.
@@
 The figure nicely highlights all the well known body traveltime branches.
-The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1376~s time bin.
+The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1,376~s time bin.
 
@@
   A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
+Major traveltime branches are labeled.
+Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
   }
@@
   \item Line search to determine the magnitude of the model update.
-  The search direction is determined using a nonlinear conjugate gradient method~\citep{wright1999numerical} (iterations 16--21) or an L-BFGS quasi-Newton method (iterations 22--25).
+  The search direction is determined using a nonlinear conjugate gradient method~\citep{wright1999numerical} (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25).
   We used a subset of 120 earthquakes to conduct the line search and determine the step length.
@@
 \section{Misfit evolution}
+\label{section:misfit_evolution}
 
@@
 \section{Model evaluation}
-
-In this section we evaluate model GLAD-M25 further based on a point-spread
-function resolution analysis as well as a ``held-out'' dataset, that is,
-a set of data not used in the actual structural inversion.
+\label{section:evaluation}
+
+% In this section we evaluate model GLAD-M25 further based on a point-spread
+% function resolution analysis as well as a ``held-out'' data set, that is,
+% a set of data not used in the actual structural inversion.
 
@@
 require roughly the same computational resources as the actual inversion.
-In lieu of such tests, we performed two point-spread function analyses~
-\citep{fichtner2011resolution,zhu2015seismic,bozdaug2016global}.
-
-\subsection{Held-out dataset}
+In lieu of such tests, we previously performed two point-spread function (PSF) analyses
+for model GLAD-M15~\citep{bozdaug2016global}.
+Since GLAD-M25 --- like its predecessor GLAD-M15 --- uses waves with a shortest period of 17~s
+but an earthquake database that is six times larger,
+we can expect improved versions of these already successful PSF tests.
+In the interest of focusing our efforts on obtaining the new model,
+we chose to direct our limited OLCF INCITE allocation towards the actual inversion
+rather than improved PSF tests.
+
+\subsection{Held-out data set}
 
@@
 and \cite{bozdaug2016global}, we selected 360 earthquakes that were not used
-in the actual inversion. This held-out dataset consists of all magnitude 6.3--7.0
+in the actual inversion. This held-out data set consists of all magnitude 6.3--7.0
 earthquakes in the global CMT catalog that were not used in the inversion.
@@
 %   \end{tabular}\\
-%   \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
+%   \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out data set}
 %   \label{table:misfit_reduction_M00_M25_360}
@@
 \section{Model GLAD-M25}
+\label{section:model}
 
@@
 We conclude by highlighting various slabs and plumes in the model.
+Vertical cross sections are plotted relative to the spherical average of MODEL-M25,
+as discussed in Appendix~\ref{sec:1Dmodel}.
+For plotting purposes and use in other applications,
+an expansion of the model in spherical harmonics and radial B-splines is
+discussed in Appendix~\ref{sec:shanalysis}.
 
@@
 
-{\color{red} Wenjie: Note: add spherical harmonic analysis later.}
+%{\color{red} Wenjie: Note: add spherical harmonic analysis later.}
 
@@
 beneath the European continent and the North Atlantic based on the assimilation of data from
-190 earthquakes recorded by 745 seismographic station.
+190 earthquakes recorded by 745 seismographic stations.
 
@@
 Map views of GLAD-M25 centered on Asia are plotted in Fig.~\ref{fig:asia-vs},
-together with S362ANI$+$M, S40RTS, and regional model EARA2014~\citep{chen2015multiparameter}.
+together with S362ANI$+$M, SL2013sv~\citep{SchaefferLebedev13}, and regional model EARA2014~\citep{chen2015multiparameter}.
 EARA2014 is a transversely isotropic model based on adjoint
@@
   \caption{Map views of shear wavespeed variations beneath Asia for GLAD-M25~(first column),
-  global models S362ANI$+$M (second column) and S40RTS (third column), and regional model EARA2014~\citep[last column;][]{chen2015multiparameter}.}
+  global models S362ANI$+$M (second column) and SL2013sv (third column), and regional model EARA2014~\citep[last column;][]{chen2015multiparameter}.}
   \label{fig:asia-vs}
@@
 At 300~km depth, we see sharpened subduction of the Nazca plate
-in GLAD-M25 compared to S372ANI+M, similar in shape to  model LLNL-G3Dv3.
+in GLAD-M25 compared to S362ANI+M, similar in shape to model LLNL-G3Dv3.
 Moving to greater depths,
@@
 
-\begin{figure}[h]
-    \centering
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:plumes_a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:plumes_b}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:plumes_c}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:plumes_d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:plumes_a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:plumes_g}}\\
+\begin{figure}[ht]
+    \centering
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}}\\
     \caption{Vertical cross sections for various plumes for models GLAD-M25 ($V_\textrm{P}$; left column), TX2015~\citep[$V_\textrm{S}$;][]{TX2015} (center column), and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad} (right column).
@@
 
-%\begin{figure}[h]
+%\begin{figure}[ht]
 %    \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
@@
 
+\section{Discussion}
+
+Seismology is a science driven by data.
+There was a time when seismologists would meticulously inspect single seismograms to glean valuable information from them.
+Today, we have easy access to data from thousands of earthquakes recorded by tens of thousands of seismographic stations, and individual inspection of all of these records has become impossible.
+Still, it would be a shame not to utilize as much as possible of the information in this massive seismographic database.
+
+To facilitate fast and effective access to such vast data resources,
+we use ASDF~\citep{krischer2016adaptable} in the preprocessing stage of the adjoint tomography workflow,
+and to accommodate I/O during postprocessing stage we use ADIOS~\citep{liu2014hello}.
+For data assimilation,
+tools, such as FLEXWIN, which automatically select data windows suitable for measurements,
+are indispensable, and we see tremendous opportunities for the use of machine learning algorithms in this context~\citep[e.g.,][]{chen2017}.
+
+Some form of automated parallel workflow management is critical for the global adjoint tomography process,
+because classical inversion workflows suffer from I/O inefficiencies, lack of fault tolerance, and an inability to work in distributed resource environments.
+The RADICAL-SAGA and RADICAL-EnTK workflow management engines~\citep{EnTK2017} facilitate tracking of tasks and job failure detection,
+enabling semi-automatic job resubmission if necessary.
+
+It should be clear from this discussion that modern seismic tomography requires close collaborations with computational scientists, HPC specialists, and visualization experts,
+as reflected in the list of authors for this article, in addition to access to the most advanced computational platforms,
+such as those offered through the DOE INCITE and NSF XSEDE programs.
+
 \section{Conclusion}
 
-In summary, the new model performs well for the held-out dataset,
-both in terms of misfit reductions and measurement distributions
-in all twelve measurement categories. We expect to see similar
-behavior for any future earthquakes.
-
-Seismology is driven by data. Back into time, seismologists would look at
-single seismograms and pick valuable information out the them. Now, we have
-ten thousands of seismograms deployed globally and it will be a pity not
-to take all the information we have. Even though GLAD-M25 is following-up
-of GLAD-M15. It has many superior advantages and improvements. We increase
-the dataset from 253 to 1480 earthquakes, with carefully inverted sources
-in the 3D earth structures. We have 360 earthquakes used in the test
-dataset, which is already larger than the most of the dataset other people used
-for their inversion. We culled every seismograms from various data centers,
-thanks to the open environment and data sharing spirit of our seismology community.
-With very careful checks by assessing the integrity of instrument response
-and deployment, evaluating the signal-to-noise ratios, picking the time windows
-using over 20 criteria, cleaning windows by their statistical behavior, and
-calculating weights to balance the uneven distribution of earthquakes and
-seismic stations, we really have done a lot to ensure the cleanness of the
-data assimilated into our inversion and make sure every piece of value information
-will be used but rejecting the crap data.
-
-There are also quite a lot of technique challenges on the way but we are seeking
-the most cutting-edge technologies to solve them. ADIOS was introduced to save mesh
-and kernel related data, since we are saving petabytes of wavefiled snapshots
-in a few hours of simulation and it is critical even for the most advanced
-supercomputers in the world. ASDF is developed by us to store the seismograms
-since we have ten millions of time series data from thousands of earthquakes.
-We have to get access and process them in a very efficient manner that most of
-the existing data format just won't meet our requirements. To handle the complex
-inversion workflow, we are working RADICAL group to develop the workflow management
-tools that will help manage every piece of task and make the user aware if there
-is anything bad happened during the computation. Those tools that help the
-automation of the workflow, is the "guard" that stand there and monitor things
-to make sure our scientific results away from contamination. Besides, the
-developer of SPECFEM packages, they dedicate more than ten years of work,
-to develop the software and make it fast, efficient and robust for global scale of simulation.
-They are working closely with hardware vendors such as Cray, IBM and NVidia to adapt
-the code to architecture of the most advanced supercomputers. We are soon
-moving our simulation to Summit, the world No.1 supercomputer at the Oak Ridge
-National Lab.
-
-\newpage
+Building on our experiences during the construction of our first-generation global adjoint tomography model GLAD-M15~\citep{bozdaug2016global},
+for this study we expanded our earthquake database from 253 to 1,480 events,
+which were collectively recorded by more than 11,000 seismographic stations.
+We used three-component seismograms in four period bands,
+namely 17--40~s body waves, 40--100~s body waves, 40--100~s surface waves, and 90--250~s surface waves,
+resulting in twelve measurement categories.
+This culminated in the assimilation of more than 18~million time windows.
+
+GLAD-M25 --- like its predecessor GLAD-M15 --- invokes no crustal corrections,
+and constrains crust and mantle shear and compressional wavespeeds simultaneously.
+The effects of attenuation are fully accommodated,
+both in forward and in adjoint simulations.
+
+GLAD-M25 was quantitatively evaluated in several ways.
+First, it produces significant misfit
+reductions in all twelve measurements categories.
+Second,
+it produces nicely-centered Gaussian traveltime \& amplitude anomaly histograms
+in all measurement categories.
+Finally,
+for a held-out data set of 360 events
+we see similar misfit reductions and traveltime \& amplitude anomaly histograms as in the actual inversion.
+
+When we compare GLAD-M25 with other global models,
+we find overall good agreement at longer wavelengths.
+However, unlike other global models, when we compare GLAD-M25 with regional models
+we also observe generally good agreement at smaller wavelengths,
+and, in particular, plumes and subduction zones feature prominently.
+
+Obvious future directions of research include growing the earthquake database further to the roughly 6,000 earthquakes in the right magnitude range already available via the Global CMT database
+and reducing the shortest simulation period further from 17~s to 8.5~s.
+The most recent machine at OLCF, called ``Summit'', an IBM Power9 accelerated by NVIDIA Tesla V100 GPUs,
+can readily accommodate such simulations.
+
+Other future directions of research involve inversions for azimuthal anisotropy
+and attenuation.
+The feasibility of such inversions on a regional scale have already been demonstrated in a studies focused on Europe by~\cite{ZhuTromp2013} and \cite{Zhuetal2013}.
+
 \begin{acknowledgments}
@@
 \section{Spherically symmetric average model}
+\label{sec:1Dmodel}
 
@@
 \section{Spherical harmonic model expansion}
-
-{\color{red} Wenjie, to save space, this appendix could also go in the supplementary online material.}
+\label{sec:shanalysis}
 

### 2019-01-25 main.tex
add p phase measurements hist

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
+  \caption{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, \textbf{Black}), GLAD-M15 (M15, \textbf{{\color{ForestGreen} Green}}) and GLAD-M25 (M25, \textbf{{\color{Red} Red}}).
+  Each column represents one component, and each row corresponds to a period band.
+  The numbers above the top right of each panel denote the number of measurements in the corresponding category.
+  The total number of measurements is 18.2 million.
+  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}
+  \label{fig:phase_hist}
+\end{figure}
+
+Fig~\ref{fig:P_phase_hist} shows histograms of the phase measurements of first P
+arrivals in 4 of the body wave measurement categories. All the
+categories show consistent reduction in both mean and variance values. 
+Even though there are many kinds of phases assimilated  and
+P arrivals only contribute ~8\% of the overall measurements,
+the histogram shows we are still doing a good job at minimizing the
+misfit of the P arrivals.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
+  \caption{Histograms of phase measurements of P arrivals in four measurement categories for S362ANI combined with CRUST2.0 (M00, \textbf{Black}), GLAD-M15 (M15, \textbf{{\color{ForestGreen} Green}}) and GLAD-M25 (M25, \textbf{{\color{Red} Red}}).
+Other settings are the same as Fig.~\ref{fig:phase_hist}.
+}
+  \label{fig:P_phase_hist}
+\end{figure}
+
 Fig~\ref{fig:amp_hist} shows histograms of the amplitude
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
-  \caption{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, \textbf{Black}), GLAD-M15 (M15, \textbf{{\color{ForestGreen} Green}}) and GLAD-M25 (M25, \textbf{{\color{Red} Red}}).
-  Each column represents one component, and each row corresponds to a period band.
-  The numbers above the top right of each panel denote the number of measurements in the corresponding category.
-  The total number of measurements is 18.2 million.
-  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}
-  \label{fig:phase_hist}
-\end{figure}
-
-\begin{figure}
-  \centering
   \includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
@@
 \end{figure}
-
-{\color{red} Wenjie: Also include the P arrival measurements here.}
 

### 2019-01-28 main.tex
Updates from ShareLaTeX

--- 2019-01-25 main.tex
@@
 \title[Global Adjoint Tomography -- Model GLAD-M25]
-  {Global adjoint tomography -- Model GLAD-M25}
+  {Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}}
 
@@
   $^2$ Nanjing University, Nanjing, China\\
-  $^3$ Department of Geophysics, Colorado School of Mines, Colden, CO 80401, USA\\
+  $^3$ Department of Geophysics, Colorado School of Mines, Golden, CO 80401, USA\\
   $^4$ Extreme Computing Research Center, King Abdullah University of Science and Technology, \\Thuwal 23955-6900, Kingdom of Saudi Arabia\\
@@
 earthquake database consisting of 1,480 events in the magnitude range $5.8\le M_w \le 7.0$,
-an almost six-fold increase over the previous generation model.
+an almost six-fold increase over the first-generation model.
 We calculated fully 3D synthetic seismograms with a shortest period of 17~s based on a GPU-accelerated spectral-element wave
 propagation solver which accommodates effects due to 3-D anelastic crust \& mantle structure, topography \& bathymetry, the ocean load, ellipticity, rotation, and self-gravitation.
-We used an adjoint-state method to calculate Fr\'echet derivatives in 3D anelastic earth models
+We used an adjoint-state method to calculate Fr\'echet derivatives in 3D anelastic Earth models
 facilitated by a parsimonious storage algorithm.
@@
 categories.
-We performed similar assessments for a held-out dataset consisting of 380 earthquakes,
+We performed similar assessments for a held-out data set consisting of 380 earthquakes,
 with results comparable to the actual inversion.
@@
 it took until the late 2000s to see the first applications of adjoint-state methods in regional- and continental-scale earthquake seismology~\citep{tape2009adjoint,Fichtner09,zhu2012structure}.
-The first global ``adjoint tomography'' model of the Earth's mantle was published in 2016~\citep{bozdaug2016global}, more than 30 years after the development of the original ``full waveform inversion'' (FWI) theory.
-
-Current global models are in general agreement regardless of data type and inversion strategy in terms of long-wavelength heterogeneity \citep{ritzwollerlavely1995,TW01,beckerboschi2002}.
+The first global ``adjoint tomography'' model of the Earth's mantle,
+GLAD-M15, was published in 2016~\citep{bozdaug2016global}, more than 30 years after the development of the original ``full waveform inversion'' (FWI) theory.
+
+Current global seismic models are in general agreement regardless of data type and inversion strategy in terms of long-wavelength heterogeneity \citep{ritzwollerlavely1995,TW01,beckerboschi2002}.
 However, discrepancies between models become noticeable as resolution increases.
@@
 in this study we use a GPU-accelerated version of the 3D spectral-element solver
-SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the Cray ``Titan'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
+SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the Cray supercomputer ``Titan'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
 These simulations accommodate the full 3D complexity of global Earth models,
@@
 thereby eschewing the need for ubiquitous ``crustal corrections''.
-The ultimate goal is to use anything and everything in seismograms,
+The ultimate goal is to use every single piece of information in seismograms,
 a task made partly feasible based on the automated window selection tool FLEXWIN~\citep{maggi2009automated}.
 
-Global adjoint tomography has a well-defined but complex workflow with multiple
-stages involving numerical simulations of synthetic seismograms (forward simulations),
-pre-processing of seismic data, making measurements, data assimilation, and Fr\'echet derivative
-calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
-updates.
+Global adjoint tomography has a well-defined but complex workflow with multiple stages.
+% including numerical simulations of synthetic seismograms (forward simulations) for all events,
+% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
+% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
+% updates.
 It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
@@
 to prevent contamination of the inversion results.
-For these reasons, we use RADICAL-SAGA and RADICAL-EnTK as our
-workflow management engines~\citep{EnTK2017}.
-These workflow engines can automatically detected job failures,
+For these reasons, we use EnTK as our
+workflow management engine~\citep{EnTK2017}.
+This workflow engine can automatically detected job failures,
 both from the high-performance computing (HPC) system and via user-defined functions.
@@
 a modification of global model SL2013sv focused on North America.
-In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison.
-EU60 is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
+In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison,
+which is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
 Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227 earthquakes recorded by more than 1,800 stations.
@@
 Sections~\ref{section:start}--\ref{section:data} describe the starting model,
-earthquake database, and the seismographic data set. 
+earthquake database, and seismographic data set. 
 Sections~\ref{section:misfit} and~\ref{section:parameterization} describe the misfit function minimized during the inversion process
@@
 Instead of relying on ubiquitous ``crustal corrections'',
-the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us accurately accommodate topography and bathymetry as well as variations in the Moho.
-GLAD-M15 was constructed using a global data base of 256 earthquakes.
+the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
+GLAD-M15 was constructed using a global database of 256 earthquakes.
 The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
@@
 
-In addition to the 256 earthquakes used for the construction of first generation
-model GLAD-M15, we initially selected 784 carefully chosen additional earthquakes
+In addition to the 256 earthquakes used for the construction of GLAD-M15, we initially carefully selected 784 additional earthquakes
 from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global},
-and added them to our database, resulting in a total number of 1,040 earthquakes.
+resulting in a total number of 1,040 earthquakes.
 To ensure a good signal-to-noise ratio on a global scale,
 the smallest moment magnitude in the database is set to~5.5,
-and to avoid complications associated with source size,
+and to avoid complications associated with source dimension and directivity,
 the largest moment magnitude is set to~7.2.
@@
 Before using the 1,040 earthquakes in our structural inversion,
-we performed CMT inversions in model GLAD-M15,
+we performed CMT inversions using model GLAD-M15,
 the results of which are summarized in Fig.~\ref{fig:source_correction}.
@@
 To balance the coverage,
+following a strategy articulated by~\cite{Ruanetal2018},
 we assign receiver weights~$\omega_{cr}$ based on the expression
@@
 number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
-The calculation of the weights may be abstracted as: given a spatial distribution of
-points on the unit sphere, determine a weighting associated with each point.
+The calculation of the weights may be abstracted as: given a distribution of
+points on the unit sphere, determine a spatial weighting associated with each point.
 
@@
 and the centroid location~(latitude, longitude, and depth).
-The calculation of each associated Fr\'echet derivative requires one full 3D forward simulation,
-so, considering we have more than one thousand events,
-these source inversions are computationally very expensive.
-
-Because we allow the synthetics to shift by an amount~$\Delta t$ relative to the data,
+These source inversions are computationally very expensive,
+because for each of the 1,040~events, nine full 3D forward simulations are required.
+
+Because we allow the synthetics to shift in phase by an amount~$\Delta t$ relative to the data,
 the CMT inversion has unreliable sensitivity to the centroid time.
@@
   \includegraphics[width=\textwidth]{figures/events_1480.pdf}
-  \caption{1,480 earthquakes used in this study.
+  \caption{The 1,480~earthquakes used in this study.
 (a) Distribution of earthquakes.
-The color of each beach ball reflects its depth range, where blue designate events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
+The color of each beach ball reflects its depth range, where blue designates events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
 (b) \& (c) Histograms of earthquake moment magnitudes and depths.}
@@
   \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
-  \caption{Distribution of 11,800 seismographic stations used in this study.
+  \caption{Distribution of the 11,800~seismographic stations used in this study.
 Colors denote the number of events for which a given station contributes waveforms to the structural inversion.
@@
     \item Data organization: the container is self-describing. Data, including waveform, source, and station information, are organized into well-defined structures.
-    \item Reproducibility: the container enables scientists to keep track of what has been done to data so that results can be reproduced.
+    \item Reproducibility: the container enables scientists to keep track of which operations have been performed on the data so that results can be reproduced.
     \item Efficiency: the format provides easy mechanisms for parallel processing.
@@
 full advantage of parallel computing. In our workflow,
-one ASDF file contains all the information needed for data processing,
-including the seismic traces, event information files (QuakeML), and station response files (StationXML).
-The related Application Programming Interfaces (API)s are carefully designed for easy data extraction and parallel implementation.
+one ASDF file contains all the information needed for processing one event,
+including the seismic traces, an event information file (in QuakeML format), and station response files (in StationXML format).
+The related Application Programming Interfaces (API)s are carefully designed for easy data extraction and parallel processing.
 
@@
 One of the biggest challenges in the construction of the misfit function is the
-highly uneven distribution of earthquakes and seismographic stations,
+highly uneven distribution of earthquakes --- discussed in Section~\ref{section:earthquakes} --- and seismographic stations,
 which must be counterbalanced by geographically weighting the data.
@@
 $R_{sc}$ the number of receivers recording source~$s$ in category~$c$,
-and~$W_{scr}$ the number of measurement windows for source~$s$, category~$c$
+and~$W_{scr}$ the number of measurement windows for source~$s$, category~$c$,
 and receiver~$r$.
@@
 and the category weight, $\omega_c$\,, is the reciprocal of the number of measurements in that
-category.
-Earthquakes are mainly confined to plate boundaries,
+category, $1/C$.
+Earthquakes mainly occur along plate boundaries,
 and most seismic stations are confined to the continents,
@@
 Following the same strategy as for the receiver weights in the source inversions,
-we define the source and receiver weights as
+we define source and receiver weights as
 \begin{equation}
@@
 
-The adjoint tomography workflow is shown in Fig.~\ref{fig:adjoint_workflow}.
+The adjoint tomography workflow is depicted in Fig.~\ref{fig:adjoint_workflow}.
 It starts with the selection of earthquakes, as discussed in Section~\ref{section:earthquakes}.
@@
 of stations, and the current earth model as input.
-The solver is GPU accelerated, and the simulations are performed on the Cray `Titan'
-at the Oak Ridge Leadership Computing Facility.
+The solver is GPU accelerated, and the simulations are performed on the Cray supercomputer ``Titan''
+at the OLCF.
 To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA
@@
   \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
-  \caption{Preprocessing workflow for seismic data.}
+  \caption{Sub-workflow workflow for preprocessing seismic data.}
   \label{fig:preprocess_workflow}
@@
 
+To illustrate which seismic phases end up being picked,
 Fig.~\ref{fig:window_density} shows a time-distance plot
@@
 A total of 4,363,719 time windows were picked in this category.
-The figure nicely highlights all the well known body traveltime branches.
+The figure nicely highlights all the well known vertical-component body traveltime branches.
 The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1,376~s time bin.
@@
 Collectively,
-the adjoint simulations are the most expensive stage of the adjoint tomography workflow. 
+the adjoint simulations are the most expensive stage of the workflow. 
 Adjoint simulations take the adjoint sources as input, and generate Fr\'echet
@@
 For every model iteration,
-we perform 1,480 forward and adjoint simulations, each involving hundreds of
+we performed up to 1,480 forward and adjoint simulations, each involving hundreds of
 compute cores and graphics cards, as well as heavy I/O.
-The workflow is prone to human error and hardware failure, making it fragile.
-For these reasons, we wish to harden the worflow by taking advantage of modern
+The workflow is prone to human error and hardware failure, making it fragile~~\citep{Lefebvre2018}.
+For these reasons, we hardened the workflow by taking advantage of modern
 workflow management software.
-With this goal in mind, we selected RADICAL-SAGA and RADICAL-EnTK as our
+We selected RADICAL-SAGA and RADICAL-EnTK as our
 workflow management engines, and developed complementary seismic tomography
@@
   (a) Evolution of the total misfit. (b)--(j) Misfit in
-  each period band (rows) on three components (columns). (e)--(g) From GLAD-M18,
+  each period band (rows) on three components (columns). (e)--(g) At iteration 18,
   we  split the 40--100~s period band into two
@@
 The total number of selected windows exceeds 18~million.
-Fig~\ref{fig:phase_hist} shows histograms of the resulting phase
+Fig.~\ref{fig:phase_hist} shows histograms of the resulting phase
 measurements in all twelve measurement categories.
@@
 
-Fig~\ref{fig:amp_hist} shows histograms of the amplitude
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
+  \caption{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
+  Each column represents one component and each row corresponds to a period band.
+  The numbers above the top right of each panel denote the number of measurements in the corresponding category.
+  The total number of measurements is 18.2 million.
+  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}
+  \label{fig:phase_hist}
+\end{figure}
+
+Fig.~\ref{fig:P_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components.
+Both components exhibit consistent reductions in terms of both mean and variance. 
+These arrivals --- almost 900,000 measurements in the 17--40~s and 40--100~s period bands, roughly~$\sim8\%$ of the database --- are of great importance, because they help constrain the compressional wavespeed structure in the model.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
+  \caption{Histograms of traveltime measurements of 17--40~s P arrivals on the vertical and radial for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
+Other settings are the same as in Fig.~\ref{fig:phase_hist}.
+{\color{red}Wenjie: remove 40--100~s.}}
+  \label{fig:P_phase_hist}
+\end{figure}
+
+Fig.~\ref{fig:amp_hist} shows histograms of the amplitude
 measurements for all twelve measurement categories,
@@
 suitably selected, because the scalar moment affects all measurement categories equally.
-In the next phase of our ongoing inversion we plan to begin assimilating amplitude measurements,
-while simultaneously adding shear attenuation as a new model parameter.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
-  \caption{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, \textbf{Black}), GLAD-M15 (M15, \textbf{{\color{ForestGreen} Green}}) and GLAD-M25 (M25, \textbf{{\color{Red} Red}}).
-  Each column represents one component, and each row corresponds to a period band.
-  The numbers above the top right of each panel denote the number of measurements in the corresponding category.
-  The total number of measurements is 18.2 million.
-  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}
-  \label{fig:phase_hist}
-\end{figure}
+In the next phase of our ongoing inversion we plan to begin assimilating amplitude measurements while simultaneously adding shear attenuation as a new model parameter.
 
@@
 Theses events were not used in the structural inversion.
-(a) Distribution of events, color coded by depth range as in Fig.~\ref{fig:event_1480}.
+(a) Distribution of events color coded by depth range as in Fig.~\ref{fig:event_1480}.
 (b) \& (c) Histograms of moment magnitude and depth.}
@@
 as well a S362ANI combined with CRUST2.0.
-It is comforting to see that the reductions are comparable to the
+It is a validation of our approach to see that the reductions are comparable to the
 values tabulated in Table~\ref{table:misfit_reduction_M15_M25} for the actual inversion.
@@
 We conclude by highlighting various slabs and plumes in the model.
-Vertical cross sections are plotted relative to the spherical average of MODEL-M25,
+Vertical cross sections are plotted relative to the spherical average of GLAD-M25,
 as discussed in Appendix~\ref{sec:1Dmodel}.
@@
 Overall, these models are in good agreement
-at the longest wavelengths, especially Glad-M25 and S362ANI$+$M.
+at the longest wavelengths, especially GLAD-M25 and S362ANI$+$M.
 The perturbations in GLAD-M25 tend to be larger than in the other models,
@@
   \caption{Map views of global shear wavespeed perturbations at various depths for  model
-  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic}
+  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic},
   and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
@@
 compressional waves simultaneously. In Fig.~\ref{fig:global-vs} we
-compare global maps of our compressional wavespeed model with P models
+compare global maps of our compressional wavespeed model with global P models
 LLNL-G3Dv3~\citep{simmons2012llnl} and GAP-P4~\citep{fukao2013subducted}.
@@
   \caption{Map views of global compressional wavespeed variations at various depths for model
-  GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl} and
+  GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl}, and
   GAP-P4~\citep[right column;][]{fukao2013subducted}.
@@
 We see slab ponding in the transition zone beneath the western Mediterranean
-associated with slab roll-back of the Appennines-Maghrebides subduction zone
-~\citep{Giordano2017Magmatic}.
+associated with slab roll-back of the Appennines-Maghrebides subduction zone.
 At shallower depths, we see low wavespeeds along its western border,
@@
 
-Beneath the Atlantic Ocean, our model strengthens slow anomalies beneath the
+Beneath the Atlantic Ocean, our model enhances slow anomalies beneath the
 ridges, especially underneath Iceland and the Azores.
@@
 TX2015~\citep[$V_\textrm{S}$;][]{TX2015}, and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad}.
-
-Some plumes originate from the CMB and extend all the way to the Earth's surface.
 The three models tend to agree near the CMB,
@@
 we use ASDF~\citep{krischer2016adaptable} in the preprocessing stage of the adjoint tomography workflow,
-and to accommodate I/O during postprocessing stage we use ADIOS~\citep{liu2014hello}.
+and to accommodate I/O during postprocessing stage we use the ADIOS library~\citep{liu2014hello}.
 For data assimilation,
@@
 Some form of automated parallel workflow management is critical for the global adjoint tomography process,
-because classical inversion workflows suffer from I/O inefficiencies, lack of fault tolerance, and an inability to work in distributed resource environments.
-The RADICAL-SAGA and RADICAL-EnTK workflow management engines~\citep{EnTK2017} facilitate tracking of tasks and job failure detection,
-enabling semi-automatic job resubmission if necessary.
+because classical inversion workflows suffer from I/O inefficiencies, lack of fault tolerance, and an inability to work in distributed resource environments~\citep{Lefebvre2018}.
+The EnTK workflow management engine~\citep{EnTK2017}
+largely overcomes these limitations by facilitating tracking of tasks and job failure detection,
+thereby enabling semi-automatic job resubmission if necessary.
 
@@
 and reducing the shortest simulation period further from 17~s to 8.5~s.
-The most recent machine at OLCF, called ``Summit'', an IBM Power9 accelerated by NVIDIA Tesla V100 GPUs,
-can readily accommodate such simulations.
+The most recent machine at OLCF, called ``Summit'', uses IBM Power9 CPUs accelerated by NVIDIA Tesla V100 GPU and can readily accommodate such simulations.
 
@@
 providing the data used in this study.
-{\color{red} Wenjie: Please add all relevant data centers.}
 We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.

### 2019-01-28 main.tex
update window figures

--- 2019-01-25 main.tex
@@
 
-Fig.~\ref{fig:window_density} shows a time-distance plot
+Fig.~\ref{fig:window_density_Z} shows a time-distance plot
 for vertical component 17--40~s body waves in which the Pyflex window count is used to identify parts of seismograms being assimilated.
@@
   }
-  \label{fig:window_density}
+  \label{fig:window_density_Z}
+\end{figure}
+
+Fig.~\ref{fig:window_density_R} and Fig.~\ref{fig:window_density_T} shows for Radial and Transverse component in 17--40~s period bands.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
+  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for Radial component 17--40~s body waves.}
+  \label{fig:window_density_R}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
+  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for Transverse component 17--40~s body waves.}
+  \label{fig:window_density_T}
 \end{figure}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
+  \caption{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, \textbf{Black}), GLAD-M15 (M15, \textbf{{\color{ForestGreen} Green}}) and GLAD-M25 (M25, \textbf{{\color{Red} Red}}).
+  Each column represents one component, and each row corresponds to a period band.
+  The numbers above the top right of each panel denote the number of measurements in the corresponding category.
+  The total number of measurements is 18.2 million.
+  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}
+  \label{fig:phase_hist}
+\end{figure}
+
+Fig~\ref{fig:P_phase_hist} shows histograms of the phase measurements of first P
+arrivals in two of the body wave measurement categories. All the
+categories show consistent reduction in both mean and variance values. 
+Although there are various phases assimilated and
+P arrivals only contribute ~8\% of the overall measurements,
+the histogram shows we are still doing a good job at minimizing the
+misfit of the P arrivals.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
+  \caption{Histograms of phase measurements of P arrivals in two measurement categories for S362ANI combined with CRUST2.0 (M00, \textbf{Black}), GLAD-M15 (M15, \textbf{{\color{ForestGreen} Green}}) and GLAD-M25 (M25, \textbf{{\color{Red} Red}}).
+Other settings are the same as Fig.~\ref{fig:phase_hist}.
+}
+  \label{fig:P_phase_hist}
+\end{figure}
+
 Fig~\ref{fig:amp_hist} shows histograms of the amplitude
@@
 
+P phase measurements were also extracted and compared in Fig.~\ref{fig:phase_hist_360_P} for 3 models. The behavior is consistent as we expected.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_360_P.pdf}
+  \caption{Histograms of phase measurements of P arrivals for the 360 events in the held-out database in Vertical and Radial 17--40~s period band .}
+  \label{fig:phase_hist_360_P}
+\end{figure}
+
 \section{Model GLAD-M25}
@@
 bathymetry and corresponds to a portion of ancient oceanic
-Lithosphere~\citep{muller2008}.
+Lithosphere~\citep{muller2008age}.
 A remnant of the Juan de Fuca plate,

### 2019-01-28 main.tex
Updates from ShareLaTeX

--- 2019-01-28 main.tex
@@
 Both components exhibit consistent reductions in terms of both mean and variance. 
-These arrivals --- almost 900,000 measurements in the 17--40~s and 40--100~s period bands, roughly~$\sim8\%$ of the database --- are of great importance, because they help constrain the compressional wavespeed structure in the model.
+These arrivals --- almost 530,000 measurements in the 17--40~s period band, roughly~$\sim3\%$ of the database --- are of great importance, because they help constrain the compressional wavespeed structure in the model.
 
@@
   \caption{Histograms of traveltime measurements of 17--40~s P arrivals on the vertical and radial for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
-Other settings are the same as in Fig.~\ref{fig:phase_hist}.
-{\color{red}Wenjie: remove 40--100~s.}}
+Other settings are the same as in Fig.~\ref{fig:phase_hist}.}
   \label{fig:P_phase_hist}

### 2019-01-29 main.tex
Updates from ShareLaTeX

--- 2019-01-28 main.tex
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
+  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
+  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
+  The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1,376~s time bin.
+  Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
+  }
+  \label{fig:window_density_Z}
+\end{figure}
+
 As illustrated in Fig.~\ref{fig:preprocess_workflow}, the preprocessing workflow
@@
 To illustrate which seismic phases end up being picked,
-Fig.~\ref{fig:window_density} shows a time-distance plot
-for vertical component 17--40~s body waves in which the Pyflex window count is used to identify parts of seismograms being assimilated.
-A total of 4,363,719 time windows were picked in this category.
-The figure nicely highlights all the well known vertical-component body traveltime branches.
-The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1,376~s time bin.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
-  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
-  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-Major traveltime branches are labeled.
-Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
+Figs.~\ref{fig:window_density_Z}, \ref{fig:window_density_R}, and \ref{fig:window_density_T} show time-distance plots
+for vertical, radial, and transverse component 17--40~s body waves,
+respectively,
+in which the Pyflex window count is used to identify parts of seismograms being assimilated.
+The figures nicely highlight all the well known body traveltime branches.
+The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
+This is something we will reconsider in future applications, perhaps by introducing aspects of machine learning.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
+  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
+   A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
+   The maximum window count is 7,542.
    }
-  \label{fig:window_density}
+  \label{fig:window_density_R}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
+  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
+   A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
+   The maximum window count is 7,208.
+   Only SH travetime branches are labeled.}
+  \label{fig:window_density_T}
 \end{figure}
@@
 workflow management software.
-We selected RADICAL-SAGA and RADICAL-EnTK as our
-workflow management engines, and developed complementary seismic tomography
-workflow tools~\citep{EnTK2017}.
+We selected EnTK as our
+workflow management engine~\citep{EnTK2017}, and developed complementary seismic tomography
+workflow tools.
 The workflow engine can automatically detected job failures both from the
@@
 Both components exhibit consistent reductions in terms of both mean and variance. 
-These arrivals --- almost 900,000 measurements in the 17--40~s and 40--100~s period bands, roughly~$\sim8\%$ of the database --- are of great importance, because they help constrain the compressional wavespeed structure in the model.
+Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are of great importance, because they help constrain the compressional wavespeed structure in the model.
 
@@
   \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
-  \caption{Histograms of traveltime measurements of 17--40~s P arrivals on the vertical and radial for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
-Other settings are the same as in Fig.~\ref{fig:phase_hist}.
-{\color{red}Wenjie: remove 40--100~s.}}
+  \caption{Histograms of 17--40~s P-wave traveltime anomalies of the vertical and radial components for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
+  }
   \label{fig:P_phase_hist}
@@
   \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
-  \caption{Histograms of phase measurements for the 360 events in the held-out database.}
+  \caption{Same as Fig.~\ref{fig:phase_hist}, except for the held-out database.
+  }
   \label{fig:phase_hist_360}
+\end{figure}
+
+P phase measurements were also extracted and compared in Fig.~\ref{fig:phase_hist_360_P} for 3 models. The behavior is consistent as we expected.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_360_P.pdf}
+  \caption{Same as Fig.~\ref{fig:P_phase_hist}, except for the held-out database.}
+  \label{fig:phase_hist_360_P}
 \end{figure}
@@
 To assess the accuracy of the expansion,
-we calculate the model norm in the GLL basis,
+we may calculate the model norm in the GLL basis,
 \begin{equation}

### 2019-01-29 main.tex
update window figureds

@@
   A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-  The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1,376~s time bin.
+  The maximum window count is 9,931 in the 85--86$^\circ$ distance and 1,375--1,376~sec time bin.
   Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
@@
    A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-   The maximum window count is 7,542.
+  The maximum window count is 7,542 in the 86--87$^\circ$ distance and 1,378--1,379~sec time bin.
    }
@@
    A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-   The maximum window count is 7,208.
+   The maximum window count is 7,208 in the 89--90$^\circ$ distance and 1,398--1,399~sec time bin.
    Only SH travetime branches are labeled.}

### 2019-01-29 main.tex
update phase histogram

@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
-  \caption{Histograms of 17--40~s P-wave traveltime anomalies of the vertical and radial components for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
+  \includegraphics[width=\textwidth]{figures/dt_histogram_phase.pdf}
+  \caption{Histograms of 17--40~s traveltime anomalies of P arrival(Vertical and Radial), and SH arrival(Transverse) for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
   }
-  \label{fig:P_phase_hist}
+  \label{fig:PS_phase_hist}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_360_P.pdf}
-  \caption{Same as Fig.~\ref{fig:P_phase_hist}, except for the held-out database.}
+  \includegraphics[width=\textwidth]{figures/dt_histogram_360_phase.pdf}
+  \caption{Same as Fig.~\ref{fig:PS_phase_hist}, except for the held-out database.}
   \label{fig:phase_hist_360_P}

### 2019-01-30 main.tex
Updates from ShareLaTeX

@@
 as well as compressional wavespeed models LLNL-G3Dv3 \citep{simmons2012llnl}, GAP-P4~\citep{fukao2013subducted}, and UU-P07~\citep{van2018atlas}.
-On the scale of North America,
+On the scale of North America
 we make comparisons with models US22~\citep{zhu2017radial},
@@
 In Section~\ref{section:workflow} we describe the adjoint tomography workflow in some detail.
-Sections~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 320 earthquakes.
+Section~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 320 earthquakes.
 Finally, in Section~\ref{section:model}, we describe the model in detail,
@@
 we continue to use the same transversely isotropic model parametrization.
-Instead of relying on ubiquitous ``crustal corrections'',
+Instead of relying on crustal corrections,
 the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
@@
   \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
-  \caption{Source corrections for 1,040 out of 1,480 events used in the structural inversion.
+  \caption{\small{Source corrections for 1,040 out of 1,480 events used in the structural inversion.
 (a) Map view of depth changes.
@@
 (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
-  }
+  }}
   \label{fig:source_correction}
@@
 These source inversions are computationally very expensive,
-because for each of the 1,040~events, nine full 3D forward simulations are required.
+because for each of the 1,040~events nine full 3D forward simulations are required.
 
@@
   \includegraphics[width=\textwidth]{figures/events_1480.pdf}
-  \caption{The 1,480~earthquakes used in this study.
+  \caption{\small{The 1,480~earthquakes used in this study.
 (a) Distribution of earthquakes.
 The color of each beach ball reflects its depth range, where blue designates events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
-(b) \& (c) Histograms of earthquake moment magnitudes and depths.}
+(b) \& (c) Histograms of earthquake moment magnitudes and depths.}}
   \label{fig:event_1480}
@@
   \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
-  \caption{Distribution of the 11,800~seismographic stations used in this study.
+  \caption{\small{Distribution of the 11,800~seismographic stations used in this study.
 Colors denote the number of events for which a given station contributes waveforms to the structural inversion.
 Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers.
-The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}
+The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}}
   \label{fig:stations}
@@
   \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
-  \caption{Adjoint tomography workflow.}
+  \caption{\small{Adjoint tomography workflow.}}
   \label{fig:adjoint_workflow}
@@
   \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
-  \caption{Sub-workflow workflow for preprocessing seismic data.}
+  \caption{\small{Sub-workflow workflow for preprocessing seismic data.}}
   \label{fig:preprocess_workflow}
@@
   \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
-  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
+  \caption{\small{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
   A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
@@
   Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
-  }
+  }}
   \label{fig:window_density_Z}
@@
 The figures nicely highlight all the well known body traveltime branches.
+Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are of great importance, because they help constrain the compressional wavespeed structure in the model.
 The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
@@
   \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
-  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
+  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
    A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-  The maximum window count is 7,542 in the 86--87$^\circ$ distance and 1,378--1,379~sec time bin.
-   }
+  The maximum window count is 7,542 in the 86--87$^\circ$ distance and 1,378--1,379~s time bin.
+   }}
   \label{fig:window_density_R}
@@
   \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
-  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
+  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
    A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-   The maximum window count is 7,208 in the 89--90$^\circ$ distance and 1,398--1,399~sec time bin.
-   Only SH travetime branches are labeled.}
+   The maximum window count is 7,208 in the 89--90$^\circ$ distance and 1,398--1,399~s time bin.
+   Only SH travetime branches are labeled.}}
   \label{fig:window_density_T}
@@
   \includegraphics[width=0.8\textwidth]{figures/misfit.pdf}
-  \caption{Evolution of the misfit function from GLAD-M15 to GLAD-M25.
+  \caption{\small{Evolution of the misfit function from GLAD-M15 to GLAD-M25.
   Each color denotes different stages of the inversion, as discussed in Sections~\ref{sec:I}--\ref{sec:III}.
@@
   (red squares).
-  }
+  }}
   \label{fig:misfit}
@@
 %   \end{tabular}\\
-%   \caption{Twelve measurement categories used for iterations 18--25.
-%   Before iteration~18, the 40--100~s body and surface waves categories were combined into a single category on each component, resulting in nine categories.}
+%   \caption{\small{Twelve measurement categories used for iterations 18--25.
+%   Before iteration~18, the 40--100~s body and surface waves categories were combined into a single category on each component, resulting in nine categories.}}
 %   \label{table:measurement_category}
@@
 
-\begin{table}[!htb]
+\begin{table}
   \centering
@@
   \end{tabular}\\
-  \caption{Changes in fit in the twelve measurement categories
+  \caption{\small{Changes in fit in the twelve measurement categories
   between the new model, GLAD-M25, and its starting model, GLAD-M15,
   and, in parentheses, between GLAD-M25 and model S362ANI combined with
-  CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
+  CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
   \label{table:misfit_reduction_M15_M25}
@@
 %   \end{tabular}\\
-%   \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
+%   \caption{\small{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion.}}
 %   \label{table:misfit_reduction_M00_M25}
@@
   \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
-  \caption{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
+  \caption{\small{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
   Each column represents one component and each row corresponds to a period band.
@@
   The total number of measurements is 18.2 million.
-  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}
+  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}}
   \label{fig:phase_hist}
@@
 
-Fig.~\ref{fig:P_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components.
-Both components exhibit consistent reductions in terms of both mean and variance. 
-Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are of great importance, because they help constrain the compressional wavespeed structure in the model.
+Fig.~\ref{fig:PS_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components, and 17-40~s S-wave traveltime anomalies on the transverse component.
+Both P and S waves exhibit consistent reductions in terms of both mean and variance.
 
@@
   \includegraphics[width=\textwidth]{figures/dt_histogram_phase.pdf}
-  \caption{Histograms of 17--40~s traveltime anomalies of P arrival(Vertical and Radial), and SH arrival(Transverse) for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
-  }
+  \caption{\small{Histograms of 17--40~s traveltime anomalies of P (vertical and radial), and SH (Transverse) arrivals for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
+  }}
   \label{fig:PS_phase_hist}
@@
   \includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
-  \caption{Same as Fig.~\ref{fig:phase_hist} except for amplitude measurements. These measurements are currently not used in the inversion.}
+  \caption{\small{Same as Fig.~\ref{fig:phase_hist} except for amplitude measurements. These measurements are currently not used in the inversion.}}
   \label{fig:amp_hist}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/events_360.pdf}
+  \caption{\small{Summary of the held-out database containing 360 earthquakes.
+Theses events were not used in the structural inversion.
+(a) Distribution of events color coded by depth range as in Fig.~\ref{fig:event_1480}.
+(b) \& (c) Histograms of moment magnitude and depth.}}
+  \label{fig:events_360}
+\end{figure}
+
 Following the approach of \cite{tape2009adjoint}, \cite{chen2015multiparameter},
@@
 Fig.~\ref{fig:events_360} summarizes the properties of the held-out database.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/events_360.pdf}
-  \caption{Summary of the held-out database containing 360 earthquakes.
-Theses events were not used in the structural inversion.
-(a) Distribution of events color coded by depth range as in Fig.~\ref{fig:event_1480}.
-(b) \& (c) Histograms of moment magnitude and depth.}
-  \label{fig:events_360}
-\end{figure}
 
@@
   \end{tabular}\\
-  \caption{Changes in fit for 360 earthquakes not used in the inversion in the twelve measurement categories
-between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
+  \caption{\small{Changes in fit for 360 earthquakes not used in the inversion in the twelve measurement categories
+between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
   \label{table:misfit_reduction_M15_M25_360}
@@
 %   \end{tabular}\\
-%   \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out data set}
+%   \caption{\small{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out data set.}}
 %   \label{table:misfit_reduction_M00_M25_360}
 % \end{table}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
+  \caption{\small{Same as Fig.~\ref{fig:phase_hist}, except for the held-out database.
+  }}
+  \label{fig:phase_hist_360}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/dt_histogram_360_phase.pdf}
+  \caption{\small{Same as Fig.~\ref{fig:PS_phase_hist}, except for the held-out database.}}
+  \label{fig:phase_hist_360_P}
+\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
-  \caption{Same as Fig.~\ref{fig:phase_hist}, except for the held-out database.
-  }
-  \label{fig:phase_hist_360}
-\end{figure}
-
-P phase measurements were also extracted and compared in Fig.~\ref{fig:phase_hist_360_P} for 3 models. The behavior is consistent as we expected.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram_360_phase.pdf}
-  \caption{Same as Fig.~\ref{fig:PS_phase_hist}, except for the held-out database.}
-  \label{fig:phase_hist_360_P}
-\end{figure}
+Finally,
+direct P and S traveltime anomaly measurements were extracted and compared for three models in Fig.~\ref{fig:phase_hist_360_P}.
+Again the histograms are consistent with the actual inversion,
+as expected.
 
@@
 \subsection{Global structure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
+  \caption{\small{Map views of global shear wavespeed perturbations at various depths for  model
+  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic},
+  and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
+  At a given radius,
+  perturbations are calculated relative to each model's average.
+  The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
+  The green circles denote locations of various
+  hotspots~\citep{montelli2006catalogue}.
+  The range of the colorbar is the same for each row,
+  and its maximum value is indicated in parentheses on the left, after
+  the depth.}}
+  \label{fig:global-vs}
+\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
-  \caption{Map views of global shear wavespeed perturbations at various depths for  model
-  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic},
-  and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
-  At a given radius,
-  perturbations are calculated relative to each model's average.
-  The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
-  The green circles denote locations of various
-  hotspots~\citep{montelli2006catalogue}.
-  The range of the colorbar is the same for each row,
-  and its maximum value is indicated in parentheses on the left, after
-  the depth.}
-  \label{fig:global-vs}
-\end{figure}
-
 %\begin{figure}
 %\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
-%  \caption{Map views of global $V_\textrm{P}$ variations at various depths for our model GLAD-M25(left column), S362ANI$+$M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
+%  \caption{\small{Map views of global $V_\textrm{P}$ variations at various depths for our model GLAD-M25(left column), S362ANI$+$M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
 For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing.
-Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
+Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}}
 %\label{fig:global-vp}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
-  \caption{Map views of global compressional wavespeed variations at various depths for model
+  \caption{\small{Map views of global compressional wavespeed variations at various depths for model
   GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl}, and
@@
   For LLNL-G3Dv3, depth ranges are labeled in the bottom right
-  bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}
+  bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}}
 \label{fig:global-vp}
@@
 \includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
-  \caption{Map views of isotropic shear wavespeed variations beneath North America 
+  \caption{\small{Map views of isotropic shear wavespeed variations beneath North America 
   for model GLAD-M25 (first column) and several global (S362ANI$+$M and S40RTS)
@@
   models. Green circles denote the locations of hotspots. For SL2013NA, we
-  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}
+  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}}
 \label{fig:america-vs}
@@
 
+\begin{figure}[ht!]
+\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
+  \caption{\small{Map views of isotropic shear wavespeed variations beneath Europe for model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
+  one regional model~\citep[EU60;][]{zhu2015seismic}. For EU60, the range of the color
+  bar is 4\% at all depths, as indicated in the bottom right bottom of the panels.}}
+\label{fig:europe-vs}
+\centering
+\end{figure}
+
 Fig.~\ref{fig:europe-vs} shows isotropic shear wavespeed perturbations beneath Europe.
@@
 
-\begin{figure}
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
-  \caption{Map views of isotropic shear wavespeed variations beneath Europe for model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
-  one regional model~\citep[EU60;][]{zhu2015seismic}. For EU60, the range of the color
-  bar is 4\% at all depths, as indicated in the bottom right bottom of the panels.}
-\label{fig:europe-vs}
-\centering
-\end{figure}
-
 \subsubsection{Asia}
+
+\begin{figure}[ht!]
+  \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
+  \caption{\small{Map views of shear wavespeed variations beneath Asia for GLAD-M25~(first column),
+  global models S362ANI$+$M (second column) and SL2013sv (third column), and regional model EARA2014~\citep[last column;][]{chen2015multiparameter}.}}
+  \label{fig:asia-vs}
+  \centering
+\end{figure}
 
@@
 
-\begin{figure}
-  \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
-  \caption{Map views of shear wavespeed variations beneath Asia for GLAD-M25~(first column),
-  global models S362ANI$+$M (second column) and SL2013sv (third column), and regional model EARA2014~\citep[last column;][]{chen2015multiparameter}.}
-  \label{fig:asia-vs}
-  \centering
-\end{figure}
-
 \subsubsection{South America}
 
-\begin{figure}
+\begin{figure}[ht!] 
   \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
-  \caption{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).}
+  \caption{\small{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).}}
   \label{fig:southamerica-vp}
@@
 
+\begin{figure}[ht!]
+    \centering
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}}\\
+    \caption{\small{Vertical cross sections for various plumes for models GLAD-M25 ($V_\textrm{P}$; left column), TX2015~\citep[$V_\textrm{S}$;][]{TX2015} (center column), and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad} (right column).
+    The map in the top left corner of each row shows the cross section with color-coded red, green, and white dots for geographical reference;
+    hotspots are denoted by red triangles.
+    The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
+    (a) Afar; (b) Bermuda (left) and Canary (middle); (c) Cape Verde (middle) and Hoggar (right); (d) Iceland (middle) and Eifel (right); (e) Easter (left) and Galapagos (right); (f) Marion (middle), and Kerguelen (right).
+}}
+    \label{fig:plumes}
+\end{figure}
+
 In this section we highlight various plume systems on Earth. Fig.~\ref{fig:plumes}
@@
 
-\begin{figure}[ht]
-    \centering
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}}\\
-    \caption{Vertical cross sections for various plumes for models GLAD-M25 ($V_\textrm{P}$; left column), TX2015~\citep[$V_\textrm{S}$;][]{TX2015} (center column), and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad} (right column).
-    The map in the top left corner of each row shows the cross section with color-coded red, green, and white dots for geographical reference;
-    hotspots are denoted by red triangles.
-    The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
-    (a) Afar; (b) Bermuda (left) and Canary (middle); (c) Cape Verde (middle) and Hoggar (right); (d) Iceland (middle) and Eifel (right); (e) Easter (left) and Galapagos (right); (f) Marion (middle), and Kerguelen (right).
-}
-    \label{fig:plumes}
-\end{figure}
-
-%\begin{figure}[ht]
+%\begin{figure}
 %    \centering
@@
 %    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
-%    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
+%    \caption{\small{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}}
 %\end{figure}
@@
 \label{section:slabs}
+
+\begin{figure}
+    \centering
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Aeg.png}\label{fig:subd_a}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Br.png}\label{fig:subd_b}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:subd_c}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:subd_d}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:subd_e}}\\[-1pt]
+    \caption{\small{Vertical cross sections of compressional wavespeed perturbations in various subduction zones
+    for models GLAD-M25 ($V_\textrm{P}$; left column), GAP-P4~\citep{fukao2013subducted} (middle column) and UU-P07~\citep{van2018atlas} (right column).
+    The map in the top left corner of each row shows the cross section with color-coded red, green, and white dots for geographical reference.
+    The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
+    (a) Aegean; (b) South America; (c) Hatteras; (d) Nepal; (e)  Wichita.}}
+    \label{fig:subd}
+\end{figure}
 
@@
 The difference may be attributed to increased data coverage thanks to USArray, as well as the use of finite-frequency Fr\'echet derivatives.
-
-\begin{figure}[ht]
-    \centering
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Aeg.png}\label{fig:subd_a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Br.png}\label{fig:subd_b}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:subd_c}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:subd_d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:subd_e}}\\[-1pt]
-    \caption{Vertical cross sections of compressional wavespeed perturbations in various subduction zones
-    for models GLAD-M25 ($V_\textrm{P}$; left column), GAP-P4~\citep{fukao2013subducted} (middle column) and UU-P07~\citep{van2018atlas} (right column).
-    The map in the top left corner of each row shows the cross section with color-coded red, green, and white dots for geographical reference.
-    The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
-    (a) Aegean; (b) South America; (c) Hatteras; (d) Nepal; (e)  Wichita.}
-    \label{fig:subd}
-\end{figure}
 
@@
 \begin{acknowledgments}
-%We want to give thanks to the Oak Ridge National Lab, for providing
-%  excellent support and computational resource that facilitate our research.
-%  We want to thanks IRIS and ORFEUS for providing seismic datas used in this
-%  study. We want to acknowledge Hejun Zhu, Min Chen, Carl Tape and Qinya Liu,
-%  for providing usefull tools and great suggetions these years.
-%  We want to thanks Ebru Bozdag, for providing GLAD-M15, data and software
-%  she used in the first generation model.
-
 This research used resources of the Oak Ridge Leadership Computing Facility,
@@
 providing the data used in this study.
-We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
+We thank Ryan Modrak, Ridvan \"{O}rsvuran, Frederik Simons, and James Smith for fruitful discussions.
 The open source spectral-element software package SPECFEM3D\_GLOBE and
@@
   \includegraphics[width=0.8\textwidth]{figures/1d_profile.pdf}
-  \caption{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
-  The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}
+  \caption{\small{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
+  The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}}
   \label{fig:global-average}
@@
   \includegraphics[width=0.9\textwidth]{figures/1d_profile_ra.pdf}
-  \caption{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}
+  \caption{\small{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}}
   \label{fig:global-ra-average}
@@
 
-\newpage
-
 \bibliographystyle{gji}

### 2019-01-30 main.tex
Updates from ShareLaTeX

@@
 categories.
-We performed similar assessments for a held-out data set consisting of 380 earthquakes,
+We performed similar assessments for a held-out data set consisting of 360 earthquakes,
 with results comparable to the actual inversion.
@@
 this requires about 1~TB of storage per earthquake,
-so for 1,480 earthquakes this amounts to 1.5~PB of storage.
+so for 1,480 earthquakes this adds up to 1.5~PB.
+This volume of data is generated during~$\sim6$~hours of simulations.
+Based on our experience, ADIOS is capable of achieving~$\sim120$~GB/s
+of sustained I/O on OLCF resources.
+Given that typical write speeds for modern hard disks are~$\sim100$~MB/s,
+it would be extremely difficult to carry out global adjoint tomography without the ADIOS library.
 

### 2019-02-07 main.tex
Updates from Overleaf

@@
 
-%\usepackage{subfig}
-
 \title[Global Adjoint Tomography -- Model GLAD-M25]
@@
 \author[Lei et al.]
-  {Wenjie Lei$^1$, Youyi Ruan$^{1.2}$, Ebru Bozda\u g$^3$, Daniel Peter$^4$, Matthieu Lefebvre$^1$, \\{\LARGE \rm Dimitri Komatitsch$^5$, Jeroen Tromp$^{1,6}$, Judith Hill$^7$, Norbert Podhorszki$^7$}, \\ {\LARGE \rm and David Pugmire$^7$} \\
+  {Wenjie Lei$^1$, Youyi Ruan$^{1,2}$, Ebru Bozda\u g$^3$, Daniel Peter$^4$, Matthieu Lefebvre$^1$, \\{\LARGE \rm Dimitri Komatitsch$^5$, Jeroen Tromp$^{1,6}$, Judith Hill$^7$, Norbert Podhorszki$^7$}, \\ {\LARGE \rm and David Pugmire$^7$} \\
   $^1$ Department of Geosciences, Princeton University, Princeton, NJ 08544, USA\\
-  $^2$ Nanjing University, Nanjing, China\\
+  $^2$ School of Earth Sciences and Engineering, Nanjing University, Nanjing, Jiangsu 210023, China\\
   $^3$ Department of Geophysics, Colorado School of Mines, Golden, CO 80401, USA\\
-  $^4$ Extreme Computing Research Center, King Abdullah University of Science and Technology, \\Thuwal 23955-6900, Kingdom of Saudi Arabia\\
+  $^4$ Extreme Computing Research Center, King Abdullah University of Science and Technology (KAUST), \\Thuwal 23955-6900, Kingdom of Saudi Arabia\\
   $^5$ LMA, CNRS UPR 7051, Aix-Marseille University, Centrale Marseille, 13453 Marseille Cedex 13, France\\
@@
 named GLAD-M25, which is the result of ten quasi-Newton tomographic iterations with an
-earthquake database consisting of 1,480 events in the magnitude range $5.8\le M_w \le 7.0$,
+earthquake database consisting of 1,480 events in the magnitude range $5.5\le M_w \le 7.2$,
 an almost six-fold increase over the first-generation model.
@@
 In Section~\ref{section:workflow} we describe the adjoint tomography workflow in some detail.
-Section~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 320 earthquakes.
+Section~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 360 earthquakes.
 Finally, in Section~\ref{section:model}, we describe the model in detail,
@@
 As a continuation of our previous work~\citep{bozdaug2016global},
-we used first-generation model GLAD-M15 as our
+we used the first-generation model GLAD-M15 as our
 starting model.
@@
 and high data quality (Fig.~\ref{fig:stations}).
-In addition to the seismic stations used for the source inversions,
+In addition to the seismographic  stations used for the source inversions,
 we included all available data for our 1,480 event earthquake database from many data centers,
@@
 Earthquakes mainly occur along plate boundaries,
-and most seismic stations are confined to the continents,
+and most seismographic  stations are confined to the continents,
 which leads to a very uneven distribution of sources and stations,
@@
     observed and synthetic seismograms. Pyflex (a Python version
-    of FLEXWIN) is
+    of FLEXWIN by \citet{krischer2015}) is
     used to automatically generate windows where observed and
@@
   (a) Evolution of the total misfit. (b)--(j) Misfit in
-  each period band (rows) on three components (columns). (e)--(g) At iteration 18,
+  each period band (rows) on three components (columns). (e)--(g) Since iteration 18,
   we  split the 40--100~s period band into two
-  measurement categories: body waves (red diamonds) and surface waves
-  (red squares).
+  measurement categories: body waves (diamonds) and surface waves
+  (squares).
   }}
@@
 assessment of misfit.
-
-%{\color{red} Wenjie: Make sure the variance reductions are calculated as ln (Phi\_M25 / Phi\_M15).}
-%{\color{red} Wenjie: I was using (Phi\_M25 - Phi\_M15) / Phi\_M15. So let me modify it?}
-%{\color{blue} Wenjie: yes please. It will only change things slightly, if at all. You need to do the same for Table~\ref{table:misfit_reduction_M15_M25_360}.}
 
@@
 to assess GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
-The total number of selected windows exceeds 18~million.
+The total number of selected windows,
+determined using model GLAD-M25, exceeds 18~million.
 Fig.~\ref{fig:phase_hist} shows histograms of the resulting phase
@@
 
-%{\color{red} Wenjie: Note: add spherical harmonic analysis later.}
-
 \begin{figure}
@@
 tomography, assimilating 1.7~million frequency-dependent traveltime
-measurements from 227 earthquakes recorded by 1,869 seismic stations.
+measurements from 227 earthquakes recorded by 1,869 seismographic  stations.
 It has superior data coverage, mainly by incorporating data from the China Array.
@@
 with profoundly different implications for mantle
-convection.
-
-In Fig.~\ref{fig:plumes}(a),
+convection:
+
+\begin{itemize}
+\item[]{\it Afar} In Fig.~\ref{fig:plumes}(a),
 we see that the Afar plume in model GLAD-M25 originates from the CMB, narrows its diameter
@@
 very similar behavior in TX2015 but differs significantly in SEMUCB-WM1.  
-
-In Fig.~\ref{fig:plumes}(b), from left to right, we see in model GLAD-M25 1) the Farallon
-slab; 2) the Bermuda hotspot above the 660~km discontinuity; 3) the Canary hotspot originating from the CMT and
-rising all the way up the Earth's surface; 4) the Afar hotspot from another angle.
-
-Fig.~\ref{fig:plumes}(c) features 1) South America subduction; 2) the Cape Verde hotspot extending from the CMB all the way to the surface; 3) the Hoggar hotspot from 660~km to the surface.
-
-Fig.~\ref{fig:plumes}(d) shows a plume which rises from the CMB right below Iceland, reaches 660~km, amplifies,
+\item[]{\it Bermuda and Canary} In Fig.~\ref{fig:plumes}(b), from left to right, we see in model GLAD-M25 (i) the Farallon
+slab; (ii) the Bermuda hotspot above the 660~km discontinuity; (iii) the Canary hotspot originating from the CMT and
+rising all the way up the Earth's surface; (iv) the Afar hotspot from another angle.
+\item[]{\it Cape Verde and Hoggar} Fig.~\ref{fig:plumes}(c) features (i) South America subduction; (ii) the Cape Verde hotspot extending from the CMB all the way to the surface; (iii) the Hoggar hotspot from 660~km to the surface.
+\item[]{\it Iceland and Eifel} Fig.~\ref{fig:plumes}(d) shows a plume which rises from the CMB right below Iceland, reaches 660~km, amplifies,
 and ascends to the surface.
 The intensification above 660~km may be an indication of partial melting.
-
-Fig.~\ref{fig:plumes}(e) contains 1) the Easter hotspot; 2) the Galapagos
-hotspot; 3) the Central America slab.
+\item[]{\it Easter and Galapagos} Fig.~\ref{fig:plumes}(e) contains (i) the Easter hotspot; (ii) the Galapagos
+hotspot; (iii) the Central America slab.
 In models GLAD-M25 and TX2015,
@@
 which is the eastern arm of the Pacific superplume.
-
+\item[]{\it Marion and Kerguelen}
 Finally,
@@
 Recovering these plumes is challenging due to poor data coverage in the southern hemisphere.
+\end{itemize}
 
@@
     \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:subd_c}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:subd_e}}\\[-1pt]
     \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:subd_d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:subd_e}}\\[-1pt]
     \caption{\small{Vertical cross sections of compressional wavespeed perturbations in various subduction zones
@@
     The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
-    (a) Aegean; (b) South America; (c) Hatteras; (d) Nepal; (e)  Wichita.}}
+    (a) Aegean; (b) South America; (c) Hatteras; (d) Wichita. (e) Nepal; }}
     \label{fig:subd}
@@
 namely, GAP-P4~\citep{fukao2013subducted} and UU-P07~\citep{van2018atlas}.
+Fig.~\ref{fig:subd}(a) features the Aegean subduction zone. All models show a slab penetrating into the lower mantle beyond a depth of 1,000~km.
+Fig.~\ref{fig:subd}(b) shows the South American slab, which, in this cross section, ponds in the shallow lower mantle in all three models, before sinking all the way to the CMB.
+Figs.~\ref{fig:subd}(c) and~(d) show cuts across the ancient Farallon slab, which penetrates deeply into the lower mantle.
+At depths greater than 1,000~km, 
+we see a very strong expression of the slab in model Glad-M25, which is much weaker in the two P models.
+The difference may be attributed to increased data coverage thanks to USArray, as well as the use of finite-frequency Fr\'echet derivatives.
+Finally, Fig.~\ref{fig:subd}(e) shows subduction beneath the Himalayas.
 
@@
 At shallow depths, model GLAD-M25 shows more distinct continental crust and cratons, thanks to the inclusion of surface waves.
-In the upper and mid mantle,
-the models share very similar features.
-At depth greater than 1000km, 
-we see a very strong expression of the ancient Farallon slab in model Glad-M25, which is much weaker in the two P models.
-The difference may be attributed to increased data coverage thanks to USArray, as well as the use of finite-frequency Fr\'echet derivatives.
+But in the upper and mid mantle,
+the models share very similar attributes.
 
@@
 and attenuation.
-The feasibility of such inversions on a regional scale have already been demonstrated in a studies focused on Europe by~\cite{ZhuTromp2013} and \cite{Zhuetal2013}.
+The feasibility of such inversions on a regional scale has already been demonstrated in studies focused on Europe by~\cite{ZhuTromp2013} and \cite{Zhuetal2013}.
 
@@
 To accomplish this,
-we first need to transform the 3D spectral-element mesh --- which includes ellipticity, topography \& bathymetry, and undulations on internal boundaries --- into a spherical volume.
+we first need to transform the 3D spectral-element mesh --- which includes ellipticity, topography/bathymetry and undulations on internal boundaries --- into a spherical volume.
 After these adjustments, we obtain a spectral-element mesh for a perfect cubed sphere~\citep{KoTr02a}.
@@
   \caption{\small{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
-  The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}}
+  The reference frequency for physical dispersion is ~7.77~mHz.}}
   \label{fig:global-average}
@@
   \includegraphics[width=0.9\textwidth]{figures/1d_profile_ra.pdf}
-  \caption{\small{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}}
+  \caption{\small{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is ~7.77~mHz.}}
   \label{fig:global-ra-average}
@@
 To accomplish the transformation,
-we first need to transform the 3D mesh --- which includes ellipticity, topography \& bathymetry, and undulations on internal boundaries --- into a spherical volume.
+we first need to transform the 3D mesh --- which includes ellipticity, topography/bathymetry and undulations on internal boundaries --- into a spherical volume.
 After these adjustments, we obtain a spectral element mesh for a perfect sphere,
@@
 and thus easily calculated.
+
 The normalized power per degree~$\ell$ may be calculated via
@@
     \sigma_\ell^2=\frac{1}{2\ell+1}\,
-    \sum_{n' = 0}^N\sum_{n = 0}^N\sum_{m = -\ell}^\ell{}_{n'}C^*_{\ell m}\,A_{n'n}\,{}_{n}C_{\ell m}
+    \sum_{n' = 0}^N\sum_{n = 0}^N\sum_{m = -\ell}^\ell\,A_{n'n}\,{}_{n'}C^*_{\ell m}\,{}_{n}C_{\ell m}
+    \quad .
+\end{equation}
+Alternatively,
+one may wish to calculate the power per degree as a function of radius,
+which is determined via
+\begin{equation}
+    \Sigma_\ell^2(r)=\frac{1}{2\ell+1}\,
+    \sum_{n' = 0}^N\sum_{n = 0}^N\sum_{m = -\ell}^\ell\,R_{n'}(r)\,R_{n}(r)\,{}_{n'}C^*_{\ell m}\,{}_{n}C_{\ell m}
     \quad .
@@
     \sigma_\ell^2=\frac{1}{2\ell+1}\,\sum_{n'=0}^N\,\sum_{n=0}^N\,A_{n'n}\,\left[{}_{n'}a_{\ell 0}\,{}_{n}a_{\ell 0}+\sum_{m=1}^\ell({}_{n'}a_{\ell m}\,{}_na_{\ell m}+{}_{n'}b_{\ell m}\,{}_nb_{\ell m})\right]
+    \quad ,
+    \label{eq:powerdegree}
+\end{equation}
+and the power per degree as a function of radius is determined via
+\begin{equation}
+    \Sigma_\ell^2(r)=\frac{1}{2\ell+1}\,\sum_{n'=0}^N\,\sum_{n=0}^N\,R_{n'}(r)\,R_{n}(r)\,\left[{}_{n'}a_{\ell 0}\,{}_{n}a_{\ell 0}+\sum_{m=1}^\ell({}_{n'}a_{\ell m}\,{}_na_{\ell m}+{}_{n'}b_{\ell m}\,{}_nb_{\ell m})\right]
     \quad .
-\end{equation}
-
-To assess the accuracy of the expansion,
-we may calculate the model norm in the GLL basis,
-\begin{equation}
-    ||m_\text{\,GLL}||^2=\int_V m_\text{\,GLL}^2(\mathbf{x})\,\mathrm{d}^3\mathbf{x}=
-    \sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,(m^{\alpha\beta\gamma})^2\,J^{\alpha\beta\gamma}
-    \quad ,
-\end{equation}
-and compare it to the model norm in the spherical harmonic basis,
-\begin{equation}
-    ||m_\text{\,SH}||^2=\int_V m_\text{\,SH}^2(\mathbf{x})\,\mathrm{d}^3\mathbf{x}=
-    \sum_{\ell = 0}^L(2\ell+1)\,\sigma_\ell^2
-    \quad ,
-\end{equation}
-by calculating the error
-\begin{equation}
-    \epsilon = \log\,\frac{||m_\text{\,SH}||^2}{||m_\text{\,GLL}||^2}
-    \quad .
-\end{equation}
+    \label{eq:powerdegreeradius}
+\end{equation}
+In Fig.~\ref{fig:powerspectra} we compare power spectra per degree~$\ell$ as a function of radius for models S362ANI, GLAD-M15, and GLAD-M25.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/powerspectra.pdf}
+  \caption{\small{Power spectra per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (left), GLAD-M15 (middle), and GLAD-M25 (right).}}
+  \label{fig:powerspectra}
+\end{figure}
+
+% To assess the accuracy of the expansion,
+% we may calculate the model norm in the GLL basis,
+% \begin{equation}
+%     ||m_\text{\,GLL}||^2=\int_V m_\text{\,GLL}^2(\mathbf{x})\,\mathrm{d}^3\mathbf{x}=
+%     \sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,(m^{\alpha\beta\gamma})^2\,J^{\alpha\beta\gamma}
+%     \quad ,
+% \end{equation}
+% and compare it to the model norm in the spherical harmonic basis,
+% \begin{equation}
+%     ||m_\text{\,SH}||^2=\int_V m_\text{\,SH}^2(\mathbf{x})\,\mathrm{d}^3\mathbf{x}=
+%     \sum_{\ell = 0}^L(2\ell+1)\,\sigma_\ell^2
+%     \quad ,
+% \end{equation}
+% by calculating the error
+% \begin{equation}
+%     \epsilon = \log\,\frac{||m_\text{\,SH}||^2}{||m_\text{\,GLL}||^2}
+%     \quad .
+% \end{equation}
 

### 2019-02-07 main.tex
add reference

@@
 where~$\Delta \tau_{scrw}$ denotes a multi-taper frequency-dependent phase measurement over the frequency interval~$\Delta\omega=\omega_2-\omega_1$\,,
-with associated standard deviation~$\sigma_{scrw}$\,.
+with associated uncertainties~$\sigma_{scrw}$\,.
 For body waves, the window misfit is simply the cross-correlation traveltime anomaly,
@@
   The search direction is determined using a nonlinear conjugate gradient method~\citep{wright1999numerical} (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25).
-  We used a subset of 120 earthquakes to conduct the line search and determine the step length.
+  We used a subset of 160 earthquakes to conduct the line search and determine the step length.
 \end{enumerate}
@@
 margin to the East. On both sides the lithosphere has been deformed by
-low wavespeed structures, thus forming sharp tectonic boundaries.
+low wavespeed structures, thus forming sharp tectonic boundaries
+~\citep{grand1984upper, masters1996shear, grand1997high,
+megnin2000three, gu2001models, schaeffer2014imaging, zhu2017radial}.
 
@@
 bathymetry and corresponds to a portion of ancient oceanic
-Lithosphere~\citep{muller2008}.
+Lithosphere~\citep{muller2008, schaeffer2014imaging}.
 A remnant of the Juan de Fuca plate,

### 2019-02-07 main.tex
Updates from Overleaf

@@
 low wavespeed structures, thus forming sharp tectonic boundaries
-~\citep{grand1984upper, masters1996shear, grand1997high,
-megnin2000three, gu2001models, schaeffer2014imaging, zhu2017radial}.
+~\citep{grand1984upper,masters1996shear,grand1997high,
+megnin2000three,gu2001models,schaeffer2014imaging,zhu2017radial}.
 

### 2019-02-07 main.tex
add reference

@@
 
-The deployment of USArray has dramatically increased data overage across the
+The deployment of USArray has dramatically increased data coverage across the
 continental United States.
@@
 bounded by the Rocky Mountain Front to the West and continental
-margin to the East. On both sides the lithosphere has been deformed by
+margin to the East~\citep{grand1984upper, whitmeyer2007tectonic}.
+On both sides the lithosphere has been deformed by
 low wavespeed structures, thus forming sharp tectonic boundaries
-~\citep{grand1984upper,masters1996shear,grand1997high,
-megnin2000three,gu2001models,schaeffer2014imaging,zhu2017radial}.
+~\citep{masters1996shear, grand1997high, megnin2000three, gu2001models}.
 
@@
 Similar observations can be made for the Yavapai and
-Mazatzal Blocks, which define the southern boundary of the large craton.
+Mazatzal Blocks, which define the southern boundary of the large craton
+~\citep{schaeffer2014imaging}.
 
@@
 Baffin Bay and the Labrador Sea, where the North American craton nicely follows
-the coastline.
+the coastline~\citep{chalmers2001development}.
 In the Northeast corner of the maps we see that the Iceland hotspot is very
@@
 separating the Precambrian East European Craton~(EEC) in the Northeast from
-Phanerozoic Europe in the Southwest.
+Phanerozoic Europe in the Southwest~\citep{zielhuis1994deep}.
 The TESZ is very consistent across all models,
@@
 The tectonic history of the Mediterranean is complex,
-involving several regional plates and multiple past and present subduction zones.
+involving several regional plates and multiple past and present subduction zones
+~\citep{dewey1989kinematics}.
 We see slab ponding in the transition zone beneath the western Mediterranean
-associated with slab roll-back of the Appennines-Maghrebides subduction zone.
+associated with slab roll-back of the Appennines-Maghrebides subduction zone
+~\citep{wortel2000subduction, zhu2012structure}.
 At shallower depths, we see low wavespeeds along its western border,
@@
 
-In Central Europe we note the Cenozoic Ridge System, characterized by low 
+In Central Europe we note the Cenozoic Ridge System~\citep{ziegler1992european},
+characterized by low 
 wavespeeds from the Massif Central to the Eifel. Both EU60 and
 GLAD-M25 exhibit a slow anomaly beneath the northern part of the Rhine Graben,
-which is interpreted as the reservoir that fuels the Eifel hotspot.
+which is interpreted as the reservoir that fuels the Eifel hotspot
+~\citep{goes1999lower, zhu2015seismic}.
 

### 2019-02-10 main.tex
Updates from Overleaf

@@
 \usepackage{amsmath}
-\usepackage[dvipsnames]{xcolor}
+
+% colors to show the corrections
+\usepackage[dvipsnames,usenames]{xcolor}
+
+% colors to show the corrections
+\newcommand{\red}[1]{\textbf{\textcolor{Red}{#1}}}
+\newcommand{\blue}[1]{\textbf{\textcolor{Blue}{#1}}}
+\newcommand{\cyan}[1]{\textbf{\textcolor{Cyan}{#1}}}
+\newcommand{\green}[1]{\textbf{\textcolor{Green}{#1}}}
+\newcommand{\magenta}[1]{\textbf{\textcolor{Magenta}{#1}}}
+\newcommand{\orange}[1]{\textbf{\textcolor{Orange}{#1}}}
+
 \floatsetup[figure]{style=plain,subcapbesideposition=top}
@@
 On a global scale, we present comparisons with model S362ANI$+$M~\citep{moulik2014anisotropic},
-which is an updated version of model S362ANI~\citep{s362ani},
+which is an updated version of model S362ANI~\citep{kustowski2008anisotropic},
 the starting model for the GLAD-M15 inversion.
@@
 starting model.
-GLAD-M15 is a 3D transversely isotropic earth model, which combined
+GLAD-M15 is a 3D transversely isotropic earth earth model, which combined
 3D mantle model S362ANI~\citep{kustowski2008anisotropic}
@@
 the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
-GLAD-M15 was constructed using a global database of 256 earthquakes.
+GLAD-M15 was constructed using a global database of 253 earthquakes.
 The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
@@
 
-In addition to the 256 earthquakes used for the construction of GLAD-M15, we initially carefully selected 784 additional earthquakes
+In addition to the 253 earthquakes used for the construction of GLAD-M15, we initially carefully selected 784 additional earthquakes
 from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global},
@@
 These source inversions are computationally very expensive,
-because for each of the 1,040~events nine full 3D forward simulations are required.
+because for each of the 1,040~events nine full 3D forward simulations are required to obtain the source parameter Fr\'echet derivatives.
 
@@
 The misfit function to be minimized during the iterative inversion process must
-be carefully constructed. It will typically involve cross-correlation traveltimes
+be carefully constructed.
+In this study,
+it typically involves cross-correlation traveltimes
 for body waves and frequency-dependent multitaper phase measurements for surface waves.
@@
 Although the inversion is designed to minimize the overall misfit,
-we will be tracking the misfit reduction in each of the categories to ensure that
+we track the misfit reduction in each of the categories to ensure that
 the model is improving the fit to the data roughly equally across the board.
@@
 with associated uncertainties~$\sigma_{scrw}$\,.
-For body waves, the window misfit is simply the cross-correlation traveltime anomaly,
+For body waves, the window misfit is often simply the cross-correlation traveltime anomaly,
 $\Delta T_{scrw}$\,, weighted by its standard deviation, i.e., $\chi_{scrw}=(\Delta T_{scrw}/\sigma_{scrw})^2$\,.
@@
 Therefore, the final four parameters are $c$, $\beta_v$, $\beta_h$, and $\eta$.
+Transverse isotropy is confined to the upper mantle; the lower mantle is assumed to be isotropic.
 
@@
 To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA
-Tesla K20X GPUs takes approximately 10~min of wall clock time.
-The calculation of Fr\'echet derivatives at a later stage of the workflow requires
-access to snapshots of the forward wavefield as part of the parsimonious storage
-algorithm developed by~\cite{KoXiBoPeSaLiTr16},
-with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
-For the current simulation setup,
-this requires about 1~TB of storage per earthquake,
-so for 1,480 earthquakes this adds up to 1.5~PB.
-This volume of data is generated during~$\sim6$~hours of simulations.
-Based on our experience, ADIOS is capable of achieving~$\sim120$~GB/s
-of sustained I/O on OLCF resources.
-Given that typical write speeds for modern hard disks are~$\sim100$~MB/s,
-it would be extremely difficult to carry out global adjoint tomography without the ADIOS library.
+Tesla K20X GPUs takes approximately 10~min of wall clock time. {\color{red} Wenjie: is that correct?}
 
@@
   \item Signal processing to remove the instrument response from observed data
-    to recover ground displacement. Both observed and synthetic data are bandpass
+    to recover ground displacement using ObsPy~\citep{obspy2010}. Both observed and synthetic data are bandpass
     filtered, and the horizontal components are rotated to obtain the radial and transverse components of motion.
@@
 a forward simulation, since the forward wavefield is recalculated for convolution with
-the adjoint wavefield during the adjoint simulation,
-as discussed in~\cite{KoXiBoPeSaLiTr16}.
+the adjoint wavefield during the adjoint simulation.
 Using this procedure,
@@
 and attenuation is accurately taken into account in both simulations.
+
+The calculation of Fr\'echet derivatives requires
+access to snapshots of the forward wavefield as part of the parsimonious storage
+algorithm developed by~\cite{KoXiBoPeSaLiTr16},
+with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
+For the current simulation setup,
+this requires about 1~TB of storage per earthquake,
+so for 1,480 earthquakes this adds up to 1.5~PB.
+This volume of data is generated during~$\sim6$~hours of simulations.
+Based on our experience, ADIOS is capable of achieving~$\sim120$~GB/s
+of sustained I/O on OLCF resources.
+Given that typical write speeds for modern hard disks are~$\sim100$~MB/s,
+it would be extremely difficult to carry out global adjoint tomography without the ADIOS library.
 
@@
 
-Starting model GLAD-M15 was constructed using a database of 256 earthquakes.
+Starting model GLAD-M15 was constructed using a database of 253 earthquakes.
 For iterations 15--17 of the inversion we used an expanded database of 520 events.
@@
 The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by
-iteration~21, prompting us to add more earthquakes and change the weighting strategy again by reintroducing 17--40~s surface waves.
+iteration~21, prompting us to add more earthquakes and change the weighting strategy again by reintroducing 40--100~s surface waves.
 
@@
 specific geographical regions.
+In this paper we focus predominantly on isotropic shear and compressional wavespeed variations.
 We conclude by highlighting various slabs and plumes in the model.
@@
 The deployment of USArray has dramatically increased data coverage across the
-continental United States.
+continental United States,
+and yet despite this tremendous increase in data coverage, there is not as much overlap between different models as one might anticipate.
 In this section, we compare GLAD-M25 in this region 
@@
 bathymetry and corresponds to a portion of ancient oceanic
-Lithosphere~\citep{muller2008, schaeffer2014imaging}.
+lithosphere~\citep{muller2008, schaeffer2014imaging}.
 A remnant of the Juan de Fuca plate,
@@
 Its southern part interacts with the Hellenic slab, which penetrates the mantle
-transition zone and extends below 1000km in our model.
+transition zone and extends below 1,000~km in our model.
 We discuss the Hellenic Arc further in Section~\ref{section:slabs}.
@@
 but barely observable in other models.
+This is probably a consequence of coverage provided by events in the region (see Fig.~\ref{fig:event_1480}).
 To the north,
@@
 At depths greater than 1,000~km, 
-we see a very strong expression of the slab in model Glad-M25, which is much weaker in the two P models.
+we see a very strong expression of the slab in model GLAD-M25, which is much weaker in the two P models.
 The difference may be attributed to increased data coverage thanks to USArray, as well as the use of finite-frequency Fr\'echet derivatives.
@@
 providing the data used in this study.
-We thank Ryan Modrak, Ridvan \"{O}rsvuran, Frederik Simons, and James Smith for fruitful discussions.
+We thank Ryan Modrak, Ridvan \"{O}rsvuran, Frederik J. Simons, and James Smith for fruitful discussions,
+and Caio Ciardelli for implementing the spherical harmonic model expansion.
 The open source spectral-element software package SPECFEM3D\_GLOBE and
@@
  (CIG; {\tt geodynamics.org}). This research was supported by NSF grant~1644826.
-
 \end{acknowledgments}
@@
 \end{equation}
-and the power per degree as a function of radius is determined via
+and the normalized power per degree as a function of radius is determined via
 \begin{equation}
@@
 \end{equation}
-In Fig.~\ref{fig:powerspectra} we compare power spectra per degree~$\ell$ as a function of radius for models S362ANI, GLAD-M15, and GLAD-M25.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/powerspectra.pdf}
-  \caption{\small{Power spectra per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (left), GLAD-M15 (middle), and GLAD-M25 (right).}}
+In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, GLAD-M15, and GLAD-M25,
+and in Fig.~\ref{fig:powerspectraradius} we plot the normalized power per degree as a function of radius
+for the same set of models.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{figures/power.pdf}
+  \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), GLAD-M15 (green), and GLAD-M25 (blue).
+  Model S362ANI has no power beyond degree~18.
+  (Courtesy of Caio Ciardelli.)
+  }}
   \label{fig:powerspectra}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.95\textwidth]{figures/power_radius.pdf}
+  \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (left), GLAD-M15 (middle), and GLAD-M25 (right).
+  (Courtesy of Caio Ciardelli.)
+  }}
+  \label{fig:powerspectraradius}
 \end{figure}

### 2019-02-11 main.tex
Updates from Overleaf

@@
 To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA
-Tesla K20X GPUs takes approximately 10~min of wall clock time. {\color{red} Wenjie: is that correct?}
+Tesla K20X GPUs takes approximately 10~min of wall clock time.
+
+The calculation of Fr\'echet derivatives requires
+access to snapshots of the forward wavefield as part of the parsimonious storage
+algorithm developed by~\cite{KoXiBoPeSaLiTr16},
+with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
+For the current simulation setup,
+this requires about 1~TB of storage per earthquake,
+so for 1,480 earthquakes this adds up to 1.5~PB.
+This volume of data is generated during~$\sim6$~hours of simulations.
+Based on our experience, ADIOS is capable of achieving~$\sim120$~GB/s
+of sustained I/O on OLCF resources.
+Given that typical write speeds for modern hard disks are~$\sim100$~MB/s,
+it would be extremely difficult to carry out global adjoint tomography without the ADIOS library.
 
@@
 and attenuation is accurately taken into account in both simulations.
-
-The calculation of Fr\'echet derivatives requires
-access to snapshots of the forward wavefield as part of the parsimonious storage
-algorithm developed by~\cite{KoXiBoPeSaLiTr16},
-with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
-For the current simulation setup,
-this requires about 1~TB of storage per earthquake,
-so for 1,480 earthquakes this adds up to 1.5~PB.
-This volume of data is generated during~$\sim6$~hours of simulations.
-Based on our experience, ADIOS is capable of achieving~$\sim120$~GB/s
-of sustained I/O on OLCF resources.
-Given that typical write speeds for modern hard disks are~$\sim100$~MB/s,
-it would be extremely difficult to carry out global adjoint tomography without the ADIOS library.
 
@@
 and, in particular, plumes and subduction zones feature prominently.
-
-Obvious future directions of research include growing the earthquake database further to the roughly 6,000 earthquakes in the right magnitude range already available via the Global CMT database
+Thus, our global inversion is bridging the gap between global and regional studies,
+approaching regional-scale resolution is areas with sufficient data coverage.
+We can observe this increase in resolution in GLAD-M25 in the normalized power per spherical harmonic degree as a function of radius, which is displayed in Fig.~\ref{fig:powerspectraradius}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.95\textwidth]{figures/power_radius2.pdf}
+  \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (first column), S40RTS (second column) GLAD-M15 (third column), and GLAD-M25 (fourth column).
+  Shown are depths greater than 120~km.
+  (Courtesy of Caio Ciardelli.)
+  }}
+  \label{fig:powerspectraradius}
+\end{figure}
+
+Obvious future directions of research include growing the earthquake database further to the roughly 6,000 earthquakes in the right magnitude range already available via the Global CMT database,
 and reducing the shortest simulation period further from 17~s to 8.5~s.
@@
 providing the data used in this study.
-We thank Ryan Modrak, Ridvan \"{O}rsvuran, Frederik J. Simons, and James Smith for fruitful discussions,
+We thank Ryan Modrak, Ridvan \"{O}rsvuran, Frederik J.\ Simons, and James Smith for fruitful discussions,
 and Caio Ciardelli for implementing the spherical harmonic model expansion.
@@
  freely available via the Computational Infrastructure for Geodynamics
- (CIG; {\tt geodynamics.org}). This research was supported by NSF grant~1644826.
+ (CIG; {\tt geodynamics.org}).
+ This research was supported by NSF grant~1644826.
 \end{acknowledgments}
@@
 \end{equation}
-In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, GLAD-M15, and GLAD-M25,
-and in Fig.~\ref{fig:powerspectraradius} we plot the normalized power per degree as a function of radius
+In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, S40RTS, GLAD-M15, and GLAD-M25,
+and Fig.~\ref{fig:powerspectraradius} shows the normalized power per degree as a function of radius
 for the same set of models.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/power.pdf}
-  \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), GLAD-M15 (green), and GLAD-M25 (blue).
-  Model S362ANI has no power beyond degree~18.
+  \includegraphics[width=0.5\textwidth]{figures/power2.pdf}
+  \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), S40RTS (orange), GLAD-M15 (green), and GLAD-M25 (blue).
+  The calculation includes depths greater than 120~km.
+  Model S362ANI has no power beyond degree~18,
+  and model S40RTS has no power beyond degree~40.
   (Courtesy of Caio Ciardelli.)
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.95\textwidth]{figures/power_radius.pdf}
-  \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (left), GLAD-M15 (middle), and GLAD-M25 (right).
-  (Courtesy of Caio Ciardelli.)
-  }}
-  \label{fig:powerspectraradius}
-\end{figure}
-
-% To assess the accuracy of the expansion,
-% we may calculate the model norm in the GLL basis,
-% \begin{equation}
-%     ||m_\text{\,GLL}||^2=\int_V m_\text{\,GLL}^2(\mathbf{x})\,\mathrm{d}^3\mathbf{x}=
-%     \sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,(m^{\alpha\beta\gamma})^2\,J^{\alpha\beta\gamma}
-%     \quad ,
-% \end{equation}
-% and compare it to the model norm in the spherical harmonic basis,
-% \begin{equation}
-%     ||m_\text{\,SH}||^2=\int_V m_\text{\,SH}^2(\mathbf{x})\,\mathrm{d}^3\mathbf{x}=
-%     \sum_{\ell = 0}^L(2\ell+1)\,\sigma_\ell^2
-%     \quad ,
-% \end{equation}
-% by calculating the error
-% \begin{equation}
-%     \epsilon = \log\,\frac{||m_\text{\,SH}||^2}{||m_\text{\,GLL}||^2}
-%     \quad .
-% \end{equation}
-
 \bibliographystyle{gji}

### 2019-02-14 coverletter.tex
Updates from Overleaf

\documentclass[11pt]{article}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{fancyhdr} \pagestyle{fancy}
%\renewcommand{\baselinestretch}{1.0} %double linespread or \linespread{1.6}
\setlength{\textwidth}{16cm}
\setlength{\textheight}{23cm}
\setlength{\hoffset}{-1.6cm}
\setlength{\voffset}{-1.cm}

\begin{document} %%

\begin{minipage}[t]{0.55\textwidth}
~ \vspace{0pt}
\end{minipage}
\begin{minipage}[t]{0.45\textwidth}
Wenjie Lei \\
Department of Geosciences \\
Princeton University \\
Princeton, New Jersey 08540\\
USA \\
~ \\
\today \\ 
\end{minipage} \hspace{0cm}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\par
\noindent
Ana Ferreira\\
Editor \\
\textit{Geophysical Journal International}\\
~ \\
Dear Editor Ferreira,\\
\par \noindent
We are pleased to submit the original research article entitled ``Global Adjoint Tomography -- Model GLAD-M25" for publication in the \textit{Geophysical Journal International}. 
We would like to suggest the following potential 
reviewers. \\
~ \\
David Al-Attar, University of Cambridge \\
Email: da380@cam.ac.uk\\
~ \\
Heiner Igel, University of M\"unich \\
Email: igel@geophysik.uni-muenchen.de \\
~ \\
Qinya Liu, University of Toronto\\
Email:  liuqy@physics.utoronto.ca \\
~ \\
Jeroen Ritsema, University of Michigan \\
Email:  jritsema@umich.edu \\
~ \\
Carl Tape, University of Alaska Fairbanks \\
Email:  ctape@alaska.edu \\
~ \\
Jeannot Trampert, University of Utrecht \\
Email: J.A.Trampert@uu.nl \\
~ \\

\par  \noindent
Thank you for your consideration.\\
\par \noindent
Sincerely, \\
\par \noindent
Wenjie Lei
\end{document} %%

### 2019-02-14 main.tex
Updates from Overleaf

@@
 Building on our first-generation global adjoint tomography model,
-GLAD-M15, we present our second-generation transversely isotropic global model,
+GLAD-M15 \citep{bozdaug2016global}, we present our second-generation transversely isotropic global model,
 named GLAD-M25, which is the result of ten quasi-Newton tomographic iterations with an
@@
 which is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
-Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227 earthquakes recorded by more than 1,800 stations.
+Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227~earthquakes recorded by more than 1,800~stations.
 
@@
 the smallest moment magnitude in the database is set to~5.5,
+thereby capturing more deep events,
 and to avoid complications associated with source dimension and directivity,
@@
 
-Before using the 1,040 earthquakes in our structural inversion,
+Before using 1,040 earthquakes in our structural inversion,
 we performed CMT inversions using model GLAD-M15,
@@
 of our database and greatly improve coverage in certain regions.
+\red{(Looks like there are also OBSs to be mentioned, mainly for my curiosity, it would be good to know their contribution to the overall inversions.)}
 
@@
 at the OLCF.
-To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA
+To simulate 120-min seismograms with a shortest period of 17~s on 384 NVIDIA
 Tesla K20X GPUs takes approximately 10~min of wall clock time.
@@
 Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are of great importance, because they help constrain the compressional wavespeed structure in the model.
-The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
+The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances \red{(Again just for my curiosity, why PcP and ScS phases together with any phase after surface waves were excluded?
+Any special reason or just a decision?)}.
 This is something we will reconsider in future applications, perhaps by introducing aspects of machine learning.
@@
 
-In this section we discuss model GLAD-M25 in detail.
-We begin with a global overview of the model before concentrating on
+In this section we discuss model GLAD-M25 in some detail.
+We begin with a global overview of the model, before concentrating on
 specific geographical regions.
-In this paper we focus predominantly on isotropic shear and compressional wavespeed variations.
-We conclude by highlighting various slabs and plumes in the model.
+We conclude by highlighting various slabs and plumes.
+The focus is on isotropic shear and compressional wavespeed variations.
+We provide comparisons with numerous other global and regional tomographic models,
+but we refrain from detailed tectonic/geodynamic interpretations,
+which will be the subject of more targeted future investigations.
+Our goal in the article is to discuss the construction of model GLAD-M25,
+and to place it into a broader tomographic context.
+
 Vertical cross sections are plotted relative to the spherical average of GLAD-M25,
@@
   and its maximum value is indicated in parentheses on the left, after
-  the depth.}}
+  the depth. \red{(Probably the numbers on top-left of each map are min/max perturbations of the associated sections, but the colorbar is fixed to 2 to 7$\%$)}}}
   \label{fig:global-vs}
@@
 The Southwestern part of China is dominated by the Himalayas,
-expressing the collision between India and Eurasia.
+expressing the collision between India and Eurasia~\citep{lebedev2003upper}.
 GLAD-M25 exhibits strong high wavespeed anomalies in this area,
@@
 at shallow depths we see clear low wavespeed impressions of the Hainan and Changbai volcanoes,
-suggesting a lithospheric rather than deeper mantle origin.
+suggesting a lithospheric rather than deeper mantle origin~\citep{yin2000geologic}.
 The Sichuan basin, a very localized high-wavespeed structure, extends below
@@
   \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
-  \caption{\small{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).}}
+  \caption{\small{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).\red{(LLNL model looks pretty interesting with the craton signature down to 300 km.
+Slab and craton anomalies together at 150 km look interesting too, as if they are two different models.
+In addition I am still wondering why are we the only one seeing Scotia Arc?
+Or why the others do not see it?
+It looks to me that it is pretty easy to add a slab signature to Scotia because of USArray.
+If there are earthquakes in their database at Scotia it should still easy to put it there even without USArray.
+Or perhaps it is indeed the bias of USArray coming from GLAD-M15?.)}}}
   \label{fig:southamerica-vp}
@@
 TX2015~\citep[$V_\textrm{S}$;][]{TX2015}, and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad}.
+All three models have common plume features where GLAD-M25 and TX2015 seem to be more in good agreement.
+
 The three models tend to agree near the CMB,
@@
 with profoundly different implications for mantle
-convection:
+convection.
 
@@
     \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:subd_d}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Su.png}\label{fig:subd_f}}\\[-1pt]
     \caption{\small{Vertical cross sections of compressional wavespeed perturbations in various subduction zones
@@
     The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
-    (a) Aegean; (b) South America; (c) Hatteras; (d) Wichita. (e) Nepal; }}
+    (a) Aegean; (b) South America; (c) Hatteras; (d) Wichita. (e) Nepal; (f) Sunda. \red{(GLAD-M25 is still Vp)}}}
     \label{fig:subd}
@@
 Fig.~\ref{fig:subd}(b) shows the South American slab, which, in this cross section, ponds in the shallow lower mantle in all three models, before sinking all the way to the CMB.
-Figs.~\ref{fig:subd}(c) and~(d) show cuts across the ancient Farallon slab, which penetrates deeply into the lower mantle.
+Figs.~\ref{fig:subd}(c) and~(d) show cuts across the ancient Farallon slab, which penetrates deeply into the lower mantle,
+as spectacularly documented by~\cite[e.g.]{grand1994,hilst1997,grand1997high}.
 At depths greater than 1,000~km, 
@@
 The difference may be attributed to increased data coverage thanks to USArray, as well as the use of finite-frequency Fr\'echet derivatives.
-Finally, Fig.~\ref{fig:subd}(e) shows subduction beneath the Himalayas.
+Fig.~\ref{fig:subd}(e) shows subduction beneath the Himalayas.
+All three models show two distinct fast anomalies below 660~km,
+one above 1,000~km and the other, further to the southwest, below 1,000~km.
+Finally, Fig.~\ref{fig:subd}(f) shows subduction beneath the Java portion of the Sunda Arc.
+At this location the slab pernetrates into the lower mantle, at which point its spreads out laterally,
+in agreement with models GAP-P4 and UU-P07.
+\cite{fukao1992} explained this flattening using a model of~\cite{ringwood1988},
+suggesting that the subducted slab thickened and buckled to form a dense megalith
+above the 660~km discontinuity before sinking into the lower mantle.
 
@@
 we use ASDF~\citep{krischer2016adaptable} in the preprocessing stage of the adjoint tomography workflow,
-and to accommodate I/O during postprocessing stage we use the ADIOS library~\citep{liu2014hello}.
+and to accommodate massive I/O during the postprocessing stage we use the ADIOS library~\citep{liu2014hello}.
 For data assimilation,
-tools, such as FLEXWIN, which automatically select data windows suitable for measurements,
+tools such as FLEXWIN, which automatically select data windows suitable for measurements,
 are indispensable, and we see tremendous opportunities for the use of machine learning algorithms in this context~\citep[e.g.,][]{chen2017}.
+Without these libraries and tools, the construction of model GLAD-M25 would have been impossible.
 
@@
 thereby enabling semi-automatic job resubmission if necessary.
+These are the attributes required for bringing global FWI to its full potential,
+enabling the assimilation of data from thousands of earthquakes on the largest HPC systems.
 
@@
 such as those offered through the DOE INCITE and NSF XSEDE programs.
+
+Although Figs.~\ref{fig:window_density_Z}--\ref{fig:window_density_T} illustrate that much information in seismograms is
+being assimilated, we still have a long way to go before explaining every wiggle in hundreds-of-minutes-long seismograms.
+Currently, we are only fitting the phase in selected time windows, and amplitude information remains completely unused.
+We accommodate the full physics of seismic wave propagation,
+but we are not exploiting the most general earth model parameterization.
+GLAD-M25 is an elastic model with radial anisotropy confined to the upper mantle.
+It is well known that the upper mantle is azimuthally anisotropic~\citep[e.g.,][]{montagner1989petrological,montagner1991},
+and we also know that amplitude information helps constrain second derivatives in phase speed~\citep[e.g.,][]{WW86,TDI,TDII},
+in addition to lateral variations in attenuation~\cite[e.g.,][]{romanowicz1998,reidetal2001,DaEkDz08}.
+Thus, the natural next step in global FWI is to use phase and amplitude information simultaneously to jointly constrain the elastic and anelastic structure of the Earth.
+To accomplish this next step, source parameters need to be constrained more carefully, especially as we push the resolution to shorter periods~\citep[e.g.,][]{valentine2010}.
+
+The global distribution of earthquakes (Fig.~\ref{fig:event_1480}) and stations (Fig.~\ref{fig:stations}) is highly uneven.
+This problem may be alleviated to some extent by using suitably chosen misfit functions with appropriate geographical weighting of sources and receivers~\citep[e.g,,][]{Li1996,Ruanetal2018}.
+The ultimate solution may be a dense network of Ocean Bottom Seismometers,
+but meanwhile an armada of floating seismometers may offer a cheaper and more practical alternative~\citep[e.g.,][]{Nolet19}.
 
@@
 
-GLAD-M25 --- like its predecessor GLAD-M15 --- invokes no crustal corrections,
-and constrains crust and mantle shear and compressional wavespeeds simultaneously.
-The effects of attenuation are fully accommodated,
-both in forward and in adjoint simulations.
+GLAD-M25 --- like its predecessor GLAD-M15 --- invokes no crustal corrections, and constrains crust and mantle shear and compressional wavespeeds simultaneously.
+Such ubiquitous crustal corrections may affect inferences about upper-mantle anisotropy~\citep[e.g.,][]{BozdagTrampert2008,PaLeRo10,Ferreira10}, and are likely the main reason for significant differences between radially anisotropic upper-mantle models~\citep[e.g.,][]{Chang14}.
+Treating the crust and mantle equally and simultaneously is one of the main strengths of GLAD-M25, accepting the additional computational costs, but thereby avoiding any approximations or corrections.
+Another strength is the fact that the effects of attenuation are fully accommodated, both in forward and in adjoint simulations.
+These points highlight the importance of taking the full physics of seismic wave propagation properly into account in seismic imaging.
+
+Another very important attribute of GLAD-M25 is that it constrains shear and compressional wavespeeds simultaneously in the same period range,
+thereby enabling us to interpret the two wavespeeds together.
+As illustrated in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R},
+numerous compressional wave arrivals are assimilated, including P, PP, PPP, PKP, PS, and PPS.
+In future work we will capitalize on this by using the $V_\text{P}/V_\text{S}$ ratio to help constrain thermo-chemical and geodynamical processes in the mantle.
 
@@
 we find overall good agreement at longer wavelengths.
-However, unlike other global models, when we compare GLAD-M25 with regional models
+In particular, GLAD-M25 and TX2015 feature very similar plume structures.
+Unlike other global models, when we compare GLAD-M25 with regional models
 we also observe generally good agreement at smaller wavelengths,
 and, in particular, plumes and subduction zones feature prominently.
-Thus, our global inversion is bridging the gap between global and regional studies,
+However, it is important to note that GLAD-M25 tends to agree well with regional models based on the same S362ANI~$+$~Crust2.0 starting model, numerical wave propagation solver, and quasi-Newton inversion technique (e.g., EU60, US22, and EARA2014).
+It is also important to point out that even in regions with dense seismographic coverage, such as North America,
+recent models can differ substantially, especially at greater depths.
+Nevertheless, our global inversion is bridging the gap between global and regional studies,
 approaching regional-scale resolution is areas with sufficient data coverage.
@@
   \centering
-  \includegraphics[width=0.95\textwidth]{figures/power_radius2.pdf}
-  \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (first column), S40RTS (second column) GLAD-M15 (third column), and GLAD-M25 (fourth column).
+  \includegraphics[width=0.95\textwidth]{figures/power_radius.pdf}
+  \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (left), GLAD-M15 (middle), and GLAD-M25 (right).
   Shown are depths greater than 120~km.
@@
 \end{figure}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.95\textwidth]{figures/power_radius2.pdf}
+%   \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (first column), S40RTS (second column), GLAD-M15 (third column), and GLAD-M25 (fourth column).
+%   Shown are depths greater than 120~km.
+%   (Courtesy of Caio Ciardelli.)
+%   }}
+%   \label{fig:powerspectraradius}
+% \end{figure}
 
@@
 The main difference between these two models and~PREM
-is the absence of the 220~km discontinuity and a lower~$V_P/V_S$ ratio in the top 200~km.
+is the absence of the 220~km discontinuity and a lower~$V_\text{P}/V_\text{S}$ ratio in the top 200~km.
 
@@
 \end{equation}
-In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, S40RTS, GLAD-M15, and GLAD-M25,
+In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, GLAD-M15, and GLAD-M25,
 and Fig.~\ref{fig:powerspectraradius} shows the normalized power per degree as a function of radius
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/power2.pdf}
-  \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), S40RTS (orange), GLAD-M15 (green), and GLAD-M25 (blue).
+  \includegraphics[width=0.5\textwidth]{figures/power.pdf}
+  \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), GLAD-M15 (green), and GLAD-M25 (blue).
   The calculation includes depths greater than 120~km.
@@
 \end{figure}
+% In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, S40RTS, GLAD-M15, and GLAD-M25,
+% and Fig.~\ref{fig:powerspectraradius} shows the normalized power per degree as a function of radius
+% for the same set of models.
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth]{figures/power2.pdf}
+%   \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), S40RTS (orange), GLAD-M15 (green), and GLAD-M25 (blue).
+%   The calculation includes depths greater than 120~km.
+%   Model S362ANI has no power beyond degree~18,
+%   and model S40RTS has no power beyond degree~40.
+%   (Courtesy of Caio Ciardelli.)
+%   }}
+%   \label{fig:powerspectra}
+% \end{figure}
 

### 2019-02-14 main.tex
Updates from Overleaf

@@
 Building on our first-generation global adjoint tomography model,
-GLAD-M15 \citep{bozdaug2016global}, we present our second-generation transversely isotropic global model,
+GLAD-M15~\citep{bozdaug2016global}, we present our second-generation transversely isotropic global model,
 named GLAD-M25, which is the result of ten quasi-Newton tomographic iterations with an
@@
 
-Before using 1,040 earthquakes in our structural inversion,
+Before using the 1,040 earthquakes in our structural inversion,
 we performed CMT inversions using model GLAD-M15,
@@
     \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}}\\
-    \caption{\small{Vertical cross sections for various plumes for models GLAD-M25 ($V_\textrm{P}$; left column), TX2015~\citep[$V_\textrm{S}$;][]{TX2015} (center column), and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad} (right column).
+    \caption{\small{Vertical cross sections for various plumes for models GLAD-M25 ($V_\textrm{S}$; left column), TX2015~\citep[$V_\textrm{S}$;][]{TX2015} (center column), and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad} (right column).
     The map in the top left corner of each row shows the cross section with color-coded red, green, and white dots for geographical reference;
@@
     (a) Afar; (b) Bermuda (left) and Canary (middle); (c) Cape Verde (middle) and Hoggar (right); (d) Iceland (middle) and Eifel (right); (e) Easter (left) and Galapagos (right); (f) Marion (middle), and Kerguelen (right).
-}}
+\red{(GLAD-M25 is still Vp)}}}
     \label{fig:plumes}
@@
     \centering
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Aeg.png}\label{fig:subd_a}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Br.png}\label{fig:subd_b}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:subd_c}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:subd_e}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:subd_d}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Su.png}\label{fig:subd_f}}\\[-1pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Aeg.png}\label{fig:subd_a}}\\[-8pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Br.png}\label{fig:subd_b}}\\[-8pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:subd_c}}\\[-8pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:subd_e}}\\[-8pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:subd_d}}\\[-8pt]
+    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Su.png}\label{fig:subd_f}}\\[-8pt]
     \caption{\small{Vertical cross sections of compressional wavespeed perturbations in various subduction zones
@@
     The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
-    (a) Aegean; (b) South America; (c) Hatteras; (d) Wichita. (e) Nepal; (f) Sunda. \red{(GLAD-M25 is still Vp)}}}
+    (a) Aegean; (b) South America; (c) Hatteras; (d) Wichita. (e) Nepal; (f) Sunda.}}
     \label{fig:subd}
@@
 Figs.~\ref{fig:subd}(c) and~(d) show cuts across the ancient Farallon slab, which penetrates deeply into the lower mantle,
-as spectacularly documented by~\cite[e.g.]{grand1994,hilst1997,grand1997high}.
+as spectacularly documented by, for instance, \citet{grand1994,hilst1997,grand1997high}.
 At depths greater than 1,000~km, 
@@
 Seismology is a science driven by data.
-There was a time when seismologists would meticulously inspect single seismograms to glean valuable information from them.
-Today, we have easy access to data from thousands of earthquakes recorded by tens of thousands of seismographic stations, and individual inspection of all of these records has become impossible.
+There was a time when seismologists would meticulously inspect single seismograms to glean valuable information from them \red{(Perhaps it is now the case for planetary seismology? )}.
+Today, we have easy access to data from thousands of earthquakes recorded by tens of thousands of seismographic stations, and individual inspection of all of these records has become impossible \red{(probably it depends on the seismologist.
+I remember Jeroen Ritsema telling that it is not a big deal to go through the entire database in a week or so with some not-so-sophisticated plotting techniques.
+Those interested in data still look at, I think..)}.
 Still, it would be a shame not to utilize as much as possible of the information in this massive seismographic database.
@@
 For data assimilation,
-tools such as FLEXWIN, which automatically select data windows suitable for measurements,
-are indispensable, and we see tremendous opportunities for the use of machine learning algorithms in this context~\citep[e.g.,][]{chen2017}.
+tools such as FLEXWIN, which automatically select data windows suitable for measurements, are indispensable, and we see tremendous opportunities for the use of machine learning algorithms in this context~\citep[e.g.,][]{chen2017}.
 Without these libraries and tools, the construction of model GLAD-M25 would have been impossible.

### 2019-02-15 main.tex
Updates from Overleaf

@@
 thereby capturing more deep events,
-and to avoid complications associated with source dimension and directivity,
+and, to avoid complications associated with source dimension and directivity,
 the largest moment magnitude is set to~7.2.
@@
 of our database and greatly improve coverage in certain regions.
-\red{(Looks like there are also OBSs to be mentioned, mainly for my curiosity, it would be good to know their contribution to the overall inversions.)}
 
@@
 quickly cripples the file system. The Adaptable Seismic Data Format
-(ASDF)~\citep[][ \texttt{https://seismic-data.org/ }]{krischer2016adaptable}
+(ASDF)~\citep[][ \texttt{https://seismic-data.org/}]{krischer2016adaptable}
 was developed with complete reproducibility and fast parallel processing in mind.
@@
 Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are of great importance, because they help constrain the compressional wavespeed structure in the model.
-The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances \red{(Again just for my curiosity, why PcP and ScS phases together with any phase after surface waves were excluded?
-Any special reason or just a decision?)}.
+The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
 This is something we will reconsider in future applications, perhaps by introducing aspects of machine learning.
@@
   and its maximum value is indicated in parentheses on the left, after
-  the depth. \red{(Probably the numbers on top-left of each map are min/max perturbations of the associated sections, but the colorbar is fixed to 2 to 7$\%$)}}}
+  the depth.}}
   \label{fig:global-vs}
@@
   \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
-  \caption{\small{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).\red{(LLNL model looks pretty interesting with the craton signature down to 300 km.
-Slab and craton anomalies together at 150 km look interesting too, as if they are two different models.
-In addition I am still wondering why are we the only one seeing Scotia Arc?
-Or why the others do not see it?
-It looks to me that it is pretty easy to add a slab signature to Scotia because of USArray.
-If there are earthquakes in their database at Scotia it should still easy to put it there even without USArray.
-Or perhaps it is indeed the bias of USArray coming from GLAD-M15?.)}}}
+  \caption{\small{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).}}
   \label{fig:southamerica-vp}
@@
     (a) Afar; (b) Bermuda (left) and Canary (middle); (c) Cape Verde (middle) and Hoggar (right); (d) Iceland (middle) and Eifel (right); (e) Easter (left) and Galapagos (right); (f) Marion (middle), and Kerguelen (right).
-\red{(GLAD-M25 is still Vp)}}}
+}}
     \label{fig:plumes}
@@
 TX2015~\citep[$V_\textrm{S}$;][]{TX2015}, and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad}.
-All three models have common plume features where GLAD-M25 and TX2015 seem to be more in good agreement.
+All three models have common plume features,
+and GLAD-M25 and TX2015 are in overall good agreement.
 
@@
     The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
-    (a) Aegean; (b) South America; (c) Hatteras; (d) Wichita. (e) Nepal; (f) Sunda.}}
+    (a) Aegean; (b) South America; (c) Hatteras; (d) Wichita. (e) Nepal; (f) Sunda. }}
     \label{fig:subd}
@@
 Seismology is a science driven by data.
-There was a time when seismologists would meticulously inspect single seismograms to glean valuable information from them \red{(Perhaps it is now the case for planetary seismology? )}.
-Today, we have easy access to data from thousands of earthquakes recorded by tens of thousands of seismographic stations, and individual inspection of all of these records has become impossible \red{(probably it depends on the seismologist.
-I remember Jeroen Ritsema telling that it is not a big deal to go through the entire database in a week or so with some not-so-sophisticated plotting techniques.
-Those interested in data still look at, I think..)}.
+There was a time when global seismologists would meticulously inspect single seismograms to glean valuable information from them.
+Today, we have easy access to data from thousands of earthquakes recorded by tens of thousands of seismographic stations, and individual inspection of all of these records has become impossible.
 Still, it would be a shame not to utilize as much as possible of the information in this massive seismographic database.

### 2019-02-21 main.tex
Updates from Overleaf

@@
 to prevent contamination of the inversion results.
-For these reasons, we use EnTK as our
+For these reasons, we are in the process of using EnTK as our
 workflow management engine~\citep{EnTK2017}.
@@
 workflow management software.
-We selected EnTK as our
+We have selected EnTK as our
 workflow management engine~\citep{EnTK2017}, and developed complementary seismic tomography

### 2019-02-21 coverletter.tex
update

@@
 We are pleased to submit the original research article entitled ``Global Adjoint Tomography -- Model GLAD-M25" for publication in the \textit{Geophysical Journal International}. 
+I performed all the simulations on Titan, constructed the model, made all the figures and wrote the first draft before inviting the coauthors to provide edits and comments.
+
+\par \noindent
+Currently, the coauthors and I have another paper under review in the \textit{Geophysical Journal International}.
+The title of the paper is "Balancing Unevenly Distributed Data in Seismic Tomography: A Global Adjoint Tomography Example".
+
+\par \noindent
 We would like to suggest the following potential 

### 2020-02-07 response_to_reviewers.tex
Updates from Overleaf

\documentclass[11pt,a4paper]{letter}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage[dvipsnames,usenames]{color}
\usepackage{listings}
\usepackage{verbatim}

\geometry{verbose,letterpaper,tmargin=1in,bmargin=2in,lmargin=1in,rmargin=1in}
%\lstdefinestyle{lat}
%{
%	style={[LaTeX]TeX},
%	basicstyle=\ttfamily
%}

\newcommand{\red}[1]{\textbf{\textcolor{Red}{#1}}}
\newcommand{\blue}[1]{\textbf{\textcolor{Blue}{#1}}}
\newcommand{\cyan}[1]{\textbf{\textcolor{Cyan}{#1}}}
\newcommand{\green}[1]{\textbf{\textcolor{Green}{#1}}}
\newcommand{\magenta}[1]{\textbf{\textcolor{Magenta}{#1}}}
\newcommand{\orange}[1]{\textbf{\textcolor{Orange}{#1}}}
%\newcommand{\red}[1]{#1}
%\newcommand{\blue}[1]{#1}
%\newcommand{\cyan}[1]{#1}

% comments between authors
\newcommand{\toall}[1]{\textbf{\orange{@@@ To all: #1 @@@}}}
\newcommand{\towenjie}[1]{\textbf{\red{*** Wenjie: #1 ***}}}
\newcommand{\tojeroen}[1]{\textbf{\green{*** Jeroen: #1 ***}}}
\newcommand{\toebru}[1]{\textbf{\cyan{*** Ebru: #1 ***}}}
\newcommand{\fromebru}[1]{\textbf{\orange{*** Ebru: #1 ***}}}
\newcommand{\fromyouyi}[1]{\textbf{\blue{*** Youyi: #1 ***}}}

\newlength{\tempheight}
\newlength{\tempwidth}

\newcommand{\rowname}[1]% #1 = text
{\rotatebox{90}{\makebox[\tempheight][c]{\textbf{#1}}}}

\newcommand{\columnname}[1]% #1 = text
{\makebox[\tempwidth][c]{\textbf{#1}}}

%\graphicspath{{./figure/}}

\def\baselinestretch{2}
\newcommand{\response}[1]{\textbf{Response:} #1}

\newcommand{\rev}[1]{{\it{#1}}}

\newcommand{\tsup}[1]{\textsuperscript{#1}}

%\address{your name and address} 
\signature{Wenjie Lei, et al.}

\begin{document}

\begin{letter}{Dr.~Ivan Vasconcelos\\
Editor, \textit{Geophysical Journal International}}

\opening{Dear Dr.~Vasconcelos,}

This is our response to the reviews of \textit{Geophysical Journal International\/} manuscript GJI-19-0247 entitled ``Global Adjoint Tomography -- Model GLAD-M25''.
We received three reviews of our paper: one was basically favorable and involved a ``light'' revision, a second (by Ritsema) was critical but constructive, suggesting helpful major revisions, and a third was unprofessional and inappropriate, especially in view of the fact the the first author of the article is a graduate student.

The three main issues raised in the reviews and editorial comments are: 1) uncertainty quantification, 2) model interpretation, and 3) manuscript structure.
We have revised the manuscript accordingly,
and moved significant portions of the original manuscript to Supplementary Online Material (SOM).

What follows is a detailed point-by-point response to the reviewer's and editor's comments.
Reviewer/editor's comments are in italics verbatim, and our response is in normal type. The citations and section number in our response refer to the revised manuscript unless we specify otherwise.

{\textbf{\large Response to Editor Vasconcelos}}

\rev{On technical advancement: the authors have made significant technical advances, as recognized by all three referees, however, the referees point out several technical points that could be better addressed (e.g., uncertainty analysis) in order to provide the credibility that the advances presented in this manuscript deserve. I leave it to the authors to decided how to address these points, e.g., either by restructuring the paper, incorporating additional studies/examples, or both.
}

\response{Uncertainty quantification is a long-standing challenge in seismic tomography that dates back to its inception. Checkerboard tests are basically useless (e.g., L\'ev\^eque, Rivera, and Wittlinger, 1993), and even ``proper'' tools, such as the resolution matrix suffer from the fact that ``resolution'' is controlled by playing with a subjective damping parameter. Bayesian
 inference would be a preferred method of inversion, but this is obviously not an option for the current study; an unavoidable fact that even Albert Tarantola grudgingly accepted.
Ideally, we would have tools that enable us to take multiple samples from the posterior model distribution, but unfortunately such tools have thus far eluded the community.
This is the reality in which the current study was conducted.

In this context we have tried, more so than other studies, to assess the quality of our model.
First, we calculate variance reductions for more than 20 million time windows and demonstrate quantitatively that M25 provides a significantly better fit to the data than both M15 and S362ANI.
We note at this point that ISC traveltime inversions often provide less than 10\% reductions in variance to \emph{only} P and S wave traveltimes (Nolet, personal communication).
Second, we present traveltime histograms for three-component measurements in four different passbands, and we demonstrate that the mean and standard deviations for model M25 are consistently reduced relative to M15 and S362ANI.
Finally, we use a held-out dataset of 320 earthquakes to demonstrate that these events, which were not used in the inversion, are fit equally well as the 1,480 events in the actual dataset (Incidentally, in this context, we find the comment by reviewer 2 that our paper lacks ``true scientific innovation'' insulting).
The original manuscript did not contain point-spread function (PSF) tests,
but several such tests are included in the revived manuscript.
A PSF does not say much about uncertainty ---like checkerboard tests and the resolution matrix--- but gives an idea of resolution and model parameter tradeoffs.
}

\rev{On interpretation of the results: the reviewers commend the technical achievements of the authors, but are simply not convinced that the model obtained is a sufficient advancement on the authors previous model, in terms of providing new insight into Earth structure and/or composition.
Because this is a significant component of the current manuscript, the authors must decide how to best address these concerns: either by better supporting their interpretation with additional evidence (related to the previous point), or by choosing to write a new version that focuses on methodological tomography advances, and not so much on interpretation just yet (as suggested by reviewers).
}

\response{To say that the new model, GLAD-M25, is not a significant advancement over the previous model, GLAD-M15, is perplexing. First, we provide quantitative evidence in the forms of misfit reductions (Tables 1 \& 2) and traveltime \& amplitude histograms (Figs.~10, 11, 12, 14 \& 15 in the original manuscript) that M25 fits the data better than M15.
Second, M25 resolves numerous new features that were entirely missing in M15, such as the Fiji-Tonga slab near New Zealand, and various hotspots in the Indian Ocean.
Rather than focusing on comparisons between M15 and M25, we chose to show comparisons with several global and regional models.
In response to the reviews,
we have reduced the number of model comparisons, focusing on plumes and subduction zones instead.
}

\rev{On manuscript structure and language: as pointed out by reviewers, this papers overall structure is indeed very similar to that of the Bozdag et al. (2016, GJI) one; it is by no means a copy-paste in content (this is a 'new' manuscript), but the structural similarity is there. In addition, reviewers and myself feel that the language used, particularly in the interpretation sections, is indeed a bit 'grandiose': while it is important to clearly highlight important points, there is also a danger of coming across as 'overselling'. As Editor, I personally would prefer if, in their new version, the authors would: i) reconsider the design/structure of the manuscript as to not be so similar to previous publications, ii) consider the language used in discussing results to indeed positively promote their advancements, while maintaining a critical, tempered tone. Please note this last point is 'Editorial preference', where the authors can improve delivery: while the two points above are the criteria used in my recommendation, this point is intended as an 'easy to implement' improvement.
}

\response{The present study involves a 6-fold increase in the number of earthquakes compared to M15 (1,480 events versus 253 events), but it uses the same model parameterization and has the same goal of constraining global mantle structure.
To enable the scale-up in the number of events, substantial advances were made in the development of the workflow management tools.
Rather than belaboring this work, we have moved much of this discussion to the SOM.
We have also taken suggestions to tone down the language to heart.
}

{\textbf{\large{Response to Reviewer~1}}}

\rev{In the introduction and conclusion it is mentioned that attenuation is fully accommodated in calculations.
I understand why the authors claim this, but nowhere is mentioned which attenuation model is used. I presume PREM, which we know is way off.
Is their model affected by this choice?
It is one thing dealing approximately with a bad model, it is another dealing exactly with a bad model.
}

\response{The 1D model is QL6~(Durek \& Ekstr\"om, 1996), which is also not ideal, but there are not really any better options,
and this is one of the main reasons why we are using phase information only.
However,
of course the reviewer is correct that any inversion is affected by the choice of and uncertainties in the attenuation model. 
This issue will be the subject of future studies.
}

\rev{In the relocation of the 1040 earthquakes, they allow for an arbitrary time shift of the synthetics. What is the justification of this and how big is this $\Delta t$.
I  think this needs explaining as later they add another 440 events without relocation and therefore no such time shift.
Is there not a risk that the centroid times of their whole dataset is now biased?
}

\response{The time shift parameter in the CMT inversion algorithm developed by~Liu et al.~(2004) accommodates structural uncertainty and has nothing to do with the centroid time.
It provides a means of estimating source parameters while minimizing contamination by lateral heterogeneity.
Note, however, that as part of every iteration we perform a grid search for the scalar moment and centroid time in the current 3D model,
and these corrections contribute to the final CMT solution.
The fact that the traveltime histograms are reasonably well centered
on zero suggests that there is no systematic bias in the centroid times.
}

\rev{They claim that the choice of the misfit function is important. I agree of course, but the reader only sees equations for the weights they use (eqs. 5 and 6). Is there a way to visualize these and what are their effects on the model.
}

\response{Yes, this is the subject of the Ruan et al.~(2019) paper, and we did not want to reproduce the related figures.}

\rev{In the model parametrization, they go from 5 Love parameters to 4 wave speeds. They   go from 5 to 4 parameters not because the introduce bulk sound speed, but because they explicitly assume A=C I presume.
}

\response{No, we assume $A=\kappa+\tfrac{4}{3}\,N$ and $C=\kappa+\tfrac{4}{3}\,L$\,. Thus the P wave anisotropy comes via the shear moduli.}

\rev{I wonder what window sorting and cleaning entails. How many outliers are eliminated?
}

\response{After plotting traveltime histograms towards the end of the window selection process, we clip the tails of the distribution, eliminating ~$3\sigma$~outliers.
This entails just a handful of ~$3\sigma$~outliers that may contaminate the model update.
}

\rev{They smooth the gradient differently to what they did in their previous 15 iterations. Has this a large effect? Obviously they must have a reason for changing this based on some tests.
}

\response{We changed the weighting scheme for sources and receivers,
which eliminates the need for the previously used variable smoothing of the gradient.
The weighting strategy is discussed in detail in~Ruan et al.~(2019), and includes examples of improved convergence.
One may still use multi-scale smoothing with the new weighting scheme to allow for smaller-scale heterogeneities under densely sampled regions.
}

\rev{Concerning the model evaluation, they refrained from point spread functions. Instead they show detailed misfits and comparisons with other published models.
I can understand that PSFs are computationally expensive (by the way they could reference the authors who suggested them first for FWI), but they are the only objective way to assess resolution.
Comparisons with existing models are not very helpful if these models have been done with different theories, data etc.
I would suggest at least to make a detailed comparison with GLAD-M15. Do we get visually a better resolution by throwing that much more data and GPU time at the problem. I suspect yes, but I still would like to see what improves where. 
}

\response{We provide detailed comparisons between M15 and M25 in Tables~1 and~2, as well as in all the traveltime and amplitude histograms.
In the revised manuscript we have also added a couple of new figures directly comparing M15 and M25, thereby highlighting distinct new features in M25.}

\rev{The authors mention that checkerboards are expensive. One could also mention that in fact they are useless for assessing resolution.
}

\response{Indeed. See our earlier discussion.}

\rev{The authors mention that the perturbations tend to be larger than in other models. I fully understand why this is, but it has a huge consequence for the interpretation of the model. We are now moving away from perturbations and enter the domain of finite difference. Trying to understand these models with partial derivatives for temperature and composition will be very misleading. If we want to infer temperature and composition, we will have to work with absolute values.
}

\response{That's correct. This is why we would prefer to share our model in the form of absolute values of wavespeeds.
Perturbations are desirable to show vertical sections, or at least the mean should be removed.
}

\rev{In that respect, I find the plume pictures for instance over-interpreted. What tells us that red in the upper mantle means the same as red at the CMB.
If they are confident that it means the same, they can say, for instance, the Iceland plume rises from the CMB, if not, it will be a different story.
The same holds for slabs. I suggest to be a bit more careful than just falling in the old habit that red is hot and blue is cold. The deviations are now so large that these analogies become misleading.
}

\response{We have modified the language.}

\rev{They don't mention anisotropy, but clearly invert for TI as claimed in the technical section. Do they see any evidence of anisotropy in the lower mantle for instance?
}

\response{As in M15, transverse isotropy in M25 is confined to the upper mantle, because it is mainly constrained by surface waves. }

{\textbf{\large{Response to Reviewer~2}}}

\rev{The authors describe a global waveform inversion based on spectral-element simulations and adjoint techniques. The outline follows numerous previous publication of roughly the same group of authors: presentation of the initial model, the distribution of events, of data and measurements, model parametrization, workflow, misfit evolution, and the final model.

I am fully aware that such an inversion is technologically challenging, and that the authors aim to publish the current state of their model. However, I have some rather serious and fundamental concerns that I would like to see addressed before making any more detailed comments. Specifically, I have difficulties to discover any true scientific innovation. To me, adding some events and slightly reducing the minimum period is clearly too incremental. If our community were to operate in such a mode, we would see a flood of tomographic models, each being an update of its predecessor with a few more iterations. This would slow down progress instead of accelerating it. Furthermore, the absence of even the slightest effort to assess the resolution of the model is hardly acceptable. Of course, nobody would request that the full resolution operator be computed for such an inversion, but some reasonable effort must be made. Simply writing that you ran out of computational resources to check the quality of the model is rather dubious.

As I wrote before, I perfectly know that this inversion is not a trivial task, and I do believe that it should be published somewhere. However, I really do not think that GJI is a suitable journal for this manuscript. My suggestion would be to refocus the manuscript on the technical and computational aspects, and to send it to a computational science journal.
}

\response{We appreciate the scientific criticisms of the reviewer.
We believe that both technically and scientifically our community will benefit from our efforts and experiences, because this is the first time this volume of data is
assimilated in such a computationally large-scale global inversion.
Therefore,
we believe that GJI is the right journal for this manuscript,
especially in view of the fact that many other papers on earthquake FWI/adjoint tomography have been published in GJI.
We do not agree with the reviewer that the slight reduction in minimum period is too incremental, and should thus not be considered scientific progress.
In fact, even though the period range of GLAD-M25 is similar to that of GLAD-M15,
we observe significant differences between the two models,
thanks to the 6-fold increase in the number of earthquakes,
including more than 500 deep events with very clean body waves.
Belittling our work with comments like ``adding some events'' when scaling the inversion up from 253 events to 1,480 events involved a herculean effort, especially on behalf of the first-author graduate student, is totally unprofessional and completely uncalled for.

We naively assumed that it was obvious from the GLAD-M15 GJI article and the histograms and comparisons with other models in this manuscript.
However, based on the comments of all the reviewers we now directly compare GLAD-M15 and GLAD-M25 in the revised manuscript,
thereby highlighting visual differences between the models, in addition to the the tables with variance reductions and traveltime and amplitude anomaly histograms.

There is still a vast amount of information to be explained in seismograms at the global scale, which requires more iterations and, probably, a more complete parameterization.
However, the reviewer is missing the main point --- or, more likely, we did not explain it well --- which is that we decided to publish GLAD-M25 because its resolution (scale-length of heterogeneities) has become comparable to the current resolution of global models from various other groups.
Thus we did not arbitrarily decide to publish this model,
and we certainly do not advocate publishing every iteration as a new model.
%We now highlight it in the manuscript that the vast amount of remaining data in the seismograms should continue changing the models which also points out the necessity of our non-linear iterative inversions.

Finally, resolution and uncertainty quantification remain a challenge in FWI,
both in exploration and earthquake seismology.
In lieu of such tools,
as in numerous other studies,
we used traveltime histograms and a held-out dataset to assess performance of our model.
We did not perform PSF tests, because these are rather limited in value, especially in view of the fact that they only tell you something about one ``point'' in the model for the set up of a particular iteration.
Therefore, a PSF does not say much about uncertainty, but gives an idea of resolution.
Nevertheless,
as mentioned earlier,
the updated manuscript now contains a few PSF tests.}

\rev{(1) By far my biggest concern is the lack of true scientific innovation. While the authors do mention some recent technological improvements (e.g., the storage algorithm for anelastic kernels and the ASDF data format), all of them have been published before, and are therefore not new. Apart from adding more events and going to slightly higher frequencies, this work is very similar to the previously published work by Bozdag et al. (2016). Also, the final model does not reveal anything about the structure of the Earth that was not known before.
}

\response{The main technical improvement is the workflow management.}

\rev{(2) In section 9.1, entitled "Point-spread function analysis", the authors explain that they actually did not perform such tests because they are computationally too expensive. Instead, they refer to 2 previous point-spread function calculations, published by Bozdag et al. (2016), using the earlier dataset.

Risking that I may sound unprofessional and harsh, I am sorry to say that this is ridiculous!

First of all, if one runs out of computational resources needed to check the quality of a model, it simply means that the inversion has been poorly planned! I am sure the authors know the number of node hours per forward run very well. It is therefore simply a matter of choosing a minimum period that leaves enough resources to run a reasonable model assessment. Simply saying that you better like to use the INCITE resources to just produce a colorful model, is a miserable excuse that I find completely unacceptable.

Second, it is not clear what to learn from 2 point-spread functions (apart from the fact that they were computed for different data). As the authors demonstrate in section 10 of their manuscript (interpretation and comparison), there are many more than 2 interesting points inside the Earth.

Third, the authors dedicate 13 pages (!!!) to the comparison of their new model to the previous and to other models. However, without any quantitative information on how much the new model has improved, this seems to be a rather meaningless exercise.
}

\response{We welcome scientific criticisms, however it is not acceptable that the reviewer completely ignores the fact that they are targeting a student,
%they is gender neutral
who is the first author of this manuscript.
We believe the reviewer is fully aware of the pitfalls of resolution analysis and uncertainty quantification in all tomographic inversions, unless a Bayesian approach is used, which is not even possible for classical global tomographic inversions.
The reason we did not perform PSF tests was not because we ran out of core-hours but chose not to use them for this purpose,
because a few PSF tests do not say much about global resolution.
}

\rev{(3) Though the authors repeatedly stress the size of their dataset, the number of events is rather small for a global model. Of course, it is an improvement to what the authors call their first-generation model, but compared to earlier global tomographies, the size of the dataset is not overwhelming.
}

\response{
Based on our estimation, there are about 6,000~events in the global CMT catalog suitable for global FWI.
So to say that at 1,480 events our dataset is ``not overwhelming'' seems rather harsh,
even more so if one considers that the only other global FWI efforts,
the Bozdag et al. (2016) and French \& Romanowicz (2015),
used just a few hundred events.
We also emphasize that the information going into the model,
as illustrated in the measurement window density maps shown in Figs.~2--4, is large.
This is another strength of our technique.
}

\rev{(4) I am also quite concerned about the writing and presentation style. The sections on supercomputing sound pretentious, which is a high risk for the authors, given that their model does not tell us many new things about the internal structure of the Earth. 
}

\response{
We did not intend for the sections on supercomputing to sound grandiose; we were merely attempting to convey the computational challenges and how these were overcome.
Much of this work was accomplished by the student first-author of the paper, and we were trying to highlight these rather nontrivial accomplishments.
Nevertheless, also in view of comments by other reviewers and the editor, we have toned down the language in the revised manuscript.

The statement ``their model does not tell us many new things about the internal structure of the Earth'' is again unnecessarily hash and uncalled for.
For example,
this is one of the few tomographic studies to constrain shear and compressional wavespeeds together in the same frequency band.
Thus, our Vp/Vs ratios certainly add scientific value.
We also invert body and surface waves simultaneously, which is important for constraining upper mantle structure.
Additionally, we make no crustal corrections, 
which too should lead to better constrained images of the deeper Earth.
Finally, in newly added figures visually comparing M15 and M25 numerous new features emerge,
such as several hotspots in the Indian Ocean, etc. 
}

\rev{Other paragraphs sound pretty grandiose, indicating that the authors may over-estimate their own achievements without being aware of what others have done before. Here is just one example from the Discussion: "Seismology is a science driven by data. There was a time when global seismologists would meticulously inspect single seismograms to glean valuable information from them. Today, we have easy access to data from thousands of earthquakes recorded by tens of thousands of seismographic stations, and individual inspection of all of these records has become impossible. Still, it would be a shame not to utilize as much as possible of the information in this massive seismographic database." To me this sounds bizarre, given that many previously computed global models actually used more data. Of course, nobody ever looks at all the wiggles individually. The measurement procedure has always been automated, for decades already! The authors may want to have a look at work by Jeroen Ritsema or by Andrew Schaeffer, for example.
}

\response{We have removed this paragraph, which an other reviewer objected to too, for different reasons.
However, the reviewer is apparently unaware that at least one of the seismologists he mentions still examines data by eye.
In fact,
many observational seismologists are still working like this!
}

{\textbf{\large{Response to Reviewer~3 (Dr.~Jeroen Ritsema)}}}

\rev{This manuscript presents GLAD\_M25 (or M25), un update of GLAD\_M15 (or M25) published by Bozdag et al. in 2016. Model M25 is an improvement because it is based on an analysis of 1400 events (250 events were used by Bozdag et al.) and the inversion has progressed by 10 iterations.
It is clear that the authors have thought deeply about the engineering of M25. I appreciate the phenomenal amount of work that has gone into developing M25 but there is unnecessary repetition of topics in Bozdag et al. (i.e., data formatting, earthquake relocation, crustal corrections, work flows, ...).
Figure 2 from Bozdag et al. is copied-and-pasted as Figure 4 in this paper and the graphs of misfit reductions and traveltime delay distributions are essentially updates of similar graphs in Bozdag et al..
}

\response{We have moved Fig.~2 (and numerous other figures) to the SOM. However, the misfit reduction plot is a rather integral part of the paper!}

\rev{I must admit that I am disappointed by the model evaluation in Section 10. The comparison with maps and cross-sections from other tomographic models is somewhat superficial and not as persuasive as the earlier sections of the paper.
}

\response{We have removed all the regional and full global comparisons, leaving just the plumes and slab figures, while adding a discussion of differences between M15 and M25, as requested by other reviewers.}

\rev{The manuscript is in decent shape but the writing is somewhat rushed after page 20 or so. The senior authors should polish the text and remove paragraphs, primarily in early sections, on topics that have been covered by Bozdag et al.
The authors don't do the point-spread function analysis so subsection 9.1 can be eliminated. I have annotated the PDF copy to suggest edits and to point out fuzzy wording.
}

\response{We have further polished the writing later in the manuscript
Thanks for the annotated manuscript! We have accommodated most comments and suggestions.
Based on suggestions by the other reviewers,
we added some PSF tests to the manuscript.}

\rev{The GLAD-M tomography stands out from the other approaches by casting the inverse without compromising the physics of wave propagation. Consequently, the workflow is laborious and iterations are slow. Ten iterations for a moderate data set (compared to the S40RTS data set, for example), took more than two years. Sections 1--9 indicate that the authors are convinced about the value of their approach but the discussion onward from Section 10 is qualitative and not serving the authors' case.
I worry that readers might wonder whether M25 is a significant step forward from M15 and whether the tremendous engineering and use of computer power justifies the (re)discovery of velocity anomalies that do not appear to change our understanding of mantle structure and dynamics.
}

\response{We have modified the manuscript substantially, as discussed previously. We focus more concretely on differences between M15 and M25.
Unfortunately,
comparisons with other models will always be rather qualitative, because we have no way of using such models in 3D wave simulations, mainly because 3D mantle models are difficult to combine with 3D crustal models. Underneath the oceans there tends to be a `gap' between the mantle model and the crust, whereas underneath the continents there tends to be a region of overlap, and this make `gluing' the two together challenging.}

\rev{I recommend therefore some restructuring of the paper by relating the modeling results to the adjoint tomography approaches. To stay on the topics raised in sections 1--9, I suggest the authors demonstrate with specific examples that the complex GLAD-M workflow is the only viable approach for making progress in global-scale seismic tomography. The paper will become more technical in tone and will cater primarily to the seismological community but that should be acceptable for GJI. Image interpretations in terms of Earth's structure and dynamics could be published in journals with a somewhat broader readership. Restructuring will involve new work for the leading student author, but I think it is worth the effort.
}

\response{We have substantially restructured the manuscript along the lines suggested.}

\rev{1. Recalculation of sensitivity kernels after each iteration is expensive. Is it necessary?
It would be helpful to see examples of how surface wave kernels changed from iteration 0 to 25 for ``simple'' paths (e.g., in ocean basins) and for ``complex'' paths (e.g., along ocean-continent margins). Are there good examples of waveforms that demonstrate that M25 is explaining surface-wave multipathing because kernels are recalculated for a 3-D structure?
}

\response{We do not calculate sensitivity kernels, as in the Dahlen \& Nolet banana-doughnut approach! Instead, we directly calculate contributions to the model gradient, which involves assimilation of the measurements for the current model. Thus, this model update must be recalculated at each iteration.
There are lots of examples of the effects of 3D structure on such kernels in the literature.}

\rev{2. Along the same lines, do the sensitivity kernels for body waves through the deep mantle change from iteration 0 to 25? Always or only when, for example, when they skirt the LLSVP? Would it be sensible to recalculate the high-frequency body-wave kernels only every 5th or 10th iteration to safe computational time? Are there good reasons not to do this?
}

\response{See our response to the previous comment. We do not calculate individual sensitivity kernels a la Dahlen \& Nolet.
%\fromebru{I think we can put such a figure as well (I mean in the response, not sure needed for the paper but may go into SOM as well). The kernels must definitely change for paths across the plumes. Also we may be able to give what I encountered in GLAD-M15 before taking full attenuation into account in adjoint simulations as an evidence that we need to compute exact kernels to further decrease the misfit and improve the model}
%\toebru{Going back to Carl and Qinya's papers, there are lots of such examples in the literature. There is no need to belabor this.}
}

\rev{3. I would like to see examples of recorded and synthetic data at long (T > 250 s), and short (T < 10 s) periods to illustrate that M25 is (close to) reproducing waveform segments and data types not yet selected by FLEXWIN. How good is the fit to waveform segments (e.g., ScS) and data types (e.g., normal mode splitting) not included in the inversion?
}

\response{Calculating synthetics at periods less than 17 s is a very expensive proposition! Going to 9~s involves a 16X increase in the computational cost.
}

\rev{4. Source finiteness is already important. A MW7.2 earthquake is assumed to have a duration of 21 seconds (an empirically determined value in the CMT catalog) comparable to the shortest periods used here. What is the effect on the traveltime measurement if the duration is overestimated by 5 or 10 seconds (deep earthquakes tend be more compact)? When higher frequencies are incorporated, do the authors plan to invert for source durations or can they rely on standard catalogs of source time functions (e.g., SCARDEC)?
}

\response{Low pass filtering at 17~s largely eliminates sensitivity to shorter half durations. 
In addition, when the waveform difference caused by the source time function is too large, it will be rejected by our data screening process. Going forward we are planning to do our own CMT inversions in M25, but including a STF estimation.
}

\rev{5. As the authors plan to include attenuation in the parameterization, will this be a new 1-D profile for Q or a fully 3-D structure? How might this affect the inversion for dVs (and dVp)? For example, assuming that dVs and dQ-1 are related linearly ---- take Colleen Dalton's model for a first-order scaling between dVs and dQ-1 ---- how would this change the traveltime fits? How should dVs and dQ-1 be parameterized (and regularized) to assure that the inversion converges to sensible models for both parameters?
}

\response{We are planning a fully 3D Q inversion. This will be a ``proper'' Q inversion,
where there full effects of attenuation, i.e., physical dispersion and dissipation, will be taken into account. We have some experience with such inversions in Europe (Zhu et al., 2013), and for problems in exploration seismology.
}

\rev{Below a long list of additional comments and questions in page order. Even more comments are included as annotations in the PDF.}

\response{Thanks! We've taken the suggestions in the PDF into account in our revision.}

\rev{a) Page 4. Are all nine layers of CRUST2.0 parameterized in the starting model? Is the crustal structure part of the model? If not, why not? If so, what is the new structure?
}

\response{The nine layers are not parameterized as layers in the spectral-element mesh. Instead,
the Moho is honored as much as possible by the mesh, whereas the crustal wavespeeds are accommodated by the Gauss-Lobatto-Legendre integration points (see Tromp et al. 2010 for a detailed description). The crust and mantle are inverted simultaneously.}

\rev{b) Figure 1. Panel (a) can be deleted. The colours are indistinguishable in my PDF copy due to event overlap, nor is it apparent to me that an interesting pattern has emerged. Panels (c) and (d) show the same info. Since Dh does not vary with source depth, (c) can be eliminated. Are Dh (in d) and Dt (in e) correlated?
}

\response{We have made a new Fig.~1 with just the sources and stations. Other source information has been moved to the SOM.}

\rev{c) Page 5. The durations of earthquakes with moment magnitude of 7 are long enough to affect T > 15 waveforms. I assume the authors use CMT half durations. These are not measured but derived empirically from MW. In my experience, they are not reliable, especially for deep earthquakes. It might be necessary (especially when going to higher frequencies) to invert for the duration in the inversion or rely on source catalogues that have estimated durations from P- waveforms (e.g., SCARDEC, Martin Vallee).
}

\response{This is on our list of things to do. We are in the process of upgrading the Princeton Global ShakeMovie system to model M25, and we will start performing our own CMT inversions in this model, including STF estimation.}

\rev{d) Page 6. ``We allow the synthetics to shift ...''. This sounds like a frowned-upon station correction.
}

\response{Only as part of the CMT inversion, which is then followed by a grid source for the centroid time and the scalar moment.}

\rev{e) Figure 2. Panel (a) is a duplication of Figure 1a. Panels (b) and (c) can be included in Figure 1.
}

\response{See our earlier response.}

\rev{f) Figure 3. This figure is fairly busy and not informative. If the authors decide to keep it, I suggest the oceans and continents are simply white.
}

\response{We like this figure, which gives a good idea of station `hit count'. It has been combined with the source figure.
}

\rev{g) Page 8. I have read the statement on SAC before in Jeroen's papers and I apologize for my quibble. The ASDF format may very well be ideal but there are options other than SAC. Many seismologists, including yours truly 20 years ago, developed data and metadata containers that are self-describing, compact, and ``cat-able'' to improve I/O and processing speeds. The bullets on page 9 are too vague.
}

\response{Point taken. We have removed the section on ASDF because the format is already discussed in the original ASDF paper, and in the Bozdag et al.~(2016) paper.}

\rev{h) Page 9. It is not clear to me which part(s) of the seismogram the data categories encompass. Can waveform segments classified as ``17-40 s body waves'' overlap with segments from the ``40-100 s body waves'' group? It would be helpful to show four seismograms for the different frequency bands that indicate where windows are typically chosen.
}

\response{The windows are taken independently of categories, based on the quality of fit. Examples of such windows may be found in Bozdag et al.~(2016).}

\rev{i) Page 10. Was the imbalance in M15 (e.g., thousands of paths between circum-Pacific events and the USArray) the motivation for the source and receiver weights in equations 5 and 6?
}

\response{Yes. M15 tried to compensate for this based on ray density weighting, but the new approach demonstrably leads to faster and better convergence (see Ruan et al.~2019).}

\rev{j) Figure 6. Both PS and SP can be strong on the vertical and radial components. So, change the label ``PS'' to ``SP+PS''. Why are there few segments close to the PPP arrival (beyond 100 degrees)? Since it is used in the caption, I would use seconds along the y-axis (also in the next two figures).
}

\response{Points taken. PPP is not prominent, and picked rarely by Pyflex.}

\rev{k) Figure 8. Why are there few segments along the SSS branch? I understand FLEXWIN does not look for ScS, ScS2, ScS3 etc. but one doesn't need to teach a machine to find them.
At T > 15 s periods they are very apparent for dip-slip earthquakes (especially deep earthquakes) and they are isolated from other phases at the shortest distances.
PcP is visible at D< 60 deg but it is otherwise a crappy phase. No one has ever found PcP2, as far as I know. Other phases to consider are the major-arc S reflections (i.e. SSm, SSSm). 
They propagate through the mantle in the southern hemisphere. We selected a few thousand but could not fit their traveltimes well (using ray theory).
}

\response{S and SS are more prominent than SSS, and Pyflex selects fewer of these arrivals. We are working on adjusting the Pyflex setting to pick ScS, ScS2, and other later arrivals, so these will be included in future iterations.}

\rev{l) Table 1. Clarify ``changes in fit'' or maybe show residual misfit instead which is used frequently. Is it correct that the 40-100 s period surface wave fit has improved the most? This would indicate that the 10 iterations have primarily adjusted the uppermost mantle.
Is the misfit reduction smallest for the ``overtones surface waves'' (the S multiples arriving before the fundamental mode) (i.e., 40-100 s body waves)?
This might indicate that the mantle transition is still resolved poorly (or was already resolved very well by S362ANI).
Section 8.4 could use more discussion regarding the misfits of the various categories and what it implies for the resolution of dVs (and dVp) as a function of depth.
}

\response{This is the variance reduction for the subset of measurements in each of the 12 categories. Surface waves show more of a reduction because the waveforms are more complex, and moving them in phase gives a greater variance reduction than improving the fit to a simpler body waveform. The categories reflect pass bands and components, not depth resolution..}

\rev{m) Figure 10. The histograms of Figure 10 also suggest the modeling of the 40-100 s surface waves has been most successful. Maybe the overtones should have more weight in the next iterations?
}

\response{See the earlier explanation.
Surface wave fits are much worse than body wave fits prior to inversion, because the former waveforms are dispersed.
Thus there are more gains to be had. We don't strip overtones, so these are not fit individually, nor can they be weighted separately.
Instead, we fit full surface waveforms.
}

\rev{n) Figure 11. Its discussion on page 21 is short. The skew in the distribution for DTp may indicate that the 1-D reference model for P-wave speed is inadequate. PP-P traveltime differences (see Ritsema and van Heijst, 2002) indicate that PREM underestimates the traveltimes of PP with oceanic bounce points by several seconds.
So, Vp in PREM is too high for the upper mantle beneath oceans but it is okay for the continents. Perhaps the 1-D background model used for S362ANI has inherited PREM characteristics and the 1-D bias has not yet been removed after 25 iterations.
I suggest the authors check similar plots for PP and SS. This might have implications for the P model.
}

\response{We removed these histograms and the amplitude histograms. However, we believe the slight skew is more likely related to depth phase, which skew the P and SH arrival and may bias the cross-correlation traveltime measurement.}

\rev{o) Figure 12. The discussion on amplitudes is also a bit brief and lacks citations to previous work (e.g., Dalton et al.).
I disagree that the ``histograms are nicely centered''. Some peaks are near -0.1 or -0.15 meaning that amplitude for some segments are, on average, 10-15\% lower than predicted. I have recorded discrepancies in the SS/S amplitude ratio by the same amount.
This ratio is insensitive to the source. I would be curious to hear what the data set used here finds for SS/S.
}

\response{We are not sure what you mean. The M25 peaks in Fig.~12 are at 0.02, -0.01, 0.02, -0.05, -0.03, -0.04, 0.05, 0.10, -0.06, -0.02, 0.07, and -0.06. So only one peak is at -0.1, and considering the standard deviations, these histograms really are ``nicely centered''.
Note that the amplitude histograms were removed in the interest of succinctness and focus.}

\rev{p) Page 26 and Figure 16. The authors must include panels for M15 in Figure 16 and discuss what has changed.
Given the variance reductions I suspect most adjustments have been made in the upper mantle. The text needs two points of clarification:

(i) Although the authors invert for dVp and dVs, the resolution of dVp is poorer than of dVs, particularly in the uppermost mantle (constrained by surface waves) and in D'' (constrained by diffracted waves).

(ii) The strength of structure in the models is for a large part determined by regularization. As shown in Ritsema et al. 2011 we can change the amplitude of S40 (and the width of the resolution kernels) by changing the damping without compromising the data fit significantly. Comparing amplitudes of structures from different models without considering resolution differences is a tricky thing.

q) In Figure 18 I suggest to include the model by Krischer et al. (JGR; 2018). Model US22 is perhaps not that useful in the context of this comparison since it is based on a similar modeling approach and data set as M25.

r) Since SL2013NA (a ``ray'' model) doesn't appear too different from M25 it is not clear from the visual comparison) whether modeling improvements (i.e., better theories) matter.
(Note that I suspect they do matter for surface waves because your variance reduction is large for the surface wave data -- see my point 1).

s) The differences among the models at depths larger than 300 km in Figure 18 is striking.
The authors draw the reader's attention to anomalies with well-understood tectonic origins but at face value the images are really very different especially for US22 (and M25) and SL2013NA.
The latter model is based on a large set of overtone surface wave data that should sample the MTZ very well. The misfit reduction obtained for the 40-100 s body + surface waves (presumably waveform segments after SS and before the fundamental mode surface wave) is relatively poor, so perhaps the MTZ in M25 is still poorly resolved (or S362 was an excellent model to begin with).
At any rate, this need further discussion. Transition zone resolution is still a sticky point and is important for understand convective flow.

t) Figure 19. Perhaps include SL2013sv and the model by Rickers et al. (EPSL; 2013).
}

\response{Based on comments from the other reviewers and the editor, we have moved
all model comparisons to the SOM, except for the plumes and slabs figures.
We have added a figure in which we directly compare M15 and M25 for a few key locations.}

We have tried to address all remarks made by both reviewers and the editors.
We hope that with these modifications our manuscript will be acceptable for publication in \textit{Geophysical Journal International}.

\closing{Sincerely,}

\end{letter}

\end{document}

### 2020-02-07 main.tex
update
Updates from Overleaf

--- 2019-02-15 main.tex
@@
 
+% comments between authors
+\newcommand{\toall}[1]{\textbf{\orange{@@@ To all: #1 @@@}}}
+\newcommand{\towenjie}[1]{\textbf{\red{*** Wenjie: #1 ***}}}
+\newcommand{\tojeroen}[1]{\textbf{\green{*** Jeroen: #1 ***}}}
+
 \floatsetup[figure]{style=plain,subcapbesideposition=top}
@@
   $^6$ Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ 08544, USA\\
-  $^7$ Oak Ridge National Laboratory, Oak Ridge, TN 37831, USA\\
+  $^7$ Oak Ridge National Laboratory, Oak Ridge, TN 37831, USA
   }
@@
 \begin{summary}
-Building on our first-generation global adjoint tomography model,
-GLAD-M15~\citep{bozdaug2016global}, we present our second-generation transversely isotropic global model,
-named GLAD-M25, which is the result of ten quasi-Newton tomographic iterations with an
+Building on global adjoint tomography model~GLAD-M15~\citep{bozdaug2016global}, we present transversely isotropic global model~GLAD-M25,
+which is the result of ten quasi-Newton tomographic iterations with an
 earthquake database consisting of 1,480 events in the magnitude range $5.5\le M_w \le 7.2$,
@@
 facilitated by a parsimonious storage algorithm.
-The simulations were performed on the Cray XK7 ``Titan'' at the Oak Ridge Leadership Computing Facility.
-We quantitatively evaluated GLAD-M25 by assessing misfit reductions and traveltime \& amplitude anomaly histograms in twelve measurement
+The simulations were performed on the Cray XK7 ``Titan'' and the IBM Power~9 ``Summit'' at the Oak Ridge Leadership Computing Facility.
+We quantitatively evaluated GLAD-M25 by assessing misfit reductions and traveltime anomaly histograms in twelve measurement
 categories.
@@
 with results comparable to the actual inversion.
-We compare GLAD-M25 with numerous other global and regional models,
-and highlight a variety of plumes and subduction zones.
+We highlight the new model for a variety of plumes and subduction zones.
 \end{summary}
@@
 
-Current global seismic models are in general agreement regardless of data type and inversion strategy in terms of long-wavelength heterogeneity \citep{ritzwollerlavely1995,TW01,beckerboschi2002}.
-However, discrepancies between models become noticeable as resolution increases.
-Using accurate 3D simulations of seismic wave propagation and the computation of data sensitivities in 3D background models are key requirements for improving resolution in tomographic images on all scales.
+Current global shear wavespeed models are in general agreement regardless of data type and inversion strategy in terms of long-wavelength heterogeneity \citep{ritzwollerlavely1995,TW01,beckerboschi2002}.
+However, discrepancies between models become noticeable at shorter wavelengths.
+Using accurate 3D simulations of seismic wave propagation and the computation of data sensitivities in 3D background models are key requirements for improving resolution in tomographic images on all scales~\citep{Tromp2020}.
 Such detailed images are essential for understanding mantle dynamics and related surface tectonic processes
----for example the origin of hotspots and the forces behind plate motions and earthquakes.
-Higher resolution wavespeed models are also important for accurately locating earthquakes, and are required from an engineering point of view to assess seismic hazard in earthquake prone regions and to detect nuclear explosions.
+---for example the origin of hotspots and the driving mechanisms of plate motions and earthquakes.
+Higher resolution wavespeed models are also important for accurately locating earthquakes, and are required from an engineering point of view to assess seismic hazard in earthquake prone regions and to detect and locate nuclear explosions.
 
@@
 in this study we use a GPU-accelerated version of the 3D spectral-element solver
-SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the Cray supercomputer ``Titan'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
+SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the supercomputers ``Titan'' and ``Summit'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
 These simulations accommodate the full 3D complexity of global Earth models,
@@
 For each iteration,
-1,480 forward and adjoint simulations need to be performed,
+1,480 forward and adjoint simulations need to be performed (one pair for each earthquake in the database),
 generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
-How to deal with hardware failures during this process is critical
-to prevent contamination of the inversion results.
-For these reasons, we use EnTK as our
-workflow management engine~\citep{EnTK2017}.
-This workflow engine can automatically detected job failures,
-both from the high-performance computing (HPC) system and via user-defined functions.
-This facilitates tracking of tasks and semi-automatic job resubmission if necessary.
-
-In this article we compare the results of our inversion with a number of previous tomographic models.
-On a global scale, we present comparisons with model S362ANI$+$M~\citep{moulik2014anisotropic},
-which is an updated version of model S362ANI~\citep{kustowski2008anisotropic},
-the starting model for the GLAD-M15 inversion.
-We also consider global shear wavespeed models S40RTS~\citep{ritsema2011s40rts},
-TX2015~\citep{TX2015}, SEMUCB-WM1~\citep{french2015broad},
-and SL2013sv~\citep{SchaefferLebedev13},
-as well as compressional wavespeed models LLNL-G3Dv3 \citep{simmons2012llnl}, GAP-P4~\citep{fukao2013subducted}, and UU-P07~\citep{van2018atlas}.
-On the scale of North America
-we make comparisons with models US22~\citep{zhu2017radial},
-a radially anisotropic model based on adjoint tomography using USArray data from 180 regional earthquakes,
-and SL2013NA~\citep{schaeffer2014imaging},
-a modification of global model SL2013sv focused on North America.
-In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison,
-which is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
-Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227~earthquakes recorded by more than 1,800~stations.
 
 This article is organized as follows.
-Sections~\ref{section:start}--\ref{section:data} describe the starting model,
-earthquake database, and seismographic data set. 
+Section~\ref{section:seismic data} illustrates the earthquakes and seismographic stations used in the inversion,
+as well as the assimilated seismic data. 
 Sections~\ref{section:misfit} and~\ref{section:parameterization} describe the misfit function minimized during the inversion process
 and the related model parameterization.
-In Section~\ref{section:workflow} we describe the adjoint tomography workflow in some detail.
-Section~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 360 earthquakes.
-Finally, in Section~\ref{section:model}, we describe the model in detail,
-offering many comparisons with various global and regional models, as described in the proceeding paragraph.
+Section~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on point-spread function analyses and a held-out data set of 360 earthquakes.
+Finally, in Section~\ref{section:model}
+we compare the results of our inversion with global shear wavespeed models 
+TX2015~\citep{TX2015} and SEMUCB-WM1~\citep{french2015broad},
+as well as compressional wavespeed models GAP-P4~\citep{fukao2013subducted} and UU-P07~\citep{van2018atlas}.
 We conclude with a discussion of future opportunities and directions.
 
-\section{Starting model GLAD-M15}
-\label{section:start}
-
-As a continuation of our previous work~\citep{bozdaug2016global},
-we used the first-generation model GLAD-M15 as our
-starting model.
-GLAD-M15 is a 3D transversely isotropic earth earth model, which combined
-3D mantle model S362ANI~\citep{kustowski2008anisotropic}
-with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
-In this study,
-we continue to use the same transversely isotropic model parametrization.
-Instead of relying on crustal corrections,
-the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
-GLAD-M15 was constructed using a global database of 253 earthquakes.
-The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
-and the final 3 iterations reduced this further to 17~s.
-In this study we also used three-component seismograms with a shortest period of 17~s.
-
-\section{Earthquakes}
-\label{section:earthquakes}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
-  \caption{\small{Source corrections for 1,040 out of 1,480 events used in the structural inversion.
-(a) Map view of depth changes.
-(b) Distribution of seismographic stations used for source inversions.
-(c) Depth change relative to the original global CMT Catalog depth.
-(d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
-  }}
-  \label{fig:source_correction}
-\end{figure}
-
-In addition to the 253 earthquakes used for the construction of GLAD-M15, we initially carefully selected 784 additional earthquakes
-from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global},
-resulting in a total number of 1,040 earthquakes.
+\section{Seismic data}
+\label{section:seismic data}
+
+Fig.~\ref{fig:eventsstations}(a) shows a map of the 1,480 earthquakes
+selected from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global}
+and used in this study.
 To ensure a good signal-to-noise ratio on a global scale,
@@
 the largest moment magnitude is set to~7.2.
-
-Before using the 1,040 earthquakes in our structural inversion,
-we performed CMT inversions using model GLAD-M15,
-the results of which are summarized in Fig.~\ref{fig:source_correction}.
-To ensure even global coverage,
-we used seismographic stations from the  Global Seismic Network (II, IU, IC, US, CU, and GT),
-GEOFON~(GE), GEOSCOPE~(G), and several regional networks, such as MedNet~(MN),
-the Brazilian Lithospheric Seismic Project~(BL), the Chilean National Seismic Network~(C),
-and the Japan Meteorological Agency Seismic Network~(JP) (Fig.~\ref{fig:source_correction}b).
-The number of stations used for CMT inversion usually ranges
-from~150 to~500.
-
-To determine the source parameters in the starting model,
-we used the CMT inversion algorithm of \cite{liu2004spectral}.
-This algorithm combines a normalized waveform difference misfit with an envelope difference misfit.
-Specifically, the algorithm minimizes the misfit function
-\begin{equation}
-   \begin{split}
-      \Phi =  \sum\limits_{c=1}^{C} \omega_c \sum\limits_{r=1}^{R_c} \omega_{cr}
-       \sum\limits_{w=1}^{W_{cr}} \omega_{crw}\,
-          & \left\{ \lambda\, \frac
-              { \int \big[ d_w(t) - s_w(t - \Delta t) \big]^2 \mathrm{d}t}
-              {\int \big[ d_w(t) \big]^2  \mathrm{d}t} \right.
-       \\ & \quad \left. \mbox{} + (1 - \lambda)\, \frac
-              {\int \big[ e(d_w(t)) - e(s_w(t - \Delta t)) \big]^2 \mathrm{d}t}
-              {\int \big[ e(d_w(t)) \big]^2\mathrm{d}t} \right\}
-              \quad ,
-   \end{split}
-\end{equation}
-where~$d_w(t)$ denotes data in time window~$w$\,,
-and~$s_w(t - \Delta t)$ the corresponding synthetic for model~GLAD-M15.
-We allow the synthetics to shift relative to the data by an amount~$\Delta t$
---- effectively a station correction --- determined by cross correlation.
-The envelope function is denoted by~$e(\,\cdot\,)$\,,
-and the parameter~$\lambda$ determines the balance between fitting waveforms versus fitting envelopes.
-The number of measurement categories is denoted by~$C$\,.
-Following~\cite{ekstrom2012global},
-seismograms were filtered between 50~s and 100~s
-to select three-component body-wave windows,
-and between 60~s and 100~s to select three-component
-surface-wave windows,
-resulting in six measurement categories, $c=1,\ldots,C$\,.
-To balance their contributions,
-each category is weighted by the reciprocal of the number of measurements in that
-category, $\omega_c$\,.
-The number of windows for a given receiver~$r$ in a given measurement category~$c$ is~$W_{cr}$\,.
-Each such window is weighted equally, i.e.,~$\omega_{crw}=1$\,.
-The number of receivers that records data in category~$c$ is denoted by~$R_c$\,.
-As shown in Fig.~\ref{fig:source_correction}b,
-the receivers are unevenly distributed across the globe,
-with several dense arrays in the Northern Hemisphere and poor coverage in the Southern Hemisphere.
-To balance the coverage,
-following a strategy articulated by~\cite{Ruanetal2018},
-we assign receiver weights~$\omega_{cr}$ based on the expression
-\begin{equation}
-\omega_{cr}^{-1} = N_c\,\sum_{r'=1}^{R_c} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_c}\right)^2\right]
-\quad ,
-\label{eq:spatial_weights}
-\end{equation}
-where~$N_c$ is a normalization factor for category~$c$,
-and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
-The reference angular distance~$\Delta_c$ for each category~$c$ needs to be chosen such that the condition 
-number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
-The calculation of the weights may be abstracted as: given a distribution of
-points on the unit sphere, determine a spatial weighting associated with each point.
-
-The algorithm inverts for the six elements of the moment tensor
-and the centroid location~(latitude, longitude, and depth).
-These source inversions are computationally very expensive,
-because for each of the 1,040~events nine full 3D forward simulations are required to obtain the source parameter Fr\'echet derivatives.
-
-Because we allow the synthetics to shift in phase by an amount~$\Delta t$ relative to the data,
-the CMT inversion has unreliable sensitivity to the centroid time.
-To alleviate this problem,
-following~\cite{zhu2012structure},
-we perform a subsequent grid search for the centroid time and the scalar moment.
-The grid-search calibration involves simple shift and multiply operations on seismograms
-and, unlike the CMT inversion, requires minimal simulation time.
-
-Most earthquakes show a shallower depth after inversion
-(Fig.~\ref{fig:source_correction}c),
-consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}.
-We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
-an average scalar moment change of~$5.31\pm3.91$\%,
-and an average centroid time shift of~$-0.60\pm1.17$~s.
-These are relatively minor corrections, especially in view of the significant expense of the source inversions.
-For this reason, when we added another 440 earthquakes during iteration~22,
-thereby bringing the total to~1,480 events,
-we only performed a grid search to calibrate the centroid times and scalar moments.
-Fig.~\ref{fig:event_1480} summarizes the characteristics of all 1,480 earthquakes used in this study.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/events_1480.pdf}
-  \caption{\small{The 1,480~earthquakes used in this study.
-(a) Distribution of earthquakes.
+Prior to the structural inversion,
+we performed source inversions using model GLAD-M15 and the CMT inversion algorithm of \cite{liu2004spectral},
+as described in the Supplementary Online Material (SOM).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figures/events_1480.pdf} \\
+  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
+  \caption{\small{(a) Distribution of 1,480~earthquakes used in this study.
 The color of each beach ball reflects its depth range, where blue designates events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
-(b) \& (c) Histograms of earthquake moment magnitudes and depths.}}
-  \label{fig:event_1480}
-\end{figure}
-
-\section{Seismic data}
-\label{section:data}
-
-The seismographic stations used in this study were carefully selected to ensure global coverage
-and high data quality (Fig.~\ref{fig:stations}).
+  (b) Distribution of the 11,800~seismographic stations used in this study.
+Colors denote the number of events for which a given station contributes waveforms to the structural inversion.
+Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers.
+The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.
+  \towenjie{Remove panels (b) and (c) and fix up the figure. Make sure the station count starts at 1, not 0.}
+  }}
+  \label{fig:eventsstations}
+\end{figure}
+
+The seismographic stations used in this study are plotted in Fig.~\ref{fig:eventsstations}(b) and
+were selected to optimize global coverage
+and high data quality.
 In addition to the seismographic  stations used for the source inversions,
-we included all available data for our 1,480 event earthquake database from many data centers,
+we included available data for our 1,480 event earthquake database from many data centers,
 including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
@@
 
-\begin{figure}
-  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
-  \caption{\small{Distribution of the 11,800~seismographic stations used in this study.
-Colors denote the number of events for which a given station contributes waveforms to the structural inversion.
-Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers.
-The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}}
-  \label{fig:stations}
-  \centering
-\end{figure}
-
-\subsection{Adaptable Seismic Data Format}
-\label{section:ASDF}
-
-Conventional seismic data formats, such as SAC, involve one file per time series
-plus related files with instrument response and event information.
-Since every earthquake in the database is typically recorded by thousands of
-instruments, I/O during the preprocessing stage of the adjoint tomography workflow
-quickly cripples the file system. The Adaptable Seismic Data Format
-(ASDF)~\citep[][ \texttt{https://seismic-data.org/}]{krischer2016adaptable}
-was developed with complete reproducibility and fast parallel processing in mind.
-
-In this context, there are four key issues ASDF resolves.
-\begin{itemize}
-    \item Robustness and stability: the data container is developed and maintained to ensure accuracy of scientific results.
-    \item Data organization: the container is self-describing. Data, including waveform, source, and station information, are organized into well-defined structures.
-    \item Reproducibility: the container enables scientists to keep track of which operations have been performed on the data so that results can be reproduced.
-    \item Efficiency: the format provides easy mechanisms for parallel processing.
-\end{itemize}
-
-ASDF serves as a self-contained-and-explained data container while taking
-full advantage of parallel computing. In our workflow,
-one ASDF file contains all the information needed for processing one event,
-including the seismic traces, an event information file (in QuakeML format), and station response files (in StationXML format).
-The related Application Programming Interfaces (API)s are carefully designed for easy data extraction and parallel processing.
+To illustrate which seismic phases end up being assimilated,
+Figs.~\ref{fig:window_density_Z}, \ref{fig:window_density_R}, and \ref{fig:window_density_T} show time-distance plots
+for vertical, radial, and transverse component 17--40~s body waves,
+respectively,
+in which the Pyflex window count is used to identify parts of seismograms being assimilated.
+The figures highlight all the well known body traveltime branches.
+Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are helpful to constrain the compressional wavespeed structure in the model.
+The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
+This is something we will reconsider in future applications by adjusting the FLEXWIN selection parameters, and perhaps also by introducing aspects of machine learning~\citep{chen2017}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
+  \caption{\small{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
+  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
+  The maximum window count is 9,931 in the 85--86$^\circ$ distance and 22~min 55~s--22~min 56~s time bin.
+  Major traveltime branches are labeled.
+Note that the plot contains data from events with a wide variety of depths, so the branches computed for a surface focal depth are for identification purposes only.
+  \towenjie{Relabel PS as PS+SP.}
+  }}
+  \label{fig:window_density_Z}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
+  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
+   A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
+  The maximum window count is 7,542 in the 86--87$^\circ$ distance and 22~min 58~s--22~min 59~s time bin.
+   }}
+  \label{fig:window_density_R}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
+  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
+   A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
+   The maximum window count is 7,208 in the 89--90$^\circ$ distance and 23~min 18~s--23~min 19~s time bin.
+   Only SH travetime branches are labeled.}}
+  \label{fig:window_density_T}
+\end{figure}
 
@@
 
-The misfit function to be minimized during the iterative inversion process must
+The misfit function to be minimized must
 be carefully constructed.
 In this study,
-it typically involves cross-correlation traveltimes
+it involves cross-correlation traveltimes
 for body waves and frequency-dependent multitaper phase measurements for surface waves.
@@
 we track the misfit reduction in each of the categories to ensure that
-the model is improving the fit to the data roughly equally across the board.
+the model is improving the fit to the data roughly equally.
 One of the biggest challenges in the construction of the misfit function is the
-highly uneven distribution of earthquakes --- discussed in Section~\ref{section:earthquakes} --- and seismographic stations,
+highly uneven distribution of earthquakes and seismographic stations,
 which must be counterbalanced by geographically weighting the data.
@@
 \Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{W_{scr}} \omega_{scrw}\, \chi_{scrw}
-\quad ,
-\end{equation}
-where~$S$ denotes the number of sources, $C$ the number of categories,
+\quad .
+\end{equation}
+Here~$S$ denotes the number of sources, $C$ the number of categories,
 $R_{sc}$ the number of receivers recording source~$s$ in category~$c$,
@@
 $\Delta T_{scrw}$\,, weighted by its standard deviation, i.e., $\chi_{scrw}=(\Delta T_{scrw}/\sigma_{scrw})^2$\,.
-As in the source inversions,
-the window weights are equal, $\omega_{scrw}=1$\,,
+The window weights are all equal, $\omega_{scrw}=1$\,,
 and the category weight, $\omega_c$\,, is the reciprocal of the number of measurements in that
@@
 and most seismographic  stations are confined to the continents,
-which leads to a very uneven distribution of sources and stations,
-as illustrated in Figs.~\ref{fig:event_1480} and~\ref{fig:stations}.
+which leads to an uneven distribution of sources and stations,
+as illustrated in Fig.~\ref{fig:eventsstations}.
 Therefore, weighting is crucial in global tomography to balance this uneven sampling
@@
 is developed to compensate for uneven spatial sampling.
-Following the same strategy as for the receiver weights in the source inversions,
-we define source and receiver weights as
+We define source and receiver weights as
 \begin{equation}
@@
 Assuming the radial anisotropy is due to shear anisotropy, these five parameters
-may be further reduced to four by introducing the bulk sound speed,
+may be reduced to the four parameters $c$, $\beta_v$, $\beta_h$, and $\eta$ by introducing the bulk sound speed,
 $c=\sqrt{\kappa/\rho}$\,.
-Therefore, the final four parameters are $c$, $\beta_v$, $\beta_h$, and $\eta$.
 Transverse isotropy is confined to the upper mantle; the lower mantle is assumed to be isotropic.
@@
 which are calculated based on an adjoint-state method~\citep[e.g.,][]{Plessix_2006_RAS,Tromp2005}.
-
-\section{Adjoint tomography workflow}
-\label{section:workflow}
-
-The adjoint tomography workflow is depicted in Fig.~\ref{fig:adjoint_workflow}.
-It starts with the selection of earthquakes, as discussed in Section~\ref{section:earthquakes}.
-Given the earthquake selection,
-observed seismographic data and related response information are acquired,
-as discussed in Section~\ref{section:data}.
-For a given earthquake,
-the corresponding seismograms and related response information are combined in a single ASDF file,
-described in Section~\ref{section:ASDF}.
-For a given earthquake data set, the conversion to ASDF needs to be performed once and for all.
-In the following sections we highlight several important aspects of the workflow.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
-  \caption{\small{Adjoint tomography workflow.}}
-  \label{fig:adjoint_workflow}
-\end{figure}
-
-\subsection{Forward simulations}
-
-The observed seismograms need to be compared to corresponding synthetic seismograms
-for the purpose of making measurements.
-The forward simulations are based on the global spectral-element solver
-SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a}, and take a CMT solution, a relevant list
-of stations, and the current earth model as input.
-The solver is GPU accelerated, and the simulations are performed on the Cray supercomputer ``Titan''
-at the OLCF.
-To simulate 120-min seismograms with a shortest period of 17~s on 384 NVIDIA
-Tesla K20X GPUs takes approximately 10~min of wall clock time.
-
-The calculation of Fr\'echet derivatives requires
-access to snapshots of the forward wavefield as part of the parsimonious storage
-algorithm developed by~\cite{KoXiBoPeSaLiTr16},
-with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
-For the current simulation setup,
-this requires about 1~TB of storage per earthquake,
-so for 1,480 earthquakes this adds up to 1.5~PB.
-This volume of data is generated during~$\sim6$~hours of simulations.
-Based on our experience, ADIOS is capable of achieving~$\sim120$~GB/s
-of sustained I/O on OLCF resources.
-Given that typical write speeds for modern hard disks are~$\sim100$~MB/s,
-it would be extremely difficult to carry out global adjoint tomography without the ADIOS library.
-
-\subsection{Seismic data processing}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
-  \caption{\small{Sub-workflow workflow for preprocessing seismic data.}}
-  \label{fig:preprocess_workflow}
-\end{figure}
-
-The seismic data preprocessing workflow takes raw observed and synthetic data as input,
-and generates adjoint sources for data assimilation as output.
-From a computational perspective, the preprocessing workflow consumes only~1\%
-of the overall computational requirements.
-But from the perspective of the tomographic inversion, this is by far the most
-important stage of the adjoint tomography workflow,
-directly and fundamentally impacting the outcome.
-Any ``bad data'' assimilated at this stage may contaminate the gradient and
-ultimately the final model.
-
-We use millions of seismograms generating tens of millions of measurement windows,
-making data selection through human interaction impossible.
-The preprocessing workflow automates this task,
-most importantly via the time window selection tool FLEXWIN~\citep{maggi2009automated}.
-Every seismogram and potential measurement goes through multiple checks and and
-balances before acceptance or rejection.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
-  \caption{\small{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
-  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-  The maximum window count is 9,931 in the 85--86$^\circ$ distance and 1,375--1,376~sec time bin.
-  Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
-  }}
-  \label{fig:window_density_Z}
-\end{figure}
-
-As illustrated in Fig.~\ref{fig:preprocess_workflow}, the preprocessing workflow
-includes the following phases.
-\begin{enumerate}
-  \item Signal processing to remove the instrument response from observed data
-    to recover ground displacement using ObsPy~\citep{obspy2010}. Both observed and synthetic data are bandpass
-    filtered, and the horizontal components are rotated to obtain the radial and transverse components of motion.
-  \item Window selection on a pair of
-    observed and synthetic seismograms. Pyflex (a Python version
-    of FLEXWIN by \citet{krischer2015}) is
-    used to automatically generate windows where observed and
-    synthetic data are sufficiently close to make measurements based on user defined
-    criteria.
-  \item Cross-correlation traveltime or multi-taper phase measurements in selected windows.
-  \item Window sorting and cleaning based on statistical analyses of all measurements to eliminate outliers.
-  \item Preliminary adjoint source construction based on the sorted windows.
-  \item Calculation and assignment of weights, as discussed in Section~\ref{section:misfit}.
-  \item Construction of the final, properly weighted, adjoint sources.
-\end{enumerate}
-
-To illustrate which seismic phases end up being picked,
-Figs.~\ref{fig:window_density_Z}, \ref{fig:window_density_R}, and \ref{fig:window_density_T} show time-distance plots
-for vertical, radial, and transverse component 17--40~s body waves,
-respectively,
-in which the Pyflex window count is used to identify parts of seismograms being assimilated.
-The figures nicely highlight all the well known body traveltime branches.
-Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are of great importance, because they help constrain the compressional wavespeed structure in the model.
-The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
-This is something we will reconsider in future applications, perhaps by introducing aspects of machine learning.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
-  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
-   A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-  The maximum window count is 7,542 in the 86--87$^\circ$ distance and 1,378--1,379~s time bin.
-   }}
-  \label{fig:window_density_R}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
-  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
-   A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-   The maximum window count is 7,208 in the 89--90$^\circ$ distance and 1,398--1,399~s time bin.
-   Only SH travetime branches are labeled.}}
-  \label{fig:window_density_T}
-\end{figure}
-
-\subsection{Adjoint Simulations}
-
-Collectively,
-the adjoint simulations are the most expensive stage of the workflow. 
-Adjoint simulations take the adjoint sources as input, and generate Fr\'echet
-derivatives of the four model parameters as output.
-The computational cost of one adjoint simulation is roughly twice ($\sim25$~min) that of
-a forward simulation, since the forward wavefield is recalculated for convolution with
-the adjoint wavefield during the adjoint simulation.
-Using this procedure,
-both the forward and adjoint wavefield are calculated in forward time,
-and attenuation is accurately taken into account in both simulations.
-
-\subsection{Postprocessing}
-
-The postprocessing stage of the workflow takes Fr\'echet derivatives as input and
-generates a model update as output.
-It involves the follow steps.
-\begin{enumerate}
-  \item Summation of the individual Fr\'echet derivatives for each earthquake to obtain the overall gradient of the misfit function. The contribution of each source is weighted to balance
-    the uneven distribution of earthquakes based on the weighting strategy discussed in Section~\ref{section:misfit} .
-  \item Smoothing of the raw misfit gradient using a 3D Gaussian, which
-    serves as a regularization procedure. Instead of using a changing
-    smoothing radius based upon the ``ray density''~\citep{bozdaug2016global},
-    we used a fixed value at a given iteration, following~\cite{zhu2012structure}.
-  \item Preconditioning of the smoothed gradient based on a technique proposed by~\cite{luo2013strategies}.
-  \item Line search to determine the magnitude of the model update.
-  The search direction is determined using a nonlinear conjugate gradient method~\citep{wright1999numerical} (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25).
-  We used a subset of 160 earthquakes to conduct the line search and determine the step length.
-\end{enumerate}
-
-\subsection{Workflow management}
-
-There are more than ten stages in the adjoint tomography workflow,
-and each stage involves thousands of small tasks.
-For every model iteration,
-we performed up to 1,480 forward and adjoint simulations, each involving hundreds of
-compute cores and graphics cards, as well as heavy I/O.
-The workflow is prone to human error and hardware failure, making it fragile~~\citep{Lefebvre2018}.
-For these reasons, we hardened the workflow by taking advantage of modern
-workflow management software.
-We selected EnTK as our
-workflow management engine~\citep{EnTK2017}, and developed complementary seismic tomography
-workflow tools.
-The workflow engine can automatically detected job failures both from the
-HPC system and via user-defined functions. This enables us to keep track of
-all tasks and semi-automatically resubmit jobs if necessary.
-Given that most HPC system time is spent waiting in the job queue, automatic
-failure detection and relaunching greatly shortens the overall time to solution.
 
@@
 
-We see an abrupt change in the value of the misfit function at iteration~18
+The value of the misfit function changes abruptly at iteration~18
 in Fig.~\ref{fig:misfit},
-reflecting the addition of 520~events to the inversion database,
+because of the addition of 520~events to the inversion database
 and a change in the weighting strategy for 40--100~s surface waves.
@@
 three key stages of the inversion.
-It is important to note that ``the misfit function'' is, in fact, a
-continually moving target, because at every iteration the number of
-measurements increases as the model improves,
+``The misfit function'' is actually a different function during every iteration,
+because the number of measurements continually increases as the model improves,
 and the number of earthquakes increases at iterations~18 and~22.
@@
 
-In all categories we observe significant misfit reductions,
+We observed misfit reductions in all categories,
 with dispersive 40--100~s surface waves exhibiting the largest improvements.
@@
   \end{tabular}\\
-  \caption{\small{Changes in fit in the twelve measurement categories
+  \caption{\small{Variance reductions in the twelve measurement categories
   between the new model, GLAD-M25, and its starting model, GLAD-M15,
@@
 
-Another way to evaluate model performance is by assessing the distribution
+Another way to evaluate model quality is by assessing the distribution
 of measurements in the various categories.
@@
 and that all standard deviations are steadily reduced.
-Again we note that the inversion is aimed at reducing the overall misfit,
+The inversion is aimed at reducing the overall misfit,
 so there are small tradeoffs between different measurement categories.
@@
   The numbers above the top right of each panel denote the number of measurements in the corresponding category.
-  The total number of measurements is 18.2 million.
+  The total number of measurements is 18.2~million.
   The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}}
   \label{fig:phase_hist}
-\end{figure}
-
-Fig.~\ref{fig:PS_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components, and 17-40~s S-wave traveltime anomalies on the transverse component.
-Both P and S waves exhibit consistent reductions in terms of both mean and variance.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram_phase.pdf}
-  \caption{\small{Histograms of 17--40~s traveltime anomalies of P (vertical and radial), and SH (Transverse) arrivals for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
-  }}
-  \label{fig:PS_phase_hist}
-\end{figure}
-
-Fig.~\ref{fig:amp_hist} shows histograms of the amplitude
-measurements for all twelve measurement categories,
-which were not used in the current inversion.
-Despite this,
-we observe modest reductions in all standard deviations of the histograms.
-The histograms are nicely centered, indicating that the moment magnitudes are
-suitably selected, because the scalar moment affects all measurement categories equally.
-In the next phase of our ongoing inversion we plan to begin assimilating amplitude measurements while simultaneously adding shear attenuation as a new model parameter.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
-  \caption{\small{Same as Fig.~\ref{fig:phase_hist} except for amplitude measurements. These measurements are currently not used in the inversion.}}
-  \label{fig:amp_hist}
 \end{figure}
@@
 
-Checkboard tests or tests involving a chosen known structure, e.g., a plume or slab,
-are frequently used to evaluate resolution in a tomographic inversion.
-Such tests are extremely expensive in FWI and adjoint tomography, because they
+Checker-board tests or tests involving a chosen known structure, e.g., a plume or slab,
+are frequently used to assess the quality of a tomographic inversion,
+despite the fact that such tests have limited relevance~\citep[e.g.,][]{Leveque1993}.
+Such tests are computationally expensive in FWI and adjoint tomography, because they
 require roughly the same computational resources as the actual inversion.
-In lieu of such tests, we previously performed two point-spread function (PSF) analyses
+In lieu of such tests, we previously performed two point-spread function (PSF) analyses~\citep{fichtner2011resolution}
 for model GLAD-M15~\citep{bozdaug2016global}.
-Since GLAD-M25 --- like its predecessor GLAD-M15 --- uses waves with a shortest period of 17~s
-but an earthquake database that is six times larger,
-we can expect improved versions of these already successful PSF tests.
-In the interest of focusing our efforts on obtaining the new model,
-we chose to direct our limited OLCF INCITE allocation towards the actual inversion
-rather than improved PSF tests.
+Here we repeat one of those tests (underneath Yellowstone) to show the improved resolution in GLAD-M25 relative to GLAD-M15,
+and we perform three additional PSF tests: in the lower mantle underneath Afar, in the lower mantle beneath the Galapagos, and below the transition zone in Indonesia.
+
+A PSF test is based on the relationship
+\begin{equation}
+    \mathsf{H}\cdot\mathsf{\Delta}\mathsf{m}\approx\mathsf{g}(\mathsf{m}+\mathsf{\Delta}\mathsf{m})-\mathsf{g}(\mathsf{m})
+    \quad .
+\end{equation}
+This expression states that the action of the Hessian~$\mathsf{H}$ on a model perturbation~$\mathsf{\Delta}\mathsf{m}$ maybe calculated by taking the difference between the misfit gradient at model~$\mathsf{m}+\mathsf{\Delta}\mathsf{m}$ and the misfit gradient at model~$\mathsf{m}$\,.
+Thus, such a test has a computational cost that is equivalent to one iteration, because it only requires the calculation of the gradient~$\mathsf{g}(\mathsf{m}+\mathsf{\Delta}\mathsf{m})$\,.
+At a minimum of the misfit function,
+perturbations in displacement~$\Delta\mathbf{s}$ are proportional to model parameter perturbations~$\mathsf{\Delta}\mathsf{m}$\,, that is~$\Delta\mathbf{s}\sim\mathsf{\Delta}\mathsf{m}$\,.
+Consequently, if we perturb model parameter~$k$ at location~$\mathbf{x}$\,,
+$\Delta m_k(\mathbf{x})$\,,
+we expect that the only nonzero element of the Hessian matrix is~$H_{kk}(\mathbf{x})$, and that~$\mathsf{H}\cdot\mathsf{\Delta}\mathsf{m}\sim\Delta m_k(\mathbf{x})$\,.
+Thus a PSF test illustrates the degree of blurring or smearing of the induced model perturbation~$\Delta m_k(\mathbf{x})$ and identifies tradeoffs with other model parameters.
+
+Figure~\ref{fig:??} shows the results of the four PSF tests we performed for model GLAD-M25.
+The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
+That test was based on 253 earthquakes,
+and Figures~\ref{fig:??}a and~\ref{fig:??}b show our results for the same location based on half our dataset (720 events) and the full dataset (1,480 events), respectively.
+Figure~\ref{fig:??} shows the results of a PSF test in the lowermost mantle at the base of the African superplume,
+in the lower mantle beneath the Galapagos,
+and in the mid mantle below Indonesia.
 
@@
 Theses events were not used in the structural inversion.
-(a) Distribution of events color coded by depth range as in Fig.~\ref{fig:event_1480}.
+(a) Distribution of events color coded by depth range as in Fig.~\ref{fig:eventsstations}(a).
 (b) \& (c) Histograms of moment magnitude and depth.}}
@@
 as well a S362ANI combined with CRUST2.0.
-It is a validation of our approach to see that the reductions are comparable to the
+It is encouraging to see that the reductions are comparable to the
 values tabulated in Table~\ref{table:misfit_reduction_M15_M25} for the actual inversion.
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram_360_phase.pdf}
-  \caption{\small{Same as Fig.~\ref{fig:PS_phase_hist}, except for the held-out database.}}
-  \label{fig:phase_hist_360_P}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=\textwidth]{figures/dt_histogram_360_phase.pdf}
+%   \caption{\small{Same as Fig.~\ref{fig:PS_phase_hist}, except for the held-out database.}}
+%   \label{fig:phase_hist_360_P}
+% \end{figure}
 
@@
 
-Finally,
-direct P and S traveltime anomaly measurements were extracted and compared for three models in Fig.~\ref{fig:phase_hist_360_P}.
-Again the histograms are consistent with the actual inversion,
-as expected.
+% Finally,
+% direct P and S traveltime anomaly measurements were extracted and compared for three models in Fig.~\ref{fig:phase_hist_360_P}.
+% Again the histograms are consistent with the actual inversion,
+% as expected.
 
@@
 
-In this section we discuss model GLAD-M25 in some detail.
-We begin with a global overview of the model, before concentrating on
-specific geographical regions.
-We conclude by highlighting various slabs and plumes.
+In this section we compare model GLAD-M25 with GLAD-M15,
+global shear wavespeed models 
+TX2015~\citep{TX2015} and SEMUCB-WM1~\citep{french2015broad},
+and compressional wavespeed models GAP-P4~\citep{fukao2013subducted} and UU-P07~\citep{van2018atlas}.
 The focus is on isotropic shear and compressional wavespeed variations.
-We provide comparisons with numerous other global and regional tomographic models,
-but we refrain from detailed tectonic/geodynamic interpretations,
+We refrain from detailed tectonic/geodynamic interpretations,
 which will be the subject of more targeted future investigations.
@@
 
-\subsection{Global structure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
-  \caption{\small{Map views of global shear wavespeed perturbations at various depths for  model
-  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic},
-  and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
-  At a given radius,
-  perturbations are calculated relative to each model's average.
-  The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
-  The green circles denote locations of various
-  hotspots~\citep{montelli2006catalogue}.
-  The range of the colorbar is the same for each row,
-  and its maximum value is indicated in parentheses on the left, after
-  the depth.}}
-  \label{fig:global-vs}
-\end{figure}
-
-We first examine model GLAD-M25 in the context of existing global tomographic models.
-In Fig.~\ref{fig:global-vs} we compare global maps of the isotropic part of our
-shear wavespeed model with model S362ANI$+$M~\citep{moulik2014anisotropic},
-which is an updated version of the starting model for the GLAD-M15 inversion,
-and model S40RTS~\citep{ritsema2011s40rts}.
-Overall, these models are in good agreement
-at the longest wavelengths, especially GLAD-M25 and S362ANI$+$M.
-The perturbations in GLAD-M25 tend to be larger than in the other models,
-consistent with observations by~\cite{french2014whole},
-whose model is also based on a form of waveform inversion.
-
-%\begin{figure}
-%\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
-%  \caption{\small{Map views of global $V_\textrm{P}$ variations at various depths for our model GLAD-M25(left column), S362ANI$+$M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}.
-For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing.
-Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}}
-%\label{fig:global-vp}
-%\centering
-%\end{figure
-
-An important aspect of our inversion is that it constrains shear and
-compressional waves simultaneously. In Fig.~\ref{fig:global-vs} we
-compare global maps of our compressional wavespeed model with global P models
-LLNL-G3Dv3~\citep{simmons2012llnl} and GAP-P4~\citep{fukao2013subducted}.
-At a depth of 100~km,
-GLAD-M25 shows prominent mid-oceanic ridges, cooling of the Pacific lithosphere,
-and the roots of numerous continental cratons. In the upper mantle, LLNL-G3Dv3
-exhibits the largest lateral variations,
-e.g., very slow compressional wavespeeds at 500~km depth below Hawaii, Samoa, and Tahiti.
-In the midmantle we can see remnants of subduction beneath South America, Indonesia,
-and Tonga-Kermadec.
-In the deep mantle, LLNL-G3Dv3 and GAP-P4 begin to fade out, but the long-wavelength patterns,
-in particular the lowerparts of the Africa and Pacific superplumes, are very similar.
-
-\begin{figure}
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
-  \caption{\small{Map views of global compressional wavespeed variations at various depths for model
-  GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl}, and
-  GAP-P4~\citep[right column;][]{fukao2013subducted}.
-  For LLNL-G3Dv3, depth ranges are labeled in the bottom right
-  bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}}
-\label{fig:global-vp}
-\centering
-\end{figure}
-
-\subsubsection{North America}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
-  \caption{\small{Map views of isotropic shear wavespeed variations beneath North America 
-  for model GLAD-M25 (first column) and several global (S362ANI$+$M and S40RTS)
-  and regional~\citep[US22;][]{zhu2017radial} and~\citep[SL2013NA;][]{schaeffer2014imaging}
-  models. Green circles denote the locations of hotspots. For SL2013NA, we
-  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}}
-\label{fig:america-vs}
-\end{figure}
-
-The deployment of USArray has dramatically increased data coverage across the
-continental United States,
-and yet despite this tremendous increase in data coverage, there is not as much overlap between different models as one might anticipate.
-In this section, we compare GLAD-M25 in this region 
-with two global models, S362ANI$+$M and S40RTS, and two regional models,
-US22~\citep{zhu2017radial} and SL2013NA~\citep{schaeffer2014imaging}.
-US22 is a radially anisotropic model based on adjoint tomography using
-USArray data from 180 regional earthquakes using 15--50~s
-body waves and 25--150~s surface waves.
-SL2013NA is a global upper-mantle shear wavespeed model based on multimode
-surface waveform tomography primarily focused on North America.
-
-North America is characterized by a large, high-wavespeed lithospheric craton,
-bounded by the Rocky Mountain Front to the West and continental
-margin to the East~\citep{grand1984upper, whitmeyer2007tectonic}.
-On both sides the lithosphere has been deformed by
-low wavespeed structures, thus forming sharp tectonic boundaries
-~\citep{masters1996shear, grand1997high, megnin2000three, gu2001models}.
-
-At a depth of 100~km, we observe that the edges of the craton are sharper in
-GLAD-M25 than in the other two global models,
-and quite similar in shape and sharpness to the two regional models.
-We can clearly see impressions of the Snake River Plain (with Yellowstone)
-and the Raton hotspot, which also have distinct slow expressions at depths of 200~km.
-The core of the craton exhibits fast wavespeeds at depths reaching 300~km Northwest of
-Hudson Bay.
-In the regional models the craton has basically faded away at these depths.
-The Wyoming and Medicine Hat Blocks show a very strong and thick lithospheric
-root from shallow depths to $\sim$400~km, similar to US22 but
-difficult to discern in SL2013NA.
-Similar observations can be made for the Yavapai and
-Mazatzal Blocks, which define the southern boundary of the large craton
-~\citep{schaeffer2014imaging}.
-
-In the 200--400~km depth range, we observe a high wavespeed
-anomaly within the Gulf of Mexico, which coincides spatially with the deepest
-bathymetry and corresponds to a portion of ancient oceanic
-lithosphere~\citep{muller2008, schaeffer2014imaging}.
-A remnant of the Juan de Fuca plate,
-with a high wavespeed footprint, is visible at depths of 300~km and 400~km,
-where SL2013NA shows a much stronger anomaly.
-
-In the North, we see a high wavespeed craton beneath Greenland which is partly
-separated from the North American craton by low wavespeed structures beneath
-Baffin Bay and the Labrador Sea, where the North American craton nicely follows
-the coastline~\citep{chalmers2001development}.
-In the Northeast corner of the maps we see that the Iceland hotspot is very
-prominent in GLAD-M25 in all depth ranges, similar to S40RTS but largely missing
-in S362ANI$+$M. In the Northwest we see a clear imprint of the Aleutian
-subduction zone in the 200--400~km depth range, comparable to SL2013NA but absent
-in the other global models.
-
-In the East, at 100~km depth,
-we see ageing of the Atlantic lithosphere, comparable to the other global models
-~\citep{muller2008, schaeffer2014imaging}.
-All models show fast anomalies beneath Newfoundland and Nova Scotia extending to
-depths of 300~km. The Bermuda hotspot shows a very nice slow wavespeed impression,
-getting sharper and stronger at depths of 200~km and 300~km (note differences in
-the scales of the maps).
-The Caribbean slab, a relatively young subduction zone, is clearly
-visible in our model in the 200--400~km depth range.
-At greater depths,
-GLAD-M25 shows a very distinct image of the Farallon slab,
-but since it goes well beyond the depth range of this comparison,
-we return to this feature in Section~\ref{section:slabs}.
-
-\subsubsection{Europe}
-
-\begin{figure}[ht!]
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
-  \caption{\small{Map views of isotropic shear wavespeed variations beneath Europe for model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
-  one regional model~\citep[EU60;][]{zhu2015seismic}. For EU60, the range of the color
-  bar is 4\% at all depths, as indicated in the bottom right bottom of the panels.}}
-\label{fig:europe-vs}
-\centering
-\end{figure}
-
-Fig.~\ref{fig:europe-vs} shows isotropic shear wavespeed perturbations beneath Europe.
-In addition to models GLAD-M25, S362ANI$+$M, and S40RTS, we included regional
-model EU60~\citep{zhu2015seismic} for comparison.
-EU60 is the result of adjoint tomography of the crust and upper mantle
-beneath the European continent and the North Atlantic based on the assimilation of data from
-190 earthquakes recorded by 745 seismographic stations.
-
-A defining tectonic feature of Europe is the Trans-European Suture Zone~(TESZ),
-also known as the Tornquist-Teisseyre Zone,
-separating the Precambrian East European Craton~(EEC) in the Northeast from
-Phanerozoic Europe in the Southwest~\citep{zielhuis1994deep}.
-The TESZ is very consistent across all models,
-even though is much sharper in GLAD-M25 and EU60.
-
-At depths of 100---250~km we observe high wavespeeds beneath the Central Graben
-in the North Sea, which is clearly separated from the EEC.
-The tectonic history of the Mediterranean is complex,
-involving several regional plates and multiple past and present subduction zones
-~\citep{dewey1989kinematics}.
-We see slab ponding in the transition zone beneath the western Mediterranean
-associated with slab roll-back of the Appennines-Maghrebides subduction zone
-~\citep{wortel2000subduction, zhu2012structure}.
-At shallower depths, we see low wavespeeds along its western border,
-which are interpreted as back-arc extension associated with  roll-back.
-Compared to S362ANI$+$M and S40RTS,
-our model shows much sharper features for these tectonic structures.
-
-In the Eastern Mediterranean, there is a distinct fast anomaly beneath the 
-Dinarides Mountains, separating the Adria plate from the Pannonian Basin,
-indicating subduction of the Adria plate beneath the Eurasian plate.
-This anomaly gets sharper at 600~km depth.
-Its southern part interacts with the Hellenic slab, which penetrates the mantle
-transition zone and extends below 1,000~km in our model.
-We discuss the Hellenic Arc further in Section~\ref{section:slabs}.
-The Pannonian Basin is characterized by a low wavespeed
-anomaly at depths from 100~km to 250~km.
-In this depth range we also see slow wavespeeds beneath Anatolia,
-stronger than in the two other global models.
-
-In Central Europe we note the Cenozoic Ridge System~\citep{ziegler1992european},
-characterized by low 
-wavespeeds from the Massif Central to the Eifel. Both EU60 and
-GLAD-M25 exhibit a slow anomaly beneath the northern part of the Rhine Graben,
-which is interpreted as the reservoir that fuels the Eifel hotspot
-~\citep{goes1999lower, zhu2015seismic}.
-
-Beneath the Atlantic Ocean, our model enhances slow anomalies beneath the
-ridges, especially underneath Iceland and the Azores.
-Compared to S362ANI$+$M, Iceland becomes much stronger in the upper mantle at
-depths from 250~km to 400~km, extending all the way to the mantle-transition zone.
-The Azores represent a much shallower hotspot, with a maximum depth of about 250~km.
-
-\subsubsection{Asia}
-
-\begin{figure}[ht!]
-  \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
-  \caption{\small{Map views of shear wavespeed variations beneath Asia for GLAD-M25~(first column),
-  global models S362ANI$+$M (second column) and SL2013sv (third column), and regional model EARA2014~\citep[last column;][]{chen2015multiparameter}.}}
-  \label{fig:asia-vs}
-  \centering
-\end{figure}
-
-Asia, like Europe, has a complex tectonic history, involving
-interactions among the Indian, Eurasian, Australian, Pacific, and Philippine
-plates.
-Map views of GLAD-M25 centered on Asia are plotted in Fig.~\ref{fig:asia-vs},
-together with S362ANI$+$M, SL2013sv~\citep{SchaefferLebedev13}, and regional model EARA2014~\citep{chen2015multiparameter}.
-EARA2014 is a transversely isotropic model based on adjoint
-tomography, assimilating 1.7~million frequency-dependent traveltime
-measurements from 227 earthquakes recorded by 1,869 seismographic  stations.
-It has superior data coverage, mainly by incorporating data from the China Array.
-
-The Southwestern part of China is dominated by the Himalayas,
-expressing the collision between India and Eurasia~\citep{lebedev2003upper}.
-GLAD-M25 exhibits strong high wavespeed anomalies in this area,
-which extend all the way from 100~km to 600~km, narrowing and sharpening with depth,
-in good agreement with EARA2014.
-The Tibetan plateau shows relatively low wavespeeds
-compared to its surroundings, including the Himalayas to its South and
-the Tianshan Mountains to its North, consistent with the other global
-and regional studies.
-
-The southern part of Asia shows major tectonic activity between the
-Philippine, Eurasian, and Australia plates.
-The Sunda trench is visible as a distinct high wavespeed anomaly below 200~km,
-nicely following the plate boundary.
-This feature remains very sharp at 600~km and extends
-down to 1000~km.
-We discuss this subducting slab further in Section~\ref{section:slabs}.
-The Manila and Philippine trenches are also much sharper in our model between 200~km and
-600~km than in the other global models, and comparable to EARA2014.
-The eastern edge of the map features a series of trenches following plate boundaries,
-including Japan, Izu-Bonin, and Mariana.
-These slabs are absent in the other global model,
-but feature more prominently in EARA2014.
-Along the northern edge we see low wavespeeds associated with the
-Altai-Sayan and Baikal rift systems.
-In terms of intra-plate activities,
-at shallow depths we see clear low wavespeed impressions of the Hainan and Changbai volcanoes,
-suggesting a lithospheric rather than deeper mantle origin~\citep{yin2000geologic}.
-The Sichuan basin, a very localized high-wavespeed structure, extends below
-250~km depth. At 600~km, most models shows a large region of high wavespeed
-beneath the Philippine plate, indicating ponding of ancient subducted plates.
-
-\subsubsection{South America}
-
-\begin{figure}[ht!] 
-  \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
-  \caption{\small{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).}}
-  \label{fig:southamerica-vp}
-  \centering
-\end{figure}
-
-Fig.~\ref{fig:southamerica-vp} shows compressional wavespeed anomalies in model GLAD-M25 in comparison with three
-global models, namely, S362ANI$+$M~\citep{moulik2014anisotropic}, LLNL-G3Dv3~\citep{simmons2012llnl}, and GAP-P4~\citep{fukao2013subducted};
-the latter two are $V_\textrm{P}$ models.
-
-At 150~km depth, the northern half of South America is covered by a large lithospheric craton, exhibiting fast anomalies in all models except GAP-P4.
-The Galapagos,
-San Felix, and Juan Fernandez hotspots are associated with distinct low wavespeed anomalies in GLAD-M25,
-but not in the other models.
-At 300~km depth, we see sharpened subduction of the Nazca plate
-in GLAD-M25 compared to S362ANI+M, similar in shape to model LLNL-G3Dv3.
-Moving to greater depths,
-we see distinct Peru and Chile slabs in GLAD-M25,
-with the Chile slab ponding in the transition zone
-and the Peru slab penetrating into the lower mantle and still clearly visible at 1000km depth.
-These differences in behavior are consistent with GAP-P4
-\citep{fukao2013subducted}.
-
-In the south,
-Scotia Arc subduction is very distinct in GLAD-M25 at all depths,
-but barely observable in other models.
-This is probably a consequence of coverage provided by events in the region (see Fig.~\ref{fig:event_1480}).
-To the north,
-Caribbean subduction is clearly discernible in model GLAD-M25 and the two $V_\textrm{P}$ models.
+\subsection{Comparisons with GLAD-M15}
+
+Relative to our first generation model GLAD-M15,
+we observe a significant increase in model perturbation amplitudes and resolution,
+both in the upper and lower mantle.
+To illustrate this point,
+Fig.~\ref{fig:power} and Fig.~\ref{fig:powerspectraradius} show normalized power per angular degree (Eqn.~\ref{eq:powerdegree}) and normalized power per angular degree as a function of radius (Eqn.~\ref{eq:powerdegreeradius}), respectively, for models S362ANI, GLAD-M15, and GLAD-M25.
+Model S362ANI has no power beyond degree~18,
+and we see and increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{figures/power.pdf}
+  \caption{\small{Normalized power per degree~$\ell$ based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), GLAD-M15 (green), and GLAD-M25 (blue).
+  Model S362ANI has no power in degrees greater than~18.
+  Included are depths greater than 120~km.
+  (Courtesy of Caio Ciardelli.)
+  }}
+  \label{fig:power}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.95\textwidth]{figures/power_radius.pdf}
+  \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (left), GLAD-M15 (middle), and GLAD-M25 (right).
+  Shown are depths greater than 120~km.
+  (Courtesy of Caio Ciardelli.)
+  }}
+  \label{fig:powerspectraradius}
+\end{figure}
+
+As illustrated in Fig.~\ref{fig:M25-AFAR},
+we see an enhancement of the Afar plume relative to GLAD-M15.
+The 3D morphology of the African superplume shows a mantle plume rising from the core-mantle boundary with a broad base tilting northward with a thinning neck, before it reaches the 660~km phase boundary and flattens.
+It then develops into two sub-plumes ---Afar and East Lake Victoria--- supplying the East Africa rift.
+The development of the superplume and its 3D morphology might be associated with water in the mantle transition zone, a possibility we will explore in a future study.
+
+Subduction along the Andes in South America is imaged from south to north all the way down to the transition zone and beyond, as shown in Fig.~\ref{fig:S_America}.
+In the contour plot of positive shear-wavespeed perturbations we observe three gaps, which may correspond to ridges or volcanic plateaus on the subducted Nazca plate, and indicate a weakened or even torn slab.
+
+Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda.
+
+\begin{figure}
+  \centering
+%  \includegraphics[width=0.9\textwidth]{./figures/M24-AFAR.png}
+  \includegraphics[width=0.45\textwidth]{./figures/afar_M15_dInVsv.png}
+  \includegraphics[width=0.45\textwidth]{./figures/afar_M25_dInVsv.png} \\
+  \includegraphics[width=0.45\textwidth]{./figures/afar_M25_dVp_Vs_ratio.png}
+  \includegraphics[width=0.45\textwidth]{./figures/afar_M25_dVsh_Vsv_ratio.png}
+  \caption{\small{Vertical cross-section of vertically polarized shear-wave-speed $(V_\textrm{SV})$ perturbations ($\pm3$\%) in GLAD-M15 (top left) and GLAD-M25 (top right) underneath Afar.
+Also shown are $V_\textrm{P}/V_\textrm{S}$ ratios (bottom left) and transverse isotropy (bottom right; $V_\textrm{SH}/V_\textrm{SV}$ ratio) in GLAD-M25 at the same location.
+In GLAD-M25, the plume becomes larger and more visible, especially in the upper mantle.
+It also shows how the plume changes its shape when crossing the 660~km discontinuity and ``feeds'' the Afar hotspot at the surface.}}
+  \label{fig:M25-AFAR}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.8\textwidth]{figures/south_america.pdf}
+\caption{\small{Contour plot (left) and cross-sections at various depths (right) of subduction underneath South America, showing improvements in resolution in GLAD-M25 compared to GLAD-M15.
+The contour plot shows positive perturbations of vertically polarized shear wavespeeds in GLAD-M25. The ball in the contour plot denotes the 660~km discontinuity.}}
+\label{fig:S_America}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{./figures/M24-Iceland.png}
+  \caption{\small{Map views of vertically polarized shear-wave-speed perturbations in GLAD-M15 (top left) and GLAD-M24 (top right) underneath Iceland.
+Also shown are vertical cross-sections(bottom row) at the same location.
+As a primary hotspot, Iceland also becomes much more prominent in GLAD-M24, especially in the upper mantle.
+\towenjie{Please update.}
+  }}
+  \label{fig:M24-Iceland}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{./figures/M24-Reunion.png}
+  \caption{\small{Map views at 250~km depth of vertically polarized shear-wave-speed perturbations in GLAD-M15 (left) and GLAD-M24 (right) at Indian Ocean.
+New features are emerging in GLAD-M24, as the hotspot at Reunion, Marion, Kerguelen, and Crozet just came out in GLAD-M24.
+\towenjie{Please update.} }}
+  \label{fig:M24-Reunion}
+\end{figure}
 
@@
 
-\begin{figure}[ht!]
+\begin{figure}
     \centering
@@
 In this section we highlight various plume systems on Earth. Fig.~\ref{fig:plumes}
-shows cross sections of several plumes, comparing models GLAD-M25 ($V_\textrm{P}$),
+shows cross sections of several plumes, comparing models GLAD-M25 ($V_\textrm{S}$),
 TX2015~\citep[$V_\textrm{S}$;][]{TX2015}, and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad}.
-All three models have common plume features,
-and GLAD-M25 and TX2015 are in overall good agreement.
-
 The three models tend to agree near the CMB,
-and there is overall good agreement between GLAD-M25 and TX2015,
-but the models can differ substantially in the mid and upper mantle,
-with profoundly different implications for mantle
+and there is overall good agreement between GLAD-M25 and TX2015.
+The models can differ substantially in the mid and upper mantle,
+with different implications for mantle
 convection.
@@
 Figs.~\ref{fig:subd}(c) and~(d) show cuts across the ancient Farallon slab, which penetrates deeply into the lower mantle,
-as spectacularly documented by, for instance, \citet{grand1994,hilst1997,grand1997high}.
+as documented by, for instance, \citet{grand1994}, \cite{hilst1997}, and \cite{grand1997high}.
 At depths greater than 1,000~km, 
@@
 Finally, Fig.~\ref{fig:subd}(f) shows subduction beneath the Java portion of the Sunda Arc.
-At this location the slab pernetrates into the lower mantle, at which point its spreads out laterally,
+At this location the slab penetrates into the lower mantle, at which point its spreads out laterally,
 in agreement with models GAP-P4 and UU-P07.
@@
 But in the upper and mid mantle,
-the models share very similar attributes.
+the models share similar attributes.
 
@@
 
-Seismology is a science driven by data.
-There was a time when global seismologists would meticulously inspect single seismograms to glean valuable information from them.
-Today, we have easy access to data from thousands of earthquakes recorded by tens of thousands of seismographic stations, and individual inspection of all of these records has become impossible.
-Still, it would be a shame not to utilize as much as possible of the information in this massive seismographic database.
-
-To facilitate fast and effective access to such vast data resources,
-we use ASDF~\citep{krischer2016adaptable} in the preprocessing stage of the adjoint tomography workflow,
-and to accommodate massive I/O during the postprocessing stage we use the ADIOS library~\citep{liu2014hello}.
+As illustrated in Figs.~\ref{fig:window_density_Z}, \ref{fig:window_density_R}, and~\ref{fig:window_density_T},
+the goal of our inversion is to assimilate as much seismic waveform information as possible.
+To facilitate fast and effective assimilation of such data,
+we use the Adaptable Seismic Data Format~\citep{krischer2016adaptable} in the preprocessing stage of the adjoint tomography workflow,
+and to accommodate I/O during the postprocessing stage we use the ADIOS library~\citep{liu2014hello}.
 For data assimilation,
-tools such as FLEXWIN, which automatically select data windows suitable for measurements, are indispensable, and we see tremendous opportunities for the use of machine learning algorithms in this context~\citep[e.g.,][]{chen2017}.
+tools such as FLEXWIN, which automatically select data windows suitable for measurements, are indispensable, and we see opportunities for the use of machine learning algorithms in this context~\citep[e.g.,][]{chen2017}.
 Without these libraries and tools, the construction of model GLAD-M25 would have been impossible.
@@
 because classical inversion workflows suffer from I/O inefficiencies, lack of fault tolerance, and an inability to work in distributed resource environments~\citep{Lefebvre2018}.
-The EnTK workflow management engine~\citep{EnTK2017}
-largely overcomes these limitations by facilitating tracking of tasks and job failure detection,
-thereby enabling semi-automatic job resubmission if necessary.
+For these reasons, we are in the process of adopting the Ensemble Tool Kit (EnTK) as our
+workflow management engine~\citep{EnTK2017}.
+This workflow engine can automatically detected job failures,
+both from the high-performance computing (HPC) system and via user-defined functions.
+This facilitates tracking of tasks and semi-automatic job resubmission if necessary.
 These are the attributes required for bringing global FWI to its full potential,
@@
 It should be clear from this discussion that modern seismic tomography requires close collaborations with computational scientists, HPC specialists, and visualization experts,
-as reflected in the list of authors for this article, in addition to access to the most advanced computational platforms,
+as reflected in the list of authors for this article, in addition to access to advanced computational platforms,
 such as those offered through the DOE INCITE and NSF XSEDE programs.
@@
 Although Figs.~\ref{fig:window_density_Z}--\ref{fig:window_density_T} illustrate that much information in seismograms is
-being assimilated, we still have a long way to go before explaining every wiggle in hundreds-of-minutes-long seismograms.
+being assimilated, we still have a long way to go before explaining every broadband wiggle in hundreds-of-minutes-long seismograms.
 Currently, we are only fitting the phase in selected time windows, and amplitude information remains completely unused.
@@
 Thus, the natural next step in global FWI is to use phase and amplitude information simultaneously to jointly constrain the elastic and anelastic structure of the Earth.
-To accomplish this next step, source parameters need to be constrained more carefully, especially as we push the resolution to shorter periods~\citep[e.g.,][]{valentine2010}.
-
-The global distribution of earthquakes (Fig.~\ref{fig:event_1480}) and stations (Fig.~\ref{fig:stations}) is highly uneven.
-This problem may be alleviated to some extent by using suitably chosen misfit functions with appropriate geographical weighting of sources and receivers~\citep[e.g,,][]{Li1996,Ruanetal2018}.
+To accomplish this next step, source parameters need to be constrained more precisely, especially as we push the resolution to shorter periods~\citep[e.g.,][]{valentine2010}.
+
+The global distribution of earthquakes and stations is highly uneven (Fig.~\ref{fig:eventsstations}).
+This problem may be alleviated to some extent by using suitably chosen misfit functions with appropriate geographical weighting of sources and receivers~\citep[e.g.,][]{Li1996,Ruanetal2018}.
 The ultimate solution may be a dense network of Ocean Bottom Seismometers,
@@
 
-Another very important attribute of GLAD-M25 is that it constrains shear and compressional wavespeeds simultaneously in the same period range,
+Another attribute of GLAD-M25 is that it constrains shear and compressional wavespeeds simultaneously in the same period range,
 thereby enabling us to interpret the two wavespeeds together.
@@
 GLAD-M25 was quantitatively evaluated in several ways.
-First, it produces significant misfit
-reductions in all twelve measurements categories.
+First, it produces 14.4--33.6\% (relative to GLAD-M15) and 37.3--77.2\% (relative to S362ANI combine with CRUST2.0) variance
+reductions in twelve measurements categories.
 Second,
-it produces nicely-centered Gaussian traveltime \& amplitude anomaly histograms
+it produces reasonably well centered Gaussian traveltime anomaly histograms
 in all measurement categories.
+Third, point-spread function tests show minimal tradeoffs between model parameters and reasonably good resolution in the frequency band of interest.
 Finally,
 for a held-out data set of 360 events
-we see similar misfit reductions and traveltime \& amplitude anomaly histograms as in the actual inversion.
+we see similar misfit reductions and traveltime anomaly histograms as in the actual inversion.
 
@@
 we find overall good agreement at longer wavelengths.
-In particular, GLAD-M25 and TX2015 feature very similar plume structures.
-Unlike other global models, when we compare GLAD-M25 with regional models
-we also observe generally good agreement at smaller wavelengths,
-and, in particular, plumes and subduction zones feature prominently.
-However, it is important to note that GLAD-M25 tends to agree well with regional models based on the same S362ANI~$+$~Crust2.0 starting model, numerical wave propagation solver, and quasi-Newton inversion technique (e.g., EU60, US22, and EARA2014).
-It is also important to point out that even in regions with dense seismographic coverage, such as North America,
+In particular, GLAD-M25 and TX2015 feature similar plume structures.
+However, even in regions with dense seismographic coverage, such as North America,
 recent models can differ substantially, especially at greater depths.
@@
 approaching regional-scale resolution is areas with sufficient data coverage.
-We can observe this increase in resolution in GLAD-M25 in the normalized power per spherical harmonic degree as a function of radius, which is displayed in Fig.~\ref{fig:powerspectraradius}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.95\textwidth]{figures/power_radius.pdf}
-  \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (left), GLAD-M15 (middle), and GLAD-M25 (right).
-  Shown are depths greater than 120~km.
-  (Courtesy of Caio Ciardelli.)
-  }}
-  \label{fig:powerspectraradius}
-\end{figure}
+We can observe this increase in resolution in GLAD-M25 in the normalized power per spherical harmonic degree as a function of radius (Fig.~\ref{fig:powerspectraradius}).
 
@@
 Obvious future directions of research include growing the earthquake database further to the roughly 6,000 earthquakes in the right magnitude range already available via the Global CMT database,
-and reducing the shortest simulation period further from 17~s to 8.5~s.
-The most recent machine at OLCF, called ``Summit'', uses IBM Power9 CPUs accelerated by NVIDIA Tesla V100 GPU and can readily accommodate such simulations.
+and reducing the shortest simulation period further from 17~s to 9~s.
 
@@
 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
-
+\bibliographystyle{gji}
+\bibliography{ref.bib}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
 \appendix
@@
 where~$r$ denotes the radius and~$\Omega$ the unit sphere.
-
 Using 2D GLL quadrature~\citep{KoTr99} in the unit sphere,
@@
   \caption{\small{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
-  The reference frequency for physical dispersion is ~7.77~mHz.}}
+  The reference frequency for physical dispersion is~1~Hz.}}
   \label{fig:global-average}
@@
   \includegraphics[width=0.9\textwidth]{figures/1d_profile_ra.pdf}
-  \caption{\small{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is ~7.77~mHz.}}
+  \caption{\small{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is~1~mHz.}}
   \label{fig:global-ra-average}
@@
 
+\newpage
 \section{Spherical harmonic model expansion}
@@
 
-\bibliographystyle{gji}
-\bibliography{ref.bib}
-
 \end{document}

### 2020-02-07 original_main.tex
Updates from Overleaf

--- 2019-02-21 main.tex
@@
 facilitated by a parsimonious storage algorithm.
-The simulations were performed on the Cray XK7 ``Titan'' at the Oak Ridge Leadership Computing Facility.
+The simulations were performed on the Cray XK7 ``Titan'' and the IBM ``Summit'' at the Oak Ridge Leadership Computing Facility.
 We quantitatively evaluated GLAD-M25 by assessing misfit reductions and traveltime \& amplitude anomaly histograms in twelve measurement
@@
 with results comparable to the actual inversion.
-We compare GLAD-M25 with numerous other global and regional models,
+We compare GLAD-M25 with several other global and regional models,
 and highlight a variety of plumes and subduction zones.
@@
 However, discrepancies between models become noticeable as resolution increases.
-Using accurate 3D simulations of seismic wave propagation and the computation of data sensitivities in 3D background models are key requirements for improving resolution in tomographic images on all scales.
+Using accurate 3D simulations of seismic wave propagation and the computation of data sensitivities in 3D background models are key requirements for improving resolution in tomographic images on all scales~\citep{Tromp2020}.
 Such detailed images are essential for understanding mantle dynamics and related surface tectonic processes
@@
 in this study we use a GPU-accelerated version of the 3D spectral-element solver
-SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the Cray supercomputer ``Titan'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
+SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the Cray supercomputer ``Titan'' and the IBM ``Summitt'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
 These simulations accommodate the full 3D complexity of global Earth models,
@@
 generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
-How to deal with hardware failures during this process is critical
+Accommodating inevitable hardware failures during this process is critical
 to prevent contamination of the inversion results.
@@
 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
-
+\bibliographystyle{gji}
+\bibliography{ref.bib}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \appendix
@@
   \caption{\small{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
-  The reference frequency for physical dispersion is ~7.77~mHz.}}
+  The reference frequency for physical dispersion is 1~Hz.}}
   \label{fig:global-average}
@@
   \includegraphics[width=0.9\textwidth]{figures/1d_profile_ra.pdf}
-  \caption{\small{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is ~7.77~mHz.}}
+  \caption{\small{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is 1~Hz.}}
   \label{fig:global-ra-average}

### 2020-02-07 supplementary_material.tex
Updates from Overleaf

--- 2019-02-21 main.tex
@@
 
-\title[Global Adjoint Tomography -- Model GLAD-M25]
-  {Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}}
+\title[Global Adjoint Tomography -- Model GLAD-M25 (Supplementary Material)]
+  {Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material}
 
@@
 \begin{summary}
-Building on our first-generation global adjoint tomography model,
-GLAD-M15~\citep{bozdaug2016global}, we present our second-generation transversely isotropic global model,
-named GLAD-M25, which is the result of ten quasi-Newton tomographic iterations with an
-earthquake database consisting of 1,480 events in the magnitude range $5.5\le M_w \le 7.2$,
-an almost six-fold increase over the first-generation model.
-We calculated fully 3D synthetic seismograms with a shortest period of 17~s based on a GPU-accelerated spectral-element wave
-propagation solver which accommodates effects due to 3-D anelastic crust \& mantle structure, topography \& bathymetry, the ocean load, ellipticity, rotation, and self-gravitation.
-We used an adjoint-state method to calculate Fr\'echet derivatives in 3D anelastic Earth models
-facilitated by a parsimonious storage algorithm.
-The simulations were performed on the Cray XK7 ``Titan'' at the Oak Ridge Leadership Computing Facility.
-We quantitatively evaluated GLAD-M25 by assessing misfit reductions and traveltime \& amplitude anomaly histograms in twelve measurement
-categories.
-We performed similar assessments for a held-out data set consisting of 360 earthquakes,
-with results comparable to the actual inversion.
-We compare GLAD-M25 with numerous other global and regional models,
-and highlight a variety of plumes and subduction zones.
+This document contains supplementary material for the article entitled ``Global Adjoint Tomography -- Model GLAD-M25''.
 \end{summary}
@@
 
-\section{Introduction}
-
-Construction of the first seismic tomographic models of the Earth dates back to the late 1970s~\citep{Aki77,Dziewonski77,SenTok77} and early 1980s~\citep[e.g.,][]{WD84,Nataf1984}.
-Around the same time,
-\cite{BaChLa77}, \cite{Lailly1983}, and~\cite{Tar84} formulated and adapted the theory of adjoint-state methods~\citep{Chavent1974} for exploration seismology with the goal of capturing the full physics of seismic wave propagation.
-Mainly due to computational challenges,
-it took until the late 2000s to see the first applications of adjoint-state methods in regional- and continental-scale earthquake seismology~\citep{tape2009adjoint,Fichtner09,zhu2012structure}.
-The first global ``adjoint tomography'' model of the Earth's mantle,
-GLAD-M15, was published in 2016~\citep{bozdaug2016global}, more than 30 years after the development of the original ``full waveform inversion'' (FWI) theory.
-
-Current global seismic models are in general agreement regardless of data type and inversion strategy in terms of long-wavelength heterogeneity \citep{ritzwollerlavely1995,TW01,beckerboschi2002}.
-However, discrepancies between models become noticeable as resolution increases.
-Using accurate 3D simulations of seismic wave propagation and the computation of data sensitivities in 3D background models are key requirements for improving resolution in tomographic images on all scales.
-Such detailed images are essential for understanding mantle dynamics and related surface tectonic processes
----for example the origin of hotspots and the forces behind plate motions and earthquakes.
-Higher resolution wavespeed models are also important for accurately locating earthquakes, and are required from an engineering point of view to assess seismic hazard in earthquake prone regions and to detect nuclear explosions.
-
-With these goals in mind,
-in this study we use a GPU-accelerated version of the 3D spectral-element solver
-SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the Cray supercomputer ``Titan'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
-These simulations accommodate the full 3D complexity of global Earth models,
-including 3D anelastic crust and mantle structure, self-gravitation, rotation, ellipticity, topography \& bathymetry, and the load of the oceans.
-No compromises are made with regards to resolving the Earth's crust,
-which is explicitly captured by the spectral-element mesh~\citep{tromp2010a},
-thereby eschewing the need for ubiquitous ``crustal corrections''.
-The ultimate goal is to use every single piece of information in seismograms,
-a task made partly feasible based on the automated window selection tool FLEXWIN~\citep{maggi2009automated}.
-
-Global adjoint tomography has a well-defined but complex workflow with multiple stages.
-% including numerical simulations of synthetic seismograms (forward simulations) for all events,
-% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
-% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
-% updates.
-It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
-For each iteration,
-1,480 forward and adjoint simulations need to be performed,
-generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
-How to deal with hardware failures during this process is critical
-to prevent contamination of the inversion results.
-For these reasons, we are in the process of using EnTK as our
-workflow management engine~\citep{EnTK2017}.
-This workflow engine can automatically detected job failures,
-both from the high-performance computing (HPC) system and via user-defined functions.
-This facilitates tracking of tasks and semi-automatic job resubmission if necessary.
-
-In this article we compare the results of our inversion with a number of previous tomographic models.
-On a global scale, we present comparisons with model S362ANI$+$M~\citep{moulik2014anisotropic},
-which is an updated version of model S362ANI~\citep{kustowski2008anisotropic},
-the starting model for the GLAD-M15 inversion.
-We also consider global shear wavespeed models S40RTS~\citep{ritsema2011s40rts},
-TX2015~\citep{TX2015}, SEMUCB-WM1~\citep{french2015broad},
-and SL2013sv~\citep{SchaefferLebedev13},
-as well as compressional wavespeed models LLNL-G3Dv3 \citep{simmons2012llnl}, GAP-P4~\citep{fukao2013subducted}, and UU-P07~\citep{van2018atlas}.
-On the scale of North America
-we make comparisons with models US22~\citep{zhu2017radial},
-a radially anisotropic model based on adjoint tomography using USArray data from 180 regional earthquakes,
-and SL2013NA~\citep{schaeffer2014imaging},
-a modification of global model SL2013sv focused on North America.
-In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison,
-which is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
-Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227~earthquakes recorded by more than 1,800~stations.
-
-This article is organized as follows.
-Sections~\ref{section:start}--\ref{section:data} describe the starting model,
-earthquake database, and seismographic data set. 
-Sections~\ref{section:misfit} and~\ref{section:parameterization} describe the misfit function minimized during the inversion process
-and the related model parameterization.
-In Section~\ref{section:workflow} we describe the adjoint tomography workflow in some detail.
-Section~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 360 earthquakes.
-Finally, in Section~\ref{section:model}, we describe the model in detail,
-offering many comparisons with various global and regional models, as described in the proceeding paragraph.
-We conclude with a discussion of future opportunities and directions.
-
 \section{Starting model GLAD-M15}
@@
 As a continuation of our previous work~\citep{bozdaug2016global},
-we used the first-generation model GLAD-M15 as our
+we use model GLAD-M15 as our
 starting model.
@@
 with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
-In this study,
-we continue to use the same transversely isotropic model parametrization.
+We continue to use the same transversely isotropic model parametrization.
+To accommodate attenuation,
+we use radial anelastic model QL6~\citep{QL6}.
+
 Instead of relying on crustal corrections,
 the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
+The mantle and crust are inverted simultaneously.
+
 GLAD-M15 was constructed using a global database of 253 earthquakes.
@@
 
-\section{Earthquakes}
+\section{Source inversions}
 \label{section:earthquakes}
@@
 
-In addition to the 253 earthquakes used for the construction of GLAD-M15, we initially carefully selected 784 additional earthquakes
+In addition to the 253 earthquakes used for the construction of GLAD-M15, we initially selected 784 additional earthquakes
 from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global},
@@
 To ensure a good signal-to-noise ratio on a global scale,
-the smallest moment magnitude in the database is set to~5.5,
+the smallest moment magnitude in the database is set to~5.5 (as in the global CMT catalog),
 thereby capturing more deep events,
@@
 the results of which are summarized in Fig.~\ref{fig:source_correction}.
-To ensure even global coverage,
+To optimize even global coverage,
 we used seismographic stations from the  Global Seismic Network (II, IU, IC, US, CU, and GT),
@@
 the receivers are unevenly distributed across the globe,
-with several dense arrays in the Northern Hemisphere and poor coverage in the Southern Hemisphere.
+with several dense arrays in the northern hemisphere and poor coverage in the southern hemisphere.
 To balance the coverage,
@@
 The algorithm inverts for the six elements of the moment tensor
-and the centroid location~(latitude, longitude, and depth).
+and the centroid location~(latitude, longitude, and depth; duration is kept constant).
 These source inversions are computationally very expensive,
@@
 
-Most earthquakes show a shallower depth after inversion
+Most earthquakes are shallower after inversion
 (Fig.~\ref{fig:source_correction}c),
@@
 we only performed a grid search to calibrate the centroid times and scalar moments.
-Fig.~\ref{fig:event_1480} summarizes the characteristics of all 1,480 earthquakes used in this study.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/events_1480.pdf}
-  \caption{\small{The 1,480~earthquakes used in this study.
-(a) Distribution of earthquakes.
-The color of each beach ball reflects its depth range, where blue designates events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
-(b) \& (c) Histograms of earthquake moment magnitudes and depths.}}
-  \label{fig:event_1480}
-\end{figure}
-
-\section{Seismic data}
-\label{section:data}
-
-The seismographic stations used in this study were carefully selected to ensure global coverage
-and high data quality (Fig.~\ref{fig:stations}).
-In addition to the seismographic  stations used for the source inversions,
-we included all available data for our 1,480 event earthquake database from many data centers,
-including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
-Regional and temporary networks,
-such as US Array~(TA),
-Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
-the Antarctic Seismographic Argentinean Italian Network~(AI),
-and the New Zealand National Seismograph Network~(NZ),
-constitute a significant part
-of our database and greatly improve coverage in certain regions.
-
-\begin{figure}
-  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
-  \caption{\small{Distribution of the 11,800~seismographic stations used in this study.
-Colors denote the number of events for which a given station contributes waveforms to the structural inversion.
-Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers.
-The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}}
-  \label{fig:stations}
-  \centering
-\end{figure}
-
-\subsection{Adaptable Seismic Data Format}
-\label{section:ASDF}
-
-Conventional seismic data formats, such as SAC, involve one file per time series
-plus related files with instrument response and event information.
-Since every earthquake in the database is typically recorded by thousands of
-instruments, I/O during the preprocessing stage of the adjoint tomography workflow
-quickly cripples the file system. The Adaptable Seismic Data Format
-(ASDF)~\citep[][ \texttt{https://seismic-data.org/}]{krischer2016adaptable}
-was developed with complete reproducibility and fast parallel processing in mind.
-
-In this context, there are four key issues ASDF resolves.
-\begin{itemize}
-    \item Robustness and stability: the data container is developed and maintained to ensure accuracy of scientific results.
-    \item Data organization: the container is self-describing. Data, including waveform, source, and station information, are organized into well-defined structures.
-    \item Reproducibility: the container enables scientists to keep track of which operations have been performed on the data so that results can be reproduced.
-    \item Efficiency: the format provides easy mechanisms for parallel processing.
-\end{itemize}
-
-ASDF serves as a self-contained-and-explained data container while taking
-full advantage of parallel computing. In our workflow,
-one ASDF file contains all the information needed for processing one event,
-including the seismic traces, an event information file (in QuakeML format), and station response files (in StationXML format).
-The related Application Programming Interfaces (API)s are carefully designed for easy data extraction and parallel processing.
-
-\section{Misfit function}
-\label{section:misfit}
-
-The misfit function to be minimized during the iterative inversion process must
-be carefully constructed.
-In this study,
-it typically involves cross-correlation traveltimes
-for body waves and frequency-dependent multitaper phase measurements for surface waves.
-Measurements are made in several passbands of three-component seismograms rotated
-into vertical, radial, and transverse components, resulting in a number of measurement
-categories.
-In this study, we consider four passbands, namely, a 17--40~s passband targeting body waves,
-two 40--100~s passbands separately targeting body and surface waves,
-and a 90--250~s passband targeting longer-period surface waves.
-Each passband involves measurements on all three components,
-which results in a total of twelve measurement categories.
-Although the inversion is designed to minimize the overall misfit,
-we track the misfit reduction in each of the categories to ensure that
-the model is improving the fit to the data roughly equally across the board.
-One of the biggest challenges in the construction of the misfit function is the
-highly uneven distribution of earthquakes --- discussed in Section~\ref{section:earthquakes} --- and seismographic stations,
-which must be counterbalanced by geographically weighting the data.
-This issue is discussed in detail by~\cite{Ruanetal2018};
-in this section we present a brief synopsis.
-
-With these considerations in mind,
-the overall misfit, $\Phi$, is defined as follows:
-\begin{equation}
-\label{eq:misfit}
-\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{W_{scr}} \omega_{scrw}\, \chi_{scrw}
-\quad ,
-\end{equation}
-where~$S$ denotes the number of sources, $C$ the number of categories,
-$R_{sc}$ the number of receivers recording source~$s$ in category~$c$,
-and~$W_{scr}$ the number of measurement windows for source~$s$, category~$c$,
-and receiver~$r$.
-The misfit for a specific source~$s$, category~$c$, receiver~$r$, and window~$w$ is
-\begin{equation}
-  \chi_{scrw} = \frac{1}{\Delta\omega}\int_{\omega_1}^{\omega_2} \Big( \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big)^2\, \mathrm{d}\omega
-\quad ,
-\end{equation}
-where~$\Delta \tau_{scrw}$ denotes a multi-taper frequency-dependent phase measurement over the frequency interval~$\Delta\omega=\omega_2-\omega_1$\,,
-with associated uncertainties~$\sigma_{scrw}$\,.
-For body waves, the window misfit is often simply the cross-correlation traveltime anomaly,
-$\Delta T_{scrw}$\,, weighted by its standard deviation, i.e., $\chi_{scrw}=(\Delta T_{scrw}/\sigma_{scrw})^2$\,.
-As in the source inversions,
-the window weights are equal, $\omega_{scrw}=1$\,,
-and the category weight, $\omega_c$\,, is the reciprocal of the number of measurements in that
-category, $1/C$.
-Earthquakes mainly occur along plate boundaries,
-and most seismographic  stations are confined to the continents,
-which leads to a very uneven distribution of sources and stations,
-as illustrated in Figs.~\ref{fig:event_1480} and~\ref{fig:stations}.
-Therefore, weighting is crucial in global tomography to balance this uneven sampling
-of Earth's interior.
-Our source and receiver weighting strategy,
-encapsulated by the weights~$\omega_s$ and $\omega_{scr}$\,,
-is developed to compensate for uneven spatial sampling.
-Following the same strategy as for the receiver weights in the source inversions,
-we define source and receiver weights as
-\begin{equation}
-\omega_{s}^{-1} = N\,\sum_{s'=1}^{S} \exp\left[\mbox{}-\left(\frac{\Delta_{ss'}}{\Delta}\right)^2\right]
-\quad ,
-\label{eq:source_weights}
-\end{equation}
-and
-\begin{equation}
-\omega_{scr}^{-1} = N_{sc}\,\sum_{r'=1}^{R_{sc}} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_{sc}}\right)^2\right]
-\quad ,
-\label{eq:receiver_weights}
-\end{equation}
-respectively.
-Here~$N$ and~$N_{sc}$ are normalization factors,
-and~$\Delta_{ss'}$ and~$\Delta_{rr'}$ denote angular distances between source and receiver pairs~$\{s,s'\}$ and~$\{r,r'\}$\,.
-The reference angular distances~$\Delta$ and~$\Delta_{sc}$ need to be chosen based on the condition 
-numbers of the diagonal weighting matrices defined by Eqns.~(\ref{eq:source_weights}) and~(\ref{eq:receiver_weights}).
-
-\section{Model parameterization}
-\label{section:parameterization}
-
-We use the same transversely isotropic model parametrization as starting model GLAD-M15.
-Such a model is described by the five Love parameters $A$, $C$, $L$, $N$, and $F$~\citep{Love27},
-or, alternatively, using the mass density~$\rho$, in terms of the wavespeeds~$\alpha_v=\sqrt{C/\rho}$, $\alpha_h=\sqrt{A/\rho}$, $\beta_v=\sqrt{L/\rho}$, $\beta_h=\sqrt{N/\rho}$ and the dimensionless parameter $\eta=F/(A-2L)$~\citep{PREM,DT98}.
-Assuming the radial anisotropy is due to shear anisotropy, these five parameters
-may be further reduced to four by introducing the bulk sound speed,
-$c=\sqrt{\kappa/\rho}$\,.
-Therefore, the final four parameters are $c$, $\beta_v$, $\beta_h$, and $\eta$.
-Transverse isotropy is confined to the upper mantle; the lower mantle is assumed to be isotropic.
-
-Since density is difficult to constrain with seismic data,
-density perturbations are scaled to isotropic (Voigt averaged) shear wavespeed perturbations based on the relationship~$\delta\ln\rho = 0.33\,\delta\ln\beta$~\citep{montagner1989petrological}.
-
-Based on this parametrization,
-the variation in the misfit function~(\ref{eq:misfit}) may be expressed as~\citep{zhu2015seismic,bozdaug2016global}
-\begin{equation}
-    \delta \Phi = \int_V
-      (\delta \ln c\,K_c + \delta \ln\beta_v\,K_{\beta_v} + \delta \ln\beta_h\,K_{\beta_h} +
-      \delta\ln\eta\,K_\eta) \mathrm{d}V
-      \quad ,
-\end{equation}
-where~$K_c$, $K_{\beta_v}$, $K_{\beta_h}$, and $K_\eta$ denote the four Fr\'echet derivatives,
-which are calculated based on an adjoint-state method~\citep[e.g.,][]{Plessix_2006_RAS,Tromp2005}.
+
+% \subsection{Adaptable Seismic Data Format}
+% \label{section:ASDF}
+
+% Conventional seismic data formats, such as SAC, involve one file per time series
+% plus related files with instrument response and event information.
+% Since every earthquake in the database is typically recorded by thousands of
+% instruments, I/O during the preprocessing stage of the adjoint tomography workflow
+% quickly cripples the file system. The Adaptable Seismic Data Format
+% (ASDF)~\citep[][ \texttt{https://seismic-data.org/}]{krischer2016adaptable}
+% was developed with complete reproducibility and fast parallel processing in mind.
+
+% In this context, there are four key issues ASDF resolves.
+% \begin{itemize}
+%     \item Robustness and stability: the data container is developed and maintained to ensure accuracy of scientific results.
+%     \item Data organization: the container is self-describing. Data, including waveform, source, and station information, are organized into well-defined structures.
+%     \item Reproducibility: the container enables scientists to keep track of which operations have been performed on the data so that results can be reproduced.
+%     \item Efficiency: the format provides easy mechanisms for parallel processing.
+% \end{itemize}
+
+% ASDF serves as a self-contained-and-explained data container while taking
+% full advantage of parallel computing. In our workflow,
+% one ASDF file contains all the information needed for processing one event,
+% including the seismic traces, an event information file (in QuakeML format), and station response files (in StationXML format).
+% The related Application Programming Interfaces (API)s are carefully designed for easy data extraction and parallel processing.
 
@@
 Given the earthquake selection,
-observed seismographic data and related response information are acquired,
-as discussed in Section~\ref{section:data}.
+observed seismographic data and related response information are acquired.
 For a given earthquake,
-the corresponding seismograms and related response information are combined in a single ASDF file,
-described in Section~\ref{section:ASDF}.
+the corresponding seismograms and related response information are combined in a single ASDF file~\citep{krischer2016adaptable}.
 For a given earthquake data set, the conversion to ASDF needs to be performed once and for all.
@@
 
-The observed seismograms need to be compared to corresponding synthetic seismograms
-for the purpose of making measurements.
 The forward simulations are based on the global spectral-element solver
-SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a}, and take a CMT solution, a relevant list
+SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a}, and take a CMT solution, a list
 of stations, and the current earth model as input.
@@
 important stage of the adjoint tomography workflow,
-directly and fundamentally impacting the outcome.
-Any ``bad data'' assimilated at this stage may contaminate the gradient and
-ultimately the final model.
+impacting the outcome.
 
@@
 most importantly via the time window selection tool FLEXWIN~\citep{maggi2009automated}.
-Every seismogram and potential measurement goes through multiple checks and and
-balances before acceptance or rejection.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
-  \caption{\small{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
-  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-  The maximum window count is 9,931 in the 85--86$^\circ$ distance and 1,375--1,376~sec time bin.
-  Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
-  }}
-  \label{fig:window_density_Z}
-\end{figure}
 
@@
   \item Preliminary adjoint source construction based on the sorted windows.
-  \item Calculation and assignment of weights, as discussed in Section~\ref{section:misfit}.
+  \item Calculation and assignment of source and receiver weights~\citep{Ruanetal2018}.
   \item Construction of the final, properly weighted, adjoint sources.
 \end{enumerate}
-
-To illustrate which seismic phases end up being picked,
-Figs.~\ref{fig:window_density_Z}, \ref{fig:window_density_R}, and \ref{fig:window_density_T} show time-distance plots
-for vertical, radial, and transverse component 17--40~s body waves,
-respectively,
-in which the Pyflex window count is used to identify parts of seismograms being assimilated.
-The figures nicely highlight all the well known body traveltime branches.
-Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are of great importance, because they help constrain the compressional wavespeed structure in the model.
-The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
-This is something we will reconsider in future applications, perhaps by introducing aspects of machine learning.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
-  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
-   A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-  The maximum window count is 7,542 in the 86--87$^\circ$ distance and 1,378--1,379~s time bin.
-   }}
-  \label{fig:window_density_R}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
-  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
-   A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
-   The maximum window count is 7,208 in the 89--90$^\circ$ distance and 1,398--1,399~s time bin.
-   Only SH travetime branches are labeled.}}
-  \label{fig:window_density_T}
-\end{figure}
 
@@
   \item Summation of the individual Fr\'echet derivatives for each earthquake to obtain the overall gradient of the misfit function. The contribution of each source is weighted to balance
-    the uneven distribution of earthquakes based on the weighting strategy discussed in Section~\ref{section:misfit} .
+    the uneven distribution of earthquakes~\citep{Ruanetal2018}.
   \item Smoothing of the raw misfit gradient using a 3D Gaussian, which
@@
   \item Preconditioning of the smoothed gradient based on a technique proposed by~\cite{luo2013strategies}.
-  \item Line search to determine the magnitude of the model update.
+  \item Line search in the direction of the negative gradient to determine the magnitude of the model update.
   The search direction is determined using a nonlinear conjugate gradient method~\citep{wright1999numerical} (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25).
@@
 There are more than ten stages in the adjoint tomography workflow,
-and each stage involves thousands of small tasks.
+and each stage involves thousands of small repeated tasks.
 For every model iteration,
@@
 
-\section{Misfit evolution}
-\label{section:misfit_evolution}
-
-The inversion went through ten iterations in a number of stages, as documented
-in this section. The evolution of the overall misfit function~(\ref{eq:misfit})
-as well as its behavior in the various measurement categories is summarized
-in Fig.~\ref{fig:misfit}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figures/misfit.pdf}
-  \caption{\small{Evolution of the misfit function from GLAD-M15 to GLAD-M25.
-  Each color denotes different stages of the inversion, as discussed in Sections~\ref{sec:I}--\ref{sec:III}.
-  (a) Evolution of the total misfit. (b)--(j) Misfit in
-  each period band (rows) on three components (columns). (e)--(g) Since iteration 18,
-  we  split the 40--100~s period band into two
-  measurement categories: body waves (diamonds) and surface waves
-  (squares).
-  }}
-  \label{fig:misfit}
-\end{figure}
-
-\subsection{Stage~I: Iterations 15--17}
-\label{sec:I}
-
-Starting model GLAD-M15 was constructed using a database of 253 earthquakes.
-For iterations 15--17 of the inversion we used an expanded database of 520 events.
-Our focus was to validate and test our software and workflow before scaling up
-to a larger database of 1,040 events.
-For these iterations we used three period bands, namely,
-17--40~s, 40--100~s, and 90--250~s,
-and we used a nonlinear conjugate
-gradient method to update the model.
-
-\subsection{Stage~II: Iterations 18--21}
-
-We see an abrupt change in the value of the misfit function at iteration~18
-in Fig.~\ref{fig:misfit},
-reflecting the addition of 520~events to the inversion database,
-and a change in the weighting strategy for 40--100~s surface waves.
-For iterations 18--21 we split the 40--100~s period band into two, separating the
-body and surface waves (Figs.~\ref{fig:misfit}e--g).
-Since body and surface waves sample different parts of the mantle,
-this split facilitated more control over the spatial distribution of the model update.
-Because the 17th iteration model explains 40--100~s surface wave data relatively well,
-we reduced their weight on all three components for iterations 18--21,
-as indicated by the lower red curves in Figs.~\ref{fig:misfit}e--g.
-
-The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by
-iteration~21, prompting us to add more earthquakes and change the weighting strategy again by reintroducing 40--100~s surface waves.
-
-% Table~\ref{table:measurement_category} shows the four passbands we used in Stage~II, tabulating misfit reductions in all four passbands on three components,
-% that is, in twelve measurement categories.
-
-% \begin{table}[!htb]
+% \subsection{Misfit assessment}
+% \label{section:Misfit assessment}
+
+% \subsection{Histogram comparisons}
+% \label{section:Histogram comparisons}
+
+% Fig.~\ref{fig:PS_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components, and 17-40~s S-wave traveltime anomalies on the transverse component.
+% Both P and S waves exhibit consistent reductions in terms of both mean and variance.
+
+% \begin{figure}
 %   \centering
-%   \begin{tabular}{|c|c|c|c|}
-%     \hline
-%     ~          &  Vertical & Radial &  Transverse \\
-%     \hline
-%     17--40~s   &   P-SV          & P-SV           & SH   \\
-%     40--100~s  &   P-SV          & P-SV            & SH \\
-%     40--100~s  &   Rayleigh   & Rayleigh    & Love \\
-%     90--250~s  &   All                 & All                  & All  \\
-%     \hline
-%   \end{tabular}\\
-%   \caption{\small{Twelve measurement categories used for iterations 18--25.
-%   Before iteration~18, the 40--100~s body and surface waves categories were combined into a single category on each component, resulting in nine categories.}}
-%   \label{table:measurement_category}
-% \end{table}
-
-\subsection{Stage~III: Iterations 22--25}
-\label{sec:III}
-
-At iteration~22 we added another 440 earthquakes to the database,
-bringing the total to 1,480 events,
-and we changed the 40--100~s surface wave weights back to their
-setting in Stage~I. During this stage we switched from a nonlinear
-conjugate gradient optimization algorithm to an L-BFGS quasi-Newton method.
-
-\subsection{Misfit assessment}
-\label{section:Misfit assessment}
-
-In the previous sections we discussed the evolution of the misfit through
-three key stages of the inversion.
-It is important to note that ``the misfit function'' is, in fact, a
-continually moving target, because at every iteration the number of
-measurements increases as the model improves,
-and the number of earthquakes increases at iterations~18 and~22.
-
-In this section we calculate specific changes in misfit using all 1,480
-earthquakes and an identical set of weights and windows for three models,
-namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
-Table~\ref{table:misfit_reduction_M15_M25} summarizes the changes in fit in
-the twelve measurement categories between the new model, GLAD-M25, and its
-starting model, GLAD-M15, and between GLAD-M25 and model S362ANI combined
-with CRUST2.0, which was the starting model for the GLAD-M15 inversion.
-
-In all categories we observe significant misfit reductions,
-with dispersive 40--100~s surface waves exhibiting the largest improvements.
-The improvements in fit per component are comparable in all period bands,
-indicating that the various categories are reasonably well balanced in the
-assessment of misfit.
-
-\begin{table}
-  \centering
-  \begin{tabular}{|c|c|c|c|}
-    \hline
-    ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
-    \hline
-    %17--40~s  body waves    &   17.4 (31.1)   &       21.1 (37.1) &       24.6 (42.2) \\
-    %40--100~s body waves    &   16.8 (31.3)  &       21.3 (40.2)  &       21.7 (42.0) \\
-    %40--100~s surface waves &   28.5 (50.1)  &       28.3 (51.1) &       28.4 (53.8)  \\
-    %90--250~s surface waves &   14.5 (36.2)  &       13.4 (38.8) &       25.7 (38.6) \\
-    17--40~s  body waves    &   19.1 (37.3)   &       23.7 (46.3) &       28.2 (54.8) \\
-    40--100~s body waves    &   18.3 (37.5)   &       24.0 (51.4) &       24.5 (54.5) \\
-    40--100~s surface waves &   33.6 (69.6)   &       33.3 (71.5) &       33.5 (77.2) \\
-    90--250~s all waves &   15.7 (44.9)   &       14.4 (49.1) &       29.6 (48.7) \\
-    \hline
-  \end{tabular}\\
-  \caption{\small{Changes in fit in the twelve measurement categories
-  between the new model, GLAD-M25, and its starting model, GLAD-M15,
-  and, in parentheses, between GLAD-M25 and model S362ANI combined with
-  CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
-  \label{table:misfit_reduction_M15_M25}
-\end{table}
-
-% \begin{table}[!htb]
+%   \includegraphics[width=\textwidth]{figures/dt_histogram_phase.pdf}
+%   \caption{\small{Histograms of 17--40~s traveltime anomalies of P (vertical and radial), and SH (Transverse) arrivals for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
+%   }}
+%   \label{fig:PS_phase_hist}
+% \end{figure}
+
+% Fig.~\ref{fig:amp_hist} shows histograms of the amplitude
+% measurements for all twelve measurement categories,
+% which were not used in the current inversion.
+% Despite this,
+% we observe modest reductions in all standard deviations of the histograms.
+% The histograms are nicely centered, indicating that the moment magnitudes are
+% suitably selected, because the scalar moment affects all measurement categories equally.
+% In the next phase of our ongoing inversion we plan to begin assimilating amplitude measurements while simultaneously adding shear attenuation as a new model parameter.
+
+% \begin{figure}
 %   \centering
-%   \begin{tabular}{|c|c|c|c|}
-%     \hline
-%      ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-%     \hline
-%     17--40s body waves     &    31.1    &       37.1 &       42.2 \\
-%     40--100s body waves    &    31.3    &       40.2 &       42.0 \\
-%     40--100s surface waves &    50.1    &       51.1 &       53.8 \\
-%     90--250s               &    36.2    &       38.8 &       38.6 \\
-%     \hline
-%   \end{tabular}\\
-%   \caption{\small{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion.}}
-%   \label{table:misfit_reduction_M00_M25}
-% \end{table}
-
-\subsection{Histogram comparisons}
-\label{section:Histogram comparisons}
-
-Another way to evaluate model performance is by assessing the distribution
-of measurements in the various categories.
-Again we use all 1,480 events and a set of identical windows on all three components
-to assess GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
-The total number of selected windows,
-determined using model GLAD-M25, exceeds 18~million.
-Fig.~\ref{fig:phase_hist} shows histograms of the resulting phase
-measurements in all twelve measurement categories.
-We observe that the distributions generally become better centered on zero,
-and that all standard deviations are steadily reduced.
-Again we note that the inversion is aimed at reducing the overall misfit,
-so there are small tradeoffs between different measurement categories.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
-  \caption{\small{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
-  Each column represents one component and each row corresponds to a period band.
-  The numbers above the top right of each panel denote the number of measurements in the corresponding category.
-  The total number of measurements is 18.2 million.
-  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}}
-  \label{fig:phase_hist}
-\end{figure}
-
-Fig.~\ref{fig:PS_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components, and 17-40~s S-wave traveltime anomalies on the transverse component.
-Both P and S waves exhibit consistent reductions in terms of both mean and variance.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram_phase.pdf}
-  \caption{\small{Histograms of 17--40~s traveltime anomalies of P (vertical and radial), and SH (Transverse) arrivals for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
-  }}
-  \label{fig:PS_phase_hist}
-\end{figure}
-
-Fig.~\ref{fig:amp_hist} shows histograms of the amplitude
-measurements for all twelve measurement categories,
-which were not used in the current inversion.
-Despite this,
-we observe modest reductions in all standard deviations of the histograms.
-The histograms are nicely centered, indicating that the moment magnitudes are
-suitably selected, because the scalar moment affects all measurement categories equally.
-In the next phase of our ongoing inversion we plan to begin assimilating amplitude measurements while simultaneously adding shear attenuation as a new model parameter.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
-  \caption{\small{Same as Fig.~\ref{fig:phase_hist} except for amplitude measurements. These measurements are currently not used in the inversion.}}
-  \label{fig:amp_hist}
-\end{figure}
-
-\section{Model evaluation}
-\label{section:evaluation}
-
-% In this section we evaluate model GLAD-M25 further based on a point-spread
-% function resolution analysis as well as a ``held-out'' data set, that is,
-% a set of data not used in the actual structural inversion.
-
-\subsection{Point-spread function analysis}
-
-Checkboard tests or tests involving a chosen known structure, e.g., a plume or slab,
-are frequently used to evaluate resolution in a tomographic inversion.
-Such tests are extremely expensive in FWI and adjoint tomography, because they
-require roughly the same computational resources as the actual inversion.
-In lieu of such tests, we previously performed two point-spread function (PSF) analyses
-for model GLAD-M15~\citep{bozdaug2016global}.
-Since GLAD-M25 --- like its predecessor GLAD-M15 --- uses waves with a shortest period of 17~s
-but an earthquake database that is six times larger,
-we can expect improved versions of these already successful PSF tests.
-In the interest of focusing our efforts on obtaining the new model,
-we chose to direct our limited OLCF INCITE allocation towards the actual inversion
-rather than improved PSF tests.
-
-\subsection{Held-out data set}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/events_360.pdf}
-  \caption{\small{Summary of the held-out database containing 360 earthquakes.
-Theses events were not used in the structural inversion.
-(a) Distribution of events color coded by depth range as in Fig.~\ref{fig:event_1480}.
-(b) \& (c) Histograms of moment magnitude and depth.}}
-  \label{fig:events_360}
-\end{figure}
-
-Following the approach of \cite{tape2009adjoint}, \cite{chen2015multiparameter},
-and \cite{bozdaug2016global}, we selected 360 earthquakes that were not used
-in the actual inversion. This held-out data set consists of all magnitude 6.3--7.0
-earthquakes in the global CMT catalog that were not used in the inversion.
-We chose larger events to generate as many measurements as possible.
-We calibrated the centroid time and scalar moment using a grid search based on
-3D synthetics calculated in GLAD-M25.
-Fig.~\ref{fig:events_360} summarizes the properties of the held-out database.
-
-First, we repeated the misfit assessment discussed in
-Section~\ref{section:Misfit assessment} for the held-out database.
-Table~\ref{table:misfit_reduction_M15_M25_360} summarizes the reductions
-in misfit for the held-out database for model GLAD-M25 compared to GLAD-M15
-as well a S362ANI combined with CRUST2.0.
-It is a validation of our approach to see that the reductions are comparable to the
-values tabulated in Table~\ref{table:misfit_reduction_M15_M25} for the actual inversion.
-Overall, the reductions are slightly smaller, partly due to the fact that we did not
-conduct full CMT inversions for the held-out database.
-
-\begin{table}
-  \centering
-  %\label{tab:category}
-  \begin{tabular}{|c|c|c|c|}
-  \hline
-  ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
-  \hline
-  17--40~s                &          11.8 (29.2) &       14.1 (33.7) &       21.5 (43.4) \\
-  40--100~s body waves    &          14.5 (26.2) &       12.9 (32.2)  &       16.9 (39.0) \\
-  40--100~s surface waves &          29.3 (49.1) &       28.1 (49.4) &       23.7 (51.2) \\
-  90--250~s               &          10.9 (30.9) &       14.3 (34.8)  &       24.0 (34.9) \\
-  \hline
-  \end{tabular}\\
-  \caption{\small{Changes in fit for 360 earthquakes not used in the inversion in the twelve measurement categories
-between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
-  \label{table:misfit_reduction_M15_M25_360}
-\end{table}
-
-% \begin{table}[!htb]
-%   \centering
-%   %\label{tag:misfit_reduction_M00_M25_360}
-%   \begin{tabular}{|c|c|c|c|}
-%     \hline
-%     ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
-%     \hline
-%     17--40s                &         29.2 &       33.7 &       43.4 \\
-%     40--100s body waves    &         26.2 &       32.2 &       39.0 \\
-%     40--100s surface waves &         49.1 &       49.4 &       51.2 \\
-%     90--250s               &         30.9 &       34.8 &       34.9 \\
-%     \hline
-%   \end{tabular}\\
-%   \caption{\small{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out data set.}}
-%   \label{table:misfit_reduction_M00_M25_360}
-% \end{table}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
-  \caption{\small{Same as Fig.~\ref{fig:phase_hist}, except for the held-out database.
-  }}
-  \label{fig:phase_hist_360}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figures/dt_histogram_360_phase.pdf}
-  \caption{\small{Same as Fig.~\ref{fig:PS_phase_hist}, except for the held-out database.}}
-  \label{fig:phase_hist_360_P}
-\end{figure}
-
-Second, we repeated the histogram comparisons discussed in
-Section~\ref{section:Histogram comparisons} for the held-out database.
-We used a set of identical windows on all three components to assess
-phase anomalies in models GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
-Fig.~\ref{fig:phase_hist_360} shows histograms of the resulting phase
-measurements in all twelve measurement categories.
-The total number of measurements exceeds 7.8~million.
-As in the actual inversion,
-we observe systematic decreases in all standard deviations in all twelve categories,
-and we note a sharpening of the distributions centered around zero.
-
-Finally,
-direct P and S traveltime anomaly measurements were extracted and compared for three models in Fig.~\ref{fig:phase_hist_360_P}.
-Again the histograms are consistent with the actual inversion,
-as expected.
+%   \includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
+%   \caption{\small{Same as Fig.~\ref{fig:phase_hist} except for amplitude measurements. These measurements are currently not used in the inversion.}}
+%   \label{fig:amp_hist}
+% \end{figure}
 
@@
 specific geographical regions.
-We conclude by highlighting various slabs and plumes.
-The focus is on isotropic shear and compressional wavespeed variations.
-We provide comparisons with numerous other global and regional tomographic models,
-but we refrain from detailed tectonic/geodynamic interpretations,
-which will be the subject of more targeted future investigations.
-Our goal in the article is to discuss the construction of model GLAD-M25,
-and to place it into a broader tomographic context.
-
-Vertical cross sections are plotted relative to the spherical average of GLAD-M25,
-as discussed in Appendix~\ref{sec:1Dmodel}.
-For plotting purposes and use in other applications,
-an expansion of the model in spherical harmonics and radial B-splines is
-discussed in Appendix~\ref{sec:shanalysis}.
 
@@
 shear wavespeed model with model S362ANI$+$M~\citep{moulik2014anisotropic},
-which is an updated version of the starting model for the GLAD-M15 inversion,
 and model S40RTS~\citep{ritsema2011s40rts}.
@@
 An important aspect of our inversion is that it constrains shear and
-compressional waves simultaneously. In Fig.~\ref{fig:global-vs} we
+compressional waves simultaneously. In Fig.~\ref{fig:global-vp} we
 compare global maps of our compressional wavespeed model with global P models
@@
 At a depth of 100~km,
-GLAD-M25 shows prominent mid-oceanic ridges, cooling of the Pacific lithosphere,
+GLAD-M25 shows mid-oceanic ridges, cooling of the Pacific lithosphere,
 and the roots of numerous continental cratons. In the upper mantle, LLNL-G3Dv3
@@
 continental United States,
-and yet despite this tremendous increase in data coverage, there is not as much overlap between different models as one might anticipate.
+and yet despite this tremendous increase in data coverage, there is not as much agreement between different models as one might anticipate.
 In this section, we compare GLAD-M25 in this region 
@@
 bounded by the Rocky Mountain Front to the West and continental
-margin to the East~\citep{grand1984upper, whitmeyer2007tectonic}.
-On both sides the lithosphere has been deformed by
-low wavespeed structures, thus forming sharp tectonic boundaries
+margin to the East~\citep{grand1984upper, whitmeyer2007tectonic},
+with sharp tectonic boundaries
 ~\citep{masters1996shear, grand1997high, megnin2000three, gu2001models}.
@@
 and quite similar in shape and sharpness to the two regional models.
-We can clearly see impressions of the Snake River Plain (with Yellowstone)
-and the Raton hotspot, which also have distinct slow expressions at depths of 200~km.
+We can see impressions of the Snake River Plain (with Yellowstone)
+and the Raton hotspot, which also have slow expressions at depths of 200~km.
 The core of the craton exhibits fast wavespeeds at depths reaching 300~km Northwest of
@@
 
-In the 200--400~km depth range, we observe a high wavespeed
+In the 200--400~km depth range, we observe a low wavespeed anomaly beneath the Arctic
+and s high wavespeed
 anomaly within the Gulf of Mexico, which coincides spatially with the deepest
@@
 All models show fast anomalies beneath Newfoundland and Nova Scotia extending to
-depths of 300~km. The Bermuda hotspot shows a very nice slow wavespeed impression,
+depths of 300~km.
+The Bermuda hotspot has a distinct slow wavespeed impression,
 getting sharper and stronger at depths of 200~km and 300~km (note differences in
@@
 At greater depths,
-GLAD-M25 shows a very distinct image of the Farallon slab,
-but since it goes well beyond the depth range of this comparison,
-we return to this feature in Section~\ref{section:slabs}.
+GLAD-M25 shows a very distinct image of the Farallon slab.
 
@@
 transition zone and extends below 1,000~km in our model.
-We discuss the Hellenic Arc further in Section~\ref{section:slabs}.
 The Pannonian Basin is characterized by a low wavespeed
@@
 down to 1000~km.
-We discuss this subducting slab further in Section~\ref{section:slabs}.
 The Manila and Philippine trenches are also much sharper in our model between 200~km and
@@
 but barely observable in other models.
-This is probably a consequence of coverage provided by events in the region (see Fig.~\ref{fig:event_1480}).
+This is probably a consequence of coverage provided by events in the region.
 To the north,
 Caribbean subduction is clearly discernible in model GLAD-M25 and the two $V_\textrm{P}$ models.
-
-\subsection{Plumes}
-\label{section:plumes}
-
-\begin{figure}[ht!]
-    \centering
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}}\\[-1pt]
-    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}}\\
-    \caption{\small{Vertical cross sections for various plumes for models GLAD-M25 ($V_\textrm{S}$; left column), TX2015~\citep[$V_\textrm{S}$;][]{TX2015} (center column), and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad} (right column).
-    The map in the top left corner of each row shows the cross section with color-coded red, green, and white dots for geographical reference;
-    hotspots are denoted by red triangles.
-    The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
-    (a) Afar; (b) Bermuda (left) and Canary (middle); (c) Cape Verde (middle) and Hoggar (right); (d) Iceland (middle) and Eifel (right); (e) Easter (left) and Galapagos (right); (f) Marion (middle), and Kerguelen (right).
-}}
-    \label{fig:plumes}
-\end{figure}
-
-In this section we highlight various plume systems on Earth. Fig.~\ref{fig:plumes}
-shows cross sections of several plumes, comparing models GLAD-M25 ($V_\textrm{P}$),
-TX2015~\citep[$V_\textrm{S}$;][]{TX2015}, and SEMUCB-WM1~\citep[$V_\textrm{S}$;][]{french2015broad}.
-All three models have common plume features,
-and GLAD-M25 and TX2015 are in overall good agreement.
-
-The three models tend to agree near the CMB,
-and there is overall good agreement between GLAD-M25 and TX2015,
-but the models can differ substantially in the mid and upper mantle,
-with profoundly different implications for mantle
-convection.
-
-\begin{itemize}
-\item[]{\it Afar} In Fig.~\ref{fig:plumes}(a),
-we see that the Afar plume in model GLAD-M25 originates from the CMB, narrows its diameter
-in the mid mantle, and broadens again above the 660~km discontinuity.
-It exhibits
-very similar behavior in TX2015 but differs significantly in SEMUCB-WM1.  
-\item[]{\it Bermuda and Canary} In Fig.~\ref{fig:plumes}(b), from left to right, we see in model GLAD-M25 (i) the Farallon
-slab; (ii) the Bermuda hotspot above the 660~km discontinuity; (iii) the Canary hotspot originating from the CMT and
-rising all the way up the Earth's surface; (iv) the Afar hotspot from another angle.
-\item[]{\it Cape Verde and Hoggar} Fig.~\ref{fig:plumes}(c) features (i) South America subduction; (ii) the Cape Verde hotspot extending from the CMB all the way to the surface; (iii) the Hoggar hotspot from 660~km to the surface.
-\item[]{\it Iceland and Eifel} Fig.~\ref{fig:plumes}(d) shows a plume which rises from the CMB right below Iceland, reaches 660~km, amplifies,
-and ascends to the surface.
-The intensification above 660~km may be an indication of partial melting.
-\item[]{\it Easter and Galapagos} Fig.~\ref{fig:plumes}(e) contains (i) the Easter hotspot; (ii) the Galapagos
-hotspot; (iii) the Central America slab.
-In models GLAD-M25 and TX2015,
-the Easter and Galapagos hotspots appear to originate from the same underlying plume in the deep mantle,
-which is the eastern arm of the Pacific superplume.
-\item[]{\it Marion and Kerguelen}
-Finally,
-in Fig.~\ref{fig:plumes}(f) we see the Marion and Kerguelen hotspots, which might be connected to Afar in the lower mantle.
-Recovering these plumes is challenging due to poor data coverage in the southern hemisphere.
-\end{itemize}
-
-%\begin{figure}
-%    \centering
-%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
-%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
-%    \caption{\small{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}}
-%\end{figure}
-
-\subsection{Subduction zones}
-\label{section:slabs}
-
-\begin{figure}
-    \centering
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Aeg.png}\label{fig:subd_a}}\\[-8pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Br.png}\label{fig:subd_b}}\\[-8pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:subd_c}}\\[-8pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:subd_e}}\\[-8pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:subd_d}}\\[-8pt]
-    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Su.png}\label{fig:subd_f}}\\[-8pt]
-    \caption{\small{Vertical cross sections of compressional wavespeed perturbations in various subduction zones
-    for models GLAD-M25 ($V_\textrm{P}$; left column), GAP-P4~\citep{fukao2013subducted} (middle column) and UU-P07~\citep{van2018atlas} (right column).
-    The map in the top left corner of each row shows the cross section with color-coded red, green, and white dots for geographical reference.
-    The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
-    (a) Aegean; (b) South America; (c) Hatteras; (d) Wichita. (e) Nepal; (f) Sunda. }}
-    \label{fig:subd}
-\end{figure}
-
-In this section we highlight various subduction systems on Earth.
-In Fig.~\ref{fig:subd} we compare GLAD-M25~($V_\textrm{P}$) with two compressional wavespeed models,
-namely, GAP-P4~\citep{fukao2013subducted} and UU-P07~\citep{van2018atlas}.
-Fig.~\ref{fig:subd}(a) features the Aegean subduction zone. All models show a slab penetrating into the lower mantle beyond a depth of 1,000~km.
-Fig.~\ref{fig:subd}(b) shows the South American slab, which, in this cross section, ponds in the shallow lower mantle in all three models, before sinking all the way to the CMB.
-Figs.~\ref{fig:subd}(c) and~(d) show cuts across the ancient Farallon slab, which penetrates deeply into the lower mantle,
-as spectacularly documented by, for instance, \citet{grand1994,hilst1997,grand1997high}.
-At depths greater than 1,000~km, 
-we see a very strong expression of the slab in model GLAD-M25, which is much weaker in the two P models.
-The difference may be attributed to increased data coverage thanks to USArray, as well as the use of finite-frequency Fr\'echet derivatives.
-Fig.~\ref{fig:subd}(e) shows subduction beneath the Himalayas.
-All three models show two distinct fast anomalies below 660~km,
-one above 1,000~km and the other, further to the southwest, below 1,000~km.
-Finally, Fig.~\ref{fig:subd}(f) shows subduction beneath the Java portion of the Sunda Arc.
-At this location the slab pernetrates into the lower mantle, at which point its spreads out laterally,
-in agreement with models GAP-P4 and UU-P07.
-\cite{fukao1992} explained this flattening using a model of~\cite{ringwood1988},
-suggesting that the subducted slab thickened and buckled to form a dense megalith
-above the 660~km discontinuity before sinking into the lower mantle.
-
-Overall, the three models are in reasonably good agreement.
-At shallow depths, model GLAD-M25 shows more distinct continental crust and cratons, thanks to the inclusion of surface waves.
-But in the upper and mid mantle,
-the models share very similar attributes.
-
-\section{Discussion}
-
-Seismology is a science driven by data.
-There was a time when global seismologists would meticulously inspect single seismograms to glean valuable information from them.
-Today, we have easy access to data from thousands of earthquakes recorded by tens of thousands of seismographic stations, and individual inspection of all of these records has become impossible.
-Still, it would be a shame not to utilize as much as possible of the information in this massive seismographic database.
-
-To facilitate fast and effective access to such vast data resources,
-we use ASDF~\citep{krischer2016adaptable} in the preprocessing stage of the adjoint tomography workflow,
-and to accommodate massive I/O during the postprocessing stage we use the ADIOS library~\citep{liu2014hello}.
-For data assimilation,
-tools such as FLEXWIN, which automatically select data windows suitable for measurements, are indispensable, and we see tremendous opportunities for the use of machine learning algorithms in this context~\citep[e.g.,][]{chen2017}.
-Without these libraries and tools, the construction of model GLAD-M25 would have been impossible.
-
-Some form of automated parallel workflow management is critical for the global adjoint tomography process,
-because classical inversion workflows suffer from I/O inefficiencies, lack of fault tolerance, and an inability to work in distributed resource environments~\citep{Lefebvre2018}.
-The EnTK workflow management engine~\citep{EnTK2017}
-largely overcomes these limitations by facilitating tracking of tasks and job failure detection,
-thereby enabling semi-automatic job resubmission if necessary.
-These are the attributes required for bringing global FWI to its full potential,
-enabling the assimilation of data from thousands of earthquakes on the largest HPC systems.
-
-It should be clear from this discussion that modern seismic tomography requires close collaborations with computational scientists, HPC specialists, and visualization experts,
-as reflected in the list of authors for this article, in addition to access to the most advanced computational platforms,
-such as those offered through the DOE INCITE and NSF XSEDE programs.
-
-Although Figs.~\ref{fig:window_density_Z}--\ref{fig:window_density_T} illustrate that much information in seismograms is
-being assimilated, we still have a long way to go before explaining every wiggle in hundreds-of-minutes-long seismograms.
-Currently, we are only fitting the phase in selected time windows, and amplitude information remains completely unused.
-We accommodate the full physics of seismic wave propagation,
-but we are not exploiting the most general earth model parameterization.
-GLAD-M25 is an elastic model with radial anisotropy confined to the upper mantle.
-It is well known that the upper mantle is azimuthally anisotropic~\citep[e.g.,][]{montagner1989petrological,montagner1991},
-and we also know that amplitude information helps constrain second derivatives in phase speed~\citep[e.g.,][]{WW86,TDI,TDII},
-in addition to lateral variations in attenuation~\cite[e.g.,][]{romanowicz1998,reidetal2001,DaEkDz08}.
-Thus, the natural next step in global FWI is to use phase and amplitude information simultaneously to jointly constrain the elastic and anelastic structure of the Earth.
-To accomplish this next step, source parameters need to be constrained more carefully, especially as we push the resolution to shorter periods~\citep[e.g.,][]{valentine2010}.
-
-The global distribution of earthquakes (Fig.~\ref{fig:event_1480}) and stations (Fig.~\ref{fig:stations}) is highly uneven.
-This problem may be alleviated to some extent by using suitably chosen misfit functions with appropriate geographical weighting of sources and receivers~\citep[e.g,,][]{Li1996,Ruanetal2018}.
-The ultimate solution may be a dense network of Ocean Bottom Seismometers,
-but meanwhile an armada of floating seismometers may offer a cheaper and more practical alternative~\citep[e.g.,][]{Nolet19}.
-
-\section{Conclusion}
-
-Building on our experiences during the construction of our first-generation global adjoint tomography model GLAD-M15~\citep{bozdaug2016global},
-for this study we expanded our earthquake database from 253 to 1,480 events,
-which were collectively recorded by more than 11,000 seismographic stations.
-We used three-component seismograms in four period bands,
-namely 17--40~s body waves, 40--100~s body waves, 40--100~s surface waves, and 90--250~s surface waves,
-resulting in twelve measurement categories.
-This culminated in the assimilation of more than 18~million time windows.
-
-GLAD-M25 --- like its predecessor GLAD-M15 --- invokes no crustal corrections, and constrains crust and mantle shear and compressional wavespeeds simultaneously.
-Such ubiquitous crustal corrections may affect inferences about upper-mantle anisotropy~\citep[e.g.,][]{BozdagTrampert2008,PaLeRo10,Ferreira10}, and are likely the main reason for significant differences between radially anisotropic upper-mantle models~\citep[e.g.,][]{Chang14}.
-Treating the crust and mantle equally and simultaneously is one of the main strengths of GLAD-M25, accepting the additional computational costs, but thereby avoiding any approximations or corrections.
-Another strength is the fact that the effects of attenuation are fully accommodated, both in forward and in adjoint simulations.
-These points highlight the importance of taking the full physics of seismic wave propagation properly into account in seismic imaging.
-
-Another very important attribute of GLAD-M25 is that it constrains shear and compressional wavespeeds simultaneously in the same period range,
-thereby enabling us to interpret the two wavespeeds together.
-As illustrated in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R},
-numerous compressional wave arrivals are assimilated, including P, PP, PPP, PKP, PS, and PPS.
-In future work we will capitalize on this by using the $V_\text{P}/V_\text{S}$ ratio to help constrain thermo-chemical and geodynamical processes in the mantle.
-
-GLAD-M25 was quantitatively evaluated in several ways.
-First, it produces significant misfit
-reductions in all twelve measurements categories.
-Second,
-it produces nicely-centered Gaussian traveltime \& amplitude anomaly histograms
-in all measurement categories.
-Finally,
-for a held-out data set of 360 events
-we see similar misfit reductions and traveltime \& amplitude anomaly histograms as in the actual inversion.
-
-When we compare GLAD-M25 with other global models,
-we find overall good agreement at longer wavelengths.
-In particular, GLAD-M25 and TX2015 feature very similar plume structures.
-Unlike other global models, when we compare GLAD-M25 with regional models
-we also observe generally good agreement at smaller wavelengths,
-and, in particular, plumes and subduction zones feature prominently.
-However, it is important to note that GLAD-M25 tends to agree well with regional models based on the same S362ANI~$+$~Crust2.0 starting model, numerical wave propagation solver, and quasi-Newton inversion technique (e.g., EU60, US22, and EARA2014).
-It is also important to point out that even in regions with dense seismographic coverage, such as North America,
-recent models can differ substantially, especially at greater depths.
-Nevertheless, our global inversion is bridging the gap between global and regional studies,
-approaching regional-scale resolution is areas with sufficient data coverage.
-We can observe this increase in resolution in GLAD-M25 in the normalized power per spherical harmonic degree as a function of radius, which is displayed in Fig.~\ref{fig:powerspectraradius}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.95\textwidth]{figures/power_radius.pdf}
-  \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (left), GLAD-M15 (middle), and GLAD-M25 (right).
-  Shown are depths greater than 120~km.
-  (Courtesy of Caio Ciardelli.)
-  }}
-  \label{fig:powerspectraradius}
-\end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.95\textwidth]{figures/power_radius2.pdf}
-%   \caption{\small{Normalized power per degree~$\ell$ as a function of radius, based on Eqn.~(\ref{eq:powerdegreeradius}), for models S362ANI (first column), S40RTS (second column), GLAD-M15 (third column), and GLAD-M25 (fourth column).
-%   Shown are depths greater than 120~km.
-%   (Courtesy of Caio Ciardelli.)
-%   }}
-%   \label{fig:powerspectraradius}
-% \end{figure}
-
-Obvious future directions of research include growing the earthquake database further to the roughly 6,000 earthquakes in the right magnitude range already available via the Global CMT database,
-and reducing the shortest simulation period further from 17~s to 8.5~s.
-The most recent machine at OLCF, called ``Summit'', uses IBM Power9 CPUs accelerated by NVIDIA Tesla V100 GPU and can readily accommodate such simulations.
-
-Other future directions of research involve inversions for azimuthal anisotropy
-and attenuation.
-The feasibility of such inversions on a regional scale has already been demonstrated in studies focused on Europe by~\cite{ZhuTromp2013} and \cite{Zhuetal2013}.
 
@@
 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
-
-\appendix
-
-\section{Spherically symmetric average model}
-\label{sec:1Dmodel}
-
-In this appendix we determine the spherically symmetric (radial) average of model GLAD-M25.
-To accomplish this,
-we first need to transform the 3D spectral-element mesh --- which includes ellipticity, topography/bathymetry and undulations on internal boundaries --- into a spherical volume.
-After these adjustments, we obtain a spectral-element mesh for a perfect cubed sphere~\citep{KoTr02a}.
-
-In the spherical mesh, the model may be expressed in the form
-\begin{equation}
-    m(\mathbf{x})=\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}m^{\alpha\beta\gamma}\,h_{\alpha}(\xi)\,h_{\beta}(\eta)\,h_{\gamma}(\zeta)\,
-    \quad ,
-\end{equation}
-where~$h_\alpha$ denotes a Lagrange polynomial, and where we have used the invertible mapping
-\begin{equation}
-    \mathbf{x}=\mathbf{x}(\xi,\eta,\zeta)
-\end{equation}
-between spatial points~$\mathbf{x}=\{x,y,z\}$ and Gauss-Lobatto-Legendre (GLL) points in the reference element~$\{\xi,\eta,\zeta\}$~\citep{KoTr99}.
-
-The spherically symmetric part of the model is defined as
-\begin{equation}
-    \overline{m}(r)=\frac{1}{4\pi}\,\int_\Omega m(\mathbf{x})\,\mathrm{d} \Omega
-    \quad,
-\end{equation}
-where~$r$ denotes the radius and~$\Omega$ the unit sphere.
-
-Using 2D GLL quadrature~\citep{KoTr99} in the unit sphere,
-the radial average may be determined numerically via GLL quadrature:
-\begin{equation}
-    \overline{m}(r)=\frac{1}{4\pi\,r^2}\,\sum_{\alpha,\beta}\omega_\alpha\omega_\beta\,m^{\alpha\beta}(r)\,J^{\alpha\beta}(r)
-    \quad.
-    \label{eq:radial_average}
-\end{equation}
-Here~$\alpha$ and~$\beta$ denote GLL points in the sphere with radius~$r$\,,
-$\omega_\alpha$ denotes a GLL quadrature weight, and $J^{\alpha\beta}(r)$ is the 2D Jacobian of the mapping to the sphere.
-%It is important to carry out the summations in~(\ref{eq:radial_average}) at the elemental level to ensure that first-order discontinuities are honored in the process.
-
-Figure~\ref{fig:global-average} shows the resulting radial averages of the isotropic shear and compressional wavespeeds for model~GLAD-M25
-compared to 1D starting model~STW105~\citep{kustowski2008anisotropic} and PREM~\citep{PREM}.
-The radial average of~GLAD-M25 remains very close to the radial starting model~STW105.
-The main difference between these two models and~PREM
-is the absence of the 220~km discontinuity and a lower~$V_\text{P}/V_\text{S}$ ratio in the top 200~km.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figures/1d_profile.pdf}
-  \caption{\small{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
-  The reference frequency for physical dispersion is ~7.77~mHz.}}
-  \label{fig:global-average}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/1d_profile_ra.pdf}
-  \caption{\small{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is ~7.77~mHz.}}
-  \label{fig:global-ra-average}
-\end{figure}
-
-\section{Spherical harmonic model expansion}
-\label{sec:shanalysis}
-
-In this appendix we express model GLAD-M25 in a spherical harmonic basis
-to facilitate easy plotting, analysis, and comparisons with other models.
-The resulting spherical harmonic model should only be used for these purposes, not for numerical simulations, which should always be based on the fully 3D spectral-element mesh.
-
-To accomplish the transformation,
-we first need to transform the 3D mesh --- which includes ellipticity, topography/bathymetry and undulations on internal boundaries --- into a spherical volume.
-After these adjustments, we obtain a spectral element mesh for a perfect sphere,
-that is, the sort of mesh used for spherically symmetric earth models, such as PREM~\citep{PREM}.
-
-In the spherical mesh, the model may be expressed in the form
-\begin{equation}
-    m(\mathbf{x})=\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}m^{\alpha\beta\gamma}\,h_{\alpha}(\xi)\,h_{\beta}(\eta)\,h_{\gamma}(\zeta)\,
-    \quad ,
-\end{equation}
-where~$h_\alpha$ denotes a Lagrange polynomial, and where we have used the invertible mapping
-\begin{equation}
-    \mathbf{x}=\mathbf{x}(\xi,\eta,\zeta)
-    \label{eq:map}
-\end{equation}
-between spatial points~$\mathbf{x}=\{x,y,z\}$ and Gauss-Lobatto-Legendre (GLL) points in the reference element~$\{\xi,\eta,\zeta\}$~\citep{KoTr99}.
-
-Our goal is to expand our spectral-element model in a spherical harmonic basis, i.e.,
-\begin{equation}
-    m(\mathbf{x})=\sum_{n=0}^N\sum_{\ell = 0}^L\sum_{m=-\ell}^\ell {}_nC_{\ell m}\,R_n(r)\,Y_{\ell m}(\theta,\phi)
-    \quad ,
-    \label{eq:m}
-\end{equation}
-where~$r$ denotes the radius, $\theta$ colatitude, and~$\phi$ longitude.
-We choose a radial basis of the form~$R_n(r)$\,, $n=0,\ldots,N$\,,
-e.g., layers or B-splines.
-These radial basis functions need to be chosen sufficiently dense to mimic the density of the radial spectral element mesh.
-The radial basis may or may not be orthogonal,
-i.e.,
-\begin{equation}
-    \int_b^a R_{n'}(r)\,R_{n}(r)\,r^2\mathrm{d}r = A_{n'n}
-    \quad ,
-    \label{eq:R}
-\end{equation}
-where~$b$ denotes the radius of the CMB and~$a$ the free surface.
-The matrix elements~$A_{n'n}$ define a positive definite matrix which is invertible.
-As lateral basis functions we use fully normalized spherical harmonics~$Y_{\ell m}(\theta,\phi)$\,, $\ell=0,\ldots,L$ and $m=\mbox{}-\ell,\ldots,\ell$\,, i.e.,~\citep{DT98}
-\begin{equation}
-    \int_0^{2\pi}\int_0^\pi Y^*_{\ell'm'}(\theta,\phi)\,Y_{\ell m}(\theta,\phi)\,\sin\theta\,\mathrm{d}\theta\,\mathrm{d}\phi = \delta_{\ell' \ell}\,\delta_{m'm}
-    \quad ,
-    \label{eq:Y}
-\end{equation}
-where an asterisk denotes complex conjugation.
-The maximum degree~$L$ needs to be chosen to resolve the spectral-element mesh laterally.
-
-To obtain the expansion coefficients~${}_nC_{\ell m}$\,, we multiply Eqn.~(\ref{eq:m}) by
-$R_{n'}(r)\,Y^*_{\ell' m'}(\theta,\phi)$ and integrate over the volume of the mantle and crust,~$V$\,, using Eqns.~(\ref{eq:R} and~(\ref{eq:Y}):
-\begin{equation}
-    \int_V m(\mathbf{x})\,R_{n'}(r)\,Y^*_{\ell' m'}(\theta,\phi)\,\mathrm{d}^3\mathbf{x}=\sum_{n=0}^N {}_nC_{\ell' m'}\,A_{n'n}
-    \quad ,
-\end{equation}
-We evaluate the integral on the left using GLL quadrature~\citep{KoTr99}:
-\begin{equation}
-    \sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,Y_{\ell'm'}^{*\,\alpha\beta\gamma}
-    =\sum_{n=0}^N {}_nC_{\ell' m'}\,A_{n'n}
-    \quad .
-\end{equation}
-Here~$\omega_\alpha$ denotes a GLL quadrature weight,
-$J_{\alpha\beta\gamma}$ the Jacobian of the mapping~(\ref{eq:map}) evaluated on the GLL points,
-and $R_{n'}^{\alpha\beta\gamma}$ and $Y_{\ell'm'}^{*\,\alpha\beta\gamma}$ the values of the radial and spherical harmonic basis functions at a GLL point.
-
-Finally, the desired model coefficients may be obtained ---one combination of $n$\,, $\ell$\,, and $m$ at a time--- via
-\begin{equation}
-    {}_nC_{\ell m}=\sum_{n'}A^{-1}_{nn'}\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,Y_{\ell m}^{*\,\alpha\beta\gamma}
-    \quad ,
-    \label{eq:Cnlm}
-\end{equation}
-where~$A^{-1}$ denotes the inverse of the~$N\times N$ matrix~$A$.
-Expressions of the form~(\ref{eq:Cnlm}) are commonplace in spectral-element simulations,
-and thus easily calculated.
-
-The normalized power per degree~$\ell$ may be calculated via
-\begin{equation}
-    \sigma_\ell^2=\frac{1}{2\ell+1}\,
-    \sum_{n' = 0}^N\sum_{n = 0}^N\sum_{m = -\ell}^\ell\,A_{n'n}\,{}_{n'}C^*_{\ell m}\,{}_{n}C_{\ell m}
-    \quad .
-\end{equation}
-Alternatively,
-one may wish to calculate the power per degree as a function of radius,
-which is determined via
-\begin{equation}
-    \Sigma_\ell^2(r)=\frac{1}{2\ell+1}\,
-    \sum_{n' = 0}^N\sum_{n = 0}^N\sum_{m = -\ell}^\ell\,R_{n'}(r)\,R_{n}(r)\,{}_{n'}C^*_{\ell m}\,{}_{n}C_{\ell m}
-    \quad .
-\end{equation}
-
-Instead of the complex spherical harmonic model expansion~(\ref{eq:m}),
-we may wish to use a real spherical harmonic expansion of the form~\citep[][Section~B.8, Eqn.~B.99]{DT98}
-\begin{equation}
-\begin{split}
-    m(\mathbf{x}) \ = & \ \sum_{n=0}^N\sum_{\ell = 0}^L \left[ {}_na_{\ell 0}\,R_n(r)\,X_{\ell 0}(\theta)
-   +\sqrt{2}\sum_{m=1}^\ell R_n(r)\,({}_na_{\ell m}\,\cos m\phi+{}_nb_{\ell m}\,\sin m\phi)\,X_{\ell m}(\theta)\right]
-    \quad ,
-\end{split}
-    \label{eq:mreal}
-\end{equation}
-where~\citep[][Eqn.~B.30]{DT98}
-\begin{equation}
-    Y_{\ell m}(\theta,\phi)=X_{\ell m}(\theta)\exp(i m\phi)
-    \quad ,
-\end{equation}
-and where
-\begin{equation}
-    {}_na_{\ell 0}=\sum_{n'}A^{-1}_{nn'}\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,X_{\ell m}^{\alpha\beta\gamma}
-    \quad ,
-\end{equation}
-and for~$1\le m\le \ell$
-\begin{equation}
-    {}_na_{\ell m}=\sqrt{2}\,\sum_{n'}A^{-1}_{nn'}\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,X_{\ell m}^{\alpha\beta\gamma}\,(\cos m \phi)^{\alpha\beta\gamma}
-    \quad ,
-\end{equation}
-\begin{equation}
-    {}_nb_{\ell m}=\sqrt{2}\,\sum_{n'}A^{-1}_{nn'}\sum_{\mathrm{elem}}\sum_{\alpha,\beta,\gamma}\omega_\alpha\,\omega_\beta\,\omega_\gamma\,m^{\alpha\beta\gamma}\,J^{\alpha\beta\gamma}\,R_{n'}^{\alpha\beta\gamma}\,X_{\ell m}^{\alpha\beta\gamma}\,(\sin m \phi)^{\alpha\beta\gamma}
-    \quad .
-\end{equation}
-The normalized power per degree~$\ell$ may then be calculated via
-\begin{equation}
-    \sigma_\ell^2=\frac{1}{2\ell+1}\,\sum_{n'=0}^N\,\sum_{n=0}^N\,A_{n'n}\,\left[{}_{n'}a_{\ell 0}\,{}_{n}a_{\ell 0}+\sum_{m=1}^\ell({}_{n'}a_{\ell m}\,{}_na_{\ell m}+{}_{n'}b_{\ell m}\,{}_nb_{\ell m})\right]
-    \quad ,
-    \label{eq:powerdegree}
-\end{equation}
-and the normalized power per degree as a function of radius is determined via
-\begin{equation}
-    \Sigma_\ell^2(r)=\frac{1}{2\ell+1}\,\sum_{n'=0}^N\,\sum_{n=0}^N\,R_{n'}(r)\,R_{n}(r)\,\left[{}_{n'}a_{\ell 0}\,{}_{n}a_{\ell 0}+\sum_{m=1}^\ell({}_{n'}a_{\ell m}\,{}_na_{\ell m}+{}_{n'}b_{\ell m}\,{}_nb_{\ell m})\right]
-    \quad .
-    \label{eq:powerdegreeradius}
-\end{equation}
-In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, GLAD-M15, and GLAD-M25,
-and Fig.~\ref{fig:powerspectraradius} shows the normalized power per degree as a function of radius
-for the same set of models.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{figures/power.pdf}
-  \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), GLAD-M15 (green), and GLAD-M25 (blue).
-  The calculation includes depths greater than 120~km.
-  Model S362ANI has no power beyond degree~18,
-  and model S40RTS has no power beyond degree~40.
-  (Courtesy of Caio Ciardelli.)
-  }}
-  \label{fig:powerspectra}
-\end{figure}
-% In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, S40RTS, GLAD-M15, and GLAD-M25,
-% and Fig.~\ref{fig:powerspectraradius} shows the normalized power per degree as a function of radius
-% for the same set of models.
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth]{figures/power2.pdf}
-%   \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), S40RTS (orange), GLAD-M15 (green), and GLAD-M25 (blue).
-%   The calculation includes depths greater than 120~km.
-%   Model S362ANI has no power beyond degree~18,
-%   and model S40RTS has no power beyond degree~40.
-%   (Courtesy of Caio Ciardelli.)
-%   }}
-%   \label{fig:powerspectra}
-% \end{figure}
-
 \bibliographystyle{gji}

### 2020-02-11 main.tex
fix issues in figures as suggested by Jeroen
Updates from Overleaf

@@
 
-Figure~\ref{fig:??} shows the results of the four PSF tests we performed for model GLAD-M25.
+Fig.~\ref{fig:??} shows the results of the four PSF tests we performed for model GLAD-M25.
 The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
 That test was based on 253 earthquakes,
-and Figures~\ref{fig:??}a and~\ref{fig:??}b show our results for the same location based on half our dataset (720 events) and the full dataset (1,480 events), respectively.
-Figure~\ref{fig:??} shows the results of a PSF test in the lowermost mantle at the base of the African superplume,
+and Figs.~\ref{fig:??}a and~\ref{fig:??}b show our results for the same location based on half our dataset (720 events) and the full dataset (1,480 events), respectively.
+We observe that the 75~km diameter anomaly is well recovered, with little tradeoff.
+Figs.~\ref{fig:??}c--f shows the results of PSF tests in the lowermost mantle at the base of the African superplume,
 in the lower mantle beneath the Galapagos,
 and in the mid mantle below Indonesia.
+In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters.
 
@@
 Model S362ANI has no power beyond degree~18,
-and we see and increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10.
+and we see and increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10 throughout the mantle.
 
@@
 
-Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda.
+Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda,
+and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model Glad-M25,
+including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.
 
@@
 
-Figure~\ref{fig:global-average} shows the resulting radial averages of the isotropic shear and compressional wavespeeds for model~GLAD-M25
+Fig.~\ref{fig:global-average} shows the resulting radial averages of the isotropic shear and compressional wavespeeds for model~GLAD-M25
 compared to 1D starting model~STW105~\citep{kustowski2008anisotropic} and PREM~\citep{PREM}.

### 2020-02-11 response_to_reviewers.tex

@@
 The original manuscript did not contain point-spread function (PSF) tests,
-but several such tests are included in the revived manuscript.
-A PSF does not say much about uncertainty ---like checkerboard tests and the resolution matrix--- but gives an idea of resolution and model parameter tradeoffs.
+but four such tests are included in the revived manuscript.
+A PSF test does not say much about uncertainty ---like checker-board tests and the resolution matrix--- but gives an idea of resolution and model parameter tradeoffs.
 }
@@
 First, we provide quantitative evidence in the forms of misfit reductions (Tables 1 \& 2) and traveltime \& amplitude histograms (Figs.~10, 11, 12, 14 \& 15 in the original manuscript) that M25 fits the data better than M15.
-Second, M25 resolves numerous new features that were entirely missing in M15, such as the Fiji-Tonga slab near New Zealand, and various hotspots in the Indian Ocean.
-Rather than focusing on comparisons between M15 and M25, we chose to show comparisons with several global and regional models.
+Second, M25 resolves numerous new features that were entirely missing in M15, such as the Fiji-Tonga slab near New Zealand, and various hotspots in the Atlantic and Indian oceans.
+Finally, even a cursory look at the figures displaying the normalized power per angular degree clearly reveals an increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10 throughout the mantle.
+
 In response to the reviews,
-we have reduced the number of model comparisons, focusing on plumes and subduction zones instead.
+we have added a section (Section~7.1) which highlights the differences between GLAD-M15 and GLAD-M25,
+and reduced the number of comparisons with other models, focusing on plumes and subduction zones instead.
 }

### 2020-02-11 main.tex
update events_360.pdf
Updates from Overleaf

@@
   \centering
-  \includegraphics[width=\textwidth]{figures/events_1480.pdf} \\
+  \includegraphics[width=0.8\textwidth]{figures/events_1480.pdf} \\
   \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
@@
 The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.
-  \towenjie{Remove panels (b) and (c) and fix up the figure. Make sure the station count starts at 1, not 0.}
   }}
@@
 Note that the plot contains data from events with a wide variety of depths, so the branches computed for a surface focal depth are for identification purposes only.
-  \towenjie{Relabel PS as PS+SP.}
   }}
@@
 (a) Distribution of events color coded by depth range as in Fig.~\ref{fig:eventsstations}(a).
-(b) \& (c) Histograms of moment magnitude and depth.}}
+(b) \& (c) Histograms of moment magnitude and depth.
+\tojeroen{Do I need to update this figure, to remove subfigure b and c?} }}
   \label{fig:events_360}
@@
 \caption{\small{Contour plot (left) and cross-sections at various depths (right) of subduction underneath South America, showing improvements in resolution in GLAD-M25 compared to GLAD-M15.
-The contour plot shows positive perturbations of vertically polarized shear wavespeeds in GLAD-M25. The ball in the contour plot denotes the 660~km discontinuity.}}
+The contour plot shows positive perturbations of vertically polarized shear wavespeeds in GLAD-M25. The ball in the contour map denotes the 660~km discontinuity.}}
 \label{fig:S_America}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{./figures/M24-Iceland.png}
-  \caption{\small{Map views of vertically polarized shear-wave-speed perturbations in GLAD-M15 (top left) and GLAD-M24 (top right) underneath Iceland.
+  \includegraphics[width=0.8\textwidth]{figures/M25-Iceland.pdf}
+  \caption{\small{Map views of vertically polarized shear-wave-speed perturbations in GLAD-M15 (top left) and GLAD-M25 (top right) underneath Iceland.
 Also shown are vertical cross-sections(bottom row) at the same location.
-As a primary hotspot, Iceland also becomes much more prominent in GLAD-M24, especially in the upper mantle.
-\towenjie{Please update.}
+As a primary hotspot, Iceland also becomes more prominent in GLAD-M25, especially in the upper mantle.
   }}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{./figures/M24-Reunion.png}
-  \caption{\small{Map views at 250~km depth of vertically polarized shear-wave-speed perturbations in GLAD-M15 (left) and GLAD-M24 (right) at Indian Ocean.
-New features are emerging in GLAD-M24, as the hotspot at Reunion, Marion, Kerguelen, and Crozet just came out in GLAD-M24.
-\towenjie{Please update.} }}
+  \includegraphics[width=0.8\textwidth]{figures/M25-Reunion.pdf}
+  \caption{\small{Map views at 250~km depth of vertically polarized shear-wave-speed perturbations in GLAD-M15 (left) and GLAD-M25 (right) in the Indian Ocean.
+New features have emerged in GLAD-M25, such as the R\'eunion, Marion, Kerguelen, Maldives, Seychelles, Cocos, and Crozet hotspots.}
+  }
   \label{fig:M24-Reunion}

### 2020-02-14 main.tex
add psf figures
Updates from Overleaf

@@
 
-\subsection{Point-spread function analysis}
+\subsection{Point-spread function analyses}
 
@@
 Here we repeat one of those tests (underneath Yellowstone) to show the improved resolution in GLAD-M25 relative to GLAD-M15,
-and we perform three additional PSF tests: in the lower mantle underneath Afar, in the lower mantle beneath the Galapagos, and below the transition zone in Indonesia.
+and we perform three additional PSF tests: in the lower mantle underneath Afar, in the lower mantle beneath Easter Island, and below the transition zone in Sumatra.
+Two additional PSF tests for anomalies below the US may be found in the SOM.
 
@@
 
-Fig.~\ref{fig:??} shows the results of the four PSF tests we performed for model GLAD-M25.
+Fig.~\ref{fig:psf_tests} shows the results of the four PSF tests we performed for model GLAD-M25.
 The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
 That test was based on 253 earthquakes,
-and Figs.~\ref{fig:??}a and~\ref{fig:??}b show our results for the same location based on half our dataset (720 events) and the full dataset (1,480 events), respectively.
-We observe that the 75~km diameter anomaly is well recovered, with little tradeoff.
-Figs.~\ref{fig:??}c--f shows the results of PSF tests in the lowermost mantle at the base of the African superplume,
-in the lower mantle beneath the Galapagos,
-and in the mid mantle below Indonesia.
-In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters.
+and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events.
+We observe that the 100~km diameter anomaly at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (See SOM).
+Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests in the lower mantle beneath Afar,
+in the lowermost mantle beneath Easter Island,
+and in the mid mantle below Sumatra.
+In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters (See SOM).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/psf_tests.pdf}
+  \caption{\small{PSF tests.
+  Each of the four panels labeled (a)--(d) shows a map view (Top Left) and cross section (Top Right) through a Gaussian perturbation, $\mathsf{\Delta}\mathsf{m}$\,, in~$\beta_\mathrm{V}$\,,
+  and a map view (Bottom Left) and cross section (Bottom Right) through the recovered perturbation, $\mathsf{H}\cdot\mathsf{\Delta}\mathsf{m}$\,, in~$\beta_\mathrm{V}$.
+  (a) 100~km diameter negative Gaussian anomaly at a depth of 300~km beneath Yellowstone.
+  (b) 400~km diameter negative Gaussian anomaly at a depth of 2,000~km beneath Afar.
+  (c) 300~km diameter negative Gaussian anomaly at a depth of 2,500~km beneath Easter Island.
+  (d) 200~km diameter positive Gaussian anomaly at a depth of 900~km beneath Sumatra.
+  }}
+  \label{fig:psf_tests}
+\end{figure}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/events_360.pdf}
-  \caption{\small{Summary of the held-out database containing 360 earthquakes.
-Theses events were not used in the structural inversion.
-(a) Distribution of events color coded by depth range as in Fig.~\ref{fig:eventsstations}(a).
-(b) \& (c) Histograms of moment magnitude and depth.
-\tojeroen{Do I need to update this figure, to remove subfigure b and c?} }}
+  \includegraphics[width=0.8\textwidth]{figures/events_360.pdf}
+  \caption{\small{Held-out database containing 360 earthquakes. These events were not used in the structural inversion and are color coded by depth range as in Fig.~\ref{fig:eventsstations}(a).}}
   \label{fig:events_360}

### 2020-02-14 supplementary_material.tex
Updates from Overleaf

@@
 
+\section{Point Spread Function tests}
+
+This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study.
+Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_su} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, and Sumatra.
+Each figure shows the original Gaussian perturbation, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{figures/psf/yellowstone.pdf}
+  \caption{\small{PSF test for Yellowstone.
+  A 100~km diameter negative Gaussian anomaly is placed at a depth of 300~km beneath Yellowstone.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
+  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
+We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  }}
+  \label{fig:psf_yellowstone}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{figures/psf/easter.pdf}
+  \caption{\small{PSF test for Easter Island.
+  A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
+  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
+We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+A 75~km diameter positive Gaussian anomaly is placed at a depth of 150~km beneath Yellowstone.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
+  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
+We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.}}
+  \label{fig:psf_easter}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{figures/psf/afar.pdf}
+  \caption{\small{PSF test for Afar.
+    A 400~km diameter negative Gaussian anomaly is placed at a depth of 2,000~km beneath Afar.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
+  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
+We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  }}
+  \label{fig:psf_afar}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{figures/psf/su.pdf}
+  \caption{\small{PSF test for Sumatra.
+    A 200~km diameter positive Gaussian anomaly is placed at a depth of 900~km beneath Sumatra.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
+  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
+We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  }}
+  \label{fig:psf_su}
+\end{figure}
+
 \section{Model GLAD-M25}

### 2020-02-16 supplementary_material.tex
add two extra psf results

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{figures/psf/usa_mid.pdf}
+  \caption{\small{PSF test for the middle of the United States.
+    A 160~km diameter positive Gaussian anomaly is placed at a depth of 500~km beneath the middle of USA.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
+  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
+We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  }}
+  \label{fig:psf_usa_mid}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.pdf}
+  \caption{\small{PSF test for the east of the United States.
+    A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the east of USA.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
+  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
+We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  }}
+  \label{fig:psf_usa_east}
+\end{figure}
+
 \section{Model GLAD-M25}

### 2020-02-16 main.tex
add combined psf figures
Updates from Overleaf

@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/psf_tests.pdf}
+  \includegraphics[width=\textwidth]{figures/psf/psf_tests.pdf}
   \caption{\small{PSF tests.
@@
 Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda,
-and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model Glad-M25,
+and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model GLAD-M25,
 including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.
@@
 \item[]{\it Bermuda and Canary} In Fig.~\ref{fig:plumes}(b), from left to right, we see in model GLAD-M25 (i) the Farallon
-slab; (ii) the Bermuda hotspot above the 660~km discontinuity; (iii) the Canary hotspot originating from the CMT and
+slab; (ii) the Bermuda hotspot above the 660~km discontinuity; (iii) the Canary hotspot originating from the CMB and
 rising all the way up the Earth's surface; (iv) the Afar hotspot from another angle.

### 2020-02-16 supplementary_material.tex
fix typos
Updates from Overleaf

--- 2020-02-14 supplementary_material.tex
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{figures/psf/usa_mid.pdf}
+  \caption{\small{PSF test for the middle of the United States.
+    A 160~km diameter negative Gaussian anomaly is placed at a depth of 500~km beneath the middle of the US.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
+  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
+We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  }}
+  \label{fig:psf_usa_mid}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.pdf}
+  \caption{\small{PSF test underneath the eastern United States.
+    A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the eastern US.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
+  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
+We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  }}
+  \label{fig:psf_usa_east}
+\end{figure}
+
 \section{Model GLAD-M25}

### 2020-02-17 response_to_reviewers.tex
Updates from Overleaf

@@
 we observe significant differences between the two models,
-thanks to the 6-fold increase in the number of earthquakes,
+thanks to the 10 additional iterations and a 6-fold increase in the number of earthquakes,
 including more than 500 deep events with very clean body waves.
@@
 as in numerous other studies,
-we used traveltime histograms and a held-out dataset to assess performance of our model.
-We did not perform PSF tests, because these are rather limited in value, especially in view of the fact that they only tell you something about one ``point'' in the model for the set up of a particular iteration.
+we used traveltime histograms and a held-out dataset to assess performance of our model (thus, it is not a fair comment that even the slightest effort to assess the resolution of the model is absent in the original submission).
+In the original submission, we did not perform PSF tests, because these are rather limited in value, especially in view of the fact that they only tell you something about one ``point'' in the model for the set up of a particular iteration.
 Therefore, a PSF does not say much about uncertainty, but gives an idea of resolution.
@@
 as mentioned earlier,
-the updated manuscript now contains a few PSF tests.}
+the updated manuscript now contains four PSF tests,
+and the SOM contains two more.}
 

### 2020-02-17 main.tex
Updates from Overleaf

@@
 It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
-For each iteration,
+In this study, for each iteration,
 1,480 forward and adjoint simulations need to be performed (one pair for each earthquake in the database),
-generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
+generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours (\cyan{on Summit or Titan node hours?
+I think 1480 was gradually assimilated}).
 
@@
 To ensure a good signal-to-noise ratio on a global scale,
-the smallest moment magnitude in the database is set to~5.5,
+the smallest moment magnitude in the database is set to~5.5 \cyan{5.5 is already the minimum period in globalcmt. Is it really the minimum? },
 thereby capturing more deep events,
@@
 the Antarctic Seismographic Argentinean Italian Network~(AI),
-and the New Zealand National Seismograph Network~(NZ),
+and the New Zealand National Seismograph Network~(NZ), \cyan{Japan?}
 constitute a significant part
@@
 In this study,
-it involves cross-correlation traveltimes
-for body waves and frequency-dependent multitaper phase measurements for surface waves.
+it involves cross-correlation traveltimes \citep[e.g.,][]{luo_wave-equation_1991}
+for body waves and frequency-dependent multitaper phase measurements for surface waves \citep[e.g.,][]{laske_constraints_1996} \cyan{no multitaper measurements for body waves?}.
 Measurements are made in several passbands of three-component seismograms rotated
@@
 highly uneven distribution of earthquakes and seismographic stations,
-which must be counterbalanced by geographically weighting the data.
+which must be counterbalanced by geographically weighting the data \citep[e.g.][]{Li1996}.
 This issue is discussed in detail by~\cite{Ruanetal2018};
@@
 category, $1/C$.
-Earthquakes mainly occur along plate boundaries,
-and most seismographic  stations are confined to the continents,
-which leads to an uneven distribution of sources and stations,
-as illustrated in Fig.~\ref{fig:eventsstations}.
-Therefore, weighting is crucial in global tomography to balance this uneven sampling
-of Earth's interior.
+%Earthquakes mainly occur along plate boundaries, and most seismographic  stations are confined to the continents, which leads to an uneven distribution of sources and stations, as illustrated in Fig.~\ref{fig:eventsstations}.
+Therefore, weighting is crucial in global tomography to balance this uneven sampling of Earth's interior.
 Our source and receiver weighting strategy,
@@
 earthquakes and an identical set of weights and windows for three models,
-namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
+namely, GLAD-M25, GLAD-M15, and S362ANI \citep{kustowski2008anisotropic} combined with CRUST2.0 \citep{bassin2000current} (S362ANI+CRUST2.0).
 Table~\ref{table:misfit_reduction_M15_M25} summarizes the changes in fit in
 the twelve measurement categories between the new model, GLAD-M25, and its
-starting model, GLAD-M15, and between GLAD-M25 and model S362ANI combined
-with CRUST2.0, which was the starting model for the GLAD-M15 inversion.
+starting model, GLAD-M15, and between GLAD-M25 and model S362ANI+CRUST2.0, which was the starting model for the GLAD-M15 inversion.
 
@@
 Again we use all 1,480 events and a set of identical windows on all three components
-to assess GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
+to assess GLAD-M25, GLAD-M15, and S362ANI+CRUST2.0.
 The total number of selected windows,
@@
 so there are small tradeoffs between different measurement categories.
+\cyan{How were source corrections applied to GLAD-M15 and S362ANI+Crust2.0?
+Did you apply the correction terms computed for GLAD-M25 to all models?}
 
@@
 That test was based on 253 earthquakes,
-and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events.
-We observe that the 100~km diameter anomaly at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (See SOM).
-Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests in the lower mantle beneath Afar,
+and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events \cyan{Did you use all events in PSF tests or only a subset of them?
+I am asking just to confirm since I remember such a comment from Jeroen before}.
+We observe that the 100~km diameter anomaly, which is smaller than that of used in GLAD-M15, at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (See SOM).
+Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests for larger Gaussian anomalies (with 200~km to 400~km diameters) in the lower mantle beneath Afar,
 in the lowermost mantle beneath Easter Island,
@@
 and \cite{bozdaug2016global}, we selected 360 earthquakes that were not used
-in the actual inversion. This held-out data set consists of all magnitude 6.3--7.0
+in the actual inversion. This held-out data set consists of magnitude 6.3--7.0
 earthquakes in the global CMT catalog that were not used in the inversion.
@@
 in misfit for the held-out database for model GLAD-M25 compared to GLAD-M15
-as well a S362ANI combined with CRUST2.0.
+as well a S362ANI+CRUST2.0.
 It is encouraging to see that the reductions are comparable to the
@@
 Overall, the reductions are slightly smaller, partly due to the fact that we did not
-conduct full CMT inversions for the held-out database.
+conduct full CMT inversions for the held-out database \cyan{not sure..}.
 
@@
   \caption{\small{Changes in fit for 360 earthquakes not used in the inversion in the twelve measurement categories
-between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
+between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI+CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
   \label{table:misfit_reduction_M15_M25_360}
@@
 an expansion of the model in spherical harmonics and radial B-splines is
-discussed in Appendix~\ref{sec:shanalysis}.
+discussed in Appendix~\ref{sec:shanalysis} \cyan{but the models were not expanded to spherics harmonics to plot in this paper, right?}.
 
@@
 Model S362ANI has no power beyond degree~18,
-and we see and increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10 throughout the mantle.
+and we see an increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10 throughout the mantle.
 
@@
 we see an enhancement of the Afar plume relative to GLAD-M15.
-The 3D morphology of the African superplume shows a mantle plume rising from the core-mantle boundary with a broad base tilting northward with a thinning neck, before it reaches the 660~km phase boundary and flattens.
+The 3D morphology of the African superplume shows a mantle plume rising from the core-mantle boundary with a broad base tilting northward \cyan{do you know why the African plume tilts?
+I think Pacific plume tilts likely because of the plate motion.
+GLAD-M25 generally shows that this tilt is happening widely in the upper mantle and perhaps the top of the lower mantle.
+But the African plume's tilt start from the CMB} with a thinning neck, before it reaches the 660~km phase boundary and flattens.
 It then develops into two sub-plumes ---Afar and East Lake Victoria--- supplying the East Africa rift.
@@
 
-Subduction along the Andes in South America is imaged from south to north all the way down to the transition zone and beyond, as shown in Fig.~\ref{fig:S_America}.
-In the contour plot of positive shear-wavespeed perturbations we observe three gaps, which may correspond to ridges or volcanic plateaus on the subducted Nazca plate, and indicate a weakened or even torn slab.
+Subduction along the Andes in South America is imaged from south to north all the way down to the transition zone and beyond in a more continuous way compared to GLAD-M15, as shown in Fig.~\ref{fig:S_America}.
+In the contour plot of positive shear-wavespeed perturbations we observe three gaps, which may correspond to ridges or volcanic plateaus on the subducted Nazca plate, and indicate a weakened or even torn slab \cyan{I think it is a great story but would you like to put the contour plot here or reserve for the future paper?}.
 
@@
 and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model GLAD-M25,
-including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.
+including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.The visual inspection of the models show significant increase in perturbation anomalies in GLAD-M25 compared to GLAD-M15 that explains the misfit reductions in histograms (Figs.~\ref{fig:phase_hist}~\&~\ref{fig:phase_hist_360}).
 
@@
 the models share similar attributes.
+Relatively smoother slabs in GLAD-M25 are likely related to our choice of smoothing considering the minimum period of body waves in our simulations, $\sim17$~s, which is longer than typical teleseismic body-wave tomography studies.
 
@@
 but we are not exploiting the most general earth model parameterization.
-GLAD-M25 is an elastic model with radial anisotropy confined to the upper mantle.
+GLAD-M25 is an elastic model with radial anisotropy confined to the upper mantle similar to its precessor GLAD-M15.
 It is well known that the upper mantle is azimuthally anisotropic~\citep[e.g.,][]{montagner1989petrological,montagner1991},

### 2020-02-17 main.tex
Updates from Overleaf

@@
 1,480 forward and adjoint simulations need to be performed (one pair for each earthquake in the database),
-generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours (\cyan{on Summit or Titan node hours?
-I think 1480 was gradually assimilated}).
+generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
 
@@
 To ensure a good signal-to-noise ratio on a global scale,
-the smallest moment magnitude in the database is set to~5.5 \cyan{5.5 is already the minimum period in globalcmt. Is it really the minimum? },
+the smallest moment magnitude in the database is set to~5.5,
 thereby capturing more deep events,
@@
 Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
-the Antarctic Seismographic Argentinean Italian Network~(AI),
-and the New Zealand National Seismograph Network~(NZ), \cyan{Japan?}
-constitute a significant part
+the Antarctic Seismographic Argentinean Italian Network~(AI), the New Zealand National Seismograph Network~(NZ), and the F-net broadband seismograph network by NIED, constitute a significant part
 of our database and greatly improve coverage in certain regions.
@@
 be carefully constructed.
-In this study,
-it involves cross-correlation traveltimes \citep[e.g.,][]{luo_wave-equation_1991}
-for body waves and frequency-dependent multitaper phase measurements for surface waves \citep[e.g.,][]{laske_constraints_1996} \cyan{no multitaper measurements for body waves?}.
+Depending on the time window length and wave period range, we use a multi-taper technique \citep[e.g.,][]{laske_constraints_1996} to make frequency-dependent phase measurement when possible and adopt a cross-correlation measurement \citep[e.g.,][]{luo_wave-equation_1991} for the rest of data.
 Measurements are made in several passbands of three-component seismograms rotated
@@
 highly uneven distribution of earthquakes and seismographic stations,
-which must be counterbalanced by geographically weighting the data \citep[e.g.][]{Li1996}.
+which must be counterbalanced by geographically weighting the data~\citep[e.g.][]{Li1996}.
 This issue is discussed in detail by~\cite{Ruanetal2018};
@@
 so there are small tradeoffs between different measurement categories.
-\cyan{How were source corrections applied to GLAD-M15 and S362ANI+Crust2.0?
-Did you apply the correction terms computed for GLAD-M25 to all models?}
+%\cyan{How were source corrections applied to GLAD-M15 and S362ANI+Crust2.0? Did you apply the correction terms computed for GLAD-M25 to all models?} I believe so.
 
@@
 That test was based on 253 earthquakes,
-and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events \cyan{Did you use all events in PSF tests or only a subset of them?
-I am asking just to confirm since I remember such a comment from Jeroen before}.
-We observe that the 100~km diameter anomaly, which is smaller than that of used in GLAD-M15, at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (See SOM).
+and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events.
+We observe that the 100~km diameter anomaly ---which is smaller than what was used in GLAD-M15--- at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (See SOM).
 Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests for larger Gaussian anomalies (with 200~km to 400~km diameters) in the lower mantle beneath Afar,
@@
 Overall, the reductions are slightly smaller, partly due to the fact that we did not
-conduct full CMT inversions for the held-out database \cyan{not sure..}.
+conduct full CMT inversions for the held-out database.
+%\cyan{not sure..}
 
@@
 an expansion of the model in spherical harmonics and radial B-splines is
-discussed in Appendix~\ref{sec:shanalysis} \cyan{but the models were not expanded to spherics harmonics to plot in this paper, right?}.
+discussed in Appendix~\ref{sec:shanalysis}
+%\cyan{but the models were not expanded to spherics harmonics to plot in this paper, right?}. No.
 
@@
 we see an enhancement of the Afar plume relative to GLAD-M15.
-The 3D morphology of the African superplume shows a mantle plume rising from the core-mantle boundary with a broad base tilting northward \cyan{do you know why the African plume tilts?
+The 3D morphology of the African superplume shows a mantle plume rising from the core-mantle boundary with a broad base tilting northward
+%\cyan{do you know why the African plume tilts?
 I think Pacific plume tilts likely because of the plate motion.
 GLAD-M25 generally shows that this tilt is happening widely in the upper mantle and perhaps the top of the lower mantle.
-But the African plume's tilt start from the CMB} with a thinning neck, before it reaches the 660~km phase boundary and flattens.
+But the African plume's tilt start from the CMB}  No.
+It's in the Texas model too.
+with a thinning neck, before it reaches the 660~km phase boundary and flattens.
 It then develops into two sub-plumes ---Afar and East Lake Victoria--- supplying the East Africa rift.
-The development of the superplume and its 3D morphology might be associated with water in the mantle transition zone, a possibility we will explore in a future study.
-
-Subduction along the Andes in South America is imaged from south to north all the way down to the transition zone and beyond in a more continuous way compared to GLAD-M15, as shown in Fig.~\ref{fig:S_America}.
-In the contour plot of positive shear-wavespeed perturbations we observe three gaps, which may correspond to ridges or volcanic plateaus on the subducted Nazca plate, and indicate a weakened or even torn slab \cyan{I think it is a great story but would you like to put the contour plot here or reserve for the future paper?}.
+The development of the superplume and its 3D morphology might be associated with the thermal and chemical states in the lower mantle and volatiles in the mantle transition zone, a possibility we will explore in a future study.
+
+% Subduction along the Andes in South America is imaged from south to north all the way down to the transition zone and beyond in a more continuous way compared to GLAD-M15, as shown in Fig.~\ref{fig:S_America}.
+% In the contour plot of positive shear-wavespeed perturbations we observe three gaps, which may correspond to ridges or volcanic plateaus on the subducted Nazca plate, and indicate a weakened or even torn slab \citep[e.g.,][]{Hu2016}
+%\cyan{I think it is a great story but would you like to put the contour plot here or reserve for the future paper?}. OK.
 
@@
 and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model GLAD-M25,
-including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.The visual inspection of the models show significant increase in perturbation anomalies in GLAD-M25 compared to GLAD-M15 that explains the misfit reductions in histograms (Figs.~\ref{fig:phase_hist}~\&~\ref{fig:phase_hist_360}).
+including Marion, Crozet, Kerguelen, and R\'eunion.
+Visual inspection of the models reveals a significant increase in perturbation anomalies in GLAD-M25 compared to GLAD-M15,
+which explains the misfit reductions in the histograms (Figs.~\ref{fig:phase_hist}~\&~\ref{fig:phase_hist_360}).
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=.8\textwidth]{figures/south_america.pdf}
-\caption{\small{Contour plot (left) and cross-sections at various depths (right) of subduction underneath South America, showing improvements in resolution in GLAD-M25 compared to GLAD-M15.
-The contour plot shows positive perturbations of vertically polarized shear wavespeeds in GLAD-M25. The ball in the contour map denotes the 660~km discontinuity.}}
-\label{fig:S_America}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=.8\textwidth]{figures/south_america.pdf}
+% \caption{\small{Contour plot (left) and cross-sections at various depths (right) of subduction underneath South America, showing improvements in resolution in GLAD-M25 compared to GLAD-M15.
+% The contour plot shows positive perturbations of vertically polarized shear wavespeeds in GLAD-M25. The ball in the contour map denotes the 660~km discontinuity.}}
+% \label{fig:S_America}
+% \end{figure}
 
@@
   \includegraphics[width=0.8\textwidth]{figures/M25-Iceland.pdf}
-  \caption{\small{Map views of vertically polarized shear-wave-speed perturbations in GLAD-M15 (top left) and GLAD-M25 (top right) underneath Iceland.
+  \caption{\small{Map views of vertically polarized shear-wave-speed perturbations in GLAD-M15 (top left) and GLAD-M25 (top right) underneath Iceland at a depth of 250~km.
 Also shown are vertical cross-sections(bottom row) at the same location.
@@
   \caption{\small{Map views at 250~km depth of vertically polarized shear-wave-speed perturbations in GLAD-M15 (left) and GLAD-M25 (right) in the Indian Ocean.
-New features have emerged in GLAD-M25, such as the R\'eunion, Marion, Kerguelen, Maldives, Seychelles, Cocos, and Crozet hotspots.}
+New features have emerged in GLAD-M25, such as the R\'eunion, Marion, Kerguelen, Maldives, Seychelles, Cocos, and Crozet hotspots.
+  }
   }
@@
 the models share similar attributes.
-Relatively smoother slabs in GLAD-M25 are likely related to our choice of smoothing considering the minimum period of body waves in our simulations, $\sim17$~s, which is longer than typical teleseismic body-wave tomography studies.
+%Relatively smoother slabs in GLAD-M25 are likely related to our choice of smoothing considering the minimum period of body waves in our simulations, $\sim17$~s, which is longer than typical teleseismic body-wave tomography studies.
 
@@
 but we are not exploiting the most general earth model parameterization.
-GLAD-M25 is an elastic model with radial anisotropy confined to the upper mantle similar to its precessor GLAD-M15.
+GLAD-M25 is an elastic model with radial anisotropy confined to the upper mantle, similar to its predecessor GLAD-M15.
 It is well known that the upper mantle is azimuthally anisotropic~\citep[e.g.,][]{montagner1989petrological,montagner1991},

### 2020-02-17 supplementary_material.tex
Updates from Overleaf

@@
 3D mantle model S362ANI~\citep{kustowski2008anisotropic}
-with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
+with 3D crustal model CRUST2.0~\citep{bassin2000current} (S362ANI+CRUST2.0) as its starting model.
 We continue to use the same transversely isotropic model parametrization.
 To accommodate attenuation,
-we use radial anelastic model QL6~\citep{QL6}.
+we use the radial anelastic model QL6~\citep{QL6}.
 
@@
 the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
-The mantle and crust are inverted simultaneously.
+To improve the sampling of the thin oceanic crust the mesh honors Moho whenever the crust is thinner than 15~km and thicker than 35~km.
+The mesh runs through the GLL (Gauss-Lobatto-Legendre) points at the ocean-continent transition (15--35~lm crustal thickness) as described in \citet{tromp2010a}.
+The mantle and crust are inverted simultaneously avoiding any simplifications and crustal corrections.
 
@@
 In this study we also used three-component seismograms with a shortest period of 17~s.
+Note that the shortest period of simulations is most crucial for taking advantage of high-frequency body waves since the minimum period of surface waves we currently fit in adjoint inversions is 40~s.
 
@@
   \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
-  \caption{\small{Source corrections for 1,040 out of 1,480 events used in the structural inversion.
+  \caption{\small{Source inversions for 1,040 out of 1,480 events used in the structural inversion.
 (a) Map view of depth changes.
@@
 Before using the 1,040 earthquakes in our structural inversion,
-we performed CMT inversions using model GLAD-M15,
+we performed CMT inversions using model GLAD-M15, similar to the 253 events reinverted in \citet{bozdaug2016global} using its starting model S362ANI+CRUST2.0,
 the results of which are summarized in Fig.~\ref{fig:source_correction}.
@@
 The number of stations used for CMT inversion usually ranges
-from~150 to~500.
+from~150 to~500 depending on the event dates.
 
-To determine the source parameters in the starting model,
+To update the source parameters (six moment tensor components, latitude, longitude and depth) using the starting model to compute the Green's functions for each source parameter,
 we used the CMT inversion algorithm of \cite{liu2004spectral}.
@@
 --- effectively a station correction --- determined by cross correlation.
+We do not invert for the origin times as we minimize the phase misfit due to the station correction which helps to reduce the nonlinearity of the problem.
+As we describe later, we take into account the uncertainty in origin times, as well as the scalar moment, by performing an additional grid search at every iteration.
 The envelope function is denoted by~$e(\,\cdot\,)$\,,
@@
 Following~\cite{ekstrom2012global},
-seismograms were filtered between 50~s and 100~s
+seismograms were filtered between 40~s and 100~s
 to select three-component body-wave windows,
@@
 These source inversions are computationally very expensive,
-because for each of the 1,040~events nine full 3D forward simulations are required to obtain the source parameter Fr\'echet derivatives.
+because for each of the 1,040~events nine full 3D forward simulations are required to obtain the source parameter Fr\'echet derivatives in addition to forward simulation of synthetic seismograms (i.e., 10 forward simulations per event).
 
@@
 
-Most earthquakes are shallower after inversion
+Most earthquakes, specifically the oceanic ridge events, are shallower after inversion
 (Fig.~\ref{fig:source_correction}c),
 consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}.
+This is partly because the minimum depth of CMT events are fixed to $\sim12$~km as the sensitivity of source parameters significantly decreases closer to the free surface.
 We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
@@
 and an average centroid time shift of~$-0.60\pm1.17$~s.
-These are relatively minor corrections, especially in view of the significant expense of the source inversions.
+These are relatively minor corrections mainly due to our choice of being conservative in source corrections to avoid nonlinearities and our not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
 For this reason, when we added another 440 earthquakes during iteration~22,
@@
 of stations, and the current earth model as input.
-The solver is GPU accelerated, and the simulations are performed on the Cray supercomputer ``Titan''
+The solver is GPU accelerated, and the simulations are performed on the Cray ``Titan'' and IBM ``Summit" supercomputers
 at the OLCF.
 To simulate 120-min seismograms with a shortest period of 17~s on 384 NVIDIA
-Tesla K20X GPUs takes approximately 10~min of wall clock time.
+Tesla K20X GPUs takes approximately 10~min of wall clock time (On Summit it takes about \cyan{1~min (??)}).
 
@@
 so for 1,480 earthquakes this adds up to 1.5~PB.
-This volume of data is generated during~$\sim6$~hours of simulations.
+This temporary volume of data is generated during~$\sim6$~hours of simulations.
 Based on our experience, ADIOS is capable of achieving~$\sim120$~GB/s
@@
 But from the perspective of the tomographic inversion, this is by far the most
-important stage of the adjoint tomography workflow,
+important and tedious stage of the adjoint tomography workflow,
 impacting the outcome.
@@
   \item Signal processing to remove the instrument response from observed data
-    to recover ground displacement using ObsPy~\citep{obspy2010}. Both observed and synthetic data are bandpass
-    filtered, and the horizontal components are rotated to obtain the radial and transverse components of motion.
+    to recover ground displacement using ObsPy~\citep{obspy2010}.
+Both observed and synthetic data are filtered using the same bandpass only once, and the horizontal components are rotated to obtain the radial and transverse components of motion.
   \item Window selection on a pair of
@@
 derivatives of the four model parameters as output.
-The computational cost of one adjoint simulation is roughly twice ($\sim25$~min) that of
+The computational cost of one adjoint simulation is roughly twice ($\sim25$~min on Titan, \cyan{less than $10$~min on Summit}) that of
 a forward simulation, since the forward wavefield is recalculated for convolution with
@@
 Using this procedure,
-both the forward and adjoint wavefield are calculated in forward time,
-and attenuation is accurately taken into account in both simulations.
+both the forward and adjoint wavefields are calculated in forward time,
+and attenuation is accurately taken into account in both simulations \citep{KoXiBoPeSaLiTr16}.
 
@@
 generates a model update as output.
-It involves the follow steps.
+It involves the following steps.
 \begin{enumerate}
-  \item Summation of the individual Fr\'echet derivatives for each earthquake to obtain the overall gradient of the misfit function. The contribution of each source is weighted to balance
+  \item Summation of the individual Fr\'echet derivatives for each earthquake, called ``event kernels", to obtain the overall gradient of the misfit function.
+The contribution of each source is weighted to balance
     the uneven distribution of earthquakes~\citep{Ruanetal2018}.
@@
     serves as a regularization procedure. Instead of using a changing
-    smoothing radius based upon the ``ray density''~\citep{bozdaug2016global},
-    we used a fixed value at a given iteration, following~\cite{zhu2012structure}.
+    smoothing radius based upon the ``kernel density''~\citep{bozdaug2016global},
+    we used a fixed value at a given iteration, following~\cite{zhu2012structure} to initially better observe the effect of our weighting scheme.
+One can also combine the source-receiver weighting with the multi-stage smoothing strategy to highlight the structure underneath densely covered regions as in~\citet{bozdaug2016global}.
   \item Preconditioning of the smoothed gradient based on a technique proposed by~\cite{luo2013strategies}.
   \item Line search in the direction of the negative gradient to determine the magnitude of the model update.
-  The search direction is determined using a nonlinear conjugate gradient method~\citep{wright1999numerical} (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25).
+  The search direction is determined using a nonlinear conjugate gradient method (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25)~\citep{wright1999numerical}.
   We used a subset of 160 earthquakes to conduct the line search and determine the step length.
+One can also determine the step length using the Wolf criteria which is commonly used in exploration studies \cyan{reference}.
+We prefer to perform the line search to be able to keep track of the evolution of misfit at every measurement category.
 \end{enumerate}
@@
 
-This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study.
+This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
 Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_su} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, and Sumatra.
-Each figure shows the original Gaussian perturbation, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
+Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
 \begin{figure}
@@
 Overall, these models are in good agreement
-at the longest wavelengths, especially GLAD-M25 and S362ANI$+$M.
+at the longest wavelengths, especially GLAD-M25 and S362ANI$+$M where S362ANI$+$M is the updated version of S362ANI~\citep{s362ani}, the starting model of GLAD-M15.
 The perturbations in GLAD-M25 tend to be larger than in the other models,
-consistent with observations by~\cite{french2014whole},
+consistent with observations by~\cite{french2014whole,french2015broad},
 whose model is also based on a form of waveform inversion.
@@
 compressional waves simultaneously. In Fig.~\ref{fig:global-vp} we
-compare global maps of our compressional wavespeed model with global P models
+compare global maps of our compressional wavespeed model with global P-wavespeed models
 LLNL-G3Dv3~\citep{simmons2012llnl} and GAP-P4~\citep{fukao2013subducted}.

### 2020-02-18 response_to_reviewers.tex
Updates from Overleaf

@@
 
-\response{We changed the weighting scheme for sources and receivers,
-which eliminates the need for the previously used variable smoothing of the gradient.
+\response{We did not use multi-scale smoothing to better observe the effect of our new weighting scheme in the inversion.
 The weighting strategy is discussed in detail in~Ruan et al.~(2019), and includes examples of improved convergence.
-One may still use multi-scale smoothing with the new weighting scheme to allow for smaller-scale heterogeneities under densely sampled regions.
+One may still use multi-scale smoothing with the new weighting scheme to allow for smaller-scale heterogeneities under densely sampled regions. We have now noted this in the main text. 
 }
@@
 \response{We provide detailed comparisons between M15 and M25 in Tables~1 and~2, as well as in all the traveltime and amplitude histograms.
-In the revised manuscript we have also added a couple of new figures directly comparing M15 and M25, thereby highlighting distinct new features in M25.}
+In the revised manuscript we have also added a couple of new figures directly comparing M15 and M25, thereby highlighting distinct new features in M25.
+In addition we have performed six PSF tests in the upper and the lower mantle which can be found in the main text and in the supplementary material.}
 
@@
 
-\response{Indeed. See our earlier discussion.}
+\response{Indeed. See our earlier discussion. We also added this in the main text.}
 
@@
 
-\response{We have modified the language.}
+\response{We have modified the language.\cyan{??}}
 
@@
 
-\response{As in M15, transverse isotropy in M25 is confined to the upper mantle, because it is mainly constrained by surface waves. }
+\response{As in M15, transverse isotropy in M25 is confined to the upper mantle, because it is mainly constrained by surface waves.
+Since the misfit reductions in all categories are consistent with each other we have not observed effects of anisotropy in the lower mantle yet.}
 
@@
 as in numerous other studies,
-we used traveltime histograms and a held-out dataset to assess performance of our model (thus, it is not a fair comment that even the slightest effort to assess the resolution of the model is absent in the original submission).
+we used traveltime histograms and a held-out dataset to assess performance of our model (thus, it is not a fair comment to say that ``even the slightest effort to assess the resolution of the model" is absent in the original submission).
 In the original submission, we did not perform PSF tests, because these are rather limited in value, especially in view of the fact that they only tell you something about one ``point'' in the model for the set up of a particular iteration.
@@
 the updated manuscript now contains four PSF tests,
-and the SOM contains two more.}
+and the SOM contains two more,
+including model parameter tradeoff.}
 
@@
 
-\response{The main technical improvement is the workflow management.}
+\response{The main technical improvement is workflow management.
+We do not understand what the reviewer considers ``true scientific innovation", but we take it as an unfortunate, insulting comment.
+Technical developments are not scientific innovations by themselves, but facilitate them.
+(For example, this paper would have been impossible without porting our solvers to GPUs.) For this reason we emphasize the technical advances which now enable us to process data from 1,480 events, and more!
+We understand the concern that the structure of the original paper was close to that of the GLAD-M15 paper,
+and we have revised the structure and added a section with direct comparisons between M15 and M25 to highlight their  differences.
+}
 
@@
 because a few PSF tests do not say much about global resolution.
+%The reason we mentioned the cost of PSF tests in the original manuscript was rather to make the point that despite the cost we will not get the full resolution.
+Otherwise, the core hours have never been an issue for our INCITE allocations but the ability to handle large data sets in FWI while carefully investigating the model evolution is the main challenge.
+Nevertheless, we added six PSF tests in the revised manuscript in addition to our existing quantitative comparisons of traveltime and amplitude misfits.
 }
@@
 
-The statement ``their model does not tell us many new things about the internal structure of the Earth'' is again unnecessarily hash and uncalled for.
+The statement ``their model does not tell us many new things about the internal structure of the Earth'' is again unnecessarily harsh and uncalled for.
+We already emphasize the advantages of our models, as we believe the reviewer knows well.
 For example,
@@
 Based on suggestions by the other reviewers,
-we added some PSF tests to the manuscript.}
+we added six PSF tests to the manuscript and the supplementary material.}
 
@@
 
-\response{We have modified the manuscript substantially, as discussed previously. We focus more concretely on differences between M15 and M25.
+\response{We have modified the manuscript substantially, as discussed previously.
+We focus more concretely on differences between M15 and M25 to better highlight the power of 10 additional iterations with $>1,000$ events.
 Unfortunately,
@@
 
-\response{Calculating synthetics at periods less than 17 s is a very expensive proposition! Going to 9~s involves a 16X increase in the computational cost.
+\response{Calculating synthetics at periods less than 17 s is a very expensive proposition!
+Going to 9~s involves a 16X increase in the computational cost.
+The long period corner of the period band is set by the Cowling approximation,
+which limits simulations to periods up to $\sim250--300$~s.
 }
@@
 In addition, when the waveform difference caused by the source time function is too large, it will be rejected by our data screening process.
-Going forward we are planning to do our own CMT inversions in M25, but including a STF estimation.
+Going forward we are planning to do our own CMT inversions in M25, but including an STF estimation.
 }
@@
 We have some experience with such inversions in Europe (Zhu et al., 2013), and for problems in exploration seismology.
+We have also started experimenting at the global scale.
+The reviewer is right that the Q model will directly affect the traveltimes;
+all tomographic inversions are affected by this.
 }
@@
 
-\response{Yes. M15 tried to compensate for this based on ray density weighting, but the new approach demonstrably leads to faster and better convergence (see Ruan et al.~2019).}
+\response{Yes. M15 tried to compensate for this based on kernel density weighting, but the new approach demonstrably leads to faster and better convergence (see Ruan et al.~2019).}
 
@@
 
-\response{Points taken. PPP is not prominent, and picked rarely by Pyflex.}
+\response{Points taken.
+PPP is not prominent, and picked rarely by Pyflex with conservative selection criteria to avoid bad-quality windows.
+It is ongoing research to improve automated phase picking algorithms.}
 
@@
 
+\response{Due to our cross-correlation measurements higher-modes may well be underrepresented in the current inversions.
+We are working on other misfit functions to effectively incorporate smaller-amplitude signals (e.g., Yuan et al.
+2020) together with better window-selection strategies.}
+
 t) Figure 19. Perhaps include SL2013sv and the model by Rickers et al. (EPSL; 2013).

### 2020-02-18 supplementary_material.tex
Updates from Overleaf

@@
 Following~\cite{ekstrom2012global},
-seismograms were filtered between 40~s and 100~s
+seismograms were filtered between 50~s and 100~s
 to select three-component body-wave windows,
@@
 and an average centroid time shift of~$-0.60\pm1.17$~s.
-These are relatively minor corrections mainly due to our choice of being conservative in source corrections to avoid nonlinearities and our not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
+These are relatively minor corrections mainly due to our choice of being conservative in source inversions to avoid nonlinearities and our not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
 For this reason, when we added another 440 earthquakes during iteration~22,
@@
 Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
+
+We used different sizes of Gaussian perturbations in the PSF tests, from 160~to~400 km diameters depending on the kernel coverage of the selected regions both in the upper and lower mantles.
+Although we observe some smearing effects the Gaussian anomalies are overall well-recovered.
+As expected PSF tests are most successful in North America, where we have the best coverage, thanks to USArray.
+However, it is also encouraging to see good recovery in the lower mantle to assess the resolution of lower-mantle plumes.
+We observe limited smearing onto other parameters where we observe a slight tradeoff in radial anisotropy in the upper mantle for the tests performed underneath North America.
+
 \begin{figure}
@@
 and the Raton hotspot, which also have slow expressions at depths of 200~km.
+The PSF test we performed in this region~(Fig.~\ref{fig:psf_yellowstone})~gives us confidence on the resolution of the observed anomalies.
+It is also promising to see the convergence of our global model to the resolution of continental-scale studies specifically in densely covered regions.
 The core of the craton exhibits fast wavespeeds at depths reaching 300~km Northwest of
@@
 root from shallow depths to $\sim$400~km, similar to US22 but
-difficult to discern in SL2013NA.
+difficult to discern in SL2013NA which may be due to similar theory and measurement techniques were used in the construction of GLAD-M25 and US22.
 Similar observations can be made for the Yavapai and
@@
 In the 200--400~km depth range, we observe a low wavespeed anomaly beneath the Arctic
-and s high wavespeed
+and high shear-wavespeed
 anomaly within the Gulf of Mexico, which coincides spatially with the deepest

### 2020-02-19 response_to_reviewers.tex
Updates from Overleaf

@@
 
-\response{We have modified the language.\cyan{??}}
+\response{We have modified the language.}
 
@@
 Otherwise, the core hours have never been an issue for our INCITE allocations but the ability to handle large data sets in FWI while carefully investigating the model evolution is the main challenge.
-Nevertheless, we added six PSF tests in the revised manuscript in addition to our existing quantitative comparisons of traveltime and amplitude misfits.
+Nevertheless, we added six PSF tests in the revised manuscript and SOM in addition to our existing quantitative comparisons of traveltime and amplitude misfits.
 }
@@
 The statement ``their model does not tell us many new things about the internal structure of the Earth'' is again unnecessarily harsh and uncalled for.
-We already emphasize the advantages of our models, as we believe the reviewer knows well.
+We already emphasize the advantages of our models, as we believe the reviewer is well aware of.
 For example,
@@
 
-\response{We have removed all the regional and full global comparisons, leaving just the plumes and slab figures, while adding a discussion of differences between M15 and M25, as requested by other reviewers.}
+\response{We have removed all the regional and full global comparisons, leaving just the plumes and slab figures, while adding a discussion of differences between M15 and M25, as requested by other reviewers.
+Please also see our PSF tests as part of model evaluations in the main text and in the SOM.}
 
@@
 \response{We have modified the manuscript substantially, as discussed previously.
-We focus more concretely on differences between M15 and M25 to better highlight the power of 10 additional iterations with $>1,000$ events.
+We focus more concretely on differences between M15 and M25 to better highlight the power of 10 additional iterations with $>1,400$ events.
+The ``two-years'' is not just the time spent for 10 iterations but code development and optimization as well as investigations of global FWI to define strategies for how to make progress.
+This is not a straightforward process as in exploration seismic yet because of the size and complex physics of the entire crust and mantle we have to take into account.
 Unfortunately,
 comparisons with other models will always be rather qualitative, because we have no way of using such models in 3D wave simulations, mainly because 3D mantle models are difficult to combine with 3D crustal models.
-Underneath the oceans there tends to be a `gap' between the mantle model and the crust, whereas underneath the continents there tends to be a region of overlap, and this make `gluing' the two together challenging.}
+Underneath the oceans there tends to be a `gap' between the mantle model and the crust, whereas underneath the continents there tends to be a region of overlap, and this make `gluing' the two together challenging.
+Thus it may be unfair to assess the models with crustal corrections with 3D numerical wave simulations.}
 
@@
 Thus, this model update must be recalculated at each iteration.
-There are lots of examples of the effects of 3D structure on such kernels in the literature.}
+There are lots of examples of the effects of 3D structure on such kernels in the literature (see, for instance, Tape et al.
+2007 for multi-pathing surface waves or in synthetic studies such as Koroni et al.
+2017 to see the effect of superposition of multiple arrivals, etc.).
+However, thanks for the comment where we indeed want to study such observations in follow-up papers.}
 
@@
 
-\response{See our response to the previous comment. We do not calculate individual sensitivity kernels a la Dahlen \& Nolet.
+\response{See our response to the previous comment.
+We do not calculate individual sensitivity kernels a la Dahlen \& Nolet.
+We compute ``event kernels" for each event combining all body- and surface-wave measurements together.
+Even if one may argue that lower mantle kernels should be simple, D'' and upper mantle definitely not.
+For instance, multiply reflected body waves from the free surface can show complicated patterns as one can expect.
+Furthermore, even though the lower mantle portion might be relatively simple, the crustal and upper-mantle portion of the kernels may still be affected by strong heterogeneities.
+Overall it does not cost extra for us to run 3D kernels for body-wave phases sampling the lower mantle.
 %\fromebru{I think we can put such a figure as well (I mean in the response, not sure needed for the paper but may go into SOM as well).
@@
 The long period corner of the period band is set by the Cowling approximation,
-which limits simulations to periods up to $\sim250--300$~s.
+which limits simulations to periods up to $\sim250--300$~s. However, all these suggestions can be good further smaller projects to be investigated.
 }
@@
 \response{We are planning a fully 3D Q inversion. This will be a ``proper'' Q inversion,
-where there full effects of attenuation, i.e., physical dispersion and dissipation, will be taken into account.
+where the full effects of attenuation, i.e., physical dispersion and dissipation, will be taken into account and inverted simultaneously with the elastic parameters.
 We have some experience with such inversions in Europe (Zhu et al., 2013), and for problems in exploration seismology.
-We have also started experimenting at the global scale.
+We have also started experimenting at the global scale with the smaller dataset used in GLAD-M15.
 The reviewer is right that the Q model will directly affect the traveltimes;
@@
 
-\response{Point taken. We have removed the section on ASDF because the format is already discussed in the original ASDF paper, and in the Bozdag et al.~(2016) paper.}
+\response{Point taken.
+Indeed there has been other data formats similar to the ASDF logic before the ASDF.
+We emphasize ASDF because of its compatibility to HPC systems.
+We have removed the section on ASDF because the format is already discussed in the original ASDF paper, and in the Bozdag et al.~(2016) paper.}
 
@@
 
-\response{The windows are taken independently of categories, based on the quality of fit. Examples of such windows may be found in Bozdag et al.~(2016).}
+\response{The windows are taken independently of categories, based on the quality of fit.
+The windows in different categories do not necessarily overlap.
+Examples of such windows may be found in Bozdag et al.~(2016).}
 
@@
 
-\response{Yes. M15 tried to compensate for this based on kernel density weighting, but the new approach demonstrably leads to faster and better convergence (see Ruan et al.~2019).}
+\response{Yes.
+M15 tried to compensate for this based on a kernel density used as the preconditioner in our post-processing stage, but the new approach demonstrably leads to faster and better convergence (see Ruan et al.~2019).}
 
@@
 PPP is not prominent, and picked rarely by Pyflex with conservative selection criteria to avoid bad-quality windows.
+In addition, to linearize our inversions, we do not select any window with large time shift and amplitude anomalies until observed and synthetic waveforms becomes comparable to make measurements.
 It is ongoing research to improve automated phase picking algorithms.}
@@
 
-\response{S and SS are more prominent than SSS, and Pyflex selects fewer of these arrivals.
-We are working on adjusting the Pyflex setting to pick ScS, ScS2, and other later arrivals, so these will be included in future iterations.}
+\response{S and SS are more prominent than SSS, and Pyflex selects fewer of these arrivals mainly because of our conservative selection criteria.
+We are working on adjusting the Pyflex setting to specifically pick ScS, ScS2, and other later arrivals, so these will be better included in future iterations.}
 
@@
 Instead, we fit full surface waveforms.
+However, we are working on new measurement techniques where higher modes and any scattered waves with smaller amplitudes can be better taken into account than cross-correlation measurements.
+See Bozdag et al.
+2011 and the recent paper Yuan et al.
+2020 for such measurements which we aim to incorporate in our future iterations.
 }
@@
 \rev{p) Page 26 and Figure 16. The authors must include panels for M15 in Figure 16 and discuss what has changed.
-Given the variance reductions I suspect most adjustments have been made in the upper mantle. The text needs two points of clarification:
+Given the variance reductions I suspect most adjustments have been made in the upper mantle. }
 
-(i) Although the authors invert for dVp and dVs, the resolution of dVp is poorer than of dVs, particularly in the uppermost mantle (constrained by surface waves) and in D'' (constrained by diffracted waves).
+\response{We have now added comparison of M25 to M15 in the revised manuscript and in the SOM.}
 
-(ii) The strength of structure in the models is for a large part determined by regularization.
+\rev{(i) Although the authors invert for dVp and dVs, the resolution of dVp is poorer than of dVs, particularly in the uppermost mantle (constrained by surface waves) and in D'' (constrained by diffracted waves).}
+
+\response{Not sure if this is a general comment for seismic tomography or for our models.
+S-wave perturbations are in general larger than those of P waves.
+It is also likely that we have less P-wave measurements than S-wave measurements because of the smaller amplitudes of P waves.
+Therefore P-wave evolution can be slower than that of S waves.
+The smoother P-wave model of GLAD-M25 compared to other P-wave models is also likely due to our minimum period of body waves which is 17~s.}
+
+\rev{(ii) The strength of structure in the models is for a large part determined by regularization.
 As shown in Ritsema et al.
 2011 we can change the amplitude of S40 (and the width of the resolution kernels) by changing the damping without compromising the data fit significantly.
-Comparing amplitudes of structures from different models without considering resolution differences is a tricky thing.
+Comparing amplitudes of structures from different models without considering resolution differences is a tricky thing.}
 
-q) In Figure 18 I suggest to include the model by Krischer et al.
+\response{We agree that the amplitude of classical tomographic models heavily depend on subjective decisions of damping, and other factors while it is required for the interpretation of the thermochemical structure and dynamics of the mantle.
+Unfortunately we cannot make a reliable assessment of amplitudes.
+All we can say is that our results show significant increase in amplitudes compared to M15 specifically on plume and slab structures where our non-linear gradient-based optimization does not involve the damping factor.}
+
+\rev{q) In Figure 18 I suggest to include the model by Krischer et al.
 (JGR; 2018).
-Model US22 is perhaps not that useful in the context of this comparison since it is based on a similar modeling approach and data set as M25.
+Model US22 is perhaps not that useful in the context of this comparison since it is based on a similar modeling approach and data set as M25.}
 
-r) Since SL2013NA (a ``ray'' model) doesn't appear too different from M25 it is not clear from the visual comparison) whether modeling improvements (i.e., better theories) matter.
-(Note that I suspect they do matter for surface waves because your variance reduction is large for the surface wave data -- see my point 1).
+\response{We could use Krischer et al.
+(2018) however looks like it is smoother than US22.
+Our point is that we have started achieving the resolution of continental-scale studies in global inversions wherever we have dense coverage.}
 
-s) The differences among the models at depths larger than 300 km in Figure 18 is striking.
+\rev{r) Since SL2013NA (a ``ray'' model) doesn't appear too different from M25 it is not clear from the visual comparison) whether modeling improvements (i.e., better theories) matter.
+(Note that I suspect they do matter for surface waves because your variance reduction is large for the surface wave data -- see my point 1).}
+
+\response{Not sure if they are very similar, in fact they show strong discrepancies below 100 km. }
+
+\rev{s) The differences among the models at depths larger than 300 km in Figure 18 is striking.
 The authors draw the reader's attention to anomalies with well-understood tectonic origins but at face value the images are really very different especially for US22 (and M25) and SL2013NA.
@@
 The misfit reduction obtained for the 40-100 s body + surface waves (presumably waveform segments after SS and before the fundamental mode surface wave) is relatively poor, so perhaps the MTZ in M25 is still poorly resolved (or S362 was an excellent model to begin with).
-At any rate, this need further discussion. Transition zone resolution is still a sticky point and is important for understand convective flow.
+At any rate, this need further discussion. Transition zone resolution is still a sticky point and is important for understand convective flow.}
 
 \response{Due to our cross-correlation measurements higher-modes may well be underrepresented in the current inversions.
-We are working on other misfit functions to effectively incorporate smaller-amplitude signals (e.g., Yuan et al.
+We are working on other misfit functions to effectively incorporate smaller-amplitude signals (e.g., Bozdag et al.
+2011, Yuan et al.
 2020) together with better window-selection strategies.}
 
-t) Figure 19. Perhaps include SL2013sv and the model by Rickers et al. (EPSL; 2013).
+\rev{t) Figure 19. Perhaps include SL2013sv and the model by Rickers et al. (EPSL; 2013).
 }
+\response{Rickers et al.
+model is more focusing on the upper mantle thus we chose to compare the Icelandic plume to those in other global models to see the continuation of the plume.
+However we now discuss it in the revised manuscript.}
 
-\response{Based on comments from the other reviewers and the editor, we have moved
+\response{Note that based on comments from the other reviewers and the editor, we have moved
 all model comparisons to the SOM, except for the plumes and slabs figures.

### 2020-02-19 supplementary_material.tex
Updates from Overleaf

@@
 the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
-To improve the sampling of the thin oceanic crust the mesh honors Moho whenever the crust is thinner than 15~km and thicker than 35~km.
-The mesh runs through the GLL (Gauss-Lobatto-Legendre) points at the ocean-continent transition (15--35~lm crustal thickness) as described in \citet{tromp2010a}.
-The mantle and crust are inverted simultaneously avoiding any simplifications and crustal corrections.
+To improve the sampling of the thin oceanic crust the mesh honors the Moho whenever the crust is thinner than 15~km and thicker than 35~km.
+The mesh runs through the GLL (Gauss-Lobatto-Legendre) points at the ocean-continent transition (15--35~km crustal thickness) as described in \citet{tromp2010a}.
+The mantle and crust are inverted simultaneously,
+thereby avoiding any simplifications or crustal corrections.
 
@@
 In this study we also used three-component seismograms with a shortest period of 17~s.
-Note that the shortest period of simulations is most crucial for taking advantage of high-frequency body waves since the minimum period of surface waves we currently fit in adjoint inversions is 40~s.
+Note that the shortest period of the simulations is most crucial for taking advantage of high-frequency body waves, since the minimum surface-wave period we currently fit is 40~s.
 
@@
 Before using the 1,040 earthquakes in our structural inversion,
-we performed CMT inversions using model GLAD-M15, similar to the 253 events reinverted in \citet{bozdaug2016global} using its starting model S362ANI+CRUST2.0,
+we performed CMT inversions using model GLAD-M15, similar to the 253 events reinverted in the \citet{bozdaug2016global} study using its starting model S362ANI+CRUST2.0,
 the results of which are summarized in Fig.~\ref{fig:source_correction}.
@@
 --- effectively a station correction --- determined by cross correlation.
-We do not invert for the origin times as we minimize the phase misfit due to the station correction which helps to reduce the nonlinearity of the problem.
+We do not invert for the origin times as we minimize the phase misfit due to the station correction, which helps to reduce the nonlinearity of the problem.
 As we describe later, we take into account the uncertainty in origin times, as well as the scalar moment, by performing an additional grid search at every iteration.
@@
 
-Most earthquakes, specifically the oceanic ridge events, are shallower after inversion
+Most earthquakes, specifically oceanic ridge events, are shallower after inversion
 (Fig.~\ref{fig:source_correction}c),
 consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}.
-This is partly because the minimum depth of CMT events are fixed to $\sim12$~km as the sensitivity of source parameters significantly decreases closer to the free surface.
+This is partly because the minimum depth of CMT events is fixed to $\sim12$~km, because the sensitivity of source parameters significantly decreases closer to the free surface.
 We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
@@
 and an average centroid time shift of~$-0.60\pm1.17$~s.
-These are relatively minor corrections mainly due to our choice of being conservative in source inversions to avoid nonlinearities and our not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
+These are relatively minor corrections, mainly due to being conservative in the source inversions to avoid nonlinearities and the not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
 For this reason, when we added another 440 earthquakes during iteration~22,
@@
 at the OLCF.
-To simulate 120-min seismograms with a shortest period of 17~s on 384 NVIDIA
-Tesla K20X GPUs takes approximately 10~min of wall clock time (On Summit it takes about \cyan{1~min (??)}).
 
@@
     to recover ground displacement using ObsPy~\citep{obspy2010}.
-Both observed and synthetic data are filtered using the same bandpass only once, and the horizontal components are rotated to obtain the radial and transverse components of motion.
+Both observed and synthetic data are filtered using the same bandpass, and the horizontal components are rotated to obtain the radial and transverse components of motion.
   \item Window selection on a pair of
@@
 derivatives of the four model parameters as output.
-The computational cost of one adjoint simulation is roughly twice ($\sim25$~min on Titan, \cyan{less than $10$~min on Summit}) that of
+The computational cost of one adjoint simulation is roughly twice ($\sim25$~min on Titan, less than $10$~min on Summit) that of
 a forward simulation, since the forward wavefield is recalculated for convolution with
@@
     smoothing radius based upon the ``kernel density''~\citep{bozdaug2016global},
-    we used a fixed value at a given iteration, following~\cite{zhu2012structure} to initially better observe the effect of our weighting scheme.
-One can also combine the source-receiver weighting with the multi-stage smoothing strategy to highlight the structure underneath densely covered regions as in~\citet{bozdaug2016global}.
+    we used a fixed value at a given iteration, following~\cite{zhu2012structure}.
+One can also combine source-receiver weighting with the multi-stage smoothing strategy to highlight structure underneath densely covered regions, as in~\citet{bozdaug2016global}.
   \item Preconditioning of the smoothed gradient based on a technique proposed by~\cite{luo2013strategies}.
@@
   We used a subset of 160 earthquakes to conduct the line search and determine the step length.
-One can also determine the step length using the Wolf criteria which is commonly used in exploration studies \cyan{reference}.
-We prefer to perform the line search to be able to keep track of the evolution of misfit at every measurement category.
+One can also determine the step length using the Wolf criteria, which are commonly used in exploration studies \cyan{reference}.
+We prefer to perform the line search to be able to keep track of the evolution of the misfit in every measurement category.
 \end{enumerate}
@@
 
-We used different sizes of Gaussian perturbations in the PSF tests, from 160~to~400 km diameters depending on the kernel coverage of the selected regions both in the upper and lower mantles.
-Although we observe some smearing effects the Gaussian anomalies are overall well-recovered.
-As expected PSF tests are most successful in North America, where we have the best coverage, thanks to USArray.
+We used different sized Gaussian perturbations in the PSF tests, from 160~to~400~km in diameter depending on the kernel coverage of the selected regions, both in the upper and lower mantle.
+Although we observe some smearing effects, the Gaussian anomalies are overall well-recovered.
+As expected, PSF tests are most successful in North America, where we have the best coverage, thanks to USArray.
 However, it is also encouraging to see good recovery in the lower mantle to assess the resolution of lower-mantle plumes.
-We observe limited smearing onto other parameters where we observe a slight tradeoff in radial anisotropy in the upper mantle for the tests performed underneath North America.
+We observe limited smearing onto other parameters, e.g., we observe a slight tradeoff in radial anisotropy in the upper mantle for the tests performed underneath North America.
 
@@
 root from shallow depths to $\sim$400~km, similar to US22 but
-difficult to discern in SL2013NA which may be due to similar theory and measurement techniques were used in the construction of GLAD-M25 and US22.
+difficult to discern in SL2013NA, which may be due to the similar theory and measurement techniques that were used in the construction of GLAD-M25 and US22.
 Similar observations can be made for the Yavapai and

### 2020-02-19 supplementary_material.tex
add comparison with M15 in SOM

--- 2020-02-18 supplementary_material.tex
@@
 
+\subsection{More Comparisons with GLAD-M15}
+
+In addition to section~7.1, we provide more detailed comparisons with GLAD-M15.
+Fig.~\ref{fig:m15_hotspot} shows the comparisons of $V_{sv}$ perturbations in the plumes and Fig.~\ref{fig:m15_subudction} shows comparisons n the subduction areas.
+In both comparison figures, GLAD-M25 shows significant enhancement and emerging features compared to GLAD-M15.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.75\textwidth]{figures/compare_M15/hotspot.pdf}
+  \caption{\small{Vertical cross sections for various plumes and hotspots for model GLAD-M15($V_\textrm{sv}$, left column) and GLAD-M25($V_\textrm{sv}$; right column).
+  The map in the middle shows the cross section with color-coded red, green, and white dots for geographical reference; hotspots are denoted by red triangles.
+  The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
+  (a) Afar; (b) Canary (left) and Hoggar (right); (c) Easter (left) and Galapagos (right); (d) Samoa; (e) Tahiti (middle) and Macdonald (right); (f) Iceland.
+  }}
+  \label{fig:m15_hotspot}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/compare_M15/subduction.pdf}
+  \caption{\small{ Vertical cross sections for various subduction regions, same as Fig.~\ref{fig:m15_hotspot}.
+  (a) Cocos; (b) India; (c) Sumatra; (d) Fiji-Tonga; (e) Farallon; (f) Scotia. }}
+  \label{fig:m15_subduction}
+\end{figure}
+
 \subsection{Global structure}

### 2020-02-19 response_to_reviewers.tex

@@
 The ``two-years'' is not just the time spent for 10 iterations but code development and optimization as well as investigations of global FWI to define strategies for how to make progress.
-This is not a straightforward process as in exploration seismic yet because of the size and complex physics of the entire crust and mantle we have to take into account.
+This is not a straightforward process yet, as in exploration seismic, because of the size and complex physics of the entire crust and mantle we have to take into account.
 Unfortunately,
 comparisons with other models will always be rather qualitative, because we have no way of using such models in 3D wave simulations, mainly because 3D mantle models are difficult to combine with 3D crustal models.
-Underneath the oceans there tends to be a `gap' between the mantle model and the crust, whereas underneath the continents there tends to be a region of overlap, and this make `gluing' the two together challenging.
+Underneath the oceans there tends to be a `gap' between the mantle model and the crust, whereas underneath the continents there tends to be a region of overlap, and this makes `gluing' the two together challenging.
 Thus it may be unfair to assess the models with crustal corrections with 3D numerical wave simulations.}
@@
 Thus, this model update must be recalculated at each iteration.
-There are lots of examples of the effects of 3D structure on such kernels in the literature (see, for instance, Tape et al.
-2007 for multi-pathing surface waves or in synthetic studies such as Koroni et al.
-2017 to see the effect of superposition of multiple arrivals, etc.).
-However, thanks for the comment where we indeed want to study such observations in follow-up papers.}
+There are lots of examples of the effects of 3D structure on such kernels in the literature.
+See, for instance, Tape et al.
+(2007) for multi-pathing surface waves, or synthetic studies such as Koroni et al.
+(2017) for the effects of superposition of multiple arrivals.
+However, thanks for the comment; we want to study such observations in follow-up papers.}
 
@@
 We compute ``event kernels" for each event combining all body- and surface-wave measurements together.
-Even if one may argue that lower mantle kernels should be simple, D'' and upper mantle definitely not.
-For instance, multiply reflected body waves from the free surface can show complicated patterns as one can expect.
-Furthermore, even though the lower mantle portion might be relatively simple, the crustal and upper-mantle portion of the kernels may still be affected by strong heterogeneities.
+Even if one may argue that lower mantle kernels should be simple, D'' and the upper mantle are definitely not.
+For instance, multiply reflected body waves from the free surface can show complicated patterns, as one might expect.
+Furthermore, even though the lower mantle portion might be relatively simple, the crustal and upper-mantle portions of the kernels may still be affected by strong heterogeneities.
 Overall it does not cost extra for us to run 3D kernels for body-wave phases sampling the lower mantle.
@@
 The long period corner of the period band is set by the Cowling approximation,
-which limits simulations to periods up to $\sim250--300$~s. However, all these suggestions can be good further smaller projects to be investigated.
+which limits simulations to periods up to $\sim250--300$~s. However, all these suggestions make interesting projects for further investigation.
 }
@@
 \response{Point taken.
-Indeed there has been other data formats similar to the ASDF logic before the ASDF.
-We emphasize ASDF because of its compatibility to HPC systems.
+Indeed other data formats have been developed based on a similar logic.
+We emphasize ASDF because of its compatibility with HPC systems.
 We have removed the section on ASDF because the format is already discussed in the original ASDF paper, and in the Bozdag et al.~(2016) paper.}
@@
 \response{Yes.
-M15 tried to compensate for this based on a kernel density used as the preconditioner in our post-processing stage, but the new approach demonstrably leads to faster and better convergence (see Ruan et al.~2019).}
+M15 tried to compensate for this by using kernel density as a preconditioner in the post-processing stage, but the new approach demonstrably leads to faster and better convergence (see Ruan et al.~2019).}
 
@@
 PPP is not prominent, and picked rarely by Pyflex with conservative selection criteria to avoid bad-quality windows.
-In addition, to linearize our inversions, we do not select any window with large time shift and amplitude anomalies until observed and synthetic waveforms becomes comparable to make measurements.
+In addition, to linearize our inversions, we do not select any window with large time shifts or amplitude anomalies until observed and synthetic waveforms become comparable.
 It is ongoing research to improve automated phase picking algorithms.}
@@
 However, we are working on new measurement techniques where higher modes and any scattered waves with smaller amplitudes can be better taken into account than cross-correlation measurements.
-See Bozdag et al.
-2011 and the recent paper Yuan et al.
-2020 for such measurements which we aim to incorporate in our future iterations.
+See Bozdag et al.~(2011) and the recent paper by Yuan et al.~(2020) for such measurements, which we aim to incorporate in our future iterations.
 }
@@
 
-\response{Not sure if this is a general comment for seismic tomography or for our models.
+\response{We are not sure if this is a general comment for seismic tomography or for our models specifically.
 S-wave perturbations are in general larger than those of P waves.
@@
 Therefore P-wave evolution can be slower than that of S waves.
-The smoother P-wave model of GLAD-M25 compared to other P-wave models is also likely due to our minimum period of body waves which is 17~s.}
+The smoother P-wave model of GLAD-M25 compared to other P-wave models is also likely due to our minimum period of body waves, which is 17~s.}
 
@@
 
-\response{We agree that the amplitude of classical tomographic models heavily depend on subjective decisions of damping, and other factors while it is required for the interpretation of the thermochemical structure and dynamics of the mantle.
+\response{We agree that the amplitude of classical tomographic models heavily depend on subjective decisions of damping and other factors while it is required for the interpretation of the thermochemical structure and dynamics of the mantle.
 Unfortunately we cannot make a reliable assessment of amplitudes.
-All we can say is that our results show significant increase in amplitudes compared to M15 specifically on plume and slab structures where our non-linear gradient-based optimization does not involve the damping factor.}
+All we can say is that our results show significant increases in amplitudes compared to M15 specifically for plume and slab structures where our non-linear gradient-based optimization does not involve a damping factor.}
 
@@
 \response{We could use Krischer et al.
-(2018) however looks like it is smoother than US22.
+(2018), however it looks like it is smoother than US22.
 Our point is that we have started achieving the resolution of continental-scale studies in global inversions wherever we have dense coverage.}
@@
 
-\response{Not sure if they are very similar, in fact they show strong discrepancies below 100 km. }
+\response{Not sure if they are very similar, in fact they show strong discrepancies below 100~km. }
 
@@
 }
-\response{Rickers et al.
-model is more focusing on the upper mantle thus we chose to compare the Icelandic plume to those in other global models to see the continuation of the plume.
-However we now discuss it in the revised manuscript.}
+\response{The Rickers et al.
+model is more focused on the upper mantle, thus we chose to compare the Icelandic plume to those in other global models to see the continuation of the plume.
+However, we now discuss it in the revised manuscript.}
 

### 2020-02-19 main.tex

@@
 so there are small tradeoffs between different measurement categories.
-%\cyan{How were source corrections applied to GLAD-M15 and S362ANI+Crust2.0? Did you apply the correction terms computed for GLAD-M25 to all models?} I believe so.
 
@@
 conduct full CMT inversions for the held-out database.
-%\cyan{not sure..}
 
@@
 discussed in Appendix~\ref{sec:shanalysis}
-%\cyan{but the models were not expanded to spherics harmonics to plot in this paper, right?}. No.
 
@@
 The 3D morphology of the African superplume shows a mantle plume rising from the core-mantle boundary with a broad base tilting northward
-%\cyan{do you know why the African plume tilts?
-I think Pacific plume tilts likely because of the plate motion.
-GLAD-M25 generally shows that this tilt is happening widely in the upper mantle and perhaps the top of the lower mantle.
-But the African plume's tilt start from the CMB}  No.
-It's in the Texas model too.
 with a thinning neck, before it reaches the 660~km phase boundary and flattens.
@@
 The development of the superplume and its 3D morphology might be associated with the thermal and chemical states in the lower mantle and volatiles in the mantle transition zone, a possibility we will explore in a future study.
-
-% Subduction along the Andes in South America is imaged from south to north all the way down to the transition zone and beyond in a more continuous way compared to GLAD-M15, as shown in Fig.~\ref{fig:S_America}.
-% In the contour plot of positive shear-wavespeed perturbations we observe three gaps, which may correspond to ridges or volcanic plateaus on the subducted Nazca plate, and indicate a weakened or even torn slab \citep[e.g.,][]{Hu2016}
-%\cyan{I think it is a great story but would you like to put the contour plot here or reserve for the future paper?}. OK.
 
@@
 the models share similar attributes.
-%Relatively smoother slabs in GLAD-M25 are likely related to our choice of smoothing considering the minimum period of body waves in our simulations, $\sim17$~s, which is longer than typical teleseismic body-wave tomography studies.
 

### 2020-02-19 supplementary_material.tex
Updates from Overleaf

@@
 In addition to section~7.1, we provide more detailed comparisons with GLAD-M15.
-Fig.~\ref{fig:m15_hotspot} shows the comparisons of $V_{sv}$ perturbations in the plumes and Fig.~\ref{fig:m15_subudction} shows comparisons n the subduction areas.
-In both comparison figures, GLAD-M25 shows significant enhancement and emerging features compared to GLAD-M15.
+Fig.~\ref{fig:m15_hotspot} shows the comparisons of $V_{sv}$ perturbations in the plumes and Fig.~\ref{fig:m15_subduction} shows comparisons n the subduction areas.
+In both figures, GLAD-M25 shows enhancements and emerging features compared to GLAD-M15.
 

### 2020-02-19 supplementary_material.tex
Updates from Overleaf

@@
 This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
-Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_su} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, and Sumatra.
+Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, ,Sumatra and two extra locations in United States..
 Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
@@
   A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
-  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
-  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
-  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
-  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
-We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
-A 75~km diameter positive Gaussian anomaly is placed at a depth of 150~km beneath Yellowstone.
   Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
@@
 
-In addition to section~7.1, we provide more detailed comparisons with GLAD-M15.
-Fig.~\ref{fig:m15_hotspot} shows the comparisons of $V_{sv}$ perturbations in the plumes and Fig.~\ref{fig:m15_subduction} shows comparisons n the subduction areas.
-In both figures, GLAD-M25 shows enhancements and emerging features compared to GLAD-M15.
+In addition to Section~7.1 in the main text, here we provide more detailed comparisons with GLAD-M15~\citep{bozdaug2016global}.
+Fig.~\ref{fig:m15_hotspot} shows comparisons of $V_{sv}$ perturbations in for plumes, and Fig.~\ref{fig:m15_subduction} shows comparisons in subduction areas.
+In both figures, GLAD-M25 shows enhancements and emerging features relative to GLAD-M15.
 
@@
   \includegraphics[width=0.75\textwidth]{figures/compare_M15/hotspot.pdf}
-  \caption{\small{Vertical cross sections for various plumes and hotspots for model GLAD-M15($V_\textrm{sv}$, left column) and GLAD-M25($V_\textrm{sv}$; right column).
+  \caption{\small{Vertical cross sections for various plumes and hotspots for model GLAD-M15 ($V_\textrm{sv}$, left column) and GLAD-M25 ($V_\textrm{sv}$; right column).
   The map in the middle shows the cross section with color-coded red, green, and white dots for geographical reference; hotspots are denoted by red triangles.
-  The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
+  The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1,000~km.
   (a) Afar; (b) Canary (left) and Hoggar (right); (c) Easter (left) and Galapagos (right); (d) Samoa; (e) Tahiti (middle) and Macdonald (right); (f) Iceland.

### 2020-02-23 main.tex
Updates from Overleaf

@@
 Mainly due to computational challenges,
-it took until the late 2000s to see the first applications of adjoint-state methods in regional- and continental-scale earthquake seismology~\citep{tape2009adjoint,Fichtner09,zhu2012structure}.
+it took until the late 2000s to see the first applications of adjoint-state methods in regional- and continental-scale earthquake seismology~\citep[e.g.,][]{tape2009adjoint,Fichtner09,zhu2012structure}.
 The first global ``adjoint tomography'' model of the Earth's mantle,
@@
 1,480 forward and adjoint simulations need to be performed (one pair for each earthquake in the database),
-generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
+generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}.
 
@@
 selected from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global}
-and used in this study.
-To ensure a good signal-to-noise ratio on a global scale,
-the smallest moment magnitude in the database is set to~5.5,
-thereby capturing more deep events,
-and, to avoid complications associated with source dimension and directivity,
+within the moment magnitude range of $5.5 \leq M_w \leq 7.2$ used in this study.
+To ensure a good coverage, specifically in the lower mantle, we incorporated data from
+about 500 deep events, and, to avoid complications associated with source dimension and directivity,
 the largest moment magnitude is set to~7.2.
 Prior to the structural inversion,
-we performed source inversions using model GLAD-M15 and the CMT inversion algorithm of \cite{liu2004spectral},
+we performed source inversions by computing Green's functions for the nine CMT source parameters (six moment tensor components, latitude, longitude, and depth) using model GLAD-M15 and the CMT inversion algorithm of~\cite{liu2004spectral},
 as described in the Supplementary Online Material (SOM).
@@
 and high data quality.
-In addition to the seismographic  stations used for the source inversions,
-we included available data for our 1,480 event earthquake database from many data centers,
+%In addition to the seismographic  stations used for the source inversions,
+We included available data from many data centers,
 including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
-Regional and temporary networks,
+Global Seismic Network (II, IU, IC, US, CU, and GT),
+GEOFON~(GE), GEOSCOPE~(G), regional and temporary networks,
 such as US Array~(TA),
 Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
-the Antarctic Seismographic Argentinean Italian Network~(AI), the New Zealand National Seismograph Network~(NZ), and the F-net broadband seismograph network by NIED, constitute a significant part
+the Antarctic Seismographic Argentinean Italian Network~(AI), the New Zealand National Seismograph Network~(NZ), and the F-net broadband seismograph network by NIED,  MedNet~(MN),
+the Brazilian Lithospheric Seismic Project~(BL), the Chilean National Seismic Network~(C),
+and the Japan Meteorological Agency Seismic Network~(JP) constitute a significant part
 of our database and greatly improve coverage in certain regions.
@@
 The misfit function to be minimized must
-be carefully constructed.
-Depending on the time window length and wave period range, we use a multi-taper technique \citep[e.g.,][]{laske_constraints_1996} to make frequency-dependent phase measurement when possible and adopt a cross-correlation measurement \citep[e.g.,][]{luo_wave-equation_1991} for the rest of data.
+be carefully constructed, because it strongly affects the convergence of the inverse problem.
+Depending on the time window length and wave period range, we use a multi-taper technique~\citep[e.g.,][]{laske_constraints_1996} to make frequency-dependent phase measurements to capture wave dispersion and adopt a cross-correlation measurement \citep[e.g.,][]{luo_wave-equation_1991} for non-dispersive waves.
 Measurements are made in several passbands of three-component seismograms rotated
@@
 
-We observed misfit reductions in all categories,
+We observe misfit reductions in all categories,
 with dispersive 40--100~s surface waves exhibiting the largest improvements.
@@
 which explains the misfit reductions in the histograms (Figs.~\ref{fig:phase_hist}~\&~\ref{fig:phase_hist_360}).
+More detailed comparisons between GLAD-M15 and GLAD-M25 are provided in the SOM.
 
@@
 the models share similar attributes.
+The P-wave model of GLAD-M25 might be smoother than the other models due to a relatively longer minimum body-wave period (17~s).
+Since there are fewer P- than S-wave measurements,
+due to the smaller amplitudes of P waves, convergence of the P-wave model is likely to be slower than the S-wave model.
 
@@
 Without these libraries and tools, the construction of model GLAD-M25 would have been impossible.
+
+Due to our cross-correlation measurements, smaller amplitude signals, such as higher-mode surface waves (which are crucial for imaging the mantle transition zone) and scattered waves (which illuminate plume features) may well be underrepresented in the current inversion.
+Thus, there is still room for extracting more information from every time series by defining appropriate measurements to effectively incorporate smaller-amplitude signals~\citep[e.g.,][]{Bozdagetal2011,yuan_double-difference_2016}.
 
@@
 To accomplish this next step, source parameters need to be constrained more precisely, especially as we push the resolution to shorter periods~\citep[e.g.,][]{valentine2010}.
+
+After ten additional iterations,
+GLAD-M25 shows a clear enhancement of plume and slab features compared to GLAD-M15 (see also the SOM).
+It is promising to observe similarities between the P- and S-wavespeed models of GLAD-M25 and models from various other groups, while the remaining discrepancies need further investigation.
+This highlights the importance of resolution and uncertainty quantification, which is one of the major challenges in seismic tomography.
+Uncertainty quantification is an active area of research in FWI \cite[e.g.,][]{FivL2015,Fang2018,Thurin2019,Eikrem2019,Liu2019a,Liu2019b}, however, to date it has been challenging in practice, especially for large-scale inversions~\citep{Rawlinson2014}.
+
+Our comparisons of different models largely focus on similarities of major patterns, such as plumes and slabs.
+Their shapes and depth  vary in detail, especially in the lithosphere, highlighting the importance of dealing with the crust properly in tomographic inversions.
+Amplitudes of seismic models are required for thermochemical and geodynamical interpretations of the structure and dynamics of the mantle.
+We observe a significant increase in the amplitude of GLAD-M25 compared to GLAD-M15 and other models.
+Such an increase in amplitude is also evident in the models of~\cite{french2014whole,french2015broad}.
+This illustrates the fact that the current generation of global models is no longer in the realm of linear perturbation theory.
 

### 2020-02-23 supplementary_material.tex
Updates from Overleaf

@@
 the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
-To improve the sampling of the thin oceanic crust the mesh honors the Moho whenever the crust is thinner than 15~km and thicker than 35~km.
-The mesh runs through the GLL (Gauss-Lobatto-Legendre) points at the ocean-continent transition (15--35~km crustal thickness) as described in \citet{tromp2010a}.
+To improve sampling of the thin oceanic crust, the mesh honors the Moho whenever the crust is thinner than 15~km and thicker than 35~km.
+The mesh runs through the Gauss-Lobatto-Legendre points at the ocean-continent transition (15--35~km crustal thickness) as described in \citet{tromp2010a}.
 The mantle and crust are inverted simultaneously,
@@
 We do not invert for the origin times as we minimize the phase misfit due to the station correction, which helps to reduce the nonlinearity of the problem.
-As we describe later, we take into account the uncertainty in origin times, as well as the scalar moment, by performing an additional grid search at every iteration.
+As described later, we take into account uncertainties in the centroid time and scalar moment by performing an additional grid search at the start of every iteration.
 The envelope function is denoted by~$e(\,\cdot\,)$\,,
@@
 consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}.
-This is partly because the minimum depth of CMT events is fixed to $\sim12$~km, because the sensitivity of source parameters significantly decreases closer to the free surface.
+This is partly because the minimum depth of CMT events is fixed to $\sim12$~km, because the sensitivity of source parameters is significantly reduced closer to the free surface.
 We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
@@
 and an average centroid time shift of~$-0.60\pm1.17$~s.
-These are relatively minor corrections, mainly due to being conservative in the source inversions to avoid nonlinearities and the not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
+These are relatively minor corrections, mainly due to being conservative in the source inversions to avoid nonlinearities and the not-so-detailed crustal model (an updated version of CRUST2.0 as a result of the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
 For this reason, when we added another 440 earthquakes during iteration~22,
@@
   \item Line search in the direction of the negative gradient to determine the magnitude of the model update.
-  The search direction is determined using a nonlinear conjugate gradient method (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25)~\citep{wright1999numerical}.
+  The search direction is determined using a nonlinear conjugate gradient method (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25)~\citep{wright1999numerical,NoWr06}.
   We used a subset of 160 earthquakes to conduct the line search and determine the step length.
-One can also determine the step length using the Wolf criteria, which are commonly used in exploration studies \cyan{reference}.
+  One can also determine the step length using the Wolfe criteria, which are commonly used in exploration studies~\citep{NoWr06}.
 We prefer to perform the line search to be able to keep track of the evolution of the misfit in every measurement category.
@@
 This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
-Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, ,Sumatra and two extra locations in United States..
+Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, ,Sumatra and two additional locations in United States..
 Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
@@
 Although we observe some smearing effects, the Gaussian anomalies are overall well-recovered.
-As expected, PSF tests are most successful in North America, where we have the best coverage, thanks to USArray.
+As expected, our PSF tests are most successful in North America, where we have the best coverage, thanks to USArray.
 However, it is also encouraging to see good recovery in the lower mantle to assess the resolution of lower-mantle plumes.

### 2020-05-16 response_to_second_review.tex

\documentclass[11pt,a4paper]{letter}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage[dvipsnames,usenames]{color}
\usepackage{listings}
\usepackage{verbatim}

\geometry{verbose,letterpaper,tmargin=1in,bmargin=2in,lmargin=1in,rmargin=1in}
%\lstdefinestyle{lat}
%{
%	style={[LaTeX]TeX},
%	basicstyle=\ttfamily
%}

\newcommand{\red}[1]{\textbf{\textcolor{Red}{#1}}}
\newcommand{\blue}[1]{\textbf{\textcolor{Blue}{#1}}}
\newcommand{\cyan}[1]{\textbf{\textcolor{Cyan}{#1}}}
\newcommand{\green}[1]{\textbf{\textcolor{Green}{#1}}}
\newcommand{\magenta}[1]{\textbf{\textcolor{Magenta}{#1}}}
\newcommand{\orange}[1]{\textbf{\textcolor{Orange}{#1}}}
%\newcommand{\red}[1]{#1}
%\newcommand{\blue}[1]{#1}
%\newcommand{\cyan}[1]{#1}

% comments between authors
\newcommand{\toall}[1]{\textbf{\orange{@@@ To all: #1 @@@}}}
\newcommand{\towenjie}[1]{\textbf{\red{*** Wenjie: #1 ***}}}
\newcommand{\tojeroen}[1]{\textbf{\green{*** Jeroen: #1 ***}}}
\newcommand{\toebru}[1]{\textbf{\cyan{*** Ebru: #1 ***}}}
\newcommand{\fromebru}[1]{\textbf{\orange{*** Ebru: #1 ***}}}
\newcommand{\fromyouyi}[1]{\textbf{\blue{*** Youyi: #1 ***}}}

\newlength{\tempheight}
\newlength{\tempwidth}

\newcommand{\rowname}[1]% #1 = text
{\rotatebox{90}{\makebox[\tempheight][c]{\textbf{#1}}}}

\newcommand{\columnname}[1]% #1 = text
{\makebox[\tempwidth][c]{\textbf{#1}}}

%\graphicspath{{./figure/}}

\def\baselinestretch{2}
\newcommand{\response}[1]{\textbf{Response:} #1}

\newcommand{\rev}[1]{{\it{#1}}}

\newcommand{\tsup}[1]{\textsuperscript{#1}}

%\address{your name and address} 
\signature{Wenjie Lei et al.}

\begin{document}

\begin{letter}{Dr.~Lapo Boschi\\
Editor, \textit{Geophysical Journal International}}

\opening{Dear Dr.~Boschi,}

This is our response to the second set of reviews of \textit{Geophysical Journal International\/} manuscript GJI-S-20-0203 entitled ``Global Adjoint Tomography -- Model GLAD-M25''.
We received two reviews of our paper, which required moderate revisions.

What follows is a detailed point-by-point response to the reviewers' and editor's comments.
Reviewer/editor's comments are in italics verbatim, and our response is in normal type. The citations and section number in our response refer to the revised manuscript unless we specify otherwise.

{\textbf{\large Response to Editor Boschi}}

\rev{
I have received two careful reviews of your manuscript that are essentially positive. Both referee provide a number of constructive comments that, I am convinced, will help to further improve your paper. This will amount to a further, moderate revision of your work. I am sorry for our delay in getting back to you, and promise that we shall do our best to handle the next version of your manuscript more rapidly.
}

\response{
We have incorporated the constructive and helpful comments from the reviewers in the revised manuscript.
}

{\textbf{\large Response to Reviewer: 1 Steve Grand}}

\rev{
1) My understanding is that SPECFEM3D-GLOBE uses an approximation for the ocean-crust interface that is good at long periods. Is that used here and if so it may be problematic for the shorter period body wave phases that bounce beneath oceans. Perhaps a sentence or two could included to discuss this issue.
}

\response{
This approximation is the so-called ``ocean-load approximation'', which works quite well for the body waves and surface waves used in this study, as independently documented by Zhou et al.~({\it Geophysical Journal International}, 206, 1315--1326, 2016).
We have added a reference.
}

\rev{
2) As far as I saw, there was no mention of discontinuities in the paper. Are the depths of discontinuities fixed? This should be mentioned if so. We found that velocities changed depending on depths of the upper mantle discontinuities (Tao et al., 2018) and the Moho is likely more problematic. Again, some mention of this issue should be made even if discontinuity depths were allowed to vary.
}

\response{
Topography on internal discontinuities is inherited from the starting model and not updated as part of the inversion. We added a sentence to clarify this.
}

\rev{
3) It is interesting to me that the improvement in fits shown in figure 6 are not that great i.e. there are still many bodywave data being misfit by several seconds.  In the response to previous reviewers, the authors mention the poor variance reduction for ISC data but there I always though it was due to data error (picking) as well as approximate theory. Those issues are not applicable here. I am curious what the authors think of this. Would more iterations help significantly? Is it a problem with fixing discontinuities? Neglect of anisotropy? Uncertainties in Q? I realize the authors can't answer this exactly but maybe a little discussion of what they think would be helpful.
}

\response{
We have added a sentence stating that remaining anomalies are presumably due to a combination of source uncertainty and an incomplete model parameterization. Uneven data coverage is another factor limiting resolution.
}

\rev{
4) The width of the Gaussian smoothing of the gradient vector is not given I think. I would be curious to know what it is.
}

\response{
The vertical smoothing radius gradually increases from a few kilometers in the crust to 120~km at 1500~km depth, and then decreases to about 100~km in the lower mantle and further to 75~km near the CMB.
}

\rev{
5) I am sympathetic to the reviewer comments about the lack of new insight into how the Earth works. I was most struck by how poor a model GLAD-M15 is but that is not a criticism of this paper. There is a long history of upgrades to tomography models and I don't think it is a reason not to publish this model - the community is likely curious to see where FWI global tomography is today. The one thing that really struck me, however, was the increase in amplitude in P in the African LLSVP at 2000 km depth relative to previous P models (figure 12 in the supplemental section). I think this is a significant finding and if the authors are required to focus on an advance in understanding the Earth, this might be something to focus on. This is just a suggestion.
}

\response{
If GLAD-M15 is a ``poor'' model, than so are S20RTS, S40RTS, and S362ANI. We do not agree with this: these models explain a significant portion of longer-period body- and surface-wave data!
Assessing a model like GLAD-M15 or GLAD-M25 requires full 3D simulations, taking into account the 3D crust, topography \& bathemetry, ellipticity.

With regards to the African LLSVP,
in current research we are investigating the Vp/Vs ratio in the superplumes, and the increased P wavespeed in the African superplume is a key aspect of this.
}

\rev{
6) I think some of the previous reviewer comments on resolution were a bit harsh. However, I don't understand why PSF tests are done on single anomalies at a time. Why not run an inversion with a 100 or more well isolated small scale anomalies? The cost is the same as a single anomaly test and even if there is some interference among the anomalies, if they are well separated and small scale, the interference is slight. I think this would give a more general impression of the resolution. Again, this is just a suggestion and perhaps there is some reason not to do it that way.
}

\response{
As mentioned by the reviewer, the problem with a pattern of anomalies is interference between neighboring anomalies.
Nevertheless, we added a figure to the SOM showing the results of such a patterned PSF test at depths of 1,200~km depth.
We are currently working on proper uncertainty quantification using the approach of Liu et al.~(2019).

Finally, we fixed the two typos noted by the reviewer.
}

{\textbf{\large Response to Reviewer: 2 Anonymous}}

\rev{
This manuscript is a significantly improved version of the original. It is well written, concise, and a pleasure to read! Most of my comments on the revision are closely related to the author's response, and so I will start from there.
}

\response{
Thanks.
}

\rev{
First, I think that calling my first review "unprofessional" really makes things too simple. Grandiose language combined with the presentation of point-spread functions from another model in order to demonstrate the quality of the present model is questionable to an extent that tough words are clearly justified, even when the first author is a student. I am sorry, but too much is too much!
}

\response{
We beg to differ.
}

\rev{
Second, we do not need to discuss that technological advances constitute scientific progress. Of course they do. The problem is that these technological advances have either been made by others, or they are not described in the manuscript. 
For instance, in their response, the authors mention that they ported their solver to GPUs. However, this was done by Daniel Peter, years ago. Have the authors made any modification to the GPU implementation of SpecFEM in the context of this work? If so, what exactly are these modifications?
Also in their response, the authors list improvements in the workflow. However, in the manuscript it is not described what exactly these improvements are. Critical components such as FLEXWIN and ASDF have now been in place for some time. In the discussion, the authors mention that they are in the process of "adopting EnTK", but it seems like it has not been used for the work presented here.
}

\response{
The fact of the matter is that all our codes are under going continual improvements, as documented on GitHub and at CIG.
In the interest of focusing on the seismology,
also based on the previous reviews, we do not elaborate on such ``technical'' advances.
The adoption of EnTK is almost complete and will be the subject of a future publication.
}

\rev{
So, just to be clear: I do not want to belittle the authors' work. I would like to ensure that readers understand what the author's work actually was! Seeing what Bozdag et al. (2016) put in place, and recognizing the high level of automation that the authors' method already had some time ago, it simply needs to be explained better why the assimilation of more data was actually a major effort. Or more explicitly: Why exactly is it not just a matter of running ObsPy's automatic downloader and then waiting longer until the calculations finish?

Personally, I know why it is not that easy. Yet, I doubt that all readers of this manuscript will easily understand this.
}

\response{
ASDF was not used during the construction of GLAD-M15.
Without it, we could not have scaled up from 253 to 1,480 earthquakes.
Other than the data container,
we put a lot of effort into developing a new set of python-based data analysis tools based on ASDF.
The modern design of the software enables us to fully utilize the parallel processing capability provided by ASDF, and allows for easier integration into any type of workflow.
Extensive usage of content-rich file format, such as JSON and YAML, allows us to store and extract information in a much easier and readable manner.

This is the first time we implemented workflow management tools into our inversion procedure,
starting from GLAD-M15.
When the number of earthquakes is scaled up to 1,500, it is inevitable to encounter data corruption issues, mostly caused by hardware failures,
both during the simulation and processing stages.
The goal of workflow management is to detect and recover from such failures, providing us with more confidence and resilience when processing large datasets.

All tools are under going continual improvement,
and we firmly believe all this effort is worthwhile.
Looking forward, they not only enables us to go from 100s to 1,000s of earthquakes, but also from 1,000s to 10,000s of earthquakes.

We added a brief comment about this to Section~5.
}

We sincerely hope that based on this response and revision the manuscript is now acceptable for publication in GJI.

\closing{Sincerely,}

\end{letter}

\end{document}

### 2020-05-16 main.tex

@@
 These simulations accommodate the full 3D complexity of global Earth models,
-including 3D anelastic crust and mantle structure, self-gravitation, rotation, ellipticity, topography \& bathymetry, and the load of the oceans.
+including 3D anelastic crust and mantle structure, self-gravitation, rotation, ellipticity, topography \& bathymetry, and the effect of the oceans based on the ``ocean-load approximation''~\citep{KoTr02b,Zhou2016}.
 No compromises are made with regards to resolving the Earth's crust,
@@
 
+Topography on internal discontinuities, including the Moho,
+the 410, and 660, is inherited from the starting model and not updated as part of the inversion.
+
 \section{Misfit evolution}
@@
 in Fig.~\ref{fig:misfit}.
+
+We take full advantage of the scalability of the Adaptable Seismic Data Format (ASDF)~\cite{krischer2016adaptable},
+and we developed python-based data analysis tools based on ASDF, using content-rich file formats, such as JSON and YAML, to store and extract information.
 
@@
 For iterations 15--17 of the inversion we used an expanded database of 520 events.
-Our focus was to validate and test our software and workflow before scaling up
+Our focus during this stage was to validate and test our software and workflow management before scaling up
 to a larger database of 1,040 events.
@@
 so there are small tradeoffs between different measurement categories.
+Remaining anomalies are presumably due to a combination of source uncertainty and an incomplete model parameterization,
+including more general anisotropy, topography on internal discontinuities, and attenuation.
 
@@
 and we perform three additional PSF tests: in the lower mantle underneath Afar, in the lower mantle beneath Easter Island, and below the transition zone in Sumatra.
-Two additional PSF tests for anomalies below the US may be found in the SOM.
+Additional PSF tests for two anomalies below the US and for an alternating pattern of 100~km diameter anomalies at 1,200~km depth may be found in the SOM.
 
@@
   \caption{\small{PSF tests.
-  Each of the four panels labeled (a)--(d) shows a map view (Top Left) and cross section (Top Right) through a Gaussian perturbation, $\mathsf{\Delta}\mathsf{m}$\,, in~$\beta_\mathrm{V}$\,,
+  Each of the four panels labeled (a)--(d) shows a map view (Top Left) and cross section (Top Right) through a Gaussian perturbation, $\mathsf{\Delta}\mathsf{m}$\,, in~$\beta_\mathrm{V}$\, (isotropic shear wavespeed~$\beta$ in the lower mantle),
   and a map view (Bottom Left) and cross section (Bottom Right) through the recovered perturbation, $\mathsf{H}\cdot\mathsf{\Delta}\mathsf{m}$\,, in~$\beta_\mathrm{V}$.
@@
 Finally, Fig.~\ref{fig:subd}(f) shows subduction beneath the Java portion of the Sunda Arc.
-At this location the slab penetrates into the lower mantle, at which point its spreads out laterally,
+At this location the slab penetrates into the lower mantle, at which point it spreads out laterally,
 in agreement with models GAP-P4 and UU-P07.
@@
 workflow management engine~\citep{EnTK2017}.
-This workflow engine can automatically detected job failures,
+This workflow engine can automatically detect job failures,
 both from the high-performance computing (HPC) system and via user-defined functions.
@@
 \begin{acknowledgments}
+We thank Jeroen Ritsema, Steve Grand, and two anonymous reviewers for detailed comments and suggestions which helped to improve an earlier version of the manuscript.
 This research used resources of the Oak Ridge Leadership Computing Facility,
@@
 \end{equation}
-In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, GLAD-M15, and GLAD-M25,
+In Fig.~\ref{fig:power} we plot the normalized power per degree~$\ell$ for models S362ANI, GLAD-M15, and GLAD-M25,
 and Fig.~\ref{fig:powerspectraradius} shows the normalized power per degree as a function of radius
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{figures/power.pdf}
-  \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), GLAD-M15 (green), and GLAD-M25 (blue).
-  The calculation includes depths greater than 120~km.
-  Model S362ANI has no power beyond degree~18,
-  and model S40RTS has no power beyond degree~40.
-  (Courtesy of Caio Ciardelli.)
-  }}
-  \label{fig:powerspectra}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth]{figures/power.pdf}
+%   \caption{\small{Normalized power per degree~$\ell$, based on Eqn.~(\ref{eq:powerdegree}), for models S362ANI (red), GLAD-M15 (green), and GLAD-M25 (blue).
+%   The calculation includes depths greater than 120~km.
+%   Model S362ANI has no power beyond degree~18,
+%   and model S40RTS has no power beyond degree~40.
+%   (Courtesy of Caio Ciardelli.)
+%   }}
+%   \label{fig:powerspectra}
+% \end{figure}
 % In Fig.~\ref{fig:powerspectra} we plot the normalized power per degree~$\ell$ for models S362ANI, S40RTS, GLAD-M15, and GLAD-M25,

### 2020-05-16 supplementary_material.tex

@@
 For a given earthquake,
-the corresponding seismograms and related response information are combined in a single ASDF file~\citep{krischer2016adaptable}.
+the corresponding seismograms and related response information are combined in a single Adaptable Seismic Data Format (ASDF) file~\citep{krischer2016adaptable}.
 For a given earthquake data set, the conversion to ASDF needs to be performed once and for all.
@@
 This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
-Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, ,Sumatra and two additional locations in United States..
-Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
+Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, Sumatra, and two additional locations underneath the United States.
+Finally, Fig.~\ref{fig:patern1200} shows the results of a patterned resolution test at a depth of 1,200~km.
+Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
 
@@
 As expected, our PSF tests are most successful in North America, where we have the best coverage, thanks to USArray.
-However, it is also encouraging to see good recovery in the lower mantle to assess the resolution of lower-mantle plumes.
-We observe limited smearing onto other parameters, e.g., we observe a slight tradeoff in radial anisotropy in the upper mantle for the tests performed underneath North America.
+However, it is also encouraging to see good recovery in the lower mantle to assess the resolution of deep-mantle plumes.
+We observe limited tradeoff with other parameters, e.g., we observe a slight tradeoff in radial anisotropy in the upper mantle for the tests performed underneath North America.
+The alternating pattern of positive and negative 100~km diameter anomalies at 1,200~km depth is reasonably well recovered, both in terms of geometry and in terms of strength.
 
@@
   \label{fig:psf_usa_east}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.95\textwidth]{figures/psf/psf-1200km.pdf}
+  \caption{\small{Patterned PSF test at a depth of 1,200~km,
+  where the model is isotropic.
+    An alternating positive and negative pattern of 100~km diameter Gaussian anomalies in shear wavespeed is placed at a depth of 1,200~km.
+  Left: input pattern for~$\beta$.
+  Middle: recovered pattern for~$\beta$.
+  Right: tradeoff with bulk sound speed~$c$.
+  We conclude that there is little tradeoff between~$\beta$ and~$c$, and that the pattern at this mid-mantle depth is reasonably well recovered, both in terms of geometry and in terms of strength.
+  }}
+  \label{fig:patern1200}
 \end{figure}

### 2020-05-16 supplementary_material.tex
merge with master and change to png

@@
   \centering
-  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
+  \includegraphics[width=\textwidth]{figures/source_corrections.png}
   \caption{\small{Source inversions for 1,040 out of 1,480 events used in the structural inversion.
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
+  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.png}
   \caption{\small{Adjoint tomography workflow.}}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
+  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.png}
   \caption{\small{Sub-workflow workflow for preprocessing seismic data.}}
@@
   \centering
-  \includegraphics[width=0.65\textwidth]{figures/psf/yellowstone.pdf}
+  \includegraphics[width=0.65\textwidth]{figures/psf/yellowstone.png}
   \caption{\small{PSF test for Yellowstone.
@@
   \centering
-  \includegraphics[width=0.65\textwidth]{figures/psf/easter.pdf}
+  \includegraphics[width=0.65\textwidth]{figures/psf/easter.png}
   \caption{\small{PSF test for Easter Island.
@@
   \centering
-  \includegraphics[width=0.65\textwidth]{figures/psf/afar.pdf}
+  \includegraphics[width=0.65\textwidth]{figures/psf/afar.png}
   \caption{\small{PSF test for Afar.
@@
   \centering
-  \includegraphics[width=0.65\textwidth]{figures/psf/su.pdf}
+  \includegraphics[width=0.65\textwidth]{figures/psf/su.png}
   \caption{\small{PSF test for Sumatra.
@@
   \centering
-  \includegraphics[width=0.65\textwidth]{figures/psf/usa_mid.pdf}
+  \includegraphics[width=0.65\textwidth]{figures/psf/usa_mid.png}
   \caption{\small{PSF test for the middle of the United States.
@@
   \centering
-  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.pdf}
+  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.png}
   \caption{\small{PSF test underneath the eastern United States.
@@
   \centering
-  \includegraphics[width=0.75\textwidth]{figures/compare_M15/hotspot.pdf}
+  \includegraphics[width=0.75\textwidth]{figures/compare_M15/hotspot.png}
   \caption{\small{Vertical cross sections for various plumes and hotspots for model GLAD-M15 ($V_\textrm{sv}$, left column) and GLAD-M25 ($V_\textrm{sv}$; right column).
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/compare_M15/subduction.pdf}
+  \includegraphics[width=0.7\textwidth]{figures/compare_M15/subduction.png}
   \caption{\small{ Vertical cross sections for various subduction regions, same as Fig.~\ref{fig:m15_hotspot}.
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
+  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.png}
   \caption{\small{Map views of global shear wavespeed perturbations at various depths for  model
@@
 \begin{figure}
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
+\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.png}
   \caption{\small{Map views of global compressional wavespeed variations at various depths for model
@@
 \centering
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
+\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.png}
   \caption{\small{Map views of isotropic shear wavespeed variations beneath North America 
@@
 \begin{figure}[ht!]
-\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
+\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.png}
   \caption{\small{Map views of isotropic shear wavespeed variations beneath Europe for model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
@@
 \begin{figure}[ht!]
-  \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
+  \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.png}
   \caption{\small{Map views of shear wavespeed variations beneath Asia for GLAD-M25~(first column),
@@
 \begin{figure}[ht!] 
-  \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
+  \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.png}
   \caption{\small{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).}}

### 2020-05-17 main.tex
merge with master and change to png
Updates from Overleaf

@@
 
-Fig.~\ref{fig:psf_tests} shows the results of the four PSF tests we performed for model GLAD-M25.
+Fig.~\ref{fig:psf_tests} summarizes the results of the four PSF tests we performed for model GLAD-M25.
 The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
@@
 and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events.
-We observe that the 100~km diameter anomaly ---which is smaller than what was used in GLAD-M15--- at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (See SOM).
-Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests for larger Gaussian anomalies (with 200~km to 400~km diameters) in the lower mantle beneath Afar,
+We observe that the 100~km diameter~$\beta_\mathrm{V}$ anomaly ---which is smaller than what was used in GLAD-M15--- at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (see the SOM).
+Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests for larger Gaussian anomalies in isotropic shear wavespeed~$\beta$ (with 200~km to 400~km diameters) in the lower mantle beneath Afar,
 in the lowermost mantle beneath Easter Island,
 and in the mid mantle below Sumatra.
-In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters (See SOM).
+In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters (also see the SOM).
 

### 2020-05-17 supplementary_material.tex
fix figure size issue
Updates from Overleaf

--- 2020-05-16 supplementary_material.tex
@@
 Finally, Fig.~\ref{fig:patern1200} shows the results of a patterned resolution test at a depth of 1,200~km.
-Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
+Each figure shows the original Gaussian perturbation in wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
 
@@
   A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
-  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
-  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
-  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
-  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
-We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.}}
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
+  }}
   \label{fig:psf_easter}
@@
     A 400~km diameter negative Gaussian anomaly is placed at a depth of 2,000~km beneath Afar.
-  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
-  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
-  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
-  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
-We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
   }}
@@
     A 200~km diameter positive Gaussian anomaly is placed at a depth of 900~km beneath Sumatra.
-  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
-  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
-  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
-  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
-We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
   }}
@@
     A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the eastern US.
-  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
-  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
-  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
-  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$.
-We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
+  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
+  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
+  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
   }}
@@
   \centering
-  \includegraphics[width=0.95\textwidth]{figures/psf/psf-1200km.pdf}
+  \includegraphics[width=0.75\textwidth]{figures/psf/psf-1200km.pdf}
   \caption{\small{Patterned PSF test at a depth of 1,200~km,

### 2020-05-17 supplementary_material.tex
fix psf figure caption issue

--- 2020-05-16 supplementary_material.tex
@@
     An alternating positive and negative pattern of 100~km diameter Gaussian anomalies in shear wavespeed is placed at a depth of 1,200~km.
-  Left: input pattern for~$\beta$.
+  Top: input pattern for~$\beta$.
   Middle: recovered pattern for~$\beta$.
-  Right: tradeoff with bulk sound speed~$c$.
+  Bottom: tradeoff with bulk sound speed~$c$.
   We conclude that there is little tradeoff between~$\beta$ and~$c$, and that the pattern at this mid-mantle depth is reasonably well recovered, both in terms of geometry and in terms of strength.
